### 2018-08-19 ms.tex
added more intro material for NIRCam lab paper.

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%

\usepackage{graphicx}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{enumitem}

%\usepackage{natbib}
%\usepackage{pdflscape}

%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\exampleConstant}{0.04}
\newcommand{\degree}{^\circ}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{July 1, 2016}
\revised{September 27, 2016}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{NIRCam Lab Studies}
\shortauthors{Schlawin et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.1 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.1 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Everett Schlawin}
\email{eas342 AT EMAIL Dot Arizona .edu}

\author[0000-0001-8291-6490]{Everett Schlawin}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Jarron Leisenring}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Karl Misselt}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Rafia Bushra}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Douglas Kelly}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Thomas Beatty}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

\author{Marcia Rieke}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.1 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres that reveal the composition and temperature structure at a level never achieved before.
This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
This is especially true in the search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are similar to the JWST NIRISS and NIRSpec instruments.
We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and NASA Johnson with the flight hardware as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{stars: atmospheres --- stars: individual (\objectname{KIC 12557548}) ---
stars: variables: general}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 12 $\mu$m
\citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}
The sensitivity of JWST combined with its unprecedented wavelength coverage on exoplanets will enable it to measure the abundance of carbon-bearing molecules (CO, CO$2$ and CH$_4$) as well as study cooler, smaller planets than previously characterized.

The extreme precision needed to study Earth-like planets is 
Section \ref{sec:obs} describes the observations.

Known detector effects that could affect stability:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
	\item Asic-specific effects - pre-amp reset
\end{itemize}

\section{Observations}\label{sec:obs}

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Tests \label{tab:mathmode}}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
CV 3       & NASA Goddard  & 2016       & 500   & LED           & WLP8 imaging \\
OTIS       & NASA Goddard  & 2017       &       & Continuum     & Grism spectroscopy \\
GL dewar   & Steward Obs.  & 2015-2016  &       & LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       & LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}

\section{Figures\label{sec:figures}}

Figure \ref{fig:sampFig} shows a sample figure on its own.
Figure \ref{fig:gridFig} shows a grid figure.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{sample_img.pdf}
\caption{Sample Image.}\label{fig:sampFig}
\end{figure}

\subsection{Grid Figures}\label{sec:gridFig}

\begin{figure*}
\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
          }
\caption{Two figures side by side.\label{fig:gridFig}}
\end{figure*}

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.
\acknowledgments

\section*{acknowledgements}
MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research has made
use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at \url{http://exoplanets.org}; SIMBAD database, operated at CDS, Strasbourg,
France; NASA'۪s Astrophysics Data System Bibliographic
Services; the M, L, T, and Y dwarf compendium
housed at \url{http://DwarfArchives.org}; the SpeX Prism
Libraries at \url{http://www.browndwarfs.org/spexprism}; and the \texttt{astropy} package \citep{astropy2013}. 
The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community. We are most fortunate to have the opportunity to conduct observations from this mountain.

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

\vspace{5mm}
\facilities{HST(WFC3), IRTF(SpeX)}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manusscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

\software{astropy \citep{astropy2013}, 
          \texttt{emcee} \citep{foreman-mackey2013emcee}, 
          \texttt{batman} \citep{kreidberg2015batman},
          \texttt{spiderman} \citep{louden2017spiderman},
          \texttt{pynrc} \url{https://github.com/JarronL/pynrc},
          \texttt{emcee} \citep{foreman-mackey2013emcee}
           }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

\appendix

\section{Extra Info}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% \aastex provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliographystyle{apj}
\bibliography{this_biblio}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample61.tex'.

### 2018-08-22 ms.tex
some upates to intro.

@@
 \newcommand{\degree}{^\circ}
+\newcommand{\spitzer}{{\it Spitzer}}
+\newcommand{\kepler}{{\it Kepler}}
 
@@
 This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
-This is especially true in the search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are similar to the JWST NIRISS and NIRSpec instruments.
+This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
+Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
 We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and NASA Johnson with the flight hardware as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.
@@
 The sensitivity of JWST combined with its unprecedented wavelength coverage on exoplanets will enable it to measure the abundance of carbon-bearing molecules (CO, CO$2$ and CH$_4$) as well as study cooler, smaller planets than previously characterized.
+
+JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
+The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
+By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possible O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
+A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.
+
+Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series \citep[e.g.][]{beichman2014pasp}.
+Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.
+
+Ground-based
 

### 2018-08-23 ms.tex
more intro stuff.

@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{July 1, 2016}
-\revised{September 27, 2016}
-\accepted{\today}
+%\received{July 1, 2016}
+%\revised{September 27, 2016}
+%\accepted{\today}
 %% Command to document which AAS Journal the manuscript was submitted to.
 %% Adds "Submitted to " the arguement.
-\submitjournal{ApJ}
+%\submitjournal{ApJ}
 
@@
 933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
+Tucson, AZ 85721, USA} q
 
@@
 Tucson, AZ 85721, USA}
+
+\author{Stephanie Striegel}
+\affiliation{Department of Physics \& Astronomy \\
+San Jose State University \\
+One Washington Square \\
+San Jose, CA 95192, USA}
+\affiliation{NASA Ames Research Center \\
+Space Science and Astrobiology Division \\
+Moffett Field, CA 94035, USA}
+
+\author{Xander Levinson}
+\affiliation{Department of Astronomy \& Astrophysics \\
+University of California, Santa Cruz \\
+1156 Highland Street \\
+Santa Cruz, CA 95062, USA}
+\affiliation{NASA Ames Research Center \\
+Space Science and Astrobiology Division \\
+Moffett Field, CA 94035, USA}
+
+\author{Thomas P Greene}
+\affiliation{NASA Ames Research Center \\
+Space Science and Astrobiology Division \\
+Moffett Field, CA 94035, USA}
 
@@
 Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
-We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and NASA Johnson with the flight hardware as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.
+We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and the full telescope element at NASA Johnson with the flight hardware, as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.
 
@@
 JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 12 $\mu$m
-\citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}
+\citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}.
 The sensitivity of JWST combined with its unprecedented wavelength coverage on exoplanets will enable it to measure the abundance of carbon-bearing molecules (CO, CO$2$ and CH$_4$) as well as study cooler, smaller planets than previously characterized.
@@
 The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
-By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possible O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
+By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possibly O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
 A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.
@@
 
-Ground-based
+The NIRCam instrument \citep{rieke2005NIRCamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
+The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
+This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
+If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m and will work for very bright targets inaccessible by other modes.
 
-The extreme precision needed to study Earth-like planets is 
-Section \ref{sec:obs} describes the observations.
+Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.
 
@@
 	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
-	\item Asic-specific effects - pre-amp reset
+	\item Asic-specific effects - pre-amp reset. 
 \end{itemize}
 
-\section{Observations}\label{sec:obs}
+The NIRCam detectors
+
+\section{Ground-based Experiments}\label{sec:experiments}
 
@@
 \end{deluxetable*}
+
+\section{Pre-amp Resets}
+The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}
 

### 2018-08-24 ms.tex
wrote up some more on summarizing the ground-based tests.

@@
 
-Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series \citep[e.g.][]{beichman2014pasp}.
+Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
 Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.
 
-The NIRCam instrument \citep{rieke2005NIRCamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
+The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
 The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
@@
 
-Known detector effects that could affect stability:
+\subsection{Known Detector Effects}
+Known detector effects that could affect stability include:
 \begin{itemize}[noitemsep]
-	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
-	\item Asic-specific effects - pre-amp reset. 
+	\item Intrapixel sensitivity - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
+	\item Pre-amp reset offsets (an Asic-related effect) The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
+The resets cause discontinuities in the (bias?) level that can be seen on reference pixels.
+The NIRCam grism subarrays include reference pixels to mitigate these pre-amp offsets.
+	\item 1/f noise - this is a noise source where most of the noise power is concentrated as low frequencies.
+1/f noise causes spatial correlations in the fast-read direction (along detector rows).
+It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage.
+1/f noise is efficiently removed by reference pixels
+	\item Even/odd offsets - alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
+	\item kTC noise - a random process due to the unknown amount of charge stored at the reset voltage level
 \end{itemize}
-
-The NIRCam detectors
 
@@
 
+Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
+The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
+The GL dewar experiments used flight detectors, but a different controller (Leach).
+The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.
+
 \begin{deluxetable*}{ccCrlc}[b!]
-\tablecaption{Summary of Tests \label{tab:mathmode}}
+\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
 \tablecolumns{7}
@@
 \end{deluxetable*}
-
-\section{Pre-amp Resets}
-The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}
 
@@
 
-\section{Extra Info}
+%\section{Extra Info}
 

### 2018-08-24 ms.tex
some more descriptions of tests.

@@
 
+The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
+The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8).
+This mode was designed for wavefront sensing, but is also useful for high-precision time series because it spreads the light over many pixels.
+The weak lens produces a point spread function (PSF) that is hexagonal like JWST's mirrors and has a flat-to-flat width of $\sim$108 pixels and a vertex-to-vertex width of $\sim$136 pixels.
+The hexagonal PSF also has a central vertical peak which can be used for aperture centering.
+The tests with dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
+One of the stability tests during the OTIS test at NASA Johnson was a grism spectroscopy mode that used the F322W2 to illuminate the detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m.
+
 \begin{deluxetable*}{ccCrlc}[b!]
@@
 CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
-OTIS       & NASA Goddard  & 2017       &       & Continuum     & Grism spectroscopy \\
+OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy \\
+OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging \\
 GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging \\

### 2018-08-30 ms.tex
added pre-amplifier ramp offsets.

@@
 The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
-By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possibly O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
+By putting together 10-30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST} and, optimistically, O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact to its atmosphere \citep{barstow2016trappist1habitable}.
 A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.
 
-Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
+Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
 Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.
@@
 
-\subsection{Known Detector Effects}
+\section{Known Detector Effects}
 Known detector effects that could affect stability include:
@@
 \end{itemize}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{allamps.pdf}
+\caption{Reference pixel time series for a two ramp integration showing pre-amplifier resets.}\label{fig:sampFig}
+\end{figure}
+
+allamps.pdf
 
@@
 
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{sample_img.pdf}
-\caption{Sample Image.}\label{fig:sampFig}
-\end{figure}
-
 \subsection{Grid Figures}\label{sec:gridFig}
 
-\begin{figure*}
-\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
-          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
-          }
-\caption{Two figures side by side.\label{fig:gridFig}}
-\end{figure*}
+%\begin{figure*}
+%\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
+%          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
+%          }
+%\caption{Two figures side by side.\label{fig:gridFig}}
+%\end{figure*}
 

### 2018-12-06 ms.tex
replaced the run104 plots with a longer time series.

@@
 %% this information may be modified by the editorial offices.
-\shorttitle{NIRCam Lab Studies}
+\shorttitle{NIRCam Lab Stability Studies}
 \shortauthors{Schlawin et al.}
@@
 
-\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors}
+\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
 
@@
 
-\author{Jarron Leisenring}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Karl Misselt}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
 \author{Rafia Bushra}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Douglas Kelly}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA} q
-
-\author{Thomas Beatty}
 \affiliation{Steward Observatory \\
@@
 Moffett Field, CA 94035, USA}
+
+\author{Jarron Leisenring}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
+\author{Karl Misselt}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
+\author{Douglas Kelly}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
+\author{Thomas Beatty}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
 
@@
 
-JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres that reveal the composition and temperature structure at a level never achieved before.
+JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
+These spectra will reveal the composition and temperature structure at a level never achieved before.
 This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
 This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
-We summarize the lessons learned from cryogenic vacuum campaigns 2 and 3 at NASA Goddard and the full telescope element at NASA Johnson with the flight hardware, as well as laboratory tests of the same detectors at the University of Arizona's Steward Observatory.
+Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detector, which will be used for exoplanet spectra.
+%and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
+We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector labs.
 
@@
 
-JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
+JWST has also been considered for observations of potentially habitable Earth-like planets that orbit their stars at a distance where water could be in liquid form on their surface.
 The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
-By putting together 10-30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST} and, optimistically, O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact to its atmosphere \citep{barstow2016trappist1habitable}.
-A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.
+By putting together 10 to 30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST}.
+Optimistically, 30 transits may contain enough photons to detect O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact on its atmosphere \citep{barstow2016trappist1habitable}.
+Alternatively, 10 transits of TRAPPIST-1e could be sufficient study if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
+A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.
 
@@
 
-The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
-The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
+The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode with its long wavelength channel \citep{greene2017jatisNIRCam}.
+This slitless grism mode is analogous to the WFC3 grism on HST that has been successfully employed on many transiting planets \citep[e.g.][]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
+The NIRCam grism mode will collect moderate resolution R$\sim$1100-1700 spectra over the wavelength range from 2.4 to 5.0~$\mu$m.
 This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
-If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m and will work for very bright targets inaccessible by other modes.
+If it becomes an approved and implemented mode, the DHS will permit spectroscopy simultaneous from 1.0 to 2.0~$\mu$m because of a dichroic beamsplitter that divides the light from NIRCam into two different channels.
+The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$) inaccessible by other modes.
 
+Section \ref{sec:detectorPrimer} gives a review of NIRCam's detector operation.
+Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.
 Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.
 
-\section{Known Detector Effects}
+\section{A Primer on Detector Operation}\label{sec:detectorPrimer}
+
+\subsection{Photosensitive Operation}
+\textcolor{red}{\textbf{NOTE: This section needs checking for factual accuracy by a detector expert}}
+
+It is helpful to review the basic operation of a NIRCam detector in order to understand the systematics affecting time series \citep[e.g.][]{rieke2007irDetectorReview}.
+Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
+The crystalline HgCdTe structure has 4 valence electrons that form covalent bonds in a tetrahedral structure.
+By varying the relative amount of Hg, Cd and Te (doping), it is possible to increase or decrease the number of electrons to create mobile charge carriers that move along the crystaline lattice.
+The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons).
+The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
+\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
+The green and blue regions depict the N-type and P-type semiconductors.
+The undepleted zones of the semiconductor (fire brick and dim gray colors) contain mobile charge carriers whereas the depletion region (dark salmon) has no mobile carriers and all electrons are in the valence state.
+The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
+The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
+\end{figure}
+
+The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
+This produces a negative charge on the P-type side.
+Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a positive charge.
+This difference is called the contact potential.
+In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
+This region spanning across the two semiconductor materials is called the depletion region, because it contains no mobile charge carriers.
+The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
+
+The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
+The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positve charge carriers (holes).
+The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
+The increased depletion region size also increases the well depth or capacity of electrons that the detector may collect before saturation.
+The reverse bias is applied at each reset at the beginning of a detector's integration.
+Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of the P-type semiconductor is much higher than the N-type, so the depletion region has a larger physical size on the N-type side.
+
+Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
+The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
+Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge.
+Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
+The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to visualize the charge trapping effect this way \citep[e.g.][]{smith2008imgPersistence}.
+
+When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
+The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
+The incoming photon has the effect of decreasing the size of the depletion region.
+A second photon will excite another electron-hole pair so that a hole moves to the P-type side.
+This continues and decreases the size of the depletion region.
+The diffusion of charge carriers across the junction changes the voltage across the NP junction, which can be measured with a sensitive amplifier circuit.
+
+As the size of the depletion region decreases, the detector becomes decreasingly sensitive to new photons.
+Thus, the NIRCam HgCdTe detectors are never strictly linear.
+Eventually, with enough photons, the depletion region is too small to create electron-hole pairs with incoming photons.
+This is where the detector approaches saturation and no longer changes voltage with more light.
+
+\subsection{Readout Circuit}\label{sec:readout}
+
+The accumulated charge from absorbed photons in the detector is measured with a multiplexor (MUX) that form a readout integrated circuit (ROIC) \citep{rieke2007irDetectorReview}.
+This readout circuitry makes allows the signal to be measured non-destructively up the ramp in so-called ``multiaccum" mode.
+
+A sensitive amplifier converts the measured voltage potential (as compared with the bias level after reset) into a signal.
+The electronic circuit that digitizes the voltages is tuned to ensure the 16 bits (65,536 possible Data Numbers) measure the voltage across the NP junction from the value just after reset (before photons are detected) to the saturation voltage where the maximum number of photons are collected and no more electron-hole pairs can be produced in the depletion region.
+The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not below 0.
+The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation.
+
+\section{Known Detector Effects}\label{sec:knownEffects}
+
 Known detector effects that could affect stability include:
 \begin{itemize}[noitemsep]
-	\item Intrapixel sensitivity - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
-	\item Pre-amp reset offsets (an Asic-related effect) The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
-The resets cause discontinuities in the (bias?) level that can be seen on reference pixels.
-The NIRCam grism subarrays include reference pixels to mitigate these pre-amp offsets.
-	\item 1/f noise - this is a noise source where most of the noise power is concentrated as low frequencies.
+	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
+	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
+The resets cause discontinuities in the pedestal level of all pixels between frames.
+This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can.
+These are discussed in Section \ref{sec:preAmp}.
+	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies.
 1/f noise causes spatial correlations in the fast-read direction (along detector rows).
@@
 1/f noise is efficiently removed by reference pixels
-	\item Even/odd offsets - alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
-	\item kTC noise - a random process due to the unknown amount of charge stored at the reset voltage level
+	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
+Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
+	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
+	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors.
+For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
+Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
+	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode.
+For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
+This temperature change is expected to be smaller in flight due to adjustments in ??
+(Marcia said in 2018-11-02 meeting)
+	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
+	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
+Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
+	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Add more details and citations}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
+If the detector fringe pattern changes with time, it will change the throughput of a grism image.
 \end{itemize}
+
+It should be noted that the detector effects related to the asic circuit can be specific to the ``personality'' of each asic.
+The asics all have different asic load files which are tuned to minimize the power consumption and dark current in a particular asic.
+Since the asic load files are specific to each detector, they may exhibit different noise properties.
+
+\subsection{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}
+
+The NIRCam detectors' pre-amplifiers (pre-amps) have a reference voltage that can drift with time.
+This can affect the pedestal level of all pixels over long ($\gtrsim$ 20 minute timescales).
+These pre-amplifier levels can either be reset at the beginning of an integration with samples up the ramp or with each frame up the ramp.
+The NIRCam detectors are usually set to reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
+However, one set of darks was collected at Lockheed CV with a reset only once per integration to study the effects of the pre-amplifier resets.
+
+In the Lockheed CV test, the pedestal level of all pixels could be seen to drift over 19.3 minute dark integrations by 5 to 100 DN.
+The drift was usually linear over these 19 minute exposures, but in one case was observed to drift downward from 100 DN to -50 DN and back to 100 DN \citep{robberto2014refPixPreAmp}.
+The timescales for pre-amp resets are relevant to exoplanet time series, which have transit durations of $\sim$0.5 to 3 hours for typical targets.
+However, reference pixel subtraction can efficiently remove pre-amp drifts, so with proper data reduction and subarrays that include reference pixels, the pre-amp drifts can be dramatically reduced.
+It is also likely that background subtraction can mitigate the pre-amp reset offsets from time series integrations.
+The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are saved with active pixels.
 
@@
 \centering
-\includegraphics[width=.4\columnwidth]{allamps.pdf}
-\caption{Reference pixel time series for a two ramp integration showing pre-amplifier resets.}\label{fig:sampFig}
+\includegraphics[width=.49\columnwidth]{allamps.pdf}
+\includegraphics[width=.49\columnwidth]{allamps_long_dark.pdf}
+\caption{Reference pixel time series for a two frame integration (Left) and a long dark integration of 108 frames (Right).
+Each of the plots show that the pre-amplifier resets between frames in an integration cause discontinuities in the reference signal.
+Amplifiers 1 and 4 track the time all through a frame with the side reference pixels, whereas amplifiers 2 and 3 in the middle only contain information on the bottom and top reference pixels at the beginning and ending of a frame.
+The long dark exposure example of 108 integrations shows the behavior over long timescales.}\label{fig:ampResetDark}
 \end{figure}
 
-allamps.pdf
+\subsection{Charge Trapping}
+All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
+The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence,leisenring2016persistence}.
+After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
+However, in real detectors, some charges are trapped within the depletion region.
+During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
+Figure \ref{fig:npSchematicTraps} shows how the size of the depletion region changes after charges have been released, highlighted with red circles.
+The persistence from trapped charge is visible after an illumination by a source, where a residual image of a bright star can appear in dark regions or dark frames following the illumination.
+
+the depletion region contains mobile charge carriers 
+These charge traps will keep electrons and holes in the depletion region even after detector reset.
+These traps then will release the charge at later times, which will create an artificial signal that affects the measured voltage the same way that incoming photons strike the depletion region.
+
+The NIRCam detector shows low levels of persistence compared to previous generation detectors.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{charge_traps_photodiode.pdf}
+\caption{A cartoon schematic of a H2RG detector with charge traps inspired by \citet{smith2008imgPersistence}, \citet{tulloch2018persistenceH2RG} and \citet{leisenring2016persistence}.
+Charged traps for negative and positive carriers (depicted as round circles) will capture charge before it can flow to the undepleted regions of the detector.
+The charge traps do not immediately empty with a detector reset, but instead release at later times causing a spurious signal.
+This spurious signal (the shrinking of the depletion region as highlighted with red circles), causes a voltage change in future integrations that appears the same as a true signal from incoming photons.}\label{fig:npSchematicTraps}
+\end{figure}
 
@@
 Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
-The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
+The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
 The GL dewar experiments used flight detectors, but a different controller (Leach).
@@
 \startdata
+Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
+OTIS & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
 CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
@@
 \enddata
-\tablecomments{Cryogenic vacuum (CV).}
+\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
 \end{deluxetable*}
 
-\section{Figures\label{sec:figures}}
+\subsection{Long Darks}\label{sec:longDarks}
 
-Figure \ref{fig:sampFig} shows a sample figure on its own.
-Figure \ref{fig:gridFig} shows a grid figure.
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{long_dark_phot.pdf}
+\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure.
+The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
+}\label{fig:longDarkPhot}
+\end{figure}
 
-\subsection{Grid Figures}\label{sec:gridFig}
+\subsection{Cryogenic Vacuum (CV) Stability Tests}
 
-%\begin{figure*}
-%\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
-%          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
-%          }
-%\caption{Two figures side by side.\label{fig:gridFig}}
-%\end{figure*}
+During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with the Optical telescope element simulator (OSIM).
+The ISIM has all the instruments with their internal optics and detectors but no telescope mirrors.
+The OSIM simulates the PSF expected when a star or other point source illuminates the JWST instruments.
+While other tests described in this work illuminated the science instrument detectors in different ways, the point spread function most closely resembled the JWST flight point spread function.
+
+CV3 included a series of exposures over nearly 24 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
+The LED was a narrowband source at 1.55 $\mu$m, which was used in imaging mode since this would result in a narrow-lined spectrum.
+While the spectroscopic modes are expected to be the most scientifically interesting modes for studying exoplanet atmospheres, the broadband lamps needed to produce a spectrum tend to be less stable than LEDs.
+Therefore, the test was designed with an LED with the hope of measuring the precision possible with the NIRCam optics and detector.
+
+As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,deming13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
+This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
+By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with telescope pointing jitter or seeing variations during an observation.
+Similarly, NIRCam can employ a weak lens to defocus a star's light.
+Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
+The hexagonal PSF is summed with circular aperture with a radius of 70 pixels.
+The central peak may used to find a centroid of the star and center the circular aperture.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
+\caption{Weak Lans +8 PSF during CV3 testing.
+The central peak is used for centroiding, while the entire PSF is used for aperture photometry.
+A 70 pixel radius aperture (shown here is a black circle) is used for the source aperture.}\label{fig:WLP8PSF}
+\end{figure}
+
+A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
+A time series of all possible modes is shown in Figure \ref{fig:CV3longTser}.
+The full frame modes (FULL1 through FULLQ) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
+This ensured that during these 4 different types of subarray/full frame window sizes, the well depths achieved were similar.
+
+It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter than the FULL1 through FULLQ tests.
+After removing a linear fit to the time series (to account for long term trends in the lamp), the standard deviation of the WLP8SUB data is 500 ppm whereas the FULL tests range from 1020 to 1540 ppm.
+For the FULL 2048$\times$2048 pixel integrations with 2 groups up the ramp, the count rate of photons is calculated in each pixel by subtracting the two groups (ie two reads for this RAPID mode) from each other and dividing by the group time (time between these two reads for this RAPID mode).
+For the WLP8SUB mode, a linear least squares fit is performed to the groups as a function of time and the slope of this line is the count rate on a pixel.
+The large number of groups used to fit this line ensures that the read noise is reduced by $\sim 1/\sqrt{N_G}$, where $N_G$ is the number of groups.
+
+There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
+\begin{enumerate}[noitemsep]
+	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
+	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
+\end{enumerate}
+The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
+If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^-1 \approx 930 $DN.
+This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
+Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm.
+{\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should correct to 20 groups)}}
+This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
+However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.
+
+Under scenario \ref{item:lampReasonCV3subFull}, the short timescale variations of efficiently averaged out by sampling the reads multiple times up the ramp.
+
+\textcolor{red}{To Do: Look at dark frames to measure how correlated the read noise is spatially (certainly the 1/f noise should be correlated}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
+\caption{Time Series plot through the CV3 photometric stability campaign.
+All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
+13 tests (FULL1 through FULLQ) are all in full frame mode, while WLP8SUB used a 320$\times$320 subarray and WLP8SUB640 used a 640$\times$640 subarray.
+The WLP8SUB showed the smallest standard deviation of any testof any NIRCam mode explored.}\label{fig:CV3longTser}
+\end{figure}
+
+\subsection{Lessons Learned from CV3 Tests}\label{sec:CV3Lessons}
+Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.
+We were able to determine the best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps to produce light curve.
+We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
+After the calibrated images are created, we experimented with different types of aperture photometry including different geometries, background calculations and aperture sizes.
+
+After experimenting with these configurations, we find the following pipeline steps are important:
+\begin{itemize}
+	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the photon noise)
+	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
+	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
+	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
+	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
+\end{itemize}
+
+We also found reduction steps that had very little impact on the final photometric precision including
+\begin{itemize}
+	\item IPC corrections ($\lesssim 0.01$ ppm)
+	\item Flat-fielding ($\lesssim 0.3$ ppm)
+\end{itemize}
+We summarize the lessons from the tests here.
+
+\subsection{OTIS Tests}
+
+A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
+However, there is no feasible way to place a point source lamp at infinity to simulate the imaging onto a JWST instrument, so an alternate lamp setup is used.
+During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain.
+
+The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
+Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
+The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
+A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which barely leak through.
+\textcolor{red}{Was this Half Pass or Pass and a Half?}
+However, the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs}.
+We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
+For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
+
+\begin{figure*}
+\gridline{\fig{wlp8_otis_psf.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{grism_otis_psf.pdf}{0.99\textwidth}{Grism Image}}
+\caption{Median images of the short wavelength (SW) and long wavelength (LW) that were used simultaneously in a grism stability long time series.
+Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
+}\label{fig:otisPSFs}
+\end{figure*}
+
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{Grism Time Series}}
+\caption{Time series of the simultaneous SW/LW Time Series Stability test
+}\label{fig:otisLWSWtser}
+\end{figure*}
+
+As with the CV3 tests in Section \ref{sec:CV3Lessons} and Figure \ref{fig:CV3longTser}, we found the highest precision lightcurves when using subarray read configurations.
+Figure \ref{fig:OTISsubarrays} shows the many subarrays explored in a set of time series.
+As the number of reads up the ramp becomes larger and larger, the standard deviation increases.
+This would be expected if the read noise contributed significantly to the standard deviation so that ramp fitting decreases the read noise.
+The perplexing thing is, though, that this is even true if we throw away all the intermediate reads.
+That is, with all readout modes, count rate (ie. slope image is approximated by the last subtracted by the first read.
+Here the number of reads in between these is irrelevant.
+A possible way to explain the superior standard deviation for the smallest 2048$\times$64 subarray is not that more reads increase precision but rather the small subarray has a smaller contribution from spatially correlated noise.
+When larger frames are read out, for example, the 1/f noise becomes increasingly uncorrelated from read to read.\textcolor{red}{Wrote this when very tired. Is this correct and logical?}
+
+Note that the integration times are different for these 4 tests.
+They are 39.9, 39.9, 32.3, 31.8 and 32.2 for the 64-STRIPE, 128-STRIPE, 256-STRIPE, 256-WIND and FULLFRAME respectively.
+Perhaps the lamp has oscillations on a timescale that are averaged out efficiently at 39.9 seconds but not 32.3 seconds?
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{subarray_config_tser.pdf}
+\caption{A variety of subarrays in the OTIS stability tests organized by increasing number of pixels (and decrease number of groups up the ramp).
+The standard deviation decreases as the number of groups up the ramp becomes more numerous.}\label{fig:OTISsubarrays}
+\end{figure}
+
+\subsection{GL Dewar Tests}
+At the University of Arizona, there is a laboratory setup for assessing NIRCam flight and spare detectors.
+The key difference with the Asic dewar is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
+The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.
+
+\begin{figure*}
+\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
+		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
+		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
+\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
+}\label{fig:GLtSeries}
+\end{figure*}
 
@@
 
+\section{Expected In-Flight Performance with JWST}
+
 \section*{acknowledgements}
@@
 use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at \url{http://exoplanets.org}; SIMBAD database, operated at CDS, Strasbourg,
-France; NASA'۪s Astrophysics Data System Bibliographic
+France; NASA's Astrophysics Data System Bibliographic
 Services; the M, L, T, and Y dwarf compendium

### 2018-12-07 ms.tex
more info on GL dewar tests.

@@
 The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-The GL dewar experiments used flight detectors, but a different controller (Leach).
+There were two dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+The GL dewar experiments used flight-like detectors, but a different controller (Leach).
 The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.
+These two different kinds of detector electronics can be compared against each other to help isolate detector-related systematics from readout electronics-related systematics.
 
@@
 \subsection{GL Dewar Tests}
-At the University of Arizona, there is a laboratory setup for assessing NIRCam flight and spare detectors.
-The key difference with the Asic dewar is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
+
+The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
+The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
 The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.
+
+An LED illumination source is pointed at the detectors and the arrays are read out in subarray mode.
+Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
+The first handful of frames show an initial "warmup" period lasting about 9 seconds.
+This quickly stabilizes to a 1200 ppm level likely dominated by lamp variations.
+If one divides the two apertures by each other, the resulting time series is very flat and stable to with 260 ppm.
+When binning the data into 2.5 minute increments, the standard deviation is only 51 ppm.
 
@@
 \end{figure*}
+
+\subsection{Asic Dewar Tests}
 

### 2018-12-12 ms.tex
edits to OTIS section.

@@
 A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
-However, there is no feasible way to place a point source lamp at infinity to simulate the imaging onto a JWST instrument, so an alternate lamp setup is used.
+However, there is no feasible way to place a point source lamp at infinity to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
 During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain.
@@
 The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
-A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which barely leak through.
-\textcolor{red}{Was this Half Pass or Pass and a Half?}
-However, the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs}.
+A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
+Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
+This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
+
+The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
 We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
+This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the oscillations
 For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
@@
 \begin{figure*}
-\gridline{\fig{wlp8_otis_psf.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{grism_otis_psf.pdf}{0.99\textwidth}{Grism Image}}
-\caption{Median images of the short wavelength (SW) and long wavelength (LW) that were used simultaneously in a grism stability long time series.
+\gridline{\fig{wlp8_otis_psf.pdf}{0.7\textwidth}{WLP8 Image} }
+\gridline{\fig{{grism_otis_psf.pdf}}{0.7\textwidth}{Grism Image}}
+\caption{Median images of the short wavelength (SW) weak lens mode and long wavelength (LW) grism spectroscopy that were used simultaneously in a grism time series stability test.
 Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
@@
 %\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{Grism Time Series}}
+\gridline{\fig{tser_LW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
 \caption{Time series of the simultaneous SW/LW Time Series Stability test
@@
 \centering
-\includegraphics[width=.7\columnwidth]{subarray_config_tser.pdf}
+\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
 \caption{A variety of subarrays in the OTIS stability tests organized by increasing number of pixels (and decrease number of groups up the ramp).

### 2018-12-25 ms.tex
added amplifier offsets as another potential systematic.
corrected int times and int starts of long dark time series.

@@
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
+	\item \textbf{Amplifier Boundary Discontinuities} 
 \end{itemize}
@@
 This spurious signal (the shrinking of the depletion region as highlighted with red circles), causes a voltage change in future integrations that appears the same as a true signal from incoming photons.}\label{fig:npSchematicTraps}
+\end{figure}
+
+\subsection{Amplifier Boundary Discontinuities}
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
+\caption{An example slope image from the LW OTIS Stability test.
+No reference pixel correction is applied, leaving offsets at the amplifier boundaries.}\label{fig:ampOffsetsOtisGrismSlope}
 \end{figure}
@@
 \includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
-\caption{A variety of subarrays in the OTIS stability tests organized by increasing number of pixels (and decrease number of groups up the ramp).
+\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
+The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
 The standard deviation decreases as the number of groups up the ramp becomes more numerous.}\label{fig:OTISsubarrays}

### 2018-12-31 ms.tex
added another long dark ramp time series, this time w/ NCDHAS applied.
fixed the time series figure after correcting the unsigned int issue in the pairwise subtraction.
more on the dark frame time series.

@@
 
-\begin{figure}[!hbtp]
+It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
+The dark frames do not contain the photon noise in the background nor the issues with the photometric stability of illumination lamps, which are a persistent challenge with ground-based tests.
+We study here the contributions from read noise and dark current.
+However, there could be subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where non-illuminated pixels in the images correlate with illuminated ones.
+
+The long dark frames used for detector characterization are 108 groups of 1 frame each read out if full frame mode and are 10.7 sec in duration for one long integration making up one exposure.
+These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 2  minus integration 1, 4 minus 3, 6 minus 5 etc.).
+Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
+In the raw data, there are 4 prominent vertical stripes due to offsets in the read-out amplifiers.
+Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.
+
+As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
+The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
+
+What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
+We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in FIgure \ref{fig:longDarkPhot}.
+In this example, reference pixel correction appears to introduce extra noise into a photometric aperture.
+However, as an order of magnitude estimate, the total noise in these frames is $\sim$10 DN, compared with the 3$\times 10^{6}$ DN in our CV3 detector stability test.
+Therefore, the read noise contributions are expected to be $\sim$ 3 ppm.
+
+\begin{figure*}[!hbtp]
 \centering
+\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
 \includegraphics[width=.49\columnwidth]{long_dark_phot.pdf}
+\includegraphics[width=.49\columnwidth]{long_dark_phot_red.pdf}
 \caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure.
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-}\label{fig:longDarkPhot}
-\end{figure}
+{\it Top Left:} The time series constructed from raw dark frames.
+{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied. 
+{\it Bottom Left:} An example read pair subtraction with an overlay of the apertures.
+{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.}\label{fig:longDarkPhot}
+\end{figure*}
 

### 2019-01-01 ms.tex
small edits to known effects and test overview sections.

@@
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
-	\item \textbf{Amplifier Boundary Discontinuities} 
+	\item \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
+The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
+The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between regions of the detector.
+If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
 \end{itemize}
@@
 Since the asic load files are specific to each detector, they may exhibit different noise properties.
+Some caution should be taken when comparing noise tests with engineering grade or rejected detectors with the flight detectors.
 
@@
 
-\begin{deluxetable*}{ccCrlc}[b!]
+\begin{deluxetable*}{ccCrlcc}[b!]
 \tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
-\tablecolumns{7}
+\tabletypesize{\footnotesize}
+%\tablecolumns{7}
 %\tablenum{2}
@@
 \colhead{Location} &
-\colhead{UT dates} &
+\colhead{Test Year} &
 \colhead{Best Stability} & 
 \colhead{Light Source} & 
-\colhead{Instrument Mode} \\
+\colhead{Instrument Mode} &
+\colhead{Flight Hardware?} \\
 \colhead{} &
 \colhead{} &
-\colhead{(YYYY-mm-dd)} &
+\colhead{(YYYY)} &
 \colhead{(ppm)} &
+\colhead{} &
+\colhead{} &
 \colhead{}
@@
 \startdata
-Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
-OTIS & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks \\ 
-CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging \\
-OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy \\
-OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging \\
-GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging \\
-Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging \\
+Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
+OTIS & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
+CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
+OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
+OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
+GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
+Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging & N\\
 \enddata

### 2019-01-01 ms.tex
more poking around with long darks.

@@
 The long dark frames used for detector characterization are 108 groups of 1 frame each read out if full frame mode and are 10.7 sec in duration for one long integration making up one exposure.
-These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 2  minus integration 1, 4 minus 3, 6 minus 5 etc.).
+These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc.
+in a zero-based counting scheme).
 Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
@@
 What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
-We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in FIgure \ref{fig:longDarkPhot}.
+We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
+Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
+For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ for the A5 detector studied here.
+The aperture contains
+
 In this example, reference pixel correction appears to introduce extra noise into a photometric aperture.
@@
 {\it Bottom Left:} An example read pair subtraction with an overlay of the apertures.
-{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.}\label{fig:longDarkPhot}
+{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.
+\textcolor{red}{To Do: redo the time series without normalization since we want to show DN.}}\label{fig:longDarkPhot}
 \end{figure*}

### 2019-01-02 ms.tex
bunch of corrections to the long dark test.

@@
 Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
-For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ for the A5 detector studied here.
-The aperture contains
-
-In this example, reference pixel correction appears to introduce extra noise into a photometric aperture.
-However, as an order of magnitude estimate, the total noise in these frames is $\sim$10 DN, compared with the 3$\times 10^{6}$ DN in our CV3 detector stability test.
-Therefore, the read noise contributions are expected to be $\sim$ 3 ppm.
+For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
+The read noise for background-subtracted photometry is expected to be 1309 DN if each pixel is completely uncorrelated with the neighbors.
+As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.
 
@@
 \includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.49\columnwidth]{long_dark_phot.pdf}
-\includegraphics[width=.49\columnwidth]{long_dark_phot_red.pdf}
+\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
+\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
 \caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure.
@@
 \end{figure*}
+
+\textcolor{red}{To do}
+\begin{itemize}
+	\item Make the two apertures have the same Y value
+	\item Make the two apertures have the same 
+	\item Put in a third aperture above the source
+	\item Re-label the aperture from "src" to 0
+	\item Use more pixels to reduce the 1/f noise (say median of another amplifier along the X direction)
+\end{itemize}
 
@@
 The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
-If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^-1 \approx 930 $DN.
+If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^- \approx 930 $DN.
 This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).

### 2019-01-04 ms.tex
more updates to long dark section.

@@
 
-The long dark frames used for detector characterization are 108 groups of 1 frame each read out if full frame mode and are 10.7 sec in duration for one long integration making up one exposure.
+The standard long dark exposures used for detector characterization are a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
+The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
 These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc.
@@
 
+In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
+If uncorrected, this extra read noise will contribution 7000 ppm to the time series!
+As can be seen in Figure \ref{fig:longDarkPhot}, there a significant correlations along the fast read (X) direction of the detector due to 1/f noise.
+These can be reduced with the side reference pixels as well as a median of the entire image along the X direction.
+In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
+
 \begin{figure*}[!hbtp]
@@
 \includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
-\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure.
+\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
+{\it Top Left:} An example read pair subtraction with an overlay of the apertures.
+{\it Top Right:} An example read pair subtraction after reduction steps with an overlay of the apertures.
 {\it Top Left:} The time series constructed from raw dark frames.
 {\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied. 
-{\it Bottom Left:} An example read pair subtraction with an overlay of the apertures.
-{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.
-\textcolor{red}{To Do: redo the time series without normalization since we want to show DN.}}\label{fig:longDarkPhot}
+}\label{fig:longDarkPhot}
 \end{figure*}
@@
 \begin{itemize}
-	\item Make the two apertures have the same Y value
-	\item Make the two apertures have the same 
-	\item Put in a third aperture above the source
-	\item Re-label the aperture from "src" to 0
-	\item Use more pixels to reduce the 1/f noise (say median of another amplifier along the X direction)
+	\item Confirm that the side reference pixels are most critical in reducing the noise
 \end{itemize}

### 2019-01-05 ms.tex
more updates to long dark sectiona after confirming that the high frequency correction makes the biggest difference of all reduction steps.

@@
 For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
-The read noise for background-subtracted photometry is expected to be 1309 DN if each pixel is completely uncorrelated with the neighbors.
+If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px} RN$ is the number of pixels and $RN$ is the read noise of a single pixel.
+If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
 As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.
@@
 If uncorrected, this extra read noise will contribution 7000 ppm to the time series!
-As can be seen in Figure \ref{fig:longDarkPhot}, there a significant correlations along the fast read (X) direction of the detector due to 1/f noise.
-These can be reduced with the side reference pixels as well as a median of the entire image along the X direction.
+As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
+These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
+As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
+We find the median of the entire image long the fast read (X) direction and subtract this from every row.
 In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
@@
 \end{figure*}
-
-\textcolor{red}{To do}
-\begin{itemize}
-	\item Confirm that the side reference pixels are most critical in reducing the noise
-\end{itemize}
 

### 2019-01-05 ms.tex
more updates to long dark sectiona after confirming that the high frequency correction makes the biggest difference of all reduction steps.

@@
 For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
-If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px} RN$ is the number of pixels and $RN$ is the read noise of a single pixel.
+If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
 If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
@@
 In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
-If uncorrected, this extra read noise will contribution 7000 ppm to the time series!
+If uncorrected, this extra read noise will contribution 7000 ppm to the time series (per frame)!
 As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.

### 2019-01-07 ms.tex
more on long dark section.

@@
 The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
-These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc.
-in a zero-based counting scheme).
+These long dark integrations are used to create simulated time series because there is less available time series data with dark frames.
+The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
 Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
-In the raw data, there are 4 prominent vertical stripes due to offsets in the read-out amplifiers.
+In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
 Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.
@@
 The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
-
-What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
-We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
-Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
-For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
-If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
-If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
-As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.
-
-In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
-If uncorrected, this extra read noise will contribution 7000 ppm to the time series (per frame)!
-As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
-These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
-As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
-We find the median of the entire image long the fast read (X) direction and subtract this from every row.
-In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
 
@@
 {\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied.
+The most important step in reducing the noise is the 1/f removed by side reference pixels. 
 }\label{fig:longDarkPhot}
 \end{figure*}
+
+What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
+We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
+Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
+The background subtraction will largely remove the offsets affecting the whole 512$\times$2048 amplifier.
+However, the correlated 1/f noise along the X direction will not be subtracted efficiently by an annulus.
+Instead, a row-by-row line fit to the background would be more effective.
+
+For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
+If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
+If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
+As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.
+
+In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
+If uncorrected, this extra read noise will contribution 7000 ppm to the time series (per frame)!
+As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
+These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
+As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
+We find the median of the entire image long the fast read (X) direction and subtract this from every row.
+In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
 

### 2019-01-07 ms.tex
more notes on long dark time series.

@@
 The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
-These long dark integrations are used to create simulated time series because there is less available time series data with dark frames.
+These long dark integrations are used to create simulated time series as if it were in full frame mode.
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
-Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
+Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
 In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
-Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.
+Additionally, there obvious correlations along the fast-read (X) direction due to 1/f noise.
 
@@
 The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
+The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 2048 reference pixels to average for each amplifier.
+However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
+Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise.
+Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
 
@@
 {\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied.
-The most important step in reducing the noise is the 1/f removed by side reference pixels. 
+The most important step in reducing the noise is the 1/f, which is reduced by side reference pixels. 
 }\label{fig:longDarkPhot}

### 2019-01-10 ms.tex
wrote in results for A3 detector.
edits to discussion of amplifier offsets and dark frames.

@@
 \caption{An example slope image from the LW OTIS Stability test.
-No reference pixel correction is applied, leaving offsets at the amplifier boundaries.}\label{fig:ampOffsetsOtisGrismSlope}
+{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
+{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
+{\it Bottom Panel:} The integrated flux (without background subtraction) shows substantially offsets in flux that are eliminated by reference pixel correction.
+}\label{fig:ampOffsetsOtisGrismSlope}
 \end{figure}
@@
 If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
-As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.
+As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^7$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm per frame.
+When averaging together $\sim$ 100 full frames over $\sim$ 60 minutes, this would only contribute 3 ppm to the transit depth uncertainty.
 
 In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
-If uncorrected, this extra read noise will contribution 7000 ppm to the time series (per frame)!
+If uncorrected, this extra read noise will contribution 700 ppm to the time series (per frame)!
 As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
@@
 In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
+
+The A3 detector used for weak lens photometry has reduced 1/f noise.
+The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
 

### 2019-01-11 ms.tex
inserted a note to myself to why I think subarray is better than full frame.

@@
 The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
-The standard deviation decreases as the number of groups up the ramp becomes more numerous.}\label{fig:OTISsubarrays}
+The standard deviation decreases as the number of groups up the ramp becomes more numerous.
+This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}
 \end{figure}

### 2019-01-12 ms.tex
updates to OTIS subarray config test.

@@
 \includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
-\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
+\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare.pdf}
+\caption{{\it Top:} A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
 The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.

### 2019-01-15 ms.tex
updated the full frame subarray comparison with a more apples-to-apples comparison.
more edits to lab paper.

@@
 The accumulated charge from absorbed photons in the detector is measured with a multiplexor (MUX) that form a readout integrated circuit (ROIC) \citep{rieke2007irDetectorReview}.
-This readout circuitry makes allows the signal to be measured non-destructively up the ramp in so-called ``multiaccum" mode.
+This readout circuitry allows the signal to be measured non-destructively up the ramp in so-called ``multiaccum" mode.
 
@@
 
+Figure \ref{fig:ampResetDark} shows an example time series of the reference pixels for a dark exposure.
+The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7 seconds in duration).
+These pre-amp resets per frame causes discontinuities over every frame within an integration, but there is an upside:
+Over long timescales (10$^3$ seconds), these resets pre-amp resets will keep the bias drifts hovering around zero without any long slopes or drifts.
+
 \begin{figure}[!hbtp]
@@
 During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
-Figure \ref{fig:npSchematicTraps} shows how the size of the depletion region changes after charges have been released, highlighted with red circles.
-The persistence from trapped charge is visible after an illumination by a source, where a residual image of a bright star can appear in dark regions or dark frames following the illumination.
 
-the depletion region contains mobile charge carriers 
-These charge traps will keep electrons and holes in the depletion region even after detector reset.
-These traps then will release the charge at later times, which will create an artificial signal that affects the measured voltage the same way that incoming photons strike the depletion region.
+Figure \ref{fig:npSchematicTraps} shows a schematic of a detector that has charge traps in the substrate.
+After illumination by a source, these traps will fill with charge that does not migrate across the depletion layer.
+When the reset voltage is applied to the detector, the trapped charge remains within the depletion layer.
+In the second integration in the schematic, charge is released, which reduces the size of the depletion layer faster than the incoming photons would otherwise.
+The consequence of charge traps is that there is a deficiency in measured charge on the first integration and an excess of measured charge on the second integration.
+Therefore, a constant astrophysical signal can be measured as a time-varying one due to the charge trapping effect.
+Over timescales longer than the charge release time, the detector will reach a steady state.
 
@@
 The dark frames do not contain the photon noise in the background nor the issues with the photometric stability of illumination lamps, which are a persistent challenge with ground-based tests.
-We study here the contributions from read noise and dark current.
+We study here the contributions from read noise, 1/f noise and dark current.
 However, there could be subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where non-illuminated pixels in the images correlate with illuminated ones.
@@
 In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
-Additionally, there obvious correlations along the fast-read (X) direction due to 1/f noise.
+These amplifier offsets are caused by drifts in the reference voltage that are reset once per frame and vary from amplifier to amplifier.
+Additionally, there are obvious correlations along the fast-read (X) direction due to 1/f noise that appear as horizontal stripes in the image.
 
@@
 \includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
-\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare.pdf}
+\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
 \caption{{\it Top:} A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 

### 2019-01-16 ms.tex
minor edits throghout.

@@
 
-The NIRCam detector shows low levels of persistence compared to previous generation detectors.
+The flight NIRCam detector shows low levels of persistence compared to previous generation detectors.
 
@@
 Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
-OTIS & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
+Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
 CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
@@
 The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
-These long dark integrations are used to create simulated time series as if it were in full frame mode.
+These long dark integrations are used to create simulated time series as if it were observing many consecutive integrations in full frame mode.
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).

### 2019-01-16 ms.tex
added rectangular background-subtracted time series.

@@
 \includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
-\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
-\caption{{\it Top:} A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
+\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
 The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
@@
 This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
+\caption{An experiment with circular background-subtracted photometry shows dramatically improved precisions over raw aperture sums in Figure \ref{fig:OTISsubarrays}.
+Additionally, a median subtraction of all background pixels per row improves the precision.}\label{fig:OTISSubConfigCircularAp}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
+\caption{With rect backub.}\label{fig:OTISRectBacksub}
 \end{figure}

### 2019-01-19 ms.tex
filled out the section on amplifier boundary discontinuities.

@@
 \subsection{Amplifier Boundary Discontinuities}
+
+NIRCam's STRIPE mode and full frame mode both employ 4 amplifiers to simultaneously read out or reset 4 pixels at once.
+This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
+On the flip side, the four amplifiers will have different behaviors such as offsets in the bias level.
+The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
+If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum of a continuum source shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (bottom panel).
+
+Fortunately, the amplifier offsets are efficiently removed by reference pixels.
+For example, we subtract the median of the 4 reference pixels from each column and this efficiently removes the bias signal from each amplifier shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (middle panel and bottom panel).
+It should be noted, however, that there are gradients in the bias signal within each amplifier.
+If we simply subtract the median value of all reference pixels within an amplifier, there are still discontinuities in the spectrum.
+In addition to reference pixels, background subtracted along each column with likely remove the ampilfier boundary effect.
+If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
+
 \begin{figure}[!hbtp]

### 2019-01-20 ms.tex
some more details on temp corrections.

@@
 For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
-Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to $\lesssim$ 1 mK.
+Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to mostly $\lesssim$ 1 mK.
+The one exception is that the Long Wavelength A-side detector (A5) exhibited $\sim$ 20 min oscillations with an amplitude of 15-20 mK when using the Temperature Monitor Control (TMC) 1 active thermal control.
+Fortunately, the TMC 2 control does not undergo these oscillations and will be employed in orbit.
+If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK.
 	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode.
@@
 
-\textcolor{red}{To Do: Look at dark frames to measure how correlated the read noise is spatially (certainly the 1/f noise should be correlated}
-
 \begin{figure}[!hbtp]
@@
 The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
-The standard deviation decreases as the number of groups up the ramp becomes more numerous.
+With this very crude box extraction (and no background subtraction), the standard deviation decreases as the number of groups up the ramp becomes more numerous.
 This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}

### 2019-01-20 ms.tex
added a time series of the GL dewar test with a background subtraction box.

@@
 		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
+\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization, if we remove absolute changes likely due to the lamp.
 }\label{fig:GLtSeries}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{ap_labels_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Apertures}
+		\fig{raw_tser_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Raw time series}
+		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
+\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular aperture subtraction box.
+}\label{fig:GLtSeriesBacksub}
 \end{figure*}

### 2019-01-21 ms.tex
minor edits throghout.

@@
 It should be noted, however, that there are gradients in the bias signal within each amplifier.
-If we simply subtract the median value of all reference pixels within an amplifier, there are still discontinuities in the spectrum.
-In addition to reference pixels, background subtracted along each column with likely remove the ampilfier boundary effect.
+If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
+In addition to reference pixels, background subtracted along each column with likely remove the amplifier boundary effect.
 If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
@@
 {\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
-{\it Bottom Panel:} The integrated flux (without background subtraction) shows substantially offsets in flux that are eliminated by reference pixel correction.
+{\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
 }\label{fig:ampOffsetsOtisGrismSlope}
@@
 The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
-The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8).
+The one test with a broadband source was an OTIS stability test at NASA Johnson was a grism spectroscopy mode, whih illuminate the long wavelength detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m for the F322W2 filter, as seen in Figure \ref{fig:ampOffsetsOtisGrismSlope}.
+The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8), as shown in Figure \ref{fig:WLP8PSF}.
 This mode was designed for wavefront sensing, but is also useful for high-precision time series because it spreads the light over many pixels.
@@
 The tests with dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
-One of the stability tests during the OTIS test at NASA Johnson was a grism spectroscopy mode that used the F322W2 to illuminate the detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m.
 

### 2019-01-21 ms.tex
wrote a bunch of to do notes to self in fig captions.

@@
 {\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
+\textcolor{red}{Things to try: 1) put in a panel w/ background subtraction and maybe one with median of all ref pixels within an amplifier 2) check if there's any fringing 3) compare scatter in spectrum to photon + read noise}
 }\label{fig:ampOffsetsOtisGrismSlope}
@@
 The most important step in reducing the noise is the 1/f, which is reduced by side reference pixels. 
+\textcolor{red}{Thing to try: show 3 panels w/ last one using row by row and column by column}
 }\label{fig:longDarkPhot}
@@
 The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
+\textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}
 
@@
 Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm.
-{\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should correct to 20 groups)}}
+{\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should corrected to 20 groups)}}
 This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
@@
 \caption{Time series of the simultaneous SW/LW Time Series Stability test
+\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
 }\label{fig:otisLWSWtser}
@@
 \includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
-\caption{With rect backub.}\label{fig:OTISRectBacksub}
+\caption{With rect backub.
+\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
 \end{figure}
@@
 		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular aperture subtraction box.
+\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular background subtraction box.
+\textcolor{red}{To do: understand why the ratio of the two box time series has a larger standard deviation than in Figure \ref{fig:GLtSeries}.
+Is it just the poor SN from a small background box?
+Also, separately, compare two different detectors.}
 }\label{fig:GLtSeriesBacksub}

### 2019-01-26 ms.tex
updated the amplifier offsets figure to show different migitation methods.

@@
 \caption{An example slope image from the LW OTIS Stability test.
-{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
-{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
-{\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
-\textcolor{red}{Things to try: 1) put in a panel w/ background subtraction and maybe one with median of all ref pixels within an amplifier 2) check if there's any fringing 3) compare scatter in spectrum to photon + read noise}
+{\it First Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
+{\it Second Panel:} Averaging all the reference pixels within an amplifier and subtracting the result reduces the offsets between amplifiers but there are still noticeable boundaries at X= 512, 1024 and 1536.
+{\it Third Panel:} Reference pixel correction using the 4 non-illuminated pixels in each column significantly reduces offsets between amplifiers, but introduces read noise to each column.
+{\it Fourth Panel:} Background subtraction with a linear fit along each column eliminates offsets between amplifiers without introducing any substantial new noise source.
+\textcolor{red}{Things to try: 1) check if there's any fringing in the spectrum 2) compare scatter in spectrum to photon + read noise}
 }\label{fig:ampOffsetsOtisGrismSlope}

### 2019-01-27 ms.tex
added short analysis of OTIS spectrum.
several plot updates and analysis of OTIS data.

@@
 The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
-If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum of a continuum source shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (bottom panel).
+If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum.
 
@@
 If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
-In addition to reference pixels, background subtracted along each column with likely remove the amplifier boundary effect.
+In addition to reference pixels, background subtraction along each column with removes the amplifier boundary effect.
 If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
@@
 {\it Third Panel:} Reference pixel correction using the 4 non-illuminated pixels in each column significantly reduces offsets between amplifiers, but introduces read noise to each column.
-{\it Fourth Panel:} Background subtraction with a linear fit along each column eliminates offsets between amplifiers without introducing any substantial new noise source.
-\textcolor{red}{Things to try: 1) check if there's any fringing in the spectrum 2) compare scatter in spectrum to photon + read noise}
+{\it Fourth Panel:} Background subtraction with the mean value of the pixels below Y=15 and above Y=190 eliminates offsets between amplifiers without introducing any substantial new noise source.
+\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum}
 }\label{fig:ampOffsetsOtisGrismSlope}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
+\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
+\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
+The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
+The sca
+A periodogram shows a peak near 19 pixels period, however, it is not an overwhelming periodic signature.
+\textcolor{red}{double check the scatter in spectrum to photon + read noise}
+}\label{fig:integratedOtisGrismSpec}
 \end{figure}
@@
 \centering
-\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
-\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
+\includegraphics[width=.32\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.32\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_Raw.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_Reduced.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_ReducedRowColSub.pdf}
 \caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-{\it Top Left:} An example read pair subtraction with an overlay of the apertures.
-{\it Top Right:} An example read pair subtraction after reduction steps with an overlay of the apertures.
-{\it Top Left:} The time series constructed from raw dark frames.
-{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied.
-The most important step in reducing the noise is the 1/f, which is reduced by side reference pixels. 
-\textcolor{red}{Thing to try: show 3 panels w/ last one using row by row and column by column}
+{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from "Raw" data using no reference pixel correction, "Reduced Data" using reference pixels and "ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
+{\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
+The most important step for reducing the noise in the time series is row-by-row subtraction to remove the 1/f noise.
 }\label{fig:longDarkPhot}

### 2019-01-30 ms.tex
wrote about correlated read noise impact

@@
 We find the median of the entire image long the fast read (X) direction and subtract this from every row.
-In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.
-
+In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
 The A3 detector used for weak lens photometry has reduced 1/f noise.
 The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
+
+\subsubsection{The impact of correlated read noise on time series}
+We consider here some example science impacts of correlated read noise in these photometric apertures.
+We will evaluate the performance of a WEAK LENS +8 mode photometric time series, as will be common with NIRCam grism time series observations.
+For a pessimistic scenario, we assume a 15,000 DN read noise contributes to every pair of reads for the 70 pixel radius aperture (and 75 to 100 pixel background subtraction annulus).
+If the read noise is tolerable under this scenario, then it should have a minimal impact to photometric time series.
+If it is a problem, we will discuss methods of mitigation such as the row-by-row subtraction above.
+
+We also assume that each read/frame is statistically independent from the other.
+We assume therefore the read noise per integration is:
+\begin{equation}
+RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}}
+\end{equation},
+where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the detector.
+If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
+\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also verify with a slope fit to multiple images.}
+For an integration that fills to a peak of $\sim$ 60\% or 35,000 DN, the integrated DN counts would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
+Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames.
+
 \textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}

### 2019-01-31 ms.tex
added plot with apertres in subarray config test.

@@
 \centering
-\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
+\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-128-STRIPE-72.pdf}
+\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-256-STRIPE-72.pdf}
+\includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
 \caption{With rect backub.

### 2019-02-13 ms.tex
more on photosensitive operation

@@
 
-It is helpful to review the basic operation of a NIRCam detector in order to understand the systematics affecting time series \citep[e.g.][]{rieke2007irDetectorReview}.
+It is helpful to review the basic operation of a NIR detector \citep[e.g.][]{rieke2007irDetectorReview} in order to understand the systematics affecting time series.
 Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
@@
 \caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
-The green and blue regions depict the N-type and P-type semiconductors.
-The undepleted zones of the semiconductor (fire brick and dim gray colors) contain mobile charge carriers whereas the depletion region (dark salmon) has no mobile carriers and all electrons are in the valence state.
+The orange and blue purple colors depict the N-type and P-type semiconductors, respectively.
+The undepleted zones of the semiconductor (darker colors with - and + signs) contain mobile charge carriers whereas the depletion region (lighter color without - and +) has no mobile carriers and all electrons are in the valence state.
 The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
+The electron-hole pairs migrate across the depletion region towards the undepleted zones due to an electric field.
 The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
@@
 This produces a negative charge on the P-type side.
-Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a positive charge.
-This difference is called the contact potential.
+Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge.
+The resulting voltage difference is called the contact potential.
 In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
-This region spanning across the two semiconductor materials is called the depletion region, because it contains no mobile charge carriers.
+This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it contains no mobile charge carriers.
 The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
+It should be noted that the ``depletion region'' is depleted in {\it mobile charge carriers}, but is {\it not} depleted in net charge because has a net positive charge in the N-type depletion region and negative charge in the P-type depletion region.
 
@@
 The reverse bias is applied at each reset at the beginning of a detector's integration.
-Figure \ref{fig:npSchematic} shows the case where the density of charge carriers is equal in the N-type and P-type semiconductors, but in reality, the density of the P-type semiconductor is much higher than the N-type, so the depletion region has a larger physical size on the N-type side.
+Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
+The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is much lower in the N-type.
 
@@
 Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
-The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to visualize the charge trapping effect this way \citep[e.g.][]{smith2008imgPersistence}.
+The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to visualize the charge trapping effect and motion of mobile charges this way \citep[e.g.][]{smith2008imgPersistence}.
 
 When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
+The depletion region has a net electric field pointed toward the P-type side, which sets the direction electrons and holes will migrate.
 The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.

### 2019-02-15 ms.tex
a few edits to photosensitive operation and known detector effects.

@@
 The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
-The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positve charge carriers (holes).
+The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positive charge carriers (holes).
 The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
@@
 Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
-The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is much lower in the N-type.
+The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type.
 
-Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only, so the depletion region, with no mobile charges is positively charged on the N-type side and negatively charged on the P-type side.
-The undepleted region is electrically neutral because the nuclei of the N-type material have an equal number of extra protons as the negatively charged electrons.
-Similarly, the undepleted region of the P-type semiconductor has fewer protons in its atomic nuclei producing an overall neutral charge.
+Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only.
 Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
@@
 When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
-The depletion region has a net electric field pointed toward the P-type side, which sets the direction electrons and holes will migrate.
+The depletion region has a net electric field pointed toward the P-type side, which controls the direction electrons and holes will migrate.
 The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
@@
 The electronic circuit that digitizes the voltages is tuned to ensure the 16 bits (65,536 possible Data Numbers) measure the voltage across the NP junction from the value just after reset (before photons are detected) to the saturation voltage where the maximum number of photons are collected and no more electron-hole pairs can be produced in the depletion region.
-The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not below 0.
-The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation.
+The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not go below 0.
+The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation of a pixel.
 
 \section{Known Detector Effects}\label{sec:knownEffects}
+Section \ref{sec:detectorPrimer} describes the operation of a HgCdTe array.
+However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
+Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics. These known detector effects that can impact stability are:
 
-Known detector effects that could affect stability include:
 \begin{itemize}[noitemsep]
@@
 Fortunately, the TMC 2 control does not undergo these oscillations and will be employed in orbit.
-If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK.
+If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK \citep{hall2005jwstArrays}.
 	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode.
@@
 The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-There were two dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+There were are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).

### 2019-02-15 ms.tex
show the aperture for grism ap on OTIS long dark

@@
 
+\subsection{Grism Aperture}
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1.pdf}
+\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5.
+As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
+The photometric aperture is made to represent a similar one to the F322W2 grism trace.
+}\label{fig:longDarkGrism}
+\end{figure*}
+
 \subsubsection{The impact of correlated read noise on time series}

### 2019-02-16 ms.tex
Repeated the long dark experiment for grism-like aperture and renamed dark files

@@
 \includegraphics[width=.32\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_Raw.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_Reduced.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_ReducedRowColSub.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_dark.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_darkRed.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
 \caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
@@
 \centering
-\includegraphics[width=.4\columnwidth]{ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.32\columnwidth]{g00_ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1}
+\includegraphics[width=.32\columnwidth]{g01_ap_labels_darkGrismApA5red_NRCALONG-DARK-7235074213_1}
+\includegraphics[width=.32\columnwidth]{g02ap_labels_darkGrismApA5redRowCol_NRCALONG-DARK-7235074213_1}
+\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5red.pdf}
+\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5redRowCol.pdf}
 \caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5.

### 2019-02-19 ms.tex
update ap labels to be all in one place

@@
 \centering
-\includegraphics[width=.32\columnwidth]{g00_ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1}
-\includegraphics[width=.32\columnwidth]{g01_ap_labels_darkGrismApA5red_NRCALONG-DARK-7235074213_1}
-\includegraphics[width=.32\columnwidth]{g02ap_labels_darkGrismApA5redRowCol_NRCALONG-DARK-7235074213_1}
+\includegraphics[width=.32\columnwidth]{aps_3_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_int_015_014.pdf}
+\includegraphics[width=.32\columnwidth]{aps_0_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014.pdf}
+\includegraphics[width=.32\columnwidth]{aps_1_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014_rowColSub.pdf}
 \includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}

### 2019-02-20 ms.tex
labeled phot and spec apertures

@@
 \textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also verify with a slope fit to multiple images.}
-For an integration that fills to a peak of $\sim$ 60\% or 35,000 DN, the integrated DN counts would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
+For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
 Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames.

### 2019-02-25 ms.tex
some calcs of photon vs correlated read noise.

--- 2019-02-19 ms.tex
@@
 
+%% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
 \subsubsection{The impact of correlated read noise on time series}
@@
 We also assume that each read/frame is statistically independent from the other.
-We assume therefore the read noise per integration is:
+Therefore, the uncorrected read noise per integration is:
 \begin{equation}
-RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}}
-\end{equation},
-where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the detector.
+RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}},
+\end{equation}
+where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the A3 detector.
 If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
-\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also verify with a slope fit to multiple images.}
-For an integration that fills to a peak of $\sim$ 60\% or 35,000 DN, the integrated DN counts would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
-Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames.
+\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also empirically verify this with a slope fit to multiple images.}
+For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
+Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames that fill to 60\% well depth.
+As an example, a $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode with 6 RAPID groups up the ramp sampling and the F210M filter would have a photon noise equal to the (uncorrected) read noise and fill the detector to 54\% well depth.
 

### 2019-04-13 ms.tex
added figures on crosshatch from flat field.

@@
 
+\subsection{Subpixel Crosshatching}
+The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
+The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
+The angle between these lines is thus 44.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
+\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
+\caption{
+The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
+}\label{fig:crossHatchA5}
+\end{figure}
+
 \subsection{Amplifier Boundary Discontinuities}

### 2019-04-27 ms.tex
added a tetrahedral/zincblende projection that matches detector angles.
more on the zincblende bond structure.

@@
 The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
-The angle between these lines is thus 44.
+The angle between these lines are 67.60$\degree$, 44.5$\degree$ and 67.8$\degree$.
+These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
+
+The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
+HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
+One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
+In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
+We therefore conclude that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
 
@@
 The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
+The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
+The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
 }\label{fig:crossHatchA5}

### 2019-04-27 ms.tex
more on subpixel level of crosshatch

@@
 
+The crosshatch structure of the detectors extends down to the subpixel level, so it may not be fully corrected with a flat field division.
+This sub-pixel structure has been imaged with microscopy \citep{shapiro2018crosshatch}.
+The width of the structures can be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
+
 \begin{figure}[!hbtp]

### 2019-04-30 ms.tex
prescription for Fourier amplitude

--- 2019-04-27 ms.tex
@@
 In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
-We therefore conclude that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
+We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
+
+The crosshatch structure of the detectors extends down to the subpixel level, so it will not be fully corrected with a flat field division.
+This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
+The width of the structures can be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
+We estimate that the crosshatch pattern oriented at 90.9$\degree$ crosses 1 horizontal pixel for every 64 vertical pixels.
+While crossing the boundary, there are $\approx 38$ rows where the crosshatch pattern spans more than 2 pixels.
+If the crosshatch pattern has a tophat response function, then these 38 rows where the pattern spans two pixels imply a tophat full width of 0.6 pixels or a physical width of 10.8~$\mu$m for an 18~$\mu$m pixel pitch.
+This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
+It is possible that the crosshatch pattern's width varies among detectors or that a tophat function is a poor approximation of the actual subpixel response.
+Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
+
+We attempt to model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency.
+We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
+\begin{equation}
+f(x',y') = \exp{\left(-y'^2/\tau_\perp\right)} \left( \frac{a}{b + x'^2} + \frac{c}{1 + \exp{\left( (|x'| - d)/\tau_\parallel \right)} } \right),
+\end{equation}
+where $x'$ and $y'$ are rotated coordinates, $\tau_\perp$ is the perpendicular exponential constant, $a$ and $b$ are polynomial constants for the central peak of the Fourier plane, $c$ is an exponential amplitude constant and $d$ is the cutoff frequency with an exponential constant $\tau_\parallel$.
+For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
+\begin{equation}
+x' = (x - x_0) \cos{\theta} + (y - y_0) \sin{\theta}
+\end{equation}
+and
+\begin{equation}
+y' = -(x - x_0) \sin{\theta} + (y - y_0) \cos{\theta}.
+\end{equation}
+We include three angles so that the total Fourier amplitude is
+\begin{equation}
+f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i,y'_i)
+\end{equation}
+for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.
 

### 2019-05-01 ms.tex
described how I plan to run the crosshatch simulation.

@@
 \subsection{Subpixel Crosshatching}
+
+\subsubsection{Subpixel Crosshatching Characterization}
 The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
@@
 
-We attempt to model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency.
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
+\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
+\caption{
+The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
+The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
+The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
+}\label{fig:crossHatchA5}
+\end{figure}
+
+\subsubsection{Subpixel Crosshatching Simulation}
+
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope jitter.
+NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
+
+We simulate the effect of this jitter on NIRCam grism time series observations with the following steps:
+\begin{itemize}
+	\item Fit the existing flat field to an crosshatch model that describes the subpixel behavior
+	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Jitter the simulated PSF over with a 6 mas Gaussian
+	\item Bin the simulated images into the native pixel size
+	\item Divide by the flat field
+	\item Measure the light curve with photometry or spectroscopic aperture
+\end{itemize}
+
+We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency as seen in Figure \ref{fig:crossHatchA5}.
 We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
@@
 for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
-\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
-\caption{
-The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
-The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
-The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
-}\label{fig:crossHatchA5}
-\end{figure}
 

### 2019-05-02 ms.tex
separated the crystal pattern drawing from the plots

@@
 \includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
+\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
 \caption{
 The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
-The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
-The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
+The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
+The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
+Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
+These three angles are similar to one possible projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom).
 }\label{fig:crossHatchA5}
 \end{figure}
+
+The crosshatch pattern is wavelength dependent.
 
@@
 	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Jitter the simulated PSF over with a 6 mas Gaussian
+	\item Low frequency ($<$ 1/10second) jitter the simulated PSF over with a 6 mas Gaussian
 	\item Bin the simulated images into the native pixel size

### 2019-05-04 ms.tex
plots of wavelength dependence.

@@
 The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
-The angle between these lines are 67.60$\degree$, 44.5$\degree$ and 67.8$\degree$.
+The angle between these lines are 67.8$\degree$, 67.7$\degree$ and 44.5$\degree$.
 These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
@@
 One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
-In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 44.4$\degree$ and 67.8$\degree$, close to the observed crosshatch angles.
+In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
 We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
@@
 Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three angles are similar to one possible projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom).
+These three angles are similar (with 0.1$\degree$) to one projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom).
 }\label{fig:crossHatchA5}
@@
 The crosshatch pattern is wavelength dependent.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{cross_sec_of_crosshatch.pdf}
+\includegraphics[width=.49\columnwidth]{fourier_power_from_fit.pdf}
+\caption{
+The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better, and thus have Fourier amplitudes.
+}\label{fig:crossHatchWavelengthDep}
+\end{figure}
 
@@
 \begin{itemize}
-	\item Fit the existing flat field to an crosshatch model that describes the subpixel behavior
+	\item Fit the existing flat field to an crosshatch model in the Fourier domain
+	\item Extrapolate the crosshatch model to high frequencies to estimate the sub-pixel structure
 	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
@@
 We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency as seen in Figure \ref{fig:crossHatchA5}.
-We model the two dimensional Fourier amplitude $f(x',y')$ for one angle as
+We model the two dimensional Fourier amplitude $f(x_i',y_i')$ for one angle $\theta_i$ as
 \begin{equation}
-f(x',y') = \exp{\left(-y'^2/\tau_\perp\right)} \left( \frac{a}{b + x'^2} + \frac{c}{1 + \exp{\left( (|x'| - d)/\tau_\parallel \right)} } \right),
+f(x'_i,y'_i, a_i, b,c) = a \exp{\left(- |x_i'| / b \right)} \left( \frac{1}{(0.5 c)^2 + y'^2} \right),
 \end{equation}
-where $x'$ and $y'$ are rotated coordinates, $\tau_\perp$ is the perpendicular exponential constant, $a$ and $b$ are polynomial constants for the central peak of the Fourier plane, $c$ is an exponential amplitude constant and $d$ is the cutoff frequency with an exponential constant $\tau_\parallel$.
+where $x'$ and $y'$ are rotated coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian width.
 For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
 \begin{equation}
-x' = (x - x_0) \cos{\theta} + (y - y_0) \sin{\theta}
+x'(\theta_i) = (x - x_0) \cos{\theta_i} + (y - y_0) \sin{\theta_i}
 \end{equation}
@@
 \begin{equation}
-y' = -(x - x_0) \sin{\theta} + (y - y_0) \cos{\theta}.
+y'(\theta_i) = -(x - x_0) \sin{\theta_i} + (y - y_0) \cos{\theta_i}.
 \end{equation}
-We include three angles so that the total Fourier amplitude is
+We include three angles so that the total power spectral density is
 \begin{equation}
-f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i,y'_i)
+f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i(\theta_i),y'_i(\theta_i),a_i,b,c).
 \end{equation}
-for $\theta_i = 0.9^\circ$, 68.7$^\circ$ and 113.2$^\circ$.
+
+This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
+
+We only fit the region of the power spectral density above r=100 to focus on the high frequency component of the flat field where the crosshatch is most prevalnt.
+We find 
+for $\theta_i = 0.9\degree$, 68.6$\degree$ and 113.1$\degree$.
 

### 2019-05-07 ms.tex
described the subpix crosshatch simulations in more detail.

@@
 
-The crosshatch pattern is wavelength dependent.
+The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the
 
@@
 \caption{
-The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better, and thus have Fourier amplitudes.
+The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better.
+The shorter wavelengths have deeper crosshatch troughs (left) and higher Fourier amplitudes (right).
 }\label{fig:crossHatchWavelengthDep}
@@
 
-The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope jitter.
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
 NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
 
-We simulate the effect of this jitter on NIRCam grism time series observations with the following steps:
+We simulate the effect of this jitter on NIRCam time series observations with the following steps:
 \begin{itemize}
@@
 	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Low frequency ($<$ 1/10second) jitter the simulated PSF over with a 6 mas Gaussian
+	\item Multiply the PSF by the simulated flat field
+	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
 	\item Bin the simulated images into the native pixel size
 	\item Divide by the flat field
-	\item Measure the light curve with photometry or spectroscopic aperture
+	\item Measure the relative flux with a photometric aperture
 \end{itemize}
@@
 \end{equation}
-where $x'$ and $y'$ are rotated coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian width.
+where $x'$ and $y'$ are rotated coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
 For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
@@
 This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
-
-We only fit the region of the power spectral density above r=100 to focus on the high frequency component of the flat field where the crosshatch is most prevalnt.
-We find 
-for $\theta_i = 0.9\degree$, 68.6$\degree$ and 113.1$\degree$.
+We only fit the region of the power spectral density above r=100 to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
+For the F300M filter and ALONG detector, we find 
+for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 6.9 \pm 0.2 \times 10^6, a_2 = 4.0 \pm 0.1 \times 10^6, a_3 = 4.4 \pm 0.1 \times 10^6, b=666 \pm 1 $ px and $c=4.9933 \pm 0.0004$ px.
+The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
+
+We take this model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
+Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
+For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel resolution of $\sim$0.063 \arcsec.
+This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
+For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
+\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
+\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
+\caption{
+The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better, and thus have Fourier amplitudes.
+}\label{fig:crossHatchSimPSF}
+\end{figure}
+
+We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
+\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
+We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
+We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
+This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
+
+We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
+The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
+For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
+These simulated operations represent pointing drift on the subpixel scale.
+
+We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
+The aperture is re-centered by the same position as the shift direction.
+For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
+While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
+The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
+\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
+\caption{
+The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
+Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
+The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
+These are correctable with smooth functions such as polynomials.
+}\label{fig:subpixScanSimulation}
+\end{figure}
+
+The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
+The amplitude of the flux changes is potentially up to 300 ppm.
+This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
+
+Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}
+Smooth functions, such as polynomials, with centroid position will likely 
+Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
+When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
+Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
+Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
+This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
 

### 2019-05-09 ms.tex
put in reminder to myself to describe new correct 1/f correction to red file instead of slope file.

@@
 We find the median of the entire image long the fast read (X) direction and subtract this from every row.
+\textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
+Here we subtract the median value from each row in each group}
 In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.

### 2019-05-10 ms.tex
include results after doing subtraction by smoothed images on each group

@@
 \textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
-Here we subtract the median value from each row in each group}
+Here we subtract the median value from each row in each group.
+Doing the subtractions for each group gave an RMS that was 50 ppm smaller for aperture 0, 80 ppm larger for aperture 1 and 31 ppm smaller for aperture 3.}
 In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
@@
 
-\subsection{Grism Aperture}
+\subsubsection{Grism Aperture}
 \begin{figure*}[!hbtp]
@@
 \textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}
+
+\subsubsection{Smoothed Kernel Subtraction}
+
+We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
+We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
+The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
+This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than $\lesssim 5$ milliseconds, which the median subtraction cannot remove.
+
+This smoothing kernel makes a dramatic improvement to the final weak lens aperture time series, as shown in Figure \ref{fig:longDarkWithRowKernel}.
+The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
+For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
+For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
+\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
+\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
+Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
+}\label{fig:longDarkWithRowKernel}
+\end{figure*}
 

### 2019-05-12 ms.tex
spelling out the read noise/shot noise calculations more clearly

@@
 It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
-The dark frames do not contain the photon noise in the background nor the issues with the photometric stability of illumination lamps, which are a persistent challenge with ground-based tests.
+The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
+They also do not contain photon noise in the background, which can mask the electronic noise sources.
 We study here the contributions from read noise, 1/f noise and dark current.
-However, there could be subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where non-illuminated pixels in the images correlate with illuminated ones.
+This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
 
 The standard long dark exposures used for detector characterization are a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
-The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
+The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure was 19.3 min.
 These long dark integrations are used to create simulated time series as if it were observing many consecutive integrations in full frame mode.
@@
 The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
-The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 2048 reference pixels to average for each amplifier.
+The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 4096 reference pixels to average for each amplifier at the bottom and top of the arrays.
+There are an additional 4 columns on the left and right side boundaries (8176 pixels) that can be used to further correct the left and right amplifier offests.
 However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
@@
 Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
+These side reference pixels also cannot give any information about the read noise correlations that happen on shorter length scales than 512 pixels (5 ms).
 
@@
 For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
-If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
+If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}} \times RN $ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
 If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
-As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^7$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm per frame.
+
+This theoretical read noise should be compared to the photon noise expected inside an aperture during photometric stability time series applications.
+The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $DN_{tot}=3.9\times 10^7$ DN during the integration.
+The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
+The Poisson shot noise for photons is $N_{phot} = \sqrt{DN_{tot}} / \sqrt{G} = 4,400$DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
+In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
+Therefore, the read noise is expected to be 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
 When averaging together $\sim$ 100 full frames over $\sim$ 60 minutes, this would only contribute 3 ppm to the transit depth uncertainty.
@@
 
+\subsubsection{Smoothed Kernel Subtraction}
+
+We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
+We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
+The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
+This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than $\lesssim 5$ milliseconds, which the median subtraction cannot remove.
+
+This smoothing kernel makes a dramatic improvement to the final weak lens aperture time series, as shown in Figure \ref{fig:longDarkWithRowKernel}.
+The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
+For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
+For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
+\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
+\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
+Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
+}\label{fig:longDarkWithRowKernel}
+\end{figure*}
+
 \subsubsection{Grism Aperture}
@@
 \textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}
-
-\subsubsection{Smoothed Kernel Subtraction}
-
-We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
-We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
-The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
-This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than $\lesssim 5$ milliseconds, which the median subtraction cannot remove.
-
-This smoothing kernel makes a dramatic improvement to the final weak lens aperture time series, as shown in Figure \ref{fig:longDarkWithRowKernel}.
-The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
-For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
-For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
-\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
-\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
-Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
-}\label{fig:longDarkWithRowKernel}
-\end{figure*}
 

### 2019-05-14 ms.tex
more details on 1/f noise and updated figures for row-by-row subtraction of each group

@@
 
-The standard long dark exposures used for detector characterization are a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
-The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure was 19.3 min.
-These long dark integrations are used to create simulated time series as if it were observing many consecutive integrations in full frame mode.
+A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
+The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
+We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
@@
 
+The ramps-to-slope pipeline \texttt{ncdhas} or the STScI JWST pipeline will apply reference pixel correction, bad pixels masks and non-linearity correction before fitting the groups up the ramp to a line.
+In this work, we use \texttt{ncdhas}.
 As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
@@
 However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
-Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise.
+Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row.
 Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
@@
 \includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.32\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.32\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1.pdf}
 \includegraphics[width=.32\columnwidth]{long_dark_dark.pdf}
@@
 If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}} \times RN $ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
-If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
+If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1310 DN.
 
 This theoretical read noise should be compared to the photon noise expected inside an aperture during photometric stability time series applications.
-The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $DN_{tot}=3.9\times 10^7$ DN during the integration.
+The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
 The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
-The Poisson shot noise for photons is $N_{phot} = \sqrt{DN_{tot}} / \sqrt{G} = 4,400$DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
+The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
 In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
 Therefore, the read noise is expected to be 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
-When averaging together $\sim$ 100 full frames over $\sim$ 60 minutes, this would only contribute 3 ppm to the transit depth uncertainty.
-
-In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
-If uncorrected, this extra read noise will contribution 700 ppm to the time series (per frame)!
+When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.
+
+In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for 1/f noise using reference pixels or otherwise).
+If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
+This would be a very inefficient observations if the read noise dominated the $\sim$113 ppm photon noise.
 As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
-These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
-As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
-We find the median of the entire image long the fast read (X) direction and subtract this from every row.
+
+These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
+We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
+The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN, but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
+
+Since these 8 reference pixels in each row are not sufficient to remove all 1/f noise in each row, so we perform another correction step:
+We find the median of each group up the ramp along the fast read (X) direction and subtract this from every row.
+This amounts to a row-by-row background subtraction.
+
 \textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
@@
 \includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
-\caption{Weak Lans +8 PSF during CV3 testing.
+\caption{Weak Lens +8 PSF during CV3 testing.
 The central peak is used for centroiding, while the entire PSF is used for aperture photometry.

### 2019-05-14 ms.tex
fixed the zoomed-in row-by-row subtraction

@@
 
+\clearpage
 \subsection{Long Darks}\label{sec:longDarks}
@@
 
-\textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
-Here we subtract the median value from each row in each group.
-Doing the subtractions for each group gave an RMS that was 50 ppm smaller for aperture 0, 80 ppm larger for aperture 1 and 31 ppm smaller for aperture 3.}
 In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
@@
 \centering
-\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
+\includegraphics[width=.37\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1}
 \includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
+\includegraphics[width=.37\columnwidth]{zoom_long_dark_row_by_row_group_sub.pdf}
 \includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
-\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
-Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
+\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image where a 40 pixel wide and 1 pixel tall averaging kernel was applied along the fast read direction of every group.
+Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise from $\sim$6,000 DN to $\sim$700 DN in the aperture.
 }\label{fig:longDarkWithRowKernel}
 \end{figure*}
+\clearpage
 

### 2019-05-17 ms.tex
added an example pixel-wise time series.

@@
 \end{figure*}
+
+\subsubsection{Other Reference Channel Subtraction}
+We note that the 4 channels have very similar 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
+Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pixeltime_series.pdf}
+\caption{The time series for all 4 amplifiers is very similar due to shared 1/f noise behavior.
+This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.}\label{fig:darkPixelTimeSeries}
+\end{figure*}
+
 \clearpage

### 2019-05-18 ms.tex
put in results of the first amplifier flip test. I am surprised that it didn't help more because the 4 channels look highly correlated.

@@
 Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
-
+We attempt to subtract an amplifier 0's time series from all amplifiers.
+Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
+The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
+However, this increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
+
+This method increases the noise over a row-by-row median subraction.
+The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
+This means the the correlations within an amplifier are not efficiently subracted (\textbf{\textcolor{red}{or there was an error in the code. I'm surprised that it didn't make a bigger difference.}}).
 \begin{figure*}[!hbtp]

### 2019-05-19 ms.tex
verified the flipped amplifier method and its drawbacks.

--- 2019-05-14 ms.tex
@@
 \end{figure*}
+
+\subsubsection{Other Reference Channel Subtraction}
+We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
+Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
+We attempt to subtract an amplifier 0's time series from all amplifiers.
+Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
+The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
+This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
+On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.
+
+The net effect of this method is to increase the noise over a row-by-row median subtraction.
+The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
+This means the the correlations within an amplifier are not efficiently subtracted and may be propagated to the remaining amplifiers.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pixeltime_series_0.pdf}
+\includegraphics[width=.4\columnwidth]{pixeltime_series_1.pdf}
+\caption{The time series for all 4 amplifiers share common-mode behaviors in some cases (left) but not always (right).
+This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.
+The left panel shows the beginning of the time series, which happens to be dominated by common-mode read noise.
+The right panel shows another part of the time series where Amplifier 3 has its own individual correlated-noise pattern.
+}\label{fig:darkPixelTimeSeries}
+\end{figure*}
+
 \clearpage

### 2019-05-21 ms.tex
adjust to time series and also show the PCA-based approach to 1/f corrections.

@@
 The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
-This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than $\lesssim 5$ milliseconds, which the median subtraction cannot remove.
+This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than 5 milliseconds, which the median subtraction cannot remove.
 
@@
 
-\subsubsection{Other Reference Channel Subtraction}
+\subsubsection{Reference Channel Subtraction}
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
@@
 \centering
-\includegraphics[width=.4\columnwidth]{pixeltime_series_0.pdf}
-\includegraphics[width=.4\columnwidth]{pixeltime_series_1.pdf}
-\caption{The time series for all 4 amplifiers share common-mode behaviors in some cases (left) but not always (right).
-This is visible in a short segment of the time series of all pixels for an example group up the ramp (53) in a dark ramp where the bias has already been subtracted.
+\includegraphics[width=.32\columnwidth]{pixeltime_series_0.pdf}
+\includegraphics[width=.32\columnwidth]{pixeltime_series_1.pdf}
+\includegraphics[width=.32\columnwidth]{all_amp_periodograms.pdf}
+\caption{The time series for all 4 amplifiers share common-mode behaviors in some cases (left) but not always (middle).
+This is visible in a short segment of the time series of all pixels for an example group up the ramp 53 in a dark ramp where the bias has already been subtracted.
 The left panel shows the beginning of the time series, which happens to be dominated by common-mode read noise.
-The right panel shows another part of the time series where Amplifier 3 has its own individual correlated-noise pattern.
+The middle panel shows another part of the time series where Amplifier 3 has its own individual correlated-noise pattern.
+The right panel shows the periodogram of each amplifier's time series over the first 10$^5$ clock cycles (0.1) seconds, which exhibits no consistent peaks.
 }\label{fig:darkPixelTimeSeries}
+\end{figure*}
+
+\subsubsection{PCA Correction}
+Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
+Here, we assume that each column is a random variable that is correlated with the rest of the columns.
+Each row represents a different noise iteration.
+We first mask all bad pixels by setting all pixels with $| f | > 200$ DN.
+The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
+These first 10 principal components explain 10\% of the total variance in each group.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp54.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
+\caption{Principal component eigenvectors identified from group 54 (left) and group 55 (right).
+}\label{fig:pcaEigenvectors}
 \end{figure*}

### 2019-05-23 ms.tex
updated figure caption of crosshatch simulation images

@@
 \caption{
-The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better, and thus have Fourier amplitudes.
+The steps of the sub-pixel crosshatch photometry simulation are shown here.
+We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
+This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
+A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
+Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
+The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
 }\label{fig:crossHatchSimPSF}

### 2019-05-29 ms.tex
added subgrism positions as well as a table summarizing read noise in dark frames.

@@
 This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detector, which will be used for exoplanet spectra.
+Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra.
 %and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
@@
 It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage.
-1/f noise is efficiently removed by reference pixels
+1/f noise can be reduced using reference pixels
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
@@
 This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
+
+\subsubsection{Position of SubGrism Array}
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_grism64flat.pdf}\\
+\vspace{0.2in}
+\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64_psd.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_grism64_psd.pdf}\\
+\caption{
+The top of the array has the smallest level of crosshatching and the middle has the largest.
+This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array, the full frame position near Y=512 and the nominal SUBGRISM64 at the bottom of the array.
+ }\label{fig:subpixScanSimulation}
+\end{figure}
 
@@
 
+\begin{deluxetable*}{ccc}[b!]
+\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
+\tabletypesize{\footnotesize}
+%\tablecolumns{7}
+%\tablenum{2}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Noise Description} &
+\colhead{$\sigma$} &
+\colhead{$\sigma$} \\
+\colhead{} &
+\colhead{DN} &
+\colhead{ppm}\\
+}
+\startdata
+Ideal Photon Noise & 4,400 & 113 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 \\
+\hline
+Measured Read Noise (no correction) & 23,500 & 600 \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
+Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
+Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
+Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
+Measured Read Noise (smoothed 40 px kernel) & 900 & 23 \\
+\enddata
+\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
+The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
+The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
+\end{deluxetable*}
+
 These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
@@
 The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
-These first 10 principal components explain 10\% of the total variance in each group.
+These first 10 principal components explain 10\% of the total variance in each group up the ramp.
 
@@
 \end{figure*}
+
+We begin by calculating new principal components and eigenvectors for each group up the ramp and then subtracting the first 10 principal component eigenvectors multiplied by their respective principal components by each image.
+It is important to mask the bad pixels before calculating the principal components so they are not driven by errant bad pixels.
+We also calculate the PCA eigenvectors after the bias has been subtracted and the reference pixel correction was applied.
+The PCA subtraction is applied to each group up the ramp and then these groups are subtracted in pairs to create a time series.
+The final time series has and measured standard deviation of 5,000 to 5,700 DN within the background-subtracted aperture.
+This is comparable to the row and column subtraction standard deviation of 5,500 to 6,500 DN.
+Adding 10 more principal components for a total of 20 eigenvectors only reduces the time series noise to 5,100 to 5,400 for the 3 apertures.
 

### 2019-05-31 ms.tex
some more notes on crosshatch as a function of location.

@@
 \subsubsection{Position of SubGrism Array}
+
+The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
+The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
+On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
+We fit the crosshatch pattern to three regions of the detector:
+\begin{itemize}
+	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
+	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
+	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
+\end{itemize}
+
 \begin{figure}[!hbtp]

### 2019-06-03 ms.tex
changing notation from x to kx for frequency

@@
 
-We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency as seen in Figure \ref{fig:crossHatchA5}.
-We model the two dimensional Fourier amplitude $f(x_i',y_i')$ for one angle $\theta_i$ as
+We 
+We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
+We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
 \begin{equation}
-f(x'_i,y'_i, a_i, b,c) = a \exp{\left(- |x_i'| / b \right)} \left( \frac{1}{(0.5 c)^2 + y'^2} \right),
+f(k_{x,i}',k_{y,i}', a_i, b,c) = a \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
 \end{equation}
-where $x'$ and $y'$ are rotated coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
+where $k_x'$ and $k_y'$ are rotated frequency coordinates coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
 For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
 \begin{equation}
-x'(\theta_i) = (x - x_0) \cos{\theta_i} + (y - y_0) \sin{\theta_i}
+k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
 \end{equation}
@@
 \begin{equation}
-y'(\theta_i) = -(x - x_0) \sin{\theta_i} + (y - y_0) \cos{\theta_i}.
+k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
 \end{equation}
@@
 \begin{equation}
-f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i(\theta_i),y'_i(\theta_i),a_i,b,c).
+f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c).
 \end{equation}

### 2019-06-05 ms.tex
fixing up notation and equations for Fourier crosshatch model.

@@
 Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three angles are similar (with 0.1$\degree$) to one projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom).
+These three relative angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to one projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
 }\label{fig:crossHatchA5}
@@
 
-The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the
+The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (resolving crystal structures) and smallest for the long wavelengths.
+We also fit the crosshatch pattern.
 
@@
 \begin{itemize}
-	\item Fit the existing flat field to an crosshatch model in the Fourier domain
+	\item Fit the existing flat field to a crosshatch model in the Fourier domain
 	\item Extrapolate the crosshatch model to high frequencies to estimate the sub-pixel structure
@@
 
-We 
 We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
@@
 \end{equation}
-where $k_x'$ and $k_y'$ are rotated frequency coordinates coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
-For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
+where $k_x'$ and $k_y'$ are rotated frequency coordinates in the parallel and perpendicular directions, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorentzian full width at half maximum of the perpendicular dependence.
+For each of the three angles, there is a set of rotated coordinates centered at $(k_{x,0},k_{y,0})$= (0,0) following:
 \begin{equation}
@@
 This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
-We only fit the region of the power spectral density above r=100 to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
+We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
 For the F300M filter and ALONG detector, we find 

### 2019-06-06 ms.tex
updating model fitting results section.

@@
 
-\subsubsection{Subpixel Crosshatching Simulation}
-
-The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
-NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
-
-We simulate the effect of this jitter on NIRCam time series observations with the following steps:
-\begin{itemize}
-	\item Fit the existing flat field to a crosshatch model in the Fourier domain
-	\item Extrapolate the crosshatch model to high frequencies to estimate the sub-pixel structure
-	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Multiply the PSF by the simulated flat field
-	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
-	\item Bin the simulated images into the native pixel size
-	\item Divide by the flat field
-	\item Measure the relative flux with a photometric aperture
-\end{itemize}
-
+\subsubsection{Crosshatch Modeling}
 We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
+We divide the 2D Fourier power spectral density by the number of pixels in an input image.
+This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
+
 We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
 \begin{equation}
-f(k_{x,i}',k_{y,i}', a_i, b,c) = a \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
+f(k_{x,i}',k_{y,i}', a_i, b,c) = a_i \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
 \end{equation}
@@
 For the F300M filter and ALONG detector, we find 
-for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 6.9 \pm 0.2 \times 10^6, a_2 = 4.0 \pm 0.1 \times 10^6, a_3 = 4.4 \pm 0.1 \times 10^6, b=666 \pm 1 $ px and $c=4.9933 \pm 0.0004$ px.
+for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 3.93 \pm 0.01 \times 10^{-7}, a_2 = 2.305 \pm 0.007 \times 10^{-7}, a_3 = 2.540 \pm 0.007 \times 10^{-7}, b=0.3243 \pm 0.0007 $ px$^{-1}$ and $c=2.44 \pm 0.03 \times 10^{-2}$ px$^{-1}$.
 The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
 
-We take this model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+\subsubsection{Subpixel Crosshatching Simulation}
+
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
+NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
+
+We simulate the effect of this jitter on NIRCam time series observations with the following steps:
+\begin{itemize}
+	\item Fit the existing flat field to a crosshatch model in the Fourier domain
+	\item Extrapolate the crosshatch model to high frequencies to estimate the sub-pixel structure
+	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Multiply the PSF by the simulated flat field
+	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
+	\item Bin the simulated images into the native pixel size
+	\item Divide by the flat field
+	\item Measure the relative flux with a photometric aperture
+\end{itemize}
+
+We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
 We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.

### 2019-06-10 ms.tex
added crosshatch amplitude fit results to plots
updated subgism position plots with best fit to active pixels onlyt.

@@
 This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
+\textcolor{red}{Can we justify this more?}
 
 We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
-\begin{equation}
+\begin{equation}\label{eq:analyticPSDradial}
 f(k_{x,i}',k_{y,i}', a_i, b,c) = a_i \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
@@
 We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
+$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
 We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
@@
 \begin{itemize}
-	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
+	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (4,5)
 	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
@@
 
+The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top fo the array because these illuminated rows are anomalous.
+
 \begin{figure}[!hbtp]
@@
 \includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_grism64flat.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64.pdf}\\
 \vspace{0.2in}
@@
 \includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_grism64_psd.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64_psd.pdf}\\
 \caption{
 The top of the array has the smallest level of crosshatching and the middle has the largest.
-This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array, the full frame position near Y=512 and the nominal SUBGRISM64 at the bottom of the array.
+This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array (first plot from top), the full frame position near Y=512 (second plot from top) and the nominal SUBGRISM64 at the bottom of the array (third plot from top).
+The bottom left corner for each subarray is listed in parentheses in the title of the flat field plot and the best-fit amplitudes are listed in the title of the power spectral density plot.
  }\label{fig:subpixScanSimulation}

### 2019-06-14 ms.tex
did sanity checks on sims and saved simulation max Diff Flux results.

@@
 
-\subsubsection{Subpixel Crosshatching Simulation}
+\subsubsection{Subpixel Crosshatching Simulation}\label{sec:CrosshatchSim}
 
@@
 The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
-We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top fo the array because these illuminated rows are anomalous.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are anomalous.
+The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
+We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
 

### 2019-06-15 ms.tex
updated notes and apertures for OTIS illum grism time series test

@@
 However, there is no feasible way to place a point source lamp at infinity to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
-During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain.
-
+During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain to the detectors.
+
+\subsubsection{Pass and a Half Grism Time Series Test}
 The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
@@
 This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
+The telescope is suspended vertically and can potentially swing under these vibrations.
 
@@
 \end{figure*}
+
+\subsubsection{Half Pass Subarray Size Tests}
 

### 2019-06-16 ms.tex
a few notes on the OTIS dark tests

@@
 \tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
+The ppm units are assuming a 60\% well depth or 3.9$\times 10^7$ DN during an integration.
 The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
@@
 \includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
-\caption{Principal component eigenvectors identified from group 54 (left) and group 55 (right).
+\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
 }\label{fig:pcaEigenvectors}
@@
 \begin{itemize}
-	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the photon noise)
+	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
 	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
@@
 Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
+We perform photometry on a single knot of emission as highlighted as the blue circular aperture.
+For the grism time series, we use a rectangular aperture and a vertically offset background box.
 }\label{fig:otisPSFs}

### 2019-06-18 ms.tex
repeating smoothing experiment without going through source aperture.

@@
 
+The dramatic difference from the smoothing kernel is beyond what is possible for a real source.
+This is because the 40 pixel wide kernel was applied all the way through the source aperture, which would subtract and distort any signal from a star/planet source.
+In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
+We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
+\textcolor{red}{\bf Continue Here!}
+
 \subsubsection{Reference Channel Subtraction}
@@
 
-\subsection{Cryogenic Vacuum (CV) Stability Tests}
+\subsection{Goddard Cryogenic Vacuum (CV) Stability Tests}
 

### 2019-06-18 ms.tex
adding in result from interpolated smoothing kernel method

@@
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from "Raw" data using no reference pixel correction, "Reduced Data" using reference pixels and "ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
+{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, ``Reduced Data" using reference pixels and ``ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
 {\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
@@
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
-Measured Read Noise (smoothed 40 px kernel) & 900 & 23 \\
+Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
+Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
 \enddata
@@
 In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
+Note that this experiment with result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
 We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
+We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
+\texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
+This efficiently interpolates over bad pixels and can also interpolate over the source aperture.
+Our smoothing kernel is a flat boxcar normalized to 1.0.
+This more realistic kernel results in higher noise because of its larger window size and because it interpolates over the aperture points.
+The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
+This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit.
+
 \textcolor{red}{\bf Continue Here!}
@@
 We begin by calculating new principal components and eigenvectors for each group up the ramp and then subtracting the first 10 principal component eigenvectors multiplied by their respective principal components by each image.
+Principal component analysis detects variations from the mean and so the data is first subtracted by the mean and then the mean is added after PCA is complete.
 It is important to mask the bad pixels before calculating the principal components so they are not driven by errant bad pixels.
+We set the value of all bad pixels to 0 so they do not add any variance.
 We also calculate the PCA eigenvectors after the bias has been subtracted and the reference pixel correction was applied.

### 2019-06-20 ms.tex
adding results when using PCA on each amplifier separately

@@
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
+Measured Read Noise (5 Component PCA on each amplifier) & 3,300 & 140 \\
 Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
@@
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
-Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by unilluminated channels.
+Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
 We attempt to subtract an amplifier 0's time series from all amplifiers.
@@
 Adding 10 more principal components for a total of 20 eigenvectors only reduces the time series noise to 5,100 to 5,400 for the 3 apertures.
+
+If we treat each amplifier separately, the PCA model is more effective in reducing 1/f noise.
+We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
+The resulting standard deviation of the time series is 2900 to 3870 DN.
 

### 2019-06-22 ms.tex
beginning to test RPI vs RPF w/ refpx

@@
 
+We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
+We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
+\begin{figure*}
+{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
+{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
+\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-06-25 ms.tex
pca eigenvector plots for individual amplifiers

@@
 
-\subsubsection{Smoothed Kernel Subtraction}
+\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
 
@@
 These first 10 principal components explain 10\% of the total variance in each group up the ramp.
+The principal components from one group to another are very similar.
+\textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
 
@@
 \caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
+}\label{fig:pcaEigenvectors}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55.pdf}
+\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
+Again, the eigenvectors are very similar other than vertical flips.
 }\label{fig:pcaEigenvectors}
@@
 The resulting standard deviation of the time series is 2900 to 3870 DN.
+This is improvement is beyond what is possible on a real source because the principal components include pixels over the source aperture.
+To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
 

### 2019-06-28 ms.tex
added results when doing individual amplifier subtraction.

@@
 Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
+Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 \\
 Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
@@
 \tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
-The ppm units are assuming a 60\% well depth or 3.9$\times 10^7$ DN during an integration.
+The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF.
 The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
@@
 The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
+
+\subsubsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
+A slight modification to the above strategy is to average each amplifier individually.
+This takes care of any differences between amplifiers.
+This individual amplifier dramatically decreases the errors.
+The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm.
+Therefore, this simple approach can dramatically decrease the 1/f noise to below the photon limit.
+This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).
 
@@
 \textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
+Indeed, an extra bias subtraction somewhat changes the character and repeatability of the first few principal components shown in Figure \ref{fig:pcaEigenvectorsExtraBias}.
 
@@
 }\label{fig:pcaEigenvectors}
+\end{figure*}
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54_extra_bias_sub.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55_extra_bias_sub.pdf}
+\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
+With a better bias subtraction, the eigenvectors are very similar other than vertical flips.
+}\label{fig:pcaEigenvectorsExtraBias}
 \end{figure*}

### 2019-07-02 ms.tex
fixed the error in the plot shows LW phot after moving the centroid using the SW
added a few plots and note on persistence from AZ lab 01

@@
 
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
+\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
+The aperture shifting appears to increase the flux errors with centroid shifts.
+}\label{fig:otisLWSWtserShift}
+\end{figure*}
+
 \subsubsection{Half Pass Subarray Size Tests}
@@
 
+\clearpage
 \subsection{Asic Dewar Tests}
 
+\subsubsection{Persistence}
+HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.
+Lamp sources in our laboratory tests typically have a warm up period lasting several tens of minutes, which makes it difficult to observe this same effect the detector ramps.
+However, the charge trap release time is expected to the same when illuminated as compared to when turning the lamp off.
+We therefore show a time series of an LED after it is turned off in Figure \ref{fig:persistence}.
+In this experiment, the detectors are illuminated for 3 hours with fluence levels of about 300 DN/s for 53 seconds.
+Thus, they are safely under saturation.
+The charge trapping release becomes undetectable after 10 minutes and is well below 0.1 DN/s.
+
+\begin{figure*}
+{\gridline{\fig{ap_labels_B4persistence_AZLabStab01refcor.pdf}{0.5\textwidth}{Box Apertures}}}
+{\gridline{\fig{phot_B4persistence_AZLabStab01refcor_tser.pdf}{0.5\textwidth}{Persistence Time Series}}}
+\caption{Persistence decays rapidly, indicating .}\label{fig:persistence}
+\end{figure*}
+
+\subsubsection{Pre-Ampflier Reset Test}
 We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.

### 2019-07-03 ms.tex
updated the pixel-wise time series with extra bias subtraction.

@@
 \includegraphics[width=.32\columnwidth]{all_amp_periodograms.pdf}
-\caption{The time series for all 4 amplifiers share common-mode behaviors in some cases (left) but not always (middle).
+\caption{The time series for all 4 amplifiers share common-mode behaviors for some intervals but not always (left and middle plots).
 This is visible in a short segment of the time series of all pixels for an example group up the ramp 53 in a dark ramp where the bias has already been subtracted.
-The left panel shows the beginning of the time series, which happens to be dominated by common-mode read noise.
-The middle panel shows another part of the time series where Amplifier 3 has its own individual correlated-noise pattern.
+The pixels tim series smoothed with a 51 pixel-wide median filter to better se the low frequency noise.
+The left panel shows the a time near the beginning of a frame, where amplifiers 1 ad 2 share some common-mode read noise.
+The middle panel shows another part of the time series where Amplifiers 1 and 2 have more disparate noise signatures.
 The right panel shows the periodogram of each amplifier's time series over the first 10$^5$ clock cycles (0.1) seconds, which exhibits no consistent peaks.

### 2019-07-04 ms.tex
explaining the difference in results with apertures on the subarray configu time series.

@@
 \includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
-\caption{With rect backub.
-\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}}\label{fig:OTISRectBacksub}
+\caption{Subarray configuration test during OTIS. The position of the background subtraction box has a dramatic effect on the precision of the time series.
+This is due to correlated 1/f noise along the horizontal fast-read direction.
+If the background subtraction box is on an adjacent amplifier, it captures a very different 1/f noise behavior than if it is on a shared amplifier.
+The amplifier boundary is shown as a vertical blue dashed line.
+\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}
+\textcolor{blue}{Now I understand it as coming from which amplifier the background box is on.}}\label{fig:OTISRectBacksub}
 \end{figure}

### 2019-07-05 ms.tex
more on persistence

@@
 We therefore show a time series of an LED after it is turned off in Figure \ref{fig:persistence}.
-In this experiment, the detectors are illuminated for 3 hours with fluence levels of about 300 DN/s for 53 seconds.
-Thus, they are safely under saturation.
-The charge trapping release becomes undetectable after 10 minutes and is well below 0.1 DN/s.
+In this experiment, the long wavelength detector is illuminated for 3 hours with fluence levels of about 300 DN/s.
+At this fluence level and integration times of 9.4 seconds, each pixel reaches about 3000 DN in an integration.
+Thus, the pixels are safely under saturation but have had plenty of time for the traps to reach equilibrium.
+
+The characteristic timescale for persistence is 12 seconds, as shown in Figure \ref{fig:persistence}.
+Thus, charge trapping release becomes undetectable after 5 minutes and is well below 0.1 DN/s per pixel.
+This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is $e^{5.4}=220$ and the slow-release timescale is $e^{10.1}=24,000$ \citep{zhou2017chargeTrap}.
 
@@
 {\gridline{\fig{phot_B4persistence_AZLabStab01refcor_tser.pdf}{0.5\textwidth}{Persistence Time Series}}}
-\caption{Persistence decays rapidly, indicating .}\label{fig:persistence}
+\caption{The detector persistence timescale decays rapidly after the LED is turned off (vertical red line in bottom figure).
+The source and background apertures are shown in the top image while the time series of counts per pixel are shown in the bottom figure.
+The characteristic timescale for charge trapping is 12 seconds.}\label{fig:persistence}
 \end{figure*}

### 2019-07-06 ms.tex
started cleaning out the PCA section where much of the first principal component variance was bias.

@@
 Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
-Here, we assume that each column is a random variable that is correlated with the rest of the columns.
+Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
 Each row represents a different noise iteration.
-We first mask all bad pixels by setting all pixels with $| f | > 200$ DN.
+First, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
+This removes all bias levels and focuses on the time variability of the pixels.
+Here, we assume the dark current is negligible.
+Next, we mask all bad pixels by setting all pixels with $| f | > 200$ DN to 0 DN to remove bad pixels that can drive the principal components.
 The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
-These first 10 principal components explain 10\% of the total variance in each group up the ramp.
-The principal components from one group to another are very similar.
+
+The first 10 principal components explain 14\% of the total variance in each group up the ramp.
+The principal components from one group to another are different, but the ordering of these components generally follows a pattern of increasing frequency with higher order principal components.
+This is expected for 1/f noise where the lowest frequencies have most of the power.
 \textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
@@
 \centering
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp54.pdf}
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_grp55.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
 \caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
-}\label{fig:pcaEigenvectors}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54.pdf}
-\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55.pdf}
-\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
-Again, the eigenvectors are very similar other than vertical flips.
 }\label{fig:pcaEigenvectors}
@@
 Thus, charge trapping release becomes undetectable after 5 minutes and is well below 0.1 DN/s per pixel.
-This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is $e^{5.4}=220$ and the slow-release timescale is $e^{10.1}=24,000$ \citep{zhou2017chargeTrap}.
+This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is 280 seconds and the slow-release timescale is 16,300 \citep{zhou2017chargeTrap}.
 

### 2019-07-06 ms.tex
more cleaning up of PCA section.

@@
 This is expected for 1/f noise where the lowest frequencies have most of the power.
-\textcolor{red}{\bf Is this just because they contain information from residuals after bias subtraction? Maybe we need a better bias subtraction?}
-Indeed, an extra bias subtraction somewhat changes the character and repeatability of the first few principal components shown in Figure \ref{fig:pcaEigenvectorsExtraBias}.
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
-\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
-}\label{fig:pcaEigenvectors}
-\end{figure*}
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54_extra_bias_sub.pdf}
-\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55_extra_bias_sub.pdf}
-\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
-With a better bias subtraction, the eigenvectors are very similar other than vertical flips.
-}\label{fig:pcaEigenvectorsExtraBias}
-\end{figure*}
-
-We begin by calculating new principal components and eigenvectors for each group up the ramp and then subtracting the first 10 principal component eigenvectors multiplied by their respective principal components by each image.
-Principal component analysis detects variations from the mean and so the data is first subtracted by the mean and then the mean is added after PCA is complete.
-It is important to mask the bad pixels before calculating the principal components so they are not driven by errant bad pixels.
-We set the value of all bad pixels to 0 so they do not add any variance.
-We also calculate the PCA eigenvectors after the bias has been subtracted and the reference pixel correction was applied.
+Since the first principal components are different from one group to another, we calculated the principal components for each group independently.
+We then create a noise model image which is the matrix multiplication of the eigenvectors by the principal components for 10 components.
+This model is subtracted from each group to create a 1/f-corrected image.
+
 The PCA subtraction is applied to each group up the ramp and then these groups are subtracted in pairs to create a time series.
@@
 Adding 10 more principal components for a total of 20 eigenvectors only reduces the time series noise to 5,100 to 5,400 for the 3 apertures.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
+\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
+The pre-amplifier reset values are seen in the first principal component, and change from one group (one read in RAPID) to another.
+The principal components generally increase 
+}\label{fig:pcaEigenvectors}
+\end{figure*}
+
+In another approach, we treat each amplifier separately so that the principal components are calculated independently.
+This approach means that a noise signature in 3 amplifiers but not the fourth does not propagate to fourth amplifier when subtracting the PCA-based model.
+This individual-amplifier essentially has four times the number of degrees of freedom, so we fit with only the first 5 principal components in each amplifier.
+The resulting eigenvectors are shown in Figure \ref{fig:pcaEigenvectorsIndAmp}.
 
@@
 To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_54_extra_bias_sub.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_ind_amp_grp_55_extra_bias_sub.pdf}
+\caption{The first 5 principal component eigenvectors identified from group 54 (left) and group 55 (right) where each amplifier has been analyzed independently.
+The amplifier boundaries are demarcated by solid vertical lines.
+}\label{fig:pcaEigenvectorsIndAmp}
+\end{figure*}
 

### 2019-07-06 ms.tex
updated RMS values for PCA after extra bias subtraction.

@@
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
-Measured Read Noise (5 Component PCA on each amplifier) & 3,300 & 140 \\
 Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
+Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 \\
 Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 \\
@@
 The PCA subtraction is applied to each group up the ramp and then these groups are subtracted in pairs to create a time series.
-The final time series has and measured standard deviation of 5,000 to 5,700 DN within the background-subtracted aperture.
+We use 20 principal components as a starting point for this method.
+The final time series has and measured standard deviation of 5,300 to 5,500 DN within the background-subtracted aperture.
 This is comparable to the row and column subtraction standard deviation of 5,500 to 6,500 DN.
@@
 We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
-The resulting standard deviation of the time series is 2900 to 3870 DN.
+The resulting standard deviation of the time series is 2500 to 3820 DN.
 This is improvement is beyond what is possible on a real source because the principal components include pixels over the source aperture.

### 2019-07-09 ms.tex
a few notes about the crosshatching across the NIRCam SCAs

@@
 The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
-The electron-hole pairs migrate across the depletion region towards the undepleted zones due to an electric field.
-The voltage can be measured non-destructively as the well fills and then reset before saturating.}\label{fig:npSchematic}
+The electron-hole pairs migrate across the depletion region towards the undepleted zones due to an electric field in the depletion zone.
+The voltage can be measured non-destructively (for many reads) as the well fills and then reset before saturating.}\label{fig:npSchematic}
 \end{figure}
@@
 
+NIRCam's 10 SCA's have very similar crosshatch angles with separations of 44.5 $\degree$ and 67.7 to 67.8 $\degree$.
+They tend to have one primary crosshatch axis oriented either along the X pixels or the Y pixels, with two flanking axes at $\sim 67.7 \degree$ to either side.
+The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
+
 \subsubsection{Subpixel Crosshatching Simulation}\label{sec:CrosshatchSim}

### 2019-07-13 ms.tex
note about B4 crosshatch
updated A5 crosshatch results with PSD 'background'

@@
 We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
+
+We also consider a model with a ``background'' so that 
+\begin{equation}
+f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e\right)},
+\end{equation}
+where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e$ is the radial background exponential constant.
+
 For the F300M filter and ALONG detector, we find 
-for $\theta_1 = 0.9013 \pm 0.0004 \degree, \theta_2 = 68.6041 \pm 0.0007 \degree, \theta_3 = 113.0741 \pm 0.0007, a_1 = 3.93 \pm 0.01 \times 10^{-7}, a_2 = 2.305 \pm 0.007 \times 10^{-7}, a_3 = 2.540 \pm 0.007 \times 10^{-7}, b=0.3243 \pm 0.0007 $ px$^{-1}$ and $c=2.44 \pm 0.03 \times 10^{-2}$ px$^{-1}$.
+for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e=0.26 \pm 0.01$ px$^{-1}$.
 The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
@@
 The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
+The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
 

### 2019-07-14 ms.tex
added a crosshatch models gallery

@@
 The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
+Figure \ref{fig:crosshatchModelGallery} shows the best-fit crosshatch 2D power spectra.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
+\caption{
+Best-fit power spectra of all the NIRCam detectors.
+The long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
+The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
+}\label{fig:crosshatchModelGallery}
+\end{figure}
 

### 2019-07-14 ms.tex
added a crosshatch models gallery

@@
 \caption{
-Best-fit power spectra of all the NIRCam detectors.
-The long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
+Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
 The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.

### 2019-07-16 ms.tex
stripe vs window from AZlab

@@
 Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
+The primary crosshatch tends to be aligned closely, but no exactly, with either the X or Y axis.
 The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
@@
 
+\subsubsection{Stripe versus Window Mode}
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
+\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
+\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistence}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-07-17 ms.tex
added plots of short timescale and long timscale persistence

@@
 \fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
-\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistence}
+\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
+\end{figure*}
+
+\subsubsection{Persistence with Long and Short Illumination}
+\begin{figure*}
+{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence}
+\fig{persistence_long_lin.pdf}{0.49\textwidth}{Long Timescale Persistence}}}
+\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistenceAZlab04}
 \end{figure*}

### 2019-07-17 ms.tex
updated sections on Asic dewar

@@
 
+\author{Karl Misselt}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
 \author{Jarron Leisenring}
@@
 
-\author{Karl Misselt}
+\author{Kenneth Don}
 \affiliation{Steward Observatory \\
@@
 \subsection{Asic Dewar Tests}
+We performed a variety of stability tests using a dewar with the same type of detectors, readout electronics and temperature control as the in-flight parts.
+The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
+The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (\textbf{Which type and wavelength?}) LEDs.
+The LEDS are type Lms17 and ???? from Electro Optical Components, Inc.
+
+The dewar has limited space for optical illumination so the LEDS light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
+The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
+The illuminated portions of the detector are used for aperture extractions while the shadows are used for background subtraction apertures.
+
+No LEDs used in ground-based tests were as stable as the desired precisions relevant to exoplanet targets (sub 30 ppm), so multiple arrays are used to correct for lamp variations during illuminated stability tests.
+The best absolute stability of an LED measured on a detector was 0.05\% ppm over 2 hours.
+More typically, the variations were 1\%, although the current measured with a multimeter was stable to 0.1\%.
+A ratio time series is constructed by dividing the time series derived from one detector to another time series from a different detector.
 
@@
 We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
+
+Each pre-amplifier is reset once per frame by the current flight parameters.
+This causes amplifier offsets because each amplifier is reset to a different value with some noise, as visible in Figure \ref{fig:RPFrefpix}.
+The pre-amplifier resets, however, can be largely corrected for by reference pixels or background subtraction.
+Figure \ref{fig:RPFrefpix} also shows a corrected image where the top reference pixels (a 512 pixel wide 4 pixel tall region per amplifier) is used to subtract the amplifier offsets.
+
 \begin{figure*}
@@
 \subsubsection{Stripe versus Window Mode}
+JWST users may select between two types of subarrays within NIRCam grism time series.
+This is specified with the Astronomy Proposal Tools (APT) software in the ``NIRCam Grism Time Series'' template with "No. of Output Channels".
+When the output channels are set to 4 (stripe mode), the frame time is approximately four times faster than 1 output channel (window mode).
+The exact timing is slightly different than a factor of 4 due to overheads.
+The advantage of stripe mode is that it allows more samples up the ramp in an integration and also shorter minimum integration times to enable observations of brighter sources.
+The stripe mode uses four different amplifiers, which could potentially lead to differences between the 4 regions each 512 pixels wide.
+The stripe mode is the same as standard full frame imaging when the height of the stripe is 2048 pixels tall.
+
+Figure \ref{fig:stripeVsWindowAZlab04} shows the time series for a stripe versus window mode test.
+In each case, these are the ratios of time series between two Long wavelength detectors derived from aperture photometry with background subtraction.
+
 \begin{figure*}

### 2019-07-18 ms.tex
added results from the subarray size comparison

@@
 \begin{itemize}
-	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (4,5)
+	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
 	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
@@
 Figure \ref{fig:stripeVsWindowAZlab04} shows the time series for a stripe versus window mode test.
+In both cases the subarray is SUBGRISM256, which is 2048 pixels wide and 256 pixels tall.
+The subarray is placed at the top of the detector where 4 rows of reference pixels are accessible.
 In each case, these are the ratios of time series between two Long wavelength detectors derived from aperture photometry with background subtraction.
@@
 
+\subsubsection{Subarray Size Comparisons}
+NIRCam grism time series users can choose between full frame, SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarray sizes, which are 2048, 256, 128 and 64 pixels tall and 2048 pixels wide.
+The taller subarrays have the advantage of more background pixels (or a reference star) to use in analysis.
+The taller subarrays also are needed to fit the short wavelength WEAK LENS +8 PSF observed simultaneously with the long wavelength grism.
+Otherwise, the WEAK LENS +4 PSF must be observed or a fraction of the WEAK LENS +8 PSF used.
+The shorter subarrays have the advantage of faster frame times, permitting observations of brighter stars or more samples up the ramp than taller subarrays.
+We used the same lamp LED current for the SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarrays and tuned the integration times to be similar by setting the number of RAPID groups as 8, 16 and 32 for the three subarrays respectively.
+The resulting integration times are 10.8995, 10.8155 and 10.7735 seconds respectively.
+No clear trend is seen in the time series shown in Figure \ref{fig:subarraySizes}.
+In this example, the background aperture was always parallel to the source aperture to best remove 1/f noise.
+\textbf{\textcolor{red}{Show what happens if the background aperture and source apertures are on different amplifiers and/or if they are vertical with respect to the source aperture}}
+
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
+\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
+\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
+\caption{The subarray size tests show very similar precision levels with a horizontal aperture.}\label{fig:subarraySizes}
+\end{figure*}
+
 \subsubsection{Persistence with Long and Short Illumination}
+We estimate the persistence level by illuminating the detectors to $\sim$80\% well depth for either 30 seconds or 30 minutes and observe the slopes after the LED is turned off.
+We find a that the slopes rapidly the noise levels ($<$ 10 e$^-$/s) in less than 10 seconds, as shown in Figure \ref{fig:persistenceAZlab04}.
+This is similar to the measurements in \citet{leisenring2016persistence}, who find that the persistence rate after saturating the detectors and turning off the lamp is 0.5 DN/sec to 15 DN/sec or 0.28$e^-$ to 6.8$e^-$ at the 30 second mark, depending on the detector.
+The flight NIRCam long wavelength detectors in \citet{leisenring2016persistence} have smaller persistence signals than the short wavelength detectors.
+The asic dewar persistence test in Figure \ref{fig:persistenceAZlab04} is for a long wavelength detector.
+
 \begin{figure*}

### 2019-07-20 ms.tex
plotting results of subarray size test with no background aperture. Trying to understand the confusing results.

@@
 \fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
-\caption{The subarray size tests show very similar precision levels with a horizontal aperture.}\label{fig:subarraySizes}
+{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
+\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
+\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
+\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
+If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable.
+\textbf{\textcolor{red}{How does this make sense?
+Did I possibly change how the side reference pix correction was done between the 3 tests?}}}\label{fig:subarraySizes}
 \end{figure*}

### 2019-07-21 ms.tex
tracking down one theory I have about the confusing results in subarray_size versus stability tests

@@
 \textbf{\textcolor{red}{How does this make sense?
-Did I possibly change how the side reference pix correction was done between the 3 tests?}}}\label{fig:subarraySizes}
+Did I possibly change how the side reference pix correction was done between the 3 tests?
+Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019.
+Processed the files on Jul 10 18:06.
+Could this be important?
+I will try and experiment on darks as well as re-processing the original baseline data to see.} }}\label{fig:subarraySizes}
 \end{figure*}

### 2019-07-23 ms.tex
investigated the subarray size confusion some more, ruling out the 1/f smoothing method. More likely reference pixels.

@@
 Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019.
-Processed the files on Jul 10 18:06.
-Could this be important?
-I will try and experiment on darks as well as re-processing the original baseline data to see.} }}\label{fig:subarraySizes}
+Processed the files on Jul 10 18:06. Indeed, they were processed slightly differently, but the smoothing method matters very little.
+Karl very astutely points out that the 2048x256 has reference pixels on the top but the 2048x128 and 2048x64 do NOT have reference pixels at the top, so pre-amp reset issues are very likely.} }}\label{fig:subarraySizes}
 \end{figure*}

### 2019-07-24 ms.tex
added some RPI vs RPF time series

@@
 \begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
+{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode Time Series}
 \fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
@@
 
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
+\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
+{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
+\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
+\caption{Reset per integration versus reset per frame.}\label{fig:subarraySizes}
+\end{figure*}
+
 \subsubsection{Persistence with Long and Short Illumination}

### 2019-07-25 ms.tex
time series test for multiple apertures on the same array

@@
 
+\begin{figure*}
+{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n487Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{}}}
+{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{Apertures}}}
+{\gridline{\fig{individual_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.49\textwidth}{Time Series of Apertures}}}
+\caption{Time series for 2 apertures on each detector.}\label{fig:twoApPerDetector}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-07-27 ms.tex
plot the reference pixels during the 1.5 mA repeat 2
filled in LW LED info

@@
 The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
-The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (\textbf{Which type and wavelength?}) LEDs.
-The LEDS are type Lms17 and ???? from Electro Optical Components, Inc.
-
-The dewar has limited space for optical illumination so the LEDS light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
+The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (3.0 to 3.6~$\mu$m) LEDs.
+The LEDS are type LMS17LED-R and LMS34LED-R from Electro Optical Components, Inc.
+
+The dewar has limited space for optical illumination so the LEDs' light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
 The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
@@
 
+\begin{figure*}
+{\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}
+\caption{Reference pixels cannot easily explain the trends between detectors.}\label{fig:refpixTSeries}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,
@@
 
+\clearpage
 \section{Expected In-Flight Performance with JWST}

### 2019-07-28 ms.tex
plots for many apertures

@@
 \begin{figure*}
+{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn487Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{}}}
+{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn489Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{Apertures}}}
+{\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
+\caption{Time series for many apertures on each detector, binned into 70 equal bins.}\label{fig:manyApPerDetector}
+\end{figure*}
+
+\begin{figure*}
 {\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}

### 2019-07-30 ms.tex
a little more text on RPF vs RPI

@@
 \begin{figure*}
-{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
-{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
+{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.8\textwidth}{No Reference Pixels RPF}}}
+{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.8\textwidth}{Reference Pixel RPF}}}
 \caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
+\end{figure*}
+
+As a further demonstration that reference pixels can subtract amplifier offsets or background subtraction, we show time series for tests with a reset per frame and a reset per integration in Figure \ref{fig:RPFvsRPItseries}.
+The resets-per-frame have similar noise to the resets-per-integration on short timescales.
+For the 2048x256 subarray, the standard deviation were 197 ppm and 183 ppm for RPF and RPI respectively.
+For the 2048x64 subarray, the standard deviations were 327 ppm and 180 ppm for RPF and RPI respectively.
+The difference between these is dominated by the slope through the test.
+We suspect the flatter slow during RPI is a coincidence because the the resets within an integration (less than one minute) are unlikely to propagate a gradual slope over several hours.
+
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
+\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
+{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
+\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
+\caption{Reset per integration versus reset per frame.}\label{fig:RPFvsRPItseries}
 \end{figure*}
@@
 
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
-\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
-{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
-\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
-\caption{Reset per integration versus reset per frame.}\label{fig:subarraySizes}
-\end{figure*}
-
 \subsubsection{Persistence with Long and Short Illumination}

### 2019-07-31 ms.tex
added examples of time series with no backsub nor refpix to show a more dramatic change between RPI and RPF

@@
 \begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf256_no_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
+\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi256_no_bsub_no_refpx_both_NRCRPIBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
+{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf064_no_bsub_no_refpx_both_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
+\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi064_no_bsub_no_refpx_both_NRCRPI64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
+\caption{Reset per integration versus reset per frame where no reference pixel correction and no background subtraction have been applied.}\label{fig:RPFvsRPItseries}
+\end{figure*}
+
+\begin{figure*}
 {\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
@@
 \fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
-\caption{Reset per integration versus reset per frame.}\label{fig:RPFvsRPItseries}
+\caption{Reset per integration versus reset per frame where both reference pixel correction and background subtraction have been applied.}\label{fig:RPFvsRPItseries}
 \end{figure*}

### 2019-08-01 ms.tex
Allan variance for within-detector ratios

@@
 
+\begin{figure*}
+{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance}
+\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance}}}
+{\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}
+\caption{Time series for the ratio of two apertures within a detector.}\label{fig:allanVarianceWithinDetector}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-08-02 ms.tex
added reference to the cyrstallographic justification of the crosshatch pattern

@@
 	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
-	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the detectors.
+	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
 For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
@@
 The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
+The surface morphology of HgCdTe shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes \citep{chang2008surfaceMorphologyHgCdTe}.
 HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
 One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
-In this perspective, the projected bond angles form angles fo 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
+In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
 We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
@@
           \texttt{pynrc} \url{https://github.com/JarronL/pynrc},
-          \texttt{emcee} \citep{foreman-mackey2013emcee}
+          \texttt{emcee} \citep{foreman-mackey2013emcee},
+          Google Sketchup
            }

### 2019-08-02 ms.tex
a few short notes about the topological defects and how they may relate to flat fields

@@
 
-The angles of the crosshatch patterns are likely set by the crystal pattern of HgCdTe.
-The surface morphology of HgCdTe shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes \citep{chang2008surfaceMorphologyHgCdTe}.
+The angles of the crosshatch patterns are likely determined by the crystal pattern of HgCdTe.
 HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
@@
 In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
-We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
+
+HgCdTe detectors are manufactured using Molecular Beam Epitaxy upon a substrate, a process which results in topological defects with peak to valley amplitudes of 5-20 nm in height variations.
+The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes \citep{chang2008surfaceMorphologyHgCdTe}.
+The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$, very close to the observed crosshatch angles.
+These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which are caused by quantum efficiency variations.
+We deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
 

### 2019-08-03 ms.tex
a few more notes on the crosshatch topological defects

--- 2019-08-02 ms.tex
@@
 In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
-We therefore deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
+
+HgCdTe detectors are manufactured using molecular beam epitaxy upon a substrate, a process which results in topological defects with peak to valley amplitudes of 5-20 nm in height variations.
+The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes.
+The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
+These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which are quantum efficiency variations.
+We deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
 
@@
 This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
-The width of the structures can be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
+Atomic force microscopy shows topological features that are approximately 1.2~$\mu$m in width \citep{chang2008surfaceMorphologyHgCdTe}.
+The width of the structures can also be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
 We estimate that the crosshatch pattern oriented at 90.9$\degree$ crosses 1 horizontal pixel for every 64 vertical pixels.
@@
 Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three relative angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to one projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
+These three relative angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$) onto the [211] miller plane.
 }\label{fig:crossHatchA5}

### 2019-08-04 ms.tex
added info about reference pixels versus no reference pixels.

@@
 
+\subsection{Reference Pixels versus No Reference Pixels}
+One question to answer is, can background subtraction subtract off noise just as well as reference pixels?
+We compare time series on source boxes subtracted by a background box on data that has been reference pixel subtracted and data that has not been reference pixel subtracted.
+As before, the background boxes are offset horizontally from the source boxes to best capture 1/f noise.
+For the baseline test, with a 2048x256 subarray, the standard deviation was 197.11 ppm with reference pixel correction.
+Repeating the experiment with no reference pixel correction, the standard deviation was 198.19 ppm.
+This test indicates that horizontally displaced background box is sufficient in removing pre-amp offsets and 1/f noise from the source aperture.
+However, for some cases (like NIRCam grism time series), the background subtraction will be done vertically and so side reference pixels will be desired.
+
+If not top reference pixels are available (such as in the 2048x64 subarray test), and only side reference pixels are available, the benefits are similar.
+For the 2048x64 1.5 mA test with reset-per-frame, the standard deviation was 326.9 ppm with reference pixel correction and 327.2 ppm without reference pixel correction.
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-08-07 ms.tex
added examples where the background aperture was vertically offset

@@
 
+\clearpage
 \subsection{Reference Pixels versus No Reference Pixels}
@@
 
-If not top reference pixels are available (such as in the 2048x64 subarray test), and only side reference pixels are available, the benefits are similar.
+If no top reference pixels are available (such as in the 2048x64 subarray test), and only side reference pixels are available, the benefits are even smaller.
 For the 2048x64 1.5 mA test with reset-per-frame, the standard deviation was 326.9 ppm with reference pixel correction and 327.2 ppm without reference pixel correction.
+
+If the background subtraction apertures have a vertical displacement from the source, then 1/f noise becomes a more significant contributor to the errors.
+This is where side reference pixel subtraction becomes a more valuable correction.
+Figure \ref{fig:RefpixWithVertOffsetBackground} shows the time series with and without reference pixel correction if the background aperture is vertically offset from the source aperture.
+
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_with_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x256}
+\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_no_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x256}}}
+{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_with_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x64}
+\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_no_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x64}}}
+\caption{If a background aperture is vertically displaced from the source aperture, the reference pixels are important in reducing 1/f noise.}\label{fig:RefpixWithVertOffsetBackground}
+\end{figure*}
 

### 2019-08-07 ms.tex
added ap labels to go with the vertically offset background aperture test

@@
 \begin{figure*}
+\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx487_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{}}
+\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx489_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{Apertures for 2048x256 stripe}}
 {\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_with_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x256}

### 2019-08-09 ms.tex
added results of dark vs illuminated e-/px comparison test

@@
 
-\subsubsection{Pre-Ampflier Reset Test}
+\subsubsection{Pre-Amplifier Reset Test}
 We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
@@
 \end{figure*}
+
+We also repeat the long baseline test with a 2048x256 subarray and 8 groups up the ramp but this time with no illumination.
+This allows us to compare the noise in e-/px when illuminated versus the noise in e-/px.
+If these two values are the same, this indicates that electronic noise enters both detectors and limits photometry precision in ppm.
+We find instead that the illuminated data has a much higher standard deviation (9 e$^-$/px, compared to the theoretical 1.8 e$^-$/px averaged over the aperture).
+The dark time series had a standard deviation of 1.9 e$^-$/px compared to the theoretical (uncorrelated) 0.2 e$^-$/px averaged over the aperture.
 

### 2019-08-10 ms.tex
assessing stripe vs window when the apertures are more than 512 px away horizontally

@@
 \fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
-\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
-\end{figure*}
+\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier), but the overall trends are similar.
+}\label{fig:stripeVsWindowAZlab04}
+\end{figure*}
+
+The window mode does have the benefit of only using one amplifier.
+This means that 1/f noise can be subtracted along rows whereas in stripe mode, 1/f noise has to be subtracted an an amplifier by amplifier basis (within 512 wide amplifier regions).
+The trade-off is that there are 4 times fewer frames per second.
+We assess the relative value of the 1/f correction versus different reads by placing the source aperture horizontally more than 512 pixels from the background aperture.
+For stripe mode, this means that the apertures are on different amplifiers.
+For window mode, this means the apertures are on the same amplifier.
 

### 2019-08-10 ms.tex
plotting stripe vs window when the source and background apertures are more than 512 px away.:

@@
 
+\clearpage
+
 \subsubsection{Stripe versus Window Mode}
@@
 
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_larger_backsep_stripe.pdf}{0.49\textwidth}{Stripe Mode Time Series, 379 ppm}
+\fig{azlab_ratio_tser_larger_backsep_window.pdf}{0.49\textwidth}{Window Mode Time series, 339 ppm}}}
+\caption{When the background aperture is displaced by more than 512 pixels from the source aperture, window mode becomes slightly preferable.
+}\label{fig:stripeVsWindowAZlab04LargerBacksep}
+\end{figure*}
+
+\clearpage
 \subsubsection{Subarray Size Comparisons}

### 2019-08-11 ms.tex
added a time series immediately after turning LED on.

@@
 
+We also show a time series immediately after where the lamp was turned on in Figure \ref{fig:indTSeriesAfterLamp}.
+Unlike with HST, there is no clear ramp-up behavior.
+
+\begin{figure*}
+{\gridline{\fig{individual_stripe64_1p5_mA_rpt2.pdf}{0.99\textwidth}{}}}
+\caption{Time series immediately after a lamp is turned on.}\label{fig:indTSeriesAfterLamp}
+\end{figure*}
+
 \clearpage

### 2019-08-16 ms.tex
show the window versus stripe mode dark images.

@@
 
+The locations of the subarrays have ROWCORNER=431.
+This means there are not top or bottom reference pixels.
+If we use a horizontally-displaced background region, the pre-amp offsets will not be properly subtracted.
+We therefore subtract the median from each column and then each row (not including the grism aperture).
+We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
+Figure \ref{fig:otisLWSWtserShift} shows the dramatic effect of subtracting the columns and rows from each aperture.
+
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
+\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
+\caption{The grism time series contains subtraction correlated read noise due to pre-amplifier offsets in the vertical direction and 1/f noise in the horizontal direction.
+Row-by-row-subtraction dramatically decreases the noise due to 1/f noise.
+}\label{fig:otisLWSWtserShift}
+\end{figure*}
+
 \subsubsection{Half Pass Subarray Size Tests}
@@
 Here the number of reads in between these is irrelevant.
-A possible way to explain the superior standard deviation for the smallest 2048$\times$64 subarray is not that more reads increase precision but rather the small subarray has a smaller contribution from spatially correlated noise.
+A possible way to explain the superior standard deviation for the smallest 2048$\times$64 subarray is not that more reads increase precision on the slopes but rather the small subarray has a smaller contribution from spatially correlated noise.
 When larger frames are read out, for example, the 1/f noise becomes increasingly uncorrelated from read to read.\textcolor{red}{Wrote this when very tired. Is this correct and logical?}
@@
 JWST users may select between two types of subarrays within NIRCam grism time series.
-This is specified with the Astronomy Proposal Tools (APT) software in the ``NIRCam Grism Time Series'' template with "No. of Output Channels".
+This is specified with the Astronomy Proposal Tools (APT) software in the ``NIRCam Grism Time Series'' template with ``No. of Output Channels".
 When the output channels are set to 4 (stripe mode), the frame time is approximately four times faster than 1 output channel (window mode).
@@
 For window mode, this means the apertures are on the same amplifier.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=0.7\columnwidth]{darkwindow_img.pdf}
+\includegraphics[width=.7\columnwidth]{darkstripe_img.pdf}
+\caption{The noise characteristics and tradeoffs of stripe (4 amplifier outputs) versus window (1 amplifier output) are visible in this dark integration.
+The stripe mode has 8 groups while the window has 2 groups for the same integration time.
+The increased number of groups allows for averaging dark frames but the individual amplifiers can have their own 1/f noise characteristics that will not be subtracted by reference pixels on the leftmost and rightmost amplifiers.}\label{fig:darkWindowVsDarkStripe}
+\end{figure}
 

### 2019-08-24 ms.tex
added temperature chagne test
added refpix vs background subtraction subsection and plot

@@
 
+\clearpage
 \section{Ground-based Experiments}\label{sec:experiments}
@@
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).
-The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.
+The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
 These two different kinds of detector electronics can be compared against each other to help isolate detector-related systematics from readout electronics-related systematics.
@@
 The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
-The one test with a broadband source was an OTIS stability test at NASA Johnson was a grism spectroscopy mode, whih illuminate the long wavelength detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m for the F322W2 filter, as seen in Figure \ref{fig:ampOffsetsOtisGrismSlope}.
+The one test with a broadband source was an OTIS stability test at NASA Johnson was a grism spectroscopy mode, which illuminated the long wavelength detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m for the F322W2 filter, as seen in Figure \ref{fig:ampOffsetsOtisGrismSlope}.
 The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8), as shown in Figure \ref{fig:WLP8PSF}.
@@
 
+\clearpage
+\subsubsection{Reference pixels versus background subtraction}
+One important question that can affect the placement of subarrays is whether background subtraction effectively achieves the same result as with reference pixel correction.
+This is tested in Figure \ref{fig:BackgVsRefpix}.
+In this case, the background aperture is displaced horizontally from the source aperture and within the same amplifier to best reduce 1/f noise and pre-amplifier offsets.
+
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf256_no_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=False, 4968 ppm}
+\fig{azlab_ratio_tser_rpi_vs_rpf_nobacksub_rpf256_no_backsub_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=True, Bsub=False, 221 ppm}}}
+{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_with_bsub_no_refpix_rpf256_with_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=True, 198 ppm}
+\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Refpix =True, Bsub=True, 197 ppm}}}
+\caption{The time series of the flux ratio between two detectors shows that background subtraction achieves most of the value (within 1 ppm) of reference pixel correction to remove pre-amplifier offsets and 1/f noise.
+Furthermore, the background subtraction can be performed on the slope images rather than on a frame-by-frame basis.
+}\label{fig:BackgVsRefpix}
+\end{figure*}
+
+\clearpage
 \subsubsection{Pre-Amplifier Reset Test}
@@
 \clearpage
+\subsection{FPA temperature change}
+\begin{figure*}
+{\gridline{\fig{individual_azlab05_baseline_tchange.pdf}{0.99\textwidth}{}}}
+\caption{Time series during an adjustment to the FPA set point.}\label{fig:indTSeriesAfterLamp}
+\end{figure*}
+
+\clearpage
 \subsection{Reference Pixels versus No Reference Pixels}

### 2019-08-25 ms.tex
added some more calculations after better 1/f noise corrections.

@@
 \textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also empirically verify this with a slope fit to multiple images.}
-For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
+For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be $1.8 \times10^8$ DN, having a photon uncertainty of 9,100 DN or 51 ppm.
 Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames that fill to 60\% well depth.
-As an example, a $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode with 6 RAPID groups up the ramp sampling and the F210M filter would have a photon noise equal to the (uncorrected) read noise and fill the detector to 54\% well depth.
+As an example, a $K$=8.5 magnitude star observed in full frame WEAK LENS +8 imaging mode with 6 RAPID groups up the ramp sampling and the F210M filter would have a photon noise equal to the (uncorrected) read noise and fill the detector to 54\% well depth.
+
+We have demonstrated that row-by-row and amplifier-by-amplifier median subtraction can substantially reduce the read noise for a correlated double sample subtraction from 23,500 DN to 2,900 DN.
+Therefore, the corrected read noise per integration should be:
+\begin{equation}
+RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}
+\end{equation}
+\textcolor{red}{\bf This is for the ALONG detector.
+Update for the A3 detector}
+For the same $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode, the read noise per integration should be 1,700 DN.
+Fortunately, this is now a small fraction of the photon uncertainty of 9,100 DN and only amounts to an increase in noise over the 51 ppm photon by 9 ppm per integration.
 

### 2019-08-26 ms.tex
more calcs for 1/f noise with grism ap.

@@
 \subsubsection{Grism Aperture}
+The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
+This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
+The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
+However, there are no side reference pixels or background regions available on the middle two amplifiers.
+Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
+Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
+Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
+For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
+Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
+
 \begin{figure*}[!hbtp]

### 2019-08-27 ms.tex
some back of the envelope calcs for read noise in grism ap.

@@
 Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
+Expressed in ppm, the read noise after processing with row-by-row subtraction is 90 ppm as compared to a photon noise of 74 ppm for a CDS subtraction (2 groups in ramp).
+
+The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
+The transit durations for most exoplanets considered is several hours long.
+We therefore quantify error source over 1 hour duration.
+If the smallest stripe subarray is used, frame time is 0.34 seconds.
+For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
+Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
 

### 2019-08-28 ms.tex
Lab paper: more multi-aperture tests across different amplifiers.

@@
 
+\clearpage
+\subsubsection{Multiple apertures within a detector}
 \begin{figure*}
@@
 {\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
-\caption{Time series for many apertures on each detector, binned into 70 equal bins.}\label{fig:manyApPerDetector}
-\end{figure*}
-
+\caption{Time series for many apertures on each detector, binned into 70 equal time bins.}\label{fig:manyApPerDetector}
+\end{figure*}
+
+\begin{figure*}
+{\gridline{\fig{ap_labels_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Apertures on Detector 489}}}
+{\gridline{\fig{raw_tser_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Time series for each aperture}}}
+\caption{Time series for many apertures on the 489 detector after row-by-row and column-by-column background subtraction.
+Each amplifier has its own 1/f noise character, but the lamp variations measured on this detector move in concert across all detectors.}\label{fig:manyApOn489}
+\end{figure*}
+
+\clearpage
+\subsubsection{Reference pixel time series}
 \begin{figure*}
@@
 \begin{figure*}
-{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance}
-\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance}}}
+{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance from Raw Series}
+\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance with Linear Detrending}}}
 {\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}

### 2019-08-30 ms.tex
giving a use case of photon noise to compare with 1/f noise.

@@
 
+For a concrete example, we consider a primary transit of WASP-80 b observed with the F444W grism time series mode.
+The exposure parameters that give a peak pixel count of 35,000 DN or 40\% well depth are a 2048$\times$256 stripe mode with BRIGHT1 read mode for 12 groups.
+These integrations are 31 seconds in duration.
+Each integration will have a 7.8$\times 10^7$ DN in a broadband aperture, so the photon noise per integration is 6,500 DN or 83 ppm.
+Over 1 hour (111 integrations), the photon noise will be 8 ppm if all integrations are independent.
+
 \begin{figure*}[!hbtp]

### 2019-08-30 ms.tex
show that the read noise goes like 1/sqrt(n) for integration to integration.

@@
 Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
+In section \ref{sec:darkBaseline}, we show from dark frames, that the read noise is statistically independent from integration to integration.
 
@@
 \clearpage
+\subsubsection{Dark Baseline Test}\label{sec:darkBaseline}
+In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
+While 1/f is highly correlated within an aperture and results in a large value.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
+\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
+Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
+While 1/f noise substantially increases the noise over the assumption that each pixel's read noise is statistically independent, each integration is statistically independent.
+}\label{fig:darkBaselineAllan}
+\end{figure*}
+
+\clearpage
 \subsubsection{Reference pixel time series}

### 2019-08-31 ms.tex
updating OTIS grism test results with dramatic improvements after row-by-row and column-by-column subtraction.

@@
 %\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
+\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
 \caption{Time series of the simultaneous SW/LW Time Series Stability test
@@
 \fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
-\caption{The grism time series contains subtraction correlated read noise due to pre-amplifier offsets in the vertical direction and 1/f noise in the horizontal direction.
-Row-by-row-subtraction dramatically decreases the noise due to 1/f noise.
+\caption{The grism time series contains correlated read noise due to pre-amplifier offsets over each amplifier and 1/f noise in the horizontal (fast read) direction.
+Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
 }\label{fig:otisLWSWtserShift}

### 2019-09-06 ms.tex
showing the results for frame-by-frame background subtraction.

@@
 \fig{azlab_ratio_tser_rpi_vs_rpf_nobacksub_rpf256_no_backsub_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=True, Bsub=False, 221 ppm}}}
-{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_with_bsub_no_refpix_rpf256_with_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=True, 198 ppm}
-\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Refpix =True, Bsub=True, 197 ppm}}}
+{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_with_bsub_no_refpix_rpf256_with_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=True, 198.2 ppm}
+\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Refpix =True, Bsub=True, 197.1 ppm}}}
+{\gridline{\fig{azlab_ratio_tser_baseline_bsub_by_frame}{0.33\textwidth}{Refpix=False, Bsub=Frame By Frame, 197.5 ppm}}}
 \caption{The time series of the flux ratio between two detectors shows that background subtraction achieves most of the value (within 1 ppm) of reference pixel correction to remove pre-amplifier offsets and 1/f noise.
-Furthermore, the background subtraction can be performed on the slope images rather than on a frame-by-frame basis.
+Furthermore, the background subtraction can be performed on the slope images rather than on a frame-by-frame basis, to get within 0.4 ppm of the value using reference pixels.
 }\label{fig:BackgVsRefpix}

### 2019-09-07 ms.tex
more Allan variance plots now across cooldowns

@@
 
+\clearpage
+\subsection{Noise floor}
+
+Allan variance plots indicate that there is a noise floor across detectors of about 50-60 ppm as shown in Figure \ref{fig:allanVarianceAZ04AZ05}.
+
+\begin{figure*}
+{\gridline{\fig{allan_var_removelinear_True_azlab05baseline.pdf}{0.48\textwidth}{AZLab05 Allan variance}
+\fig{allan_var_removelinear_True_azlab06lamp_warm.pdf}{0.48\textwidth}{AZLab06 Allan variance}}}
+\caption{Allan variance across two detectors in the AZ Lab stability tests.}\label{fig:allanVarianceAZ04AZ05}
+\end{figure*}
+
 %% If you wish to include an acknowledgments section in your paper,

### 2019-09-07 ms.tex
added GL dewar cross-detector stuff

@@
 Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm.
-{\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should corrected to 20 groups)}}
+{\textbf{\textcolor{red}{(Note, here I have used the effective read noise for 90 groups on JDox, but should corrected to 20 groups)}}}
 This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
@@
 
+\clearpage
 \subsection{GL Dewar Tests}
@@
 }\label{fig:GLtSeriesBacksub}
+\end{figure*}
+
+\subsubsection{Across Detectors}
+We also examine the time series across detectors from ``Run104''.
+
+\begin{figure*}
+\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
+		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
+\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.}\label{fig:GLtSeriesAcrossDetectors}
 \end{figure*}

### 2019-09-08 ms.tex
added more stuff on Allan variance and updated plots of the GL dewar time series

@@
 		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
-\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.}\label{fig:GLtSeriesAcrossDetectors}
+		\fig{allan_var_removelinear_True_gl_across_detectors.pdf}{0.48\textwidth}{Allan variance diagram for the ratio of the S02 to S03 background-subtracted detector fluxes}
+\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
+The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
 \end{figure*}

### 2019-09-09 ms.tex
updates to FPA temp change plot and text.

@@
 Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
-While 1/f noise substantially increases the noise over the assumption that each pixel's read noise is statistically independent, each integration is statistically independent.
+While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent.
 }\label{fig:darkBaselineAllan}
@@
 \subsection{FPA temperature change}
+We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
+As can be seen in Figure \ref{fig:indTSeriesAfterLamp} (bottom panel) the Lakeshore temperature controlling a baseplate where the largest thermal mass sits is constant to within 3 mK.
+The FPA temperature is adjusted upward by 300 mK about 75 minutes into the test and held at this higher value.
+The change in temperature results in a 0.1\% increase in flux (ie. 1000 ppm).
+In terms of slopes, this resulted in a change of 2.3 DN/s/px for detector 487 and 3.6 DN/s/px for detector 489.
+For the integration times of 10.77 seconds, this amounts to 25 to 39 DN accumulated within an integration.
+This is lower than the value of 80 DN for a 100 mK change in \citet{hall2005jwstArrays}, likely because it is calculated over the slope of an image rather than the absolute counts.
+
+The reaction to FPA changes in temperature is likely a fractional effect rather than an absolute number of DN.
+This is because both detectors change by about 0.10\% even though their relative peak counts were 25,000 DN/px and 39,000 DN/px for detectors 487 and 489.
+
+In flight, the FPA is expected to be stable to about 1 mK.
+If we take the observed flux change (1000 ppm per 300 mK), the fractional change will be about 3 ppm.
+We therefore expect detector temperature fluctuations to be a relatively small part of the time series error budget.
+
 \begin{figure*}
@@
 \section{Expected In-Flight Performance with JWST}
+
+\section{Conclusions}
+
+\begin{itemize}
+	\item \textbf{1/f Noise:} This is a major contributor to the noise.
+It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
+Fortunately, 1/f noise appears to average like $1/\sqrt{N} $
+	\item \textbf{Subpixel Sensitivity:}
+	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} Expected to be much smaller than HST and timescales are much faster.
+Long timescale traps contribute less then 1e-/DN/px so they are less problematic.
+\end{itemize}
 

### 2019-09-12 ms.tex
more on conclusions section.

@@
 \section{Conclusions}
+The NIRCam instrument will be a valuable tool to characterize the atmospheres of exoplanets with its grism time series mode.
+This mode can be used on some of the brightest valuable exoplanet host stars without saturation and also offers a fine pixel sampling at near-Nyquist to Nyquist sampling depending on the wavelength.
+In order to reap the benefits of NIRCam's grism time series mode, however, it is critical to understand the various systematic error sources and noise floors that will impact the science of transiting planets.
+
+We evaluate results of ground-based tests of the NIRCam instrument for exoplanet time series.
+These tests include a variety of optical setups from the full telescope structure and flight components to small lab dewar tests with flight-like components and flight-like electronics.
+We evaluate the largest sources of noise that add to JWST's error budget and list them below.
 
@@
 	It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
-Fortunately, 1/f noise appears to average like $1/\sqrt{N} $
-	\item \textbf{Subpixel Sensitivity:}
-	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} Expected to be much smaller than HST and timescales are much faster.
+	Fortunately, 1/f noise appears to average like $1/\sqrt{N_{int}} $ from integration to integration.
+	We found efficient reductions in 1/f noise by subtracting the median value from each row in each amplifier.
+	This will be possible for imaging time series but not grism spectroscopy, where one must use the outer background regions in the spectral dispersion direction to reduce 1/f noise.
+	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise.
+	\item \textbf{Subpixel Sensitivity:} The NIRCam detectors all exhibit some degree of crosshatching patterns along crystallographic planes of HgCdTe.
+	Crosshatching structures extend down to the subpixel level where they will not be corrected for in standard flat fielding procedures, especially at the wavelengths that are below Nyquist sampling ($< 3.7\mu$m for the long wavelength and ($1.8\mu$m for the short wavelength).
+	The ALONG detector (used for grism time series) experiences the most pronounced crosshatching amplitudes.
+	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
+	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.
+	Accurate target acquisition will ensure that the same sets of pixels will be used for all grism time series, which permits detailed characterization of the subpixel behavior for re-use on multiple different visits.
+	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} HST observations of exoplanets experience a well-known ``hook effect'' at the beginning of each orbit that rises like an exponential function of time.
+	This is now understood as charge trapping in the detectors \citep{zhou2017chargeTrap}.
+	JWST shows a much smaller ``hook effect'' and also much faster charge trap timescales, such that we expect it to be a negligible contributor so the NIRCam error budget.
 	Long timescale traps contribute less then 1e-/DN/px so they are less problematic.

### 2019-09-18 ms.tex
minor edits to section 2

@@
 Over long timescales (10$^3$ seconds), these resets pre-amp resets will keep the bias drifts hovering around zero without any long slopes or drifts.
+This is helpful in keeping the detector counts below the 65,536 DN saturation limit and thus pre-amp resets permit a larger usable well depth over the counts from 0 to 65,536 DN.
+Without pre-amp resets, the counts in a detector could potentially drift towards 65,536 DN and shrinks the usable well depth.
 
@@
 All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
-The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence,leisenring2016persistence}.
+The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence}
+This was specifically measured for the NIRCam detectors in \citet{leisenring2016persistence}.
 After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
@@
 Over timescales longer than the charge release time, the detector will reach a steady state.
-
-The flight NIRCam detector shows low levels of persistence compared to previous generation detectors.
+As will be discussed in Section \ref{sec:persistence}, the flight NIRCam detector shows low levels of persistence compared to previous generation detectors used in HST.
 
@@
 
-\subsubsection{Persistence}
+\subsubsection{Persistence}\label{sec:persistence}
 HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.

### 2019-09-18 ms.tex
edits to section 3

@@
 The angle between these lines are 67.8$\degree$, 67.7$\degree$ and 44.5$\degree$.
-These are best visualized with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
+These angles and patterns can be analyzed with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
 
@@
 HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
+HgCdTe detectors are manufactured using molecular beam epitaxy upon a substrate, a process which can result in topological defects with peak to valley amplitudes of 5-20 nm in height variations \citep{chang2008surfaceMorphologyHgCdTe}.
+The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes.
+
+The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
 One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
-In this perspective, the projected bond angles form angles of 67.8 $\degree$, 67.8 $\degree$ and 44.4$\degree$, close to the observed crosshatch angles.
-
-HgCdTe detectors are manufactured using molecular beam epitaxy upon a substrate, a process which results in topological defects with peak to valley amplitudes of 5-20 nm in height variations.
-The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes.
-The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
-These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which are quantum efficiency variations.
-We deduce that the crosshatch pattern is mostly likely related to the crystal lattice of the HgCdTe substrate and not the pixels or circuitry.
+In this perspective, the projected bond angles are 44.4$\degree$, 67.8$\degree$ and 67.8$\degree$.
+These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which appear as quantum efficiency variations.
+We deduce that the crosshatch pattern is mostly likely related to the crystal lattice structure of the HgCdTe substrate and not the pixel circuitry.
 
@@
 Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three relative angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$) onto the [211] miller plane.
+These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$) onto the [211] miller plane.
 }\label{fig:crossHatchA5}
@@
 The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (resolving crystal structures) and smallest for the long wavelengths.
-We also fit the crosshatch pattern.
+This is visible both in the throughput cross section of the flat field and the Fourier amplitude of the crosshatch as a function of wavelength.
+We find a steeper wavelength dependence to the crosshatch pattern near 0.9$\degree$ from horizontal in the frequency domain or 0.9$\degree$ from vertical in the length domain.
+%We also fit the crosshatch pattern.
 
@@
 \begin{equation}
-f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c).
-\end{equation}
-
-This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
-We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
-
-We also consider a model with a ``background'' so that 
-\begin{equation}
 f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e\right)},
 \end{equation}
+
+This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
+Finally, we include an exponential term that fits the broad azimuthally symmetric background to all the power spectra,
 where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e$ is the radial background exponential constant.
+We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
 
@@
 	\item Bin the simulated images into the native pixel size
-	\item Divide by the flat field
+	\item Divide by the pixel-to-pixel flat field
 	\item Measure the relative flux with a photometric aperture
@@
 Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
-For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel resolution of $\sim$0.063 \arcsec.
+For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
 This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.

### 2019-09-20 ms.tex
added a comparison of the nint=4 versus nint=1 cases.

@@
 \clearpage
+\subsubsection{Co-added Versus Un-coadded data}\label{sec:coadds}
+In Figure \ref{fig:coaddedData}, we compare data that was taken in READ mode.
+In this case, there were 1000 integrations with a 2048x256 stripe illuminated with the lamp on all four detectors.
+In the case of NFRAME=4, the data are co-added with bit-shift operations whereas for NFRAME=1, all data is used.
+There are 2 groups with NFRAME=4 and 8 groups with NFRAME=1.
+The primary difference between the two are
+\begin{itemize}
+\item the reference pixel correction is performed on frame-by-frame basis for NFRAME=1 and on a co-added group of 4 for NFRAME=4
+\item the slope is calculated with all 8 groups
+\end{itemize}.
+This differences did not have a large overall impact on stability of the lightcurves.
+
+\begin{figure*}
+{\gridline{\fig{azlab_ratio_tser_azlab06_baseline3}{0.47\textwidth}{RAPID mode with NFRAME=1}
+\fig{azlab_ratio_tser_azlab06_nint4.pdf}{0.47\textwidth}{Co-added with NFRAME=4}}}
+\caption{Co-added with NFRAME=4 versus 8 groups RAPID data.
+Using reference pixel subtraction on the individual reads in RAPID mode does not substantially improve the ratio time series of the two detectors as compared with co-added data where reference pixel correction was applied to the group (which is an average of the 4 frames).}\label{fig:coaddedData}
+\end{figure*}
+
+\clearpage
 \subsubsection{Reference pixel time series}

### 2019-09-22 ms.tex
added time series and allan variance for GL dewar Run 112

@@
 
+\subsection{Run 112}
+We also investigate a slightly longer time series for GL dewar.
+
+\begin{figure*}
+\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4_no_backsub.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio No Background Sub}
+\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
+\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}}\label{fig:GLtSeriesRun112}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
+\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
+\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
+The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
+\end{figure*}
+
 \clearpage

### 2019-09-23 ms.tex
added results of GL dewar analysis on subarray 6 data.

@@
 \caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
-The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
-\end{figure*}
-
-\subsection{Run 112}
+The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works below the 100 ppm is not measurable with this test.}\label{fig:GLtSeriesAcrossDetectors}
+\end{figure*}
+
+\clearpage
+
+\subsection{Run 112 - Subarray 4}
 We also investigate a slightly longer time series for GL dewar.
@@
 \fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
-\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}}\label{fig:GLtSeriesRun112}
+\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}\label{fig:GLtSeriesRun112}
 \end{figure*}
@@
 \fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
-\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
-The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
+\caption{Allans for background-subtracted rectangular photometry on the S02 and S03 detectors.
+The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
+\end{figure*}
+
+\subsection{Run 112 - Subarray 6}
+Subarray 6 had higher lamp current and thus higher counts and lower photon noise.
+It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
+
+\begin{figure*}
+\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_no_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio No Background Sub}
+\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_side_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio With {\it Side} Background Sub}}
+\caption{Time series for rectangular photometry on the S01 and S03 detectors as well as side background-subtracted Rectangular photometry.
+The background aperture was placed on the side reference pixels to reduce 1/f noise.}\label{fig:GLtSeriesRun112sub6}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
+\caption{Allan variance for background-subtracted rectangular photometry on the S01 and S03 detectors.
+The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
 \end{figure*}

### 2019-09-27 ms.tex
some more details on GL dewar run104. Need to discuss Run112 more.

@@
 The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
-The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
+The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
 The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.
 
-An LED illumination source is pointed at the detectors and the arrays are read out in subarray mode.
+An LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
 Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
-The first handful of frames show an initial "warmup" period lasting about 9 seconds.
+The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
 This quickly stabilizes to a 1200 ppm level likely dominated by lamp variations.
@@
 When binning the data into 2.5 minute increments, the standard deviation is only 51 ppm.
+As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
+This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detetor.
 
@@
 		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization, if we remove absolute changes likely due to the lamp.
+\caption{Two photometric apertures are placed on the subarray, where they both see common-mode variations in the lamp.
+The ratio of the time series of each aperture shows a handful of integrations at the beginning that stand out, which quickly stabilize to the 240 ppm level.
 }\label{fig:GLtSeries}
@@
 		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{The same time series as Figure \ref{fig:GLtSeries} but with a rectangular background subtraction box.
-\textcolor{red}{To do: understand why the ratio of the two box time series has a larger standard deviation than in Figure \ref{fig:GLtSeries}.
-Is it just the poor SN from a small background box?
-Also, separately, compare two different detectors.}
+\caption{We repeat the time series as Figure \ref{fig:GLtSeries} but add a vertically displaced background subtraction box to each aperture.
+The background boxes reduce the ``ramp-up'' effect and longer timescale variations of the detector.
+The ratio of the time series of each aperture has a larger scatter larger than Figure \ref{fig:GLtSeries} because subtracting the background adds to the 1/f noise (correlated along the horizontal direction) rather than reducing the 1/f noise.
 }\label{fig:GLtSeriesBacksub}
@@
 We also examine the time series across detectors from ``Run104''.
+This approach will test whether there are systematics unique to each detector/readout electronics.
+We compare aperture photometry on the S02 versus S03 detector with background subtraction.
+The resulting time series are shown in Figure \ref{fig:GLtSeriesAcrossDetectors}.
+We do not approach the noise levels interesting to the exoplanet noise regime.
 

### 2019-09-29 ms.tex
tiny wording changes

@@
 The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
-This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit.
+This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit when integrations reach 60\% well depth.
 
@@
 
+\clearpage
+
 \subsubsection{Half Pass Subarray Size Tests}
@@
 The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
-This quickly stabilizes to a 1200 ppm level likely dominated by lamp variations.
-If one divides the two apertures by each other, the resulting time series is very flat and stable to with 260 ppm.
-When binning the data into 2.5 minute increments, the standard deviation is only 51 ppm.
+This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
+If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
 As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.

### 2019-09-29 ms.tex
more minor word edits

@@
 If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
-In addition to reference pixels, background subtraction along each column with removes the amplifier boundary effect.
+In addition to reference pixels, background subtraction along each column removes the amplifier boundary effect.
 If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
@@
 This is visible in a short segment of the time series of all pixels for an example group up the ramp 53 in a dark ramp where the bias has already been subtracted.
-The pixels tim series smoothed with a 51 pixel-wide median filter to better se the low frequency noise.
+The pixels time series smoothed with a 51 pixel-wide median filter to better see the low frequency noise.
 The left panel shows the a time near the beginning of a frame, where amplifiers 1 ad 2 share some common-mode read noise.

### 2019-10-01 ms.tex
updated the long time series through all CV3 data

@@
 \centering
-\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
+\includegraphics[width=.79\columnwidth]{plot_mmm.pdf}
 \caption{Time Series plot through the CV3 photometric stability campaign.
 All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
-13 tests (FULL1 through FULLQ) are all in full frame mode, while WLP8SUB used a 320$\times$320 subarray and WLP8SUB640 used a 640$\times$640 subarray.
-The WLP8SUB showed the smallest standard deviation of any testof any NIRCam mode explored.}\label{fig:CV3longTser}
+13 tests (FULL1 through FULL6) are all in full frame mode, while SUB used a 320$\times$320 subarray and SUB640 used a 640$\times$640 subarray.
+The WLP8SUB showed smaller standard deviation that the full frame tests, when the linear trend is removed.}\label{fig:CV3longTser}
 \end{figure}

### 2019-10-04 ms.tex
added a side-by-side comparison with Asic and GL dewars

@@
 It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
+This is surprising given that S01 is a short wavelength cutoff detector, S02 is a short wavelength cutoff detector and SO3 is a long wavelength cutoff detector.
+Furthermore, the S01 and S02 detectors are powered by a different pair of cards than the S03 detector.
 
@@
 \begin{figure*}
-\gridline{\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
+\gridline{\fig{all_var_azlab_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Baseline}
+\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
 \caption{Allan variance for background-subtracted rectangular photometry on the S01 and S03 detectors.

### 2019-10-05 ms.tex
added 320x320 results and compared to 2048x256

@@
 \clearpage
+\subsection{320 Subarray test}
+We also explored the stability of a $320 \times 320$ subarray.
+The subarray was placed at a strategic location on each detector to allow horizontally-displaced background aperture as shown in Figure \ref{fig:sub320AperturesAZlab06}.
+
+Surprisingly, the subarray mode had considerably higher scatter from integration to integration than stripe mode.
+They both had 1000 integrations, a 6.0 mA LED current and similar aperture widths.
+The subarray mode had 10 groups versus 8 groups with the stripe mode.
+The subarray was $320 \times 320$ with one amplifier output whereas the stripe mode was $2048 \times 256$ with 4 amplifier outputs.
+
+\begin{figure*}
+\gridline{
+\fig{ap_labels_azlab06sub320Baseline487_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 487}\\
+\fig{ap_labels_azlab06sub320Baseline488_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 488}
+}
+\gridline{
+\fig{ap_labels_azlab06sub320Baseline489_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 489}\\
+\fig{ap_labels_azlab06sub320Baseline490_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 490}
+}
+\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
+\end{figure*}
+
+\begin{figure*}
+\gridline{
+\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
+\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
+}
+\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.}\label{fig:sub320vsStripeBaseline2}
+\end{figure*}
+
+\clearpage
 \subsection{Noise floor}

### 2019-10-07 ms.tex
showing oscillatory behavior with the subarray. I wonder what's causing it.

@@
 }
-\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
+\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 test with a $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
 \end{figure*}
@@
 }
-\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.}\label{fig:sub320vsStripeBaseline2}
+\gridline{
+\fig{individual_azlab06_sub320_6p0mA_t100_110.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$}\\
+\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{100-110 min Zoom $320 \times 320$}
+}
+\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.
+A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
+}\label{fig:sub320vsStripeBaseline2}
 \end{figure*}

### 2019-10-09 ms.tex
show the drastic improvement from NFF=512 to NFF=2048

@@
 
+The subarray time series is very sensitive to the fast-frame resets where the entire array is quickly reset at the beginning of an integration.
+These resets are needed to ensure that pixels outside a subarray don't overfill their well capacity and leak into the subarray.
+When NFF=512, the fast-frame resets are cycled through 4 different sections of the detector.
+This results in a cycling pattern with a period of 4 integrations shown in Figure \ref{fig:sub320vsStripeBaseline2}.
+When NFF=2048, there is no cycling pattern shown in Figure \ref{fig:sub320NFF512vs2048}.
+
 \begin{figure*}
@@
 }
-\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.
+\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher oscillations than the stripe mode.
 A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
+NGROUP=10, NINT=1000.
 }\label{fig:sub320vsStripeBaseline2}
+\end{figure*}
+
+\begin{figure*}
+\gridline{
+\fig{individual_azlab06_sub320_9p0mA}{0.49\textwidth}{5-8 min Zoom $320 \times 320$ NGROUP=2}
+}
+\caption{The time series of the AZLab 06 $320 \times 320$ subarray still has oscillations every 4 integrations with NGROUP=2, NINT=3600.
+}\label{fig:sub320vsStripeBaseline2}
+\end{figure*}
+
+\begin{figure*}
+\gridline{
+\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=512}\\
+\fig{individual_azlab06_sub320_nff2048_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=2048}
+}
+\caption{The time series of the AZLab 06 $320 \times 320$ subarray is very sensitive tot he fast frame resets.
+When NFF=512, the fast frame resets cycle through the $320 \times 320$ subarray every 4 integrations, resulting in a 4-integration cycle.
+When NFF=2048, there is no long a pattern and each integration is consistent.
+}\label{fig:sub320NFF512vs2048}
 \end{figure*}

### 2019-10-10 ms.tex
idle versus exposing test

@@
 \clearpage
+
+\subsection{Idle versus exposing residuals}
+The current loads on the asics are different when they are in idle mode (resetting and not collecting data) versus exposing (collecting reads up the ramps).
+We induced a higher load on detector 487 on purpose by running a $\sim$ 3 hour exposure while the remaining detectors ran in idle mode.
+We then started an exposure with all 4 detectors to see if detector 487 exhibited a different time series than the remaining 3 detectors.
+The result shown in Figure \ref{fig:idleVersusExposing320}.
+\begin{figure*}
+\gridline{
+\fig{individual_azlab06_sub320_idle_vs_exp.pdf}{0.49\textwidth}{Data collection versus idle reset}
+}
+\caption{The time series of the AZLab 06 $320 \times 320$ subarrays on all four detectors look the same for the first hour even though detector 487 had a higher current draw 3 hours preceding the exposure because it had a higher current draw.}\label{fig:idleVersusExposing320}
+\end{figure*}
+
+\clearpage
+
 \subsection{Noise floor}

### 2019-10-11 ms.tex
showing results of long sub320 multi exposure test

@@
 
+\subsection{Long multi-exposure Test}
+\textbf{\textcolor{red}{Show exposure boundaries}}
+
+\begin{figure*}
+{\gridline{\fig{individual_azlab06_sub320_multi_exp.pdf}{0.48\textwidth}{AZLab06 Long Multi-Exposure Time series}
+\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
+\caption{We strung together 4 long exposures to create an extended time series.
+There are no obvious transients or exponentials at the exposure boundaries.
+As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.}\label{fig:AZlab06LongMultiExp}
+\end{figure*}
+
+\clearpage
 \subsection{Noise floor}

### 2019-10-12 ms.tex
mark the exposure breaks in multi-exposure time series

@@
 \caption{We strung together 4 long exposures to create an extended time series.
-There are no obvious transients or exponentials at the exposure boundaries.
-As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.}\label{fig:AZlab06LongMultiExp}
+There are no obvious transients or exponentials at the exposure boundaries, which are marked as vertical blue lines.
+As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
+}\label{fig:AZlab06LongMultiExp}
 \end{figure*}

### 2019-10-13 ms.tex
show the trends with time for the multiple exposures.

@@
 \subsection{Long multi-exposure Test}
-\textbf{\textcolor{red}{Show exposure boundaries}}
+A long multi-exposure time series shows the noise properties on timescales up to a few hours.
+This long series also enables a clearer trending with temperature and flux.
 
@@
 \fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
+\fig{individual_azlab06_sub320_multi_exp_w_time}{0.48\textwidth}{Multi-Exposure Time series with temperature data}
 \caption{We strung together 4 long exposures to create an extended time series.

### 2019-10-14 ms.tex
showing that the TMC current is correlated with flux

@@
 
+The measured fluxes are highly correlated with the TMC current.
+
 \begin{figure*}
@@
 \fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
-\fig{individual_azlab06_sub320_multi_exp_w_time}{0.48\textwidth}{Multi-Exposure Time series with temperature data}
+\fig{individual_azlab06_sub320_multi_exp_w_temp}{0.48\textwidth}{Multi-Exposure Time series with temperature data}
 \caption{We strung together 4 long exposures to create an extended time series.
 There are no obvious transients or exponentials at the exposure boundaries, which are marked as vertical blue lines.
-As with previous tests, the standard deviation is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
+As with previous tests, the standard deviation of the flux ratio between two detectors (487 and 489) is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
 }\label{fig:AZlab06LongMultiExp}

### 2019-10-17 ms.tex
showing the Lakeshore T-change test

@@
 \clearpage
-\subsection{FPA temperature change}
+\subsection{Temperature Changes}
+\subsubsection{FPA temperature change}
 We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
@@
 \caption{Time series during an adjustment to the FPA set point.}\label{fig:indTSeriesAfterLamp}
+\end{figure*}
+
+\subsubsection{Lakeshore Temperature Change}
+
+\begin{figure*}
+{\gridline{\fig{individual_azlab06_sub320_lakeshore_to_39p7.pdf}{0.99\textwidth}{}}}
+\caption{Time series during an adjustment to the Lakeshore set point.}\label{fig:indTSeriesLakeshore39p7}
 \end{figure*}

### 2019-10-17 ms.tex
showing behavior during TMC oscillations

@@
 
+\subsubsection{FPA Temperature Oscillations}
+When the temperature control loop on the FPA is working improperly, there can be oscillations in the FPA temperature, as shown in Figure \ref{fig:indTSeriesTMCoscillations}.
+In this example, the oscillations happen at a period of 19.3 minutes.
+The LED fluctuations are signfiicantly longer with a period of $\sim$100 to $\sim$125 minutes.
+
+\begin{figure*}
+{\gridline{\fig{individual_azlab06_sub320_tmc_oscillations.pdf}{0.99\textwidth}{}}}
+\caption{Time series during a $\sim$ 20 minute oscillation in the TMC temperature.}\label{fig:indTSeriesTMCoscillations}
+\end{figure*}
+
 \clearpage

### 2019-10-19 ms.tex
plotting the subtle illumination chnages on Detector 488

@@
 When NFF=512, the fast frame resets cycle through the $320 \times 320$ subarray every 4 integrations, resulting in a 4-integration cycle.
-When NFF=2048, there is no long a pattern and each integration is consistent.
+When NFF=2048, there is no long a 4-integration long pattern.
 }\label{fig:sub320NFF512vs2048}
@@
 \caption{The time series of the AZLab 06 $320 \times 320$ subarrays on all four detectors look the same for the first hour even though detector 487 had a higher current draw 3 hours preceding the exposure because it had a higher current draw.}\label{fig:idleVersusExposing320}
+\end{figure*}
+
+\clearpage
+
+\subsection{Illumination Variations}
+
+The illumination pattern varies slightly over the course of the AZLab 06 baseline stability test.
+The illumination changes are small enough that large amounts of averaging are needed to view it.
+We first create a ``flat-field'' image by averaging all illuminated data (images 24 through 1000) during the AZLab 06 baseline test.
+We then create an ``average1'' image toward the early parts of the lightcurve (images 24-165) where the flux is lower.
+We create an ``average2'' image at late parts of the lightcurve (images 700-1000) where the flux is higher.
+Both of the ``average'' and ``average2'' images are divided by the ``flat field'' to reveal subtle changes in illumination.
+Finally, a crosscut along the X direction is plotted while averaging 126 pixels in the vertical direction.
+The results is that the illumination pattern is not constant in time, with a subtle band centered at X$\approx$ 730 pixels that varies in amplitude.
+
+\begin{figure*}
+\gridline{\fig{azlab06_illum_baseline_plot_region.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
+\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test}}
+\gridline{\fig{azlab06_illum_baselin_differential_profile_plot.pdf}{0.49\textwidth}{Differential fluxes during the early and late parts of the baseline test}}
+\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
+There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange}
 \end{figure*}

### 2019-10-19 ms.tex
added differential illumination analysis of detector 490

@@
 Finally, a crosscut along the X direction is plotted while averaging 126 pixels in the vertical direction.
-The results is that the illumination pattern is not constant in time, with a subtle band centered at X$\approx$ 730 pixels that varies in amplitude.
-
-\begin{figure*}
-\gridline{\fig{azlab06_illum_baseline_plot_region.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
-\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test}}
-\gridline{\fig{azlab06_illum_baselin_differential_profile_plot.pdf}{0.49\textwidth}{Differential fluxes during the early and late parts of the baseline test}}
+The results is that the illumination pattern is not constant in time, with a subtle band centered near X$\approx$ 730 pixels on Detector 488 that varies in amplitude.
+
+\begin{figure*}
+\gridline{\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
+\fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
+\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
+\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
 \caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.

### 2019-10-20 ms.tex
more illum variation tests on 487-490

@@
 \begin{figure*}
-\gridline{\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
+\gridline{\fig{azlab06_illum_baseline_plot_region_487.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
+\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
+\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_487.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
+\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
+\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
+There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange487-488}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{azlab06_illum_baseline_plot_region_489.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
 \fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
-\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
+\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_489.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
 \fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
 \caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
-There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange}
+There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange489-490}
 \end{figure*}

### 2019-10-22 ms.tex
better side-by-side comparison

@@
 \begin{figure*}
-\gridline{\fig{all_var_azlab_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Baseline}
+\gridline{\fig{all_var_azlab06_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
 \fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
-\caption{Allan variance for background-subtracted rectangular photometry on the S01 and S03 detectors.
+\caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
+%Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
 The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}

### 2019-10-22 ms.tex
better-yet side-by-side Asic vs GL comparison

@@
 \begin{figure*}
-\gridline{\fig{all_var_azlab06_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
+\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
 \fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
 \caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
-%Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
+Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
 The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}

### 2019-10-25 ms.tex
more text describing the GL dewar tests

@@
 \subsection{GL Dewar Tests}
-
-The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
-The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
-The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.
-
-An LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
-Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
-The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
-This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
-If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
-As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
-This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detetor.
-
 \begin{figure*}
@@
 \end{figure*}
+
+The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
+The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
+Comparing the GL dewar results to the asic dewar can be helpful in isolating the source of noise sources in the NIRCam system.
+If the GL dewar and asic dewar share the same types of correlated noise sources, these can be attributed to the detectors.
+If the asic dewar introduces or eliminates some correlated noise sources, these can be attributed to the readout electronics.
+
+For the GL dewar, an LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
+Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
+The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
+This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
+If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
+As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
+This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detector.
 
@@
 
+We also introduce a background aperture, shown in Figure \ref{fig:GLtSeriesBacksub} to remove background variations and any amplifier offsets that could affect the flux.
+The resulting time series has a smaller amplitude ``warmup'' and smaller oscillations than Figure \ref{fig:GLtSeries}.
+When we divide the background-subtracted flux for each aperture by the other to make a ratio time series, the resulting noise is higher than in Figure \ref{fig:GLtSeries}.
+This indicates that the background subtraction step introduces more noise than it removes when comparing the differential flux between the two apertures.
+We suspect that 1/f noise in the background aperture causes this increase.
+To conclude, background subtraction improves the absolute flux stability but worsens the differential flux across the apertures.
+When observing an exoplanet time series, for example, scientists may wish to use one reduction technique for the absolute time series to derive the planet orbital parameters, say.
+Then, when analyzing the spectrum, they may wish to use an alternate technique to assess the differential flux from one wavelength to another.
+
 \subsubsection{Across Detectors}
-We also examine the time series across detectors from ``Run104''.
-This approach will test whether there are systematics unique to each detector/readout electronics.
+We also examine the time series across detectors from ``Run104'' to test whether there are systematics unique to each detector/readout electronics.
 We compare aperture photometry on the S02 versus S03 detector with background subtraction.
 The resulting time series are shown in Figure \ref{fig:GLtSeriesAcrossDetectors}.
-We do not approach the noise levels interesting to the exoplanet noise regime.
+We an Allan variance diagram to show how well the flux scales like $\sqrt{N}$ statistics for $N$ integrations.
+The curves track the expected $\sqrt{N}$ behavior but lie well above the theoretical read and photon noise limit.
+This is likely because the 1/f noise is highly correlated within the aperture whereas the theoretical and photon noise limit assumes that the noise in each pixel is independent.
+We do not quire reach the noise levels interesting to the exoplanet noise regime (30-100 ppm).
 
@@
 \subsection{Run 112 - Subarray 4}
-We also investigate a slightly longer time series for GL dewar.
+We also investigate a slightly longer time series for GL dewar which approaches the timescales of interest to exoplanet transit lightcurves.
+Figure \ref{fig:GLtSeriesRun112} shows the flux ratio between detectors S01 and S02 for the Run 112 Subarray 4 ``Hi4'' test.
+The Allan variance plot again scales like the $\sqrt{N}$ statistics but above the theoretical noise limit.
 
@@
 \fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
-\caption{Allans for background-subtracted rectangular photometry on the S02 and S03 detectors.
+\caption{Allans variance for background-subtracted rectangular photometry on the S02 and S03 detectors.
 The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
@@
 \subsection{Run 112 - Subarray 6}
-Subarray 6 had higher lamp current and thus higher counts and lower photon noise.
+Subarray 6 had higher lamp current and thus higher counts and lower photon noise, which approaches the exoplanet atmospheric feature regime (30-100 ppm).
+In this test, we take the ratio of flux on one detector to the other.
+This removes the lamp variations but allows the
+
 It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
@@
 \begin{figure*}
-\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
+\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long 320 Multi-Exposure Baseline}
 \fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
@@
 Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
-The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
+For the GL dewar, the ratio of the two detectors' fluxes (after background subtraction) scales like $\sqrt{N}$ statistics down to the $\sim$60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
 \end{figure*}

### 2019-10-25 ms.tex
some clarifications on persistence tests

@@
 \begin{figure*}
-{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence}
+{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence. }
 \fig{persistence_long_lin.pdf}{0.49\textwidth}{Long Timescale Persistence}}}
-\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistenceAZlab04}
+\caption{The NIRCam long wavelength detectors show very rapid charge trap release timescales, such that the count rates fall below the read noise level in 20 seconds.
+The data are binned to show that there is no detectable persistence on 3000 second timescales.
+An arbitrary offset of 4$e^-$ is added on the short timescale plot to keep the values positive and possible to plot on a log scale.}\label{fig:persistenceAZlab04}
 \end{figure*}
@@
 Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
-While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent.
+While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent when examining this dark (un-illuminated) data.
 }\label{fig:darkBaselineAllan}

### 2019-10-26 ms.tex
another dramatic display of what happens if a horizontally-displayed aperture is used.

@@
 
+\begin{figure*}
+\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_side_backsub_removelinear_True_3.pdf}{0.48\textwidth}{Allan Variance}}
+\caption{The same test as Figure \ref{fig:GLtSeriesAcrossDetectors} shows {\bf dramatically} smaller noise if (1) the aperture size is increased and (2) a horizontally displaced aperture is used to reduce 1/f noise.}\label{fig:GLtSeriesRun112}
+\end{figure*}
+
 \clearpage

### 2019-10-29 ms.tex
showing time-dependence of illumination gradient.

@@
 
+We also examine the slope and intercept of the illumination as a function of time.
+It is clear that there is a gradient in the image that also correlates with the flux.
+This may explain detector 490's different behavior over time.
+
+\begin{figure*}
+\gridline{
+\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
+}
+\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487..}\label{fig:illumGradientChangeOverTime}
+\end{figure*}
+
 \clearpage

### 2019-10-30 ms.tex
compared the illum changes to the 487/489 slope ratio.

@@
 }
-\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487..}\label{fig:illumGradientChangeOverTime}
+\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487.
+The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}
 \end{figure*}

### 2019-10-31 ms.tex
tracking illumination gradient on detector 489 as well.

@@
 \gridline{
-\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
+\fig{illum_slope_and_intercept_487.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 487}
+\fig{illum_slope_and_intercept_489.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 489}
 }
-\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487.
+\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detectors on detectors 487 and 489.
 The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}

### 2019-11-01 ms.tex
using the profile line fit as a way to estimate flux

@@
 
+\begin{figure*}
+\gridline{
+\fig{ratio_for_AZLab06_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489}
+\fig{allan_variance_for_AZLab06_Baseline_487_intercepts}{0.49\textwidth}{Allan variance of the ratio line series}
+}
+\caption{We can take the line intercept from Figure \ref{fig:illumGradientChangeOverTime} to calculate the flux.
+This averages like $\sqrt{N}$ statistics.
+}\label{fig:illumGradientChangeOverTime}
+\end{figure*}
+
 \clearpage

### 2019-11-03 ms.tex
describing how the illumination gradient was calculated

@@
 We also examine the slope and intercept of the illumination as a function of time.
+We applying the following processing steps:
+\begin{enumerate}
+	\item Apply side and top reference pixels to all frames
+	\item	Calculate slope images from ramp images using \texttt{ncdas}
+	\item Subtract 1/f noise with a row-by-row subtraction by the average of un-illuminated pixels
+	\item Calculate an average flat field over the entire time series of illuminated ata
+	\item Divide each image by the flat field
+	\item Collapse the illuminated region along the Y direction to make an illumination profile
+	\item Fit the illumination profile to a line and save the slope and intercept
+\end{enumerate}
+Figure \ref{fig:illumGradientChangeOverTime} shows the slope and intercept calculated for the illumination profile over time.
 It is clear that there is a gradient in the image that also correlates with the flux.

### 2019-11-03 ms.tex
beginning to investigate 1/f stuff more and still working on illumination gradients of long multi-exposure time series.

@@
 
-A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
+A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
 The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
@@
 For a pessimistic scenario, we assume a 15,000 DN read noise contributes to every pair of reads for the 70 pixel radius aperture (and 75 to 100 pixel background subtraction annulus).
-If the read noise is tolerable under this scenario, then it should have a minimal impact to photometric time series.
+If the read noise is tolerable under this scenario, then it should have a minimal impact on photometric time series.
 If it is a problem, we will discuss methods of mitigation such as the row-by-row subtraction above.
@@
 Therefore, the corrected read noise per integration should be:
-\begin{equation}
+\begin{equation}\label{bestRNCorrection}
 RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}

### 2019-11-04 ms.tex
showing the profile fitting results from the long multi-exposure time series

@@
 
+Given how well the Line Intercept ratio between detectors 487 and 489 averages like $\sqrt{N}$ statistics in Figure \ref{fig:illumGradientChangeOverTime}, we look at the multi-exposure test to examine longer baselines.
+
+\begin{figure*}
+\gridline{\fig{ratio_for_AZLab06_Multi-Exposure_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489 over the long multi-exposure test}}
+\gridline{
+\fig{allan_variance_for_AZLab06_Multi-Exposure_Baseline_487_intercepts.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from the best-fit slope intercept}
+\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from Aperture Photometry}
+}
+\caption{We repeat the experiment from Figure \ref{fig:illumGradientChangeOverTime} but this time over a long multi-exposure test.
+The line-fit method achieves worse results on short timescales but better results on long timescales.}\label{fig:illumGradientChangeOverTimeMultiExpBaseline}
+\end{figure*}
+
 \clearpage

### 2019-11-05 ms.tex
reorganizing sections so it's readable and shorter

@@
 
-Section \ref{sec:detectorPrimer} gives a review of NIRCam's detector operation.
 Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.
 Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.
-
-\section{A Primer on Detector Operation}\label{sec:detectorPrimer}
-
-\subsection{Photosensitive Operation}
-\textcolor{red}{\textbf{NOTE: This section needs checking for factual accuracy by a detector expert}}
-
-It is helpful to review the basic operation of a NIR detector \citep[e.g.][]{rieke2007irDetectorReview} in order to understand the systematics affecting time series.
-Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
-The crystalline HgCdTe structure has 4 valence electrons that form covalent bonds in a tetrahedral structure.
-By varying the relative amount of Hg, Cd and Te (doping), it is possible to increase or decrease the number of electrons to create mobile charge carriers that move along the crystaline lattice.
-The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons).
-The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
-\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
-The orange and blue purple colors depict the N-type and P-type semiconductors, respectively.
-The undepleted zones of the semiconductor (darker colors with - and + signs) contain mobile charge carriers whereas the depletion region (lighter color without - and +) has no mobile carriers and all electrons are in the valence state.
-The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
-The electron-hole pairs migrate across the depletion region towards the undepleted zones due to an electric field in the depletion zone.
-The voltage can be measured non-destructively (for many reads) as the well fills and then reset before saturating.}\label{fig:npSchematic}
-\end{figure}
-
-The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
-This produces a negative charge on the P-type side.
-Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge.
-The resulting voltage difference is called the contact potential.
-In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
-This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it contains no mobile charge carriers.
-The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
-It should be noted that the ``depletion region'' is depleted in {\it mobile charge carriers}, but is {\it not} depleted in net charge because has a net positive charge in the N-type depletion region and negative charge in the P-type depletion region.
-
-The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
-The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positive charge carriers (holes).
-The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
-The increased depletion region size also increases the well depth or capacity of electrons that the detector may collect before saturation.
-The reverse bias is applied at each reset at the beginning of a detector's integration.
-Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
-The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type.
-
-Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only.
-Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
-The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to visualize the charge trapping effect and motion of mobile charges this way \citep[e.g.][]{smith2008imgPersistence}.
-
-When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
-The depletion region has a net electric field pointed toward the P-type side, which controls the direction electrons and holes will migrate.
-The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
-The incoming photon has the effect of decreasing the size of the depletion region.
-A second photon will excite another electron-hole pair so that a hole moves to the P-type side.
-This continues and decreases the size of the depletion region.
-The diffusion of charge carriers across the junction changes the voltage across the NP junction, which can be measured with a sensitive amplifier circuit.
-
-As the size of the depletion region decreases, the detector becomes decreasingly sensitive to new photons.
-Thus, the NIRCam HgCdTe detectors are never strictly linear.
-Eventually, with enough photons, the depletion region is too small to create electron-hole pairs with incoming photons.
-This is where the detector approaches saturation and no longer changes voltage with more light.
-
-\subsection{Readout Circuit}\label{sec:readout}
-
-The accumulated charge from absorbed photons in the detector is measured with a multiplexor (MUX) that form a readout integrated circuit (ROIC) \citep{rieke2007irDetectorReview}.
-This readout circuitry allows the signal to be measured non-destructively up the ramp in so-called ``multiaccum" mode.
-
-A sensitive amplifier converts the measured voltage potential (as compared with the bias level after reset) into a signal.
-The electronic circuit that digitizes the voltages is tuned to ensure the 16 bits (65,536 possible Data Numbers) measure the voltage across the NP junction from the value just after reset (before photons are detected) to the saturation voltage where the maximum number of photons are collected and no more electron-hole pairs can be produced in the depletion region.
-The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not go below 0.
-The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation of a pixel.
 
@@
 These are discussed in Section \ref{sec:preAmp}.
-	\item \textbf{1/f noise:} This is a noise source where most of the noise power is concentrated as low frequencies.
+		\subitem \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
+The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
+The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between regions of the detector.
+If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
+	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) that introduces noise to the images \citep{rauscher2011irsSquared}.
+	This is a noise source where most of the noise power is concentrated at low frequencies.
 	1/f noise causes spatial correlations in the fast-read direction (along detector rows).
@@
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
-	\item \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
-The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
-The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between regions of the detector.
-If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
+	\item \textbf{Charge Trapping}
 \end{itemize}
@@
 The long dark exposure example of 108 integrations shows the behavior over long timescales.}\label{fig:ampResetDark}
-\end{figure}
-
-\subsection{Charge Trapping}
-All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
-The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence}
-This was specifically measured for the NIRCam detectors in \citet{leisenring2016persistence}.
-After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
-However, in real detectors, some charges are trapped within the depletion region.
-During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
-
-Figure \ref{fig:npSchematicTraps} shows a schematic of a detector that has charge traps in the substrate.
-After illumination by a source, these traps will fill with charge that does not migrate across the depletion layer.
-When the reset voltage is applied to the detector, the trapped charge remains within the depletion layer.
-In the second integration in the schematic, charge is released, which reduces the size of the depletion layer faster than the incoming photons would otherwise.
-The consequence of charge traps is that there is a deficiency in measured charge on the first integration and an excess of measured charge on the second integration.
-Therefore, a constant astrophysical signal can be measured as a time-varying one due to the charge trapping effect.
-Over timescales longer than the charge release time, the detector will reach a steady state.
-As will be discussed in Section \ref{sec:persistence}, the flight NIRCam detector shows low levels of persistence compared to previous generation detectors used in HST.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{charge_traps_photodiode.pdf}
-\caption{A cartoon schematic of a H2RG detector with charge traps inspired by \citet{smith2008imgPersistence}, \citet{tulloch2018persistenceH2RG} and \citet{leisenring2016persistence}.
-Charged traps for negative and positive carriers (depicted as round circles) will capture charge before it can flow to the undepleted regions of the detector.
-The charge traps do not immediately empty with a detector reset, but instead release at later times causing a spurious signal.
-This spurious signal (the shrinking of the depletion region as highlighted with red circles), causes a voltage change in future integrations that appears the same as a true signal from incoming photons.}\label{fig:npSchematicTraps}
 \end{figure}
@@
 
+\appendix
+
+\section{A Primer on Detector Operation}\label{sec:detectorPrimer}
+
+\subsection{Photosensitive Operation}
+\textcolor{red}{\textbf{NOTE: This section needs checking for factual accuracy by a detector expert}}
+
+It is helpful to review the basic operation of a NIR detector \citep[e.g.][]{rieke2007irDetectorReview} in order to understand the systematics affecting time series.
+Figure \ref{fig:npSchematic} shows a schematic of an NP semiconductor junction for a H2RG detector from \citet{smith2008imgPersistence}.
+The crystalline HgCdTe structure has 4 valence electrons that form covalent bonds in a tetrahedral structure.
+By varying the relative amount of Hg, Cd and Te (doping), it is possible to increase or decrease the number of electrons to create mobile charge carriers that move along the crystaline lattice.
+The N-type semiconductor is a negatively-doped HgCdTe crystalline structure that has negative charge carriers (electrons).
+The P-type semiconductor is a positively-doped HgCdTe crystalline structure that has positive charge carriers (vacant holes in the lattice structure than can move like electrons).
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{ideal_photodiode.pdf}
+\caption{A cartoon schematic of a H2RG detector inspired by \citet{smith2008imgPersistence} and \citet{tulloch2018persistenceH2RG}.
+The orange and blue purple colors depict the N-type and P-type semiconductors, respectively.
+The undepleted zones of the semiconductor (darker colors with - and + signs) contain mobile charge carriers whereas the depletion region (lighter color without - and +) has no mobile carriers and all electrons are in the valence state.
+The depletion region is widest after detector reset and shrinks as the detector is illuminated with photons that create electron-hole pairs.
+The electron-hole pairs migrate across the depletion region towards the undepleted zones due to an electric field in the depletion zone.
+The voltage can be measured non-destructively (for many reads) as the well fills and then reset before saturating.}\label{fig:npSchematic}
+\end{figure}
+
+The junction of these two materials enables electrons to flow from the N-type material to the P-type material where it can complete a valence shell in the semiconductor material.
+This produces a negative charge on the P-type side.
+Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge.
+The resulting voltage difference is called the contact potential.
+In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
+This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it contains no mobile charge carriers.
+The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
+It should be noted that the ``depletion region'' is depleted in {\it mobile charge carriers}, but is {\it not} depleted in net charge because has a net positive charge in the N-type depletion region and negative charge in the P-type depletion region.
+
+The NP junction in Figure \ref{fig:npSchematic} is ``reverse-biased'' with a positive potential on the N-type material and negative potential on the P-type.
+The positive potential on the N-type material attracts the negative charge carriers (electrons) whereas the negative potential on the P-type material attracts the  positive charge carriers (holes).
+The reverse bias thus reduces the number of mobile charge carriers and increases the size of the depletion region.
+The increased depletion region size also increases the well depth or capacity of electrons that the detector may collect before saturation.
+The reverse bias is applied at each reset at the beginning of a detector's integration.
+Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
+The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type.
+
+Note that Figure \ref{fig:npSchematic} shows the mobile charge carriers only.
+Textbook NP junction schematics often show the net charge and thus symbolize the regions with charge carriers as empty and the depletion region with ``+'' symbols on the N-type semiconductor and ``-'' symbols on the P-type˚ \citep[e.g.][]{halliday2004physicsText}.
+The schematic in Figure \ref{fig:npSchematic} instead shows the mobile charge carriers as ``+'' and ``-'' because it is easier to visualize the charge trapping effect and motion of mobile charges this way \citep[e.g.][]{smith2008imgPersistence}.
+
+When an incoming photon strikes the N-type depletion region, it will excite an electron from the valence to conduction band which creates an electron-hole pair \citep{rieke2007irDetectorReview}.
+The depletion region has a net electric field pointed toward the P-type side, which controls the direction electrons and holes will migrate.
+The electron moves to the extremity of the depletion zone in the N-type material whereas the positive hole generated crosses the NP junction and adds a mobile charge to the P-type side.
+The incoming photon has the effect of decreasing the size of the depletion region.
+A second photon will excite another electron-hole pair so that a hole moves to the P-type side.
+This continues and decreases the size of the depletion region.
+The diffusion of charge carriers across the junction changes the voltage across the NP junction, which can be measured with a sensitive amplifier circuit.
+
+As the size of the depletion region decreases, the detector becomes decreasingly sensitive to new photons.
+Thus, the NIRCam HgCdTe detectors are never strictly linear.
+Eventually, with enough photons, the depletion region is too small to create electron-hole pairs with incoming photons.
+This is where the detector approaches saturation and no longer changes voltage with more light.
+
+\subsection{Readout Circuit}\label{sec:readout}
+
+The accumulated charge from absorbed photons in the detector is measured with a multiplexor (MUX) that form a readout integrated circuit (ROIC) \citep{rieke2007irDetectorReview}.
+This readout circuitry allows the signal to be measured non-destructively up the ramp in so-called ``multiaccum" mode.
+
+A sensitive amplifier converts the measured voltage potential (as compared with the bias level after reset) into a signal.
+The electronic circuit that digitizes the voltages is tuned to ensure the 16 bits (65,536 possible Data Numbers) measure the voltage across the NP junction from the value just after reset (before photons are detected) to the saturation voltage where the maximum number of photons are collected and no more electron-hole pairs can be produced in the depletion region.
+The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not go below 0.
+The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation of a pixel.
+
+\subsection{Charge Trapping}
+All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
+The physical mechanism that explain persistence is that charges are trapped in the depletion region after illumination by photons as the detector well fills \citep{smith2008imgPersistence}
+This was specifically measured for the NIRCam detectors in \citet{leisenring2016persistence}.
+After the reverse-bias voltage is applied (a reset) in an ideal detector, the depletion region will be devoid of mobile charge carriers (electrons and holes).
+However, in real detectors, some charges are trapped within the depletion region.
+During a future integration, these charges will be released and shrink the size of the depletion region, filling a pixel with spurious signal (Data Numbers) not related to that integration's illumination by photons.
+
+Figure \ref{fig:npSchematicTraps} shows a schematic of a detector that has charge traps in the substrate.
+After illumination by a source, these traps will fill with charge that does not migrate across the depletion layer.
+When the reset voltage is applied to the detector, the trapped charge remains within the depletion layer.
+In the second integration in the schematic, charge is released, which reduces the size of the depletion layer faster than the incoming photons would otherwise.
+The consequence of charge traps is that there is a deficiency in measured charge on the first integration and an excess of measured charge on the second integration.
+Therefore, a constant astrophysical signal can be measured as a time-varying one due to the charge trapping effect.
+Over timescales longer than the charge release time, the detector will reach a steady state.
+As will be discussed in Section \ref{sec:persistence}, the flight NIRCam detector shows low levels of persistence compared to previous generation detectors used in HST.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{charge_traps_photodiode.pdf}
+\caption{A cartoon schematic of a H2RG detector with charge traps inspired by \citet{smith2008imgPersistence}, \citet{tulloch2018persistenceH2RG} and \citet{leisenring2016persistence}.
+Charged traps for negative and positive carriers (depicted as round circles) will capture charge before it can flow to the undepleted regions of the detector.
+The charge traps do not immediately empty with a detector reset, but instead release at later times causing a spurious signal.
+This spurious signal (the shrinking of the depletion region as highlighted with red circles), causes a voltage change in future integrations that appears the same as a true signal from incoming photons.}\label{fig:npSchematicTraps}
+\end{figure}
+
 %% To help institutions obtain information on the effectiveness of their 

### 2019-11-12 ms.tex
fitting the 1/f noise as an example
showing asic voltages w/ time series

@@
 
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pixeltime_series_amp_0_full_fft_cleaned_True.pdf}
+\caption{The discreet Fourier transform of the entire time series from one amplifier shows 1/f noise at low frequencies that levels off at high frequencies.
+}\label{fig:pixelTSeriesFFT}
+\end{figure*}
+
 \subsubsection{PCA Correction}
@@
 }\label{fig:sub320NFF512vs2048}
+\end{figure*}
+
+\clearpage
+
+\subsection{Asic Voltages}
+\begin{figure*}
+\gridline{
+\fig{individual_azlab07_baseline2_487_and_490_binned.pdf}{0.89\textwidth}{Asic Voltages and Detector fluxes on 487 and 489}\\
+}
+\caption{Asic voltages do not show obvious strong correlations with flux. There's a slight correlation with VRST\_V.
+}\label{fig:asicVoltageAndFlux}
 \end{figure*}

### 2019-11-14 ms.tex
more on intrapixel sensitivity and 1/f

@@
 %and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
-We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector labs.
+We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector lab.
 
@@
 \begin{itemize}[noitemsep]
-	\item \textbf{Intrapixel sensitivity:} - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
+	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
+	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
+	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
+	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) have been measured to extend to the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
 The resets cause discontinuities in the pedestal level of all pixels between frames.
+Pre-amp resets can also appear in slope images (DN/second) because NIRCam's amplifiers are reset once per frame (not once per integration).
 This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can.
-These are discussed in Section \ref{sec:preAmp}.
+These are discussed further in Section \ref{sec:preAmp}.
 		\subitem \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
@@
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
-	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) that introduces noise to the images \citep{rauscher2011irsSquared}.
+	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
 	This is a noise source where most of the noise power is concentrated at low frequencies.
@@
 It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage.
-1/f noise can be reduced using reference pixels
+1/f noise can be reduced by subtracting the values from background pixels or reference pixels.
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.

### 2019-11-16 ms.tex
edits to section 2.

@@
 \begin{itemize}[noitemsep]
-	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
-	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
-	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
-	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) have been measured to extend to the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
@@
 These are discussed further in Section \ref{sec:preAmp}.
-		\subitem \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
+	\item \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
 The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
@@
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
+	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
+	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
+	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
+	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
@@
 Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
-	\item \textbf{kTC noise:} A random process due to the unknown amount of charge stored at the reset voltage level
+	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
+	Fortunately, the bias offset produces by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
+	This noise would  only become relevant when attempting to observe integrations of 1 group up the ramp.
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
@@
 For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
-This temperature change is expected to be smaller in flight due to adjustments in ??
-(Marcia said in 2018-11-02 meeting)
+	This temperature change is expected to be smaller in flight due to adjustments in the operations to run all four amplifiers regardless of how many are used to collect science data.
 	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
@@
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
-	\item \textbf{Charge Trapping}
+	\item \textbf{Charge Trapping} A major correlated error source on HST WFC3 is the ``hook effect'' \citep{berta2012flat_gj1214}.
+	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
+	JWST's NIRCam instrument has very lower rates of persistence (<1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
 \end{itemize}
@@
 These pre-amplifier levels can either be reset at the beginning of an integration with samples up the ramp or with each frame up the ramp.
-The NIRCam detectors are usually set to reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
-However, one set of darks was collected at Lockheed CV with a reset only once per integration to study the effects of the pre-amplifier resets.
+The NIRCam detectors are reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
+One set of darks was collected at Lockheed CV with a reset only once per integration to study the effects of the pre-amplifier resets.
 
@@
 
-The angles of the crosshatch patterns are likely determined by the crystal pattern of HgCdTe.
+The angles of the crosshatch patterns are determined by the crystal pattern of HgCdTe.
 HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
@@
 This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
-Atomic force microscopy shows topological features that are approximately 1.2~$\mu$m in width \citep{chang2008surfaceMorphologyHgCdTe}.
+Atomic force microscopy shows topological features that are approximately 1.2~$\mu$m in width \citep{chang2008surfaceMorphologyHgCdTe} compared to the 18~$\mu$m pixel sizes.
 The width of the structures can also be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
@@
 This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
-It is possible that the crosshatch pattern's width varies among detectors or that a tophat function is a poor approximation of the actual subpixel response.
+We expect that the crosshatch pattern's width varies among detectors and that a tophat function is a poor approximation of the actual subpixel response.
 Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
@@
 \begin{equation}
-f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e\right)},
+f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e_b\right)},
 \end{equation}
@@
 Finally, we include an exponential term that fits the broad azimuthally symmetric background to all the power spectra,
-where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e$ is the radial background exponential constant.
+where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e_b$ is the radial background exponential constant.
 We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
@@
 For the F300M filter and ALONG detector, we find 
-for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e=0.26 \pm 0.01$ px$^{-1}$.
+for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e_b=0.26 \pm 0.01$ px$^{-1}$.
 The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.

### 2019-11-17 ms.tex
small updates to crosshatching section

@@
 	\item Fit the existing flat field to a crosshatch model in the Fourier domain
-	\item Extrapolate the crosshatch model to high frequencies to estimate the sub-pixel structure
-	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
+	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
 	\item Multiply the PSF by the simulated flat field

### 2019-11-17 ms.tex
more general info on detector tests

@@
 The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$) inaccessible by other modes.
+
+Given the finite lifetime of the JWST mission set by onboard fuel, it is important to understand the systematic errors before launch to maximize the science return of the observatory.
+We discuss the major sources of systematic errors that can affect the NIRCam instrument.
+Parallel efforts to characterize other instrument's noise sources are being done, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
 
@@
 
-Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
+Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
 The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-There were are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+There are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).
 The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
-These two different kinds of detector electronics can be compared against each other to help isolate detector-related systematics from readout electronics-related systematics.
+These two different kinds of detector electronics can be compared against each other to help isolate optical-related systematics, detector-related systematics and electronics-related systematics.
 
@@
 The hexagonal PSF also has a central vertical peak which can be used for aperture centering.
-The tests with dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
+The tests with the GL and ASIC dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
 
@@
 \clearpage
-\subsection{Long Darks}\label{sec:longDarks}
+\subsection{OTIS Long Darks}\label{sec:longDarks}
 

### 2019-11-18 ms.tex
edits to intro and fix to long CV3 plot

@@
 The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
-By putting together 10 to 30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST}.
+By putting together 10 to 30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST,lustig-yaeger2019detectabilityTRAPPIST-1}.
 Optimistically, 30 transits may contain enough photons to detect O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact on its atmosphere \citep{barstow2016trappist1habitable}.
-Alternatively, 10 transits of TRAPPIST-1e could be sufficient study if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
+More detailed modeling of atmospheric evolution indicates that biogenic oxygen may be too difficult to detect with any JWST instrument but desiccated oceans may produce detectable abiogenic oxygen \citep{lustig-yaeger2019detectabilityTRAPPIST-1}.
+Alternatively, 10 transits of TRAPPIST-1e could be sufficient if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
 A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.

### 2019-11-20 ms.tex
better LS periodogram to show 1/f noise

@@
 \centering
-\includegraphics[width=.4\columnwidth]{pixeltime_series_amp_0_full_fft_cleaned_True.pdf}
-\caption{The discreet Fourier transform of the entire time series from one amplifier shows 1/f noise at low frequencies that levels off at high frequencies.
+\includegraphics[width=.4\columnwidth]{avg_psd_amp_0.pdf}
+\caption{The average Lomb Scargle periodogram from Amplifier 0's time series over 108 groups.
+The line shows a 1/f slope law.
 }\label{fig:pixelTSeriesFFT}

### 2019-11-20 ms.tex
reorganizing to match the known detector effects section
updated the 1/f section

@@
 
+\subsection{Amplifier Boundary Discontinuities}
+
+NIRCam's STRIPE mode and full frame mode both employ 4 amplifiers to simultaneously read out or reset 4 pixels at once.
+This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
+On the flip side, the four amplifiers will have different behaviors such as offsets in the bias level.
+The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
+If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum.
+
+Fortunately, the amplifier offsets are efficiently removed by reference pixels.
+For example, we subtract the median of the 4 reference pixels from each column and this efficiently removes the bias signal from each amplifier shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (middle panel and bottom panel).
+It should be noted, however, that there are gradients in the bias signal within each amplifier.
+If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
+In addition to reference pixels, background subtraction along each column removes the amplifier boundary effect.
+If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.79\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
+\caption{An example slope image from the LW OTIS Stability test.
+{\it First Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
+{\it Second Panel:} Averaging all the reference pixels within an amplifier and subtracting the result reduces the offsets between amplifiers but there are still noticeable boundaries at X= 512, 1024 and 1536.
+{\it Third Panel:} Reference pixel correction using the 4 non-illuminated pixels in each column significantly reduces offsets between amplifiers, but introduces read noise to each column.
+{\it Fourth Panel:} Background subtraction with the mean value of the pixels below Y=15 and above Y=190 eliminates offsets between amplifiers without introducing any substantial new noise source.
+}\label{fig:ampOffsetsOtisGrismSlope}
+\end{figure}
+
+\subsection{1/f Noise}
+The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
+This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
+The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops roughly like a 1/f power law.
+Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
+To create the periodogram, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{avg_psd_amp_1.pdf}
+\caption{The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
+The line shows a 1/f slope law.
+}\label{fig:pixelTSeriesPSpec}
+\end{figure*}
+
+\subsection{Fringing}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
+\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
+\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
+The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
+The sca
+A periodogram shows a peak near 19 pixels period, however, it is not an overwhelming periodic signature.
+\textcolor{red}{double check the scatter in spectrum to photon + read noise}
+\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum}
+}\label{fig:integratedOtisGrismSpec}
+\end{figure}
+
 \subsection{Subpixel Crosshatching}
@@
  }\label{fig:subpixScanSimulation}
-\end{figure}
-
-\subsection{Amplifier Boundary Discontinuities}
-
-NIRCam's STRIPE mode and full frame mode both employ 4 amplifiers to simultaneously read out or reset 4 pixels at once.
-This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
-On the flip side, the four amplifiers will have different behaviors such as offsets in the bias level.
-The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
-If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum.
-
-Fortunately, the amplifier offsets are efficiently removed by reference pixels.
-For example, we subtract the median of the 4 reference pixels from each column and this efficiently removes the bias signal from each amplifier shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (middle panel and bottom panel).
-It should be noted, however, that there are gradients in the bias signal within each amplifier.
-If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
-In addition to reference pixels, background subtraction along each column removes the amplifier boundary effect.
-If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
-\caption{An example slope image from the LW OTIS Stability test.
-{\it First Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
-{\it Second Panel:} Averaging all the reference pixels within an amplifier and subtracting the result reduces the offsets between amplifiers but there are still noticeable boundaries at X= 512, 1024 and 1536.
-{\it Third Panel:} Reference pixel correction using the 4 non-illuminated pixels in each column significantly reduces offsets between amplifiers, but introduces read noise to each column.
-{\it Fourth Panel:} Background subtraction with the mean value of the pixels below Y=15 and above Y=190 eliminates offsets between amplifiers without introducing any substantial new noise source.
-\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum}
-}\label{fig:ampOffsetsOtisGrismSlope}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
-\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
-\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
-The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
-The sca
-A periodogram shows a peak near 19 pixels period, however, it is not an overwhelming periodic signature.
-\textcolor{red}{double check the scatter in spectrum to photon + read noise}
-}\label{fig:integratedOtisGrismSpec}
 \end{figure}
@@
 
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{avg_psd_amp_0.pdf}
-\caption{The average Lomb Scargle periodogram from Amplifier 0's time series over 108 groups.
-The line shows a 1/f slope law.
-}\label{fig:pixelTSeriesFFT}
-\end{figure*}
-
 \subsubsection{PCA Correction}

### 2019-11-21 ms.tex
more details on 1/f power spec

@@
 
+\clearpage
+
 \subsection{1/f Noise}
@@
 \includegraphics[width=.4\columnwidth]{avg_psd_amp_1.pdf}
-\caption{The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
-The line shows a 1/f slope law.
+\includegraphics[width=.4\columnwidth]{preamp_removed_grp_54.pdf}
+\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
+The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000, Hz.
+{\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal).
+The amplifier offsets have been removed, but the 1/f noise from these adjacent amplifiers shows different behavior.
 }\label{fig:pixelTSeriesPSpec}

### 2019-11-22 ms.tex
put in examples of RTN and RC as well as other edits to section 2.

@@
 \section{Known Detector Effects}\label{sec:knownEffects}
-Section \ref{sec:detectorPrimer} describes the operation of a HgCdTe array.
+An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
 However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
-Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics. These known detector effects that can impact stability are:
+Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics.
+These known detector effects that can impact stability are listed briefly and then in more detail as related to the JWST NIRCam detectors below that.
 
@@
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
-	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
-	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
-	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
-	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
@@
 1/f noise can be reduced by subtracting the values from background pixels or reference pixels.
+	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
+	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
+	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
+	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
@@
 The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000, Hz.
-{\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal).
+{\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal) on a dark frame.
 The amplifier offsets have been removed, but the 1/f noise from these adjacent amplifiers shows different behavior.
@@
 \end{figure}
+
+\clearpage
+
+\subsection{Random Telegraph Noise and RC pixels}
+Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
+
+\begin{figure*}
+\gridline{\fig{rtn_placeholder.png}{0.45\textwidth}{RTN Pixel} 
+\fig{{rc_placeholder.png}}{0.5\textwidth}{RC pixel}}
+\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
+Examples are shown for RTN and RC pixels.
+}\label{fig:RTNandRC}
+\end{figure*}
 

### 2019-11-27 ms.tex
plot of example RTN
calculations and updates to RTN

@@
 Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
-
-\begin{figure*}
-\gridline{\fig{rtn_placeholder.png}{0.45\textwidth}{RTN Pixel} 
+The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
+These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.
+
+For Weak Lens photometric aperture (such as a 70 pixel radius aperture), there will be of order 2-4 pixels exhibiting RTN.
+The RTN may not be removed by jump detection algorithms if they are similar order of magnitude to the photon noise for a single pixel ($\sim$180 DN).
+If these are not identified, the RTN can contribute $\sim$200 counts in 4$\times 10^7$ or 5 ppm changes.
+
+\begin{figure*}
+\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{RTN Pixel} 
 \fig{{rc_placeholder.png}}{0.5\textwidth}{RC pixel}}

### 2019-12-04 ms.tex
replaced placeholder RC pixels plot
showing white noise comparison power spectrum to better illustrate what 1/f noise does

@@
 This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
-The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops roughly like a 1/f power law.
+The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops roughly like a 1/f power law in the power spectrum of the time series.
 Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
 To create the periodogram, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
+The periodogram shows many spikes at high frequency including one at the line reset time (the time to read out all the pixels in a row before moving to the next row).
 
@@
 \caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
-The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000, Hz.
+The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000 Hz.
+Above 1000 Hz, it is closer to white noise (green line) with spikes at specific frequencies.
 {\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal) on a dark frame.
@@
 \end{figure*}
+
+The 1/f noise can be reduced by subtracting reference pixels and/or active pixels over the aperture of interest.
+As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (ie.
+timescales longer than 100 cycles as measured in the 10$\mu$s time to address the pixels).
+Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
+NIRCam has a "GRISMC" grism that will disperse along the column direction but this mode would not allow stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
 
@@
 
-\begin{figure*}
-\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{RTN Pixel} 
-\fig{{rc_placeholder.png}}{0.5\textwidth}{RC pixel}}
+There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
+These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
+There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
+
+\begin{figure*}
+\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{RTN Pixels} 
+\fig{{example_rc.pdf}}{0.45\textwidth}{RC pixels}}
 \caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.

### 2019-12-05 ms.tex
a few small notes on 1/f stuff and RC pixels

@@
 The periodogram shows many spikes at high frequency including one at the line reset time (the time to read out all the pixels in a row before moving to the next row).
+The 1/f noise is compared to a simulated time series with the same robust standard deviation but with Gaussian white noise where each pixel is independent and identically distributed as a Gaussian.
+It is clear from Figure \ref{fig:pixelTSeriesPSpec} that the 1/f noise and the periodic signatures significantly increase the power over uncorrelated white noise (green line).
 
@@
 There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
-These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
+These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation (ie. applied a weight of zero in a weighted sum).
 There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
@@
 The pre-amplifier reset values are seen in the first principal component, and change from one group (one read in RAPID) to another.
-The principal components generally increase 
+The principal components generally increase in frequency with principal component number.
+In other words, the highest frequency principal components explain the least amount of the variance as would be expected for 1/f noise.
 }\label{fig:pcaEigenvectors}

### 2019-12-09 ms.tex
working on temperature offsets and correlations.
added results of temperature correlations

@@
 \clearpage
+\subsubsection{Box Temperature}
+The box temperature leads the flux variations by 4.9 minutes, likely due to the thermal delay between the box and the LED mounted to the box.
+
+\begin{figure*}
+{\gridline{\fig{azlab08_sub320_multiexp_temp_correlation.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
+\fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
+\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}
+\end{figure*}
+
+\clearpage
 \subsection{Reference Pixels versus No Reference Pixels}

### 2019-12-10 ms.tex
adding temperature corrections

@@
 \fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
-\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}
+\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}\label{fig:LEDTcorrelation}
+\end{figure*}
+
+\begin{figure*}
+{\gridline{\fig{azlab08_sub320_multiexp_corrected.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
+\fig{azlab08_sub320_lakeshore_tchange_corrected.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}\label{fig:LEDTcorrection}
+\caption{After removing the 4.9 hour time offset and a linear trend with temperature, the fluctuations are greatly reduced.}
 \end{figure*}

### 2019-12-14 ms.tex
more 1/f noise discussion

@@
 To create the periodogram, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
-The periodogram shows many spikes at high frequency including one at the line reset time (the time to read out all the pixels in a row before moving to the next row).
+The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
+
 The 1/f noise is compared to a simulated time series with the same robust standard deviation but with Gaussian white noise where each pixel is independent and identically distributed as a Gaussian.
-It is clear from Figure \ref{fig:pixelTSeriesPSpec} that the 1/f noise and the periodic signatures significantly increase the power over uncorrelated white noise (green line).
+It is clear from Figure \ref{fig:pixelTSeriesPSpec} that the 1/f noise and the periodic signatures significantly increase the power over uncorrelated white noise (green line) at low frequencies.
+1/f rises above the white noise level at 70 cycles / 1400 Hz for amplifier 1 and the intersection ranges from 70 to 135 across the 4 amplifiers.
 
@@
 {\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal) on a dark frame.
-The amplifier offsets have been removed, but the 1/f noise from these adjacent amplifiers shows different behavior.
+The amplifier offsets have been removed, but the 1/f noise from these adjacent amplifiers (separated at X=512) shows different behavior.
 }\label{fig:pixelTSeriesPSpec}
@@
 Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
-NIRCam has a "GRISMC" grism that will disperse along the column direction but this mode would not allow stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
+NIRCam has a "GRISMC" grism that will disperse along the column direction but this mode would not work with horizontal stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
+The benefits of a horizontal stripe subarray and a faster sampling rate must be weighed against the price of correlated 1/f noise along the spectrum that is not easily subtracted.
 
 \subsection{Fringing}
+
+The thin layer of NIRCam's HgCdTe detector can result in an interference pattern.
 

### 2019-12-14 ms.tex
updated the OTIS fringe search stuff

@@
 
-The thin layer of NIRCam's HgCdTe detector can result in an interference pattern.
+The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
+We investigate whether this can manifest itself on the spectrum with the NIRCam grism.
 
@@
 The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
-The sca
-A periodogram shows a peak near 19 pixels period, however, it is not an overwhelming periodic signature.
+A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
 \textcolor{red}{double check the scatter in spectrum to photon + read noise}
-\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum}
+\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
 }\label{fig:integratedOtisGrismSpec}

### 2019-12-15 ms.tex
fringing investigation from CV3 spectrum.

@@
 
+The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
+However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
+\textcolor{red}{\bf Is this fringing?}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
+\caption{The CV3 extracted spectrum shows dramatic structure.
+Is this fringing?}\label{fig:cv3ExtractedSpectrum}
+\end{figure}
+
 \subsection{Subpixel Crosshatching}

### 2019-12-17 ms.tex
showing the pointing simulation

@@
 
-\subsubsection{Crosshatch Modeling}
+\subsubsection{Crosshatch Pattern Modeling}
 We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
@@
 
-\subsubsection{Subpixel Crosshatching Simulation}\label{sec:CrosshatchSim}
+\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
 
@@
 This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
+
+\subsubsection{Time Series Simulation}
+The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
+The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointing}.
+
+\begin{figure*}
+\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Histograms} 
+\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Time Series} }
+\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
+Examples are shown for RTN and RC pixels.
+}\label{fig:tserPointing}
+\end{figure*}
 

### 2019-12-17 ms.tex
showing pointing series and zooms

@@
 \begin{figure*}
-\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Histograms} 
-\fig{example_rtn.pdf}{0.45\textwidth}{Pointing Time Series} }
-\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
-Examples are shown for RTN and RC pixels.
+\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
+\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
+\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
+}\label{fig:tserPointing}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
+\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
+\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
 }\label{fig:tserPointing}

### 2019-12-19 ms.tex
added plot with subpixel jitter simulation
describing the pointing simulation more with info about sources of pointing error.

@@
 
+The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
+These are moves are designed to keep the antenna pointing at ground-based Antennas for telemetry or data download.
+Fortunately, the errors due to High Gain Antenna moves damp quickly on $\lesssim$ 1 minute e-folding timescales.
+This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
+Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
+The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
+Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
+Therefore, the largest contributor to pointing variations will likely be
+
+\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
+
 \begin{figure*}
@@
 \caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
-}\label{fig:tserPointing}
+This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
+}\label{fig:tserPointingFull}
 \end{figure*}
@@
 \caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
-}\label{fig:tserPointing}
+}\label{fig:tserPointingZoom}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
+\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
+The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
+}\label{fig:tserPointingAndFlux}
 \end{figure*}

### 2019-12-20 ms.tex
a few minor edits/clarifications

@@
 Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
-To create the periodogram, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
+To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
+Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
 The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
@@
 The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
-The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointing}.
+The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
 

### 2019-12-21 ms.tex
added FPA small T change test showing clear correlation w/ detector temperature

@@
 The data are binned to show that there is no detectable persistence on 3000 second timescales.
-An arbitrary offset of 4$e^-$ is added on the short timescale plot to keep the values positive and possible to plot on a log scale.}\label{fig:persistenceAZlab04}
+An arbitrary offset of 4$e^-$/s is added on the short timescale plot to keep the values positive and possible to plot on a log scale.}\label{fig:persistenceAZlab04}
 \end{figure*}
@@
 \caption{After removing the 4.9 hour time offset and a linear trend with temperature, the fluctuations are greatly reduced.}
+\end{figure*}
+
+\subsubsection{Detector Temperature}
+
+\begin{figure*}
+{\gridline{\fig{individual_azlab08_sub320_multi_exp_fpat_dt.pdf}{0.98\textwidth}{}}}
+\caption{A small change of the FPA temperatures is inserted without heating up the box.
+The FPA temperature clearly correlates with flux, but has a different scaling with each detector.}\label{fig:fpaTChangeSmall}
 \end{figure*}

### 2019-12-30 ms.tex
updated spectra fig w/ axes labels
adding periodogram of spectra
false alarm probability for periodogram

@@
 \centering
-\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
-\caption{The CV3 extracted spectrum shows dramatic structure.
-Is this fringing?}\label{fig:cv3ExtractedSpectrum}
+\includegraphics[width=.49\columnwidth]{labLED_ind_spec_CV3NRCN036810.pdf}
+\includegraphics[width=.49\columnwidth]{labLED_spec_periodo_CV3NRCN036810.pdf}
+\caption{The CV3 extracted spectrum shows large structure.
+After normalizing, the periodogram shows a significant peak at a period of 37 pixels with a formal false alarm probability of $10^{-18}$.
+Is this fringing?
+There are also peaks at 1px and 20 px that are likely spurious.}\label{fig:cv3ExtractedSpectrum}
 \end{figure}

### 2019-12-31 ms.tex
added some more details on the subpixel crosshatch simulation

@@
 Is this fringing?
-There are also peaks at 1px and 20 px that are likely spurious.}\label{fig:cv3ExtractedSpectrum}
+There are also peaks at 1px and 20 px that are likely spurious aliases of the pixel grid.}\label{fig:cv3ExtractedSpectrum}
 \end{figure}
@@
 
-Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}
-Smooth functions, such as polynomials, with centroid position will likely 
+Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
+A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
+Alternatively, a Gaussian process regression could be applied.
 Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
@@
 The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
-These are moves are designed to keep the antenna pointing at ground-based Antennas for telemetry or data download.
-Fortunately, the errors due to High Gain Antenna moves damp quickly on $\lesssim$ 1 minute e-folding timescales.
+These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
+Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
 This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
@@
 Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
-Therefore, the largest contributor to pointing variations will likely be
+Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
 
@@
 \end{figure*}
+
+We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
+First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
+We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
+The resulting flux variations are very small compared to factors like the 1/f noise.
+The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
+Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
+Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
 

### 2019-12-31 ms.tex
fixed up the subgrism crosshatch fits

@@
 \begin{itemize}
-	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
-	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
+	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (0,0)
+	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (0,1983)
 	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
@@
 The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+The first position is the SUBGRISM64 subarray and the same field point that will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
+we exclude
 The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.

### 2020-01-02 ms.tex
explained the subgrism cutout positions better (and reminded myself again why one is at (4,5))

--- 2019-12-31 ms.tex
@@
 
-\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
-
-The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
-NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
-
-We simulate the effect of this jitter on NIRCam time series observations with the following steps:
-\begin{itemize}
-	\item Fit the existing flat field to a crosshatch model in the Fourier domain
-	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
-	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Multiply the PSF by the simulated flat field
-	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
-	\item Bin the simulated images into the native pixel size
-	\item Divide by the pixel-to-pixel flat field
-	\item Measure the relative flux with a photometric aperture
-\end{itemize}
-
-We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
-We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
-$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
-We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
-Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
-For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
-This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
-For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
-\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
-\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
-\caption{
-The steps of the sub-pixel crosshatch photometry simulation are shown here.
-We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
-This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
-A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
-Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
-The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
-}\label{fig:crossHatchSimPSF}
-\end{figure}
-
-We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
-\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
-We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
-We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
-This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
-
-We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
-The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
-For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
-These simulated operations represent pointing drift on the subpixel scale.
-
-We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
-The aperture is re-centered by the same position as the shift direction.
-For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
-While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
-The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
-\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
-\caption{
-The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
-Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
-The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
-These are correctable with smooth functions such as polynomials.
-}\label{fig:subpixScanSimulation}
-\end{figure}
-
-The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
-The amplitude of the flux changes is potentially up to 300 ppm.
-This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
-
-Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
-A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
-Alternatively, a Gaussian process regression could be applied.
-Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
-When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
-Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
-Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
-This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
-
-\subsubsection{Time Series Simulation}
-The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
-The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
-
-The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
-These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
-Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
-This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
-Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
-The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
-Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
-Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
-
-\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
-
-\begin{figure*}
-\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
-\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
-\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
-This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
-}\label{fig:tserPointingFull}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
-\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
-\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
-}\label{fig:tserPointingZoom}
-\end{figure*}
-
-We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
-First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
-We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
-The resulting flux variations are very small compared to factors like the 1/f noise.
-The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
-Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
-Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
-
-\begin{figure*}
-\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
-\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
-The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
-}\label{fig:tserPointingAndFlux}
-\end{figure*}
-
+\clearpage
 \subsubsection{Position of SubGrism Array}
@@
 On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
-We fit the crosshatch pattern to three regions of the detector:
-\begin{itemize}
-	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
-	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
+We fit the crosshatch pattern to three regions of the ALONG detector, which is the one used for the NIRCam grism time series mode:
+\begin{enumerate}
+	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (4,5) \label{subgrism64pos}
+	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (4,1984)
 	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
-\end{itemize}
+\end{enumerate}
 
 The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
+The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
+The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
 The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
-We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are anomalous.
 The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
@@
 
+\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
+
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
+NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
+
+We simulate the effect of this jitter on NIRCam time series observations with the following steps:
+\begin{itemize}
+	\item Fit the existing flat field to a crosshatch model in the Fourier domain
+	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
+	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Multiply the PSF by the simulated flat field
+	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
+	\item Bin the simulated images into the native pixel size
+	\item Divide by the pixel-to-pixel flat field
+	\item Measure the relative flux with a photometric aperture
+\end{itemize}
+
+We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
+$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
+We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
+Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
+For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
+This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
+For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
+\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
+\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
+\caption{
+The steps of the sub-pixel crosshatch photometry simulation are shown here.
+We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
+This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
+A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
+Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
+The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
+}\label{fig:crossHatchSimPSF}
+\end{figure}
+
+We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
+\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
+We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
+We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
+This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
+
+We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
+The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
+For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
+These simulated operations represent pointing drift on the subpixel scale.
+
+We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
+The aperture is re-centered by the same position as the shift direction.
+For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
+While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
+The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
+\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
+\caption{
+The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
+Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
+The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
+These are correctable with smooth functions such as polynomials.
+}\label{fig:subpixScanSimulation}
+\end{figure}
+
+The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
+The amplitude of the flux changes is potentially up to 300 ppm.
+This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
+
+Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
+A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
+Alternatively, a Gaussian process regression could be applied.
+Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
+When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
+Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
+Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
+This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
+
+\subsubsection{Time Series Simulation}
+The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
+The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
+
+The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
+These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
+Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
+This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
+Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
+The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
+Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
+Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
+
+\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
+
+\begin{figure*}
+\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
+\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
+\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
+This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
+}\label{fig:tserPointingFull}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
+\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
+\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
+}\label{fig:tserPointingZoom}
+\end{figure*}
+
+We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
+First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
+We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
+The resulting flux variations are very small compared to factors like the 1/f noise.
+The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
+Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
+Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
+
+\begin{figure*}
+\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
+\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
+The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
+}\label{fig:tserPointingAndFlux}
+\end{figure*}
+
 \clearpage
@@
 There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
-These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation (ie. applied a weight of zero in a weighted sum).
+These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
 There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.

### 2020-01-02 ms.tex
some edits to long dark section

@@
 The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-There are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+There are also dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).
@@
 However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
-Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row.
+Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row and the 4 amplifiers can exhibit different 1/f noise. 
 Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
@@
 If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
-This would be a very inefficient observations if the read noise dominated the $\sim$113 ppm photon noise.
-As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
+This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
+Fortunately, there are ways to significantly reduce the 1/f noise.
 

### 2020-01-08 ms.tex
dynamic spectra from OTIS test
fixing up dynamic spectrum
further updates to dynamic spectrum image, also including spec pipeline fixes
plotting representative spectrum and broadband time series

@@
 
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.79\textwidth}{Dynamic Spectrum}}
+\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Representative Spectrum}
+\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Broadband Time Series}}
+\caption{Dynamic spectrum with grism on the LW channel.
+}\label{fig:otisLWdynSpec}
+\end{figure*}
+
 \clearpage

### 2020-01-10 ms.tex
improved dynamic spec

--- 2020-01-02 ms.tex
@@
 
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.55\textwidth}{Dynamic Spectrum}
+\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Broadband Time Series}}
+%\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}
+%}
+\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes), that also show up in the integrated broadband time series.
+The effect of image motion along the dispersion direction is visible as broad stripes
+}\label{fig:otisLWdynSpec}
+\end{figure*}
+
 \clearpage

### 2020-01-11 ms.tex
showing comparisons w/ flat fielding of OTIS data

@@
 
-\subsubsection{Pass and a Half Grism Time Series Test}
+\subsubsection{Pass and a Half Grism Time Series Test - Photometry}
 The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
@@
 \end{figure*}
+
+\subsubsection{Pass and a Half Grism Time Series Test - Spectroscopy}
 
@@
 }\label{fig:otisLWdynSpec}
+\end{figure*}
+
+We also analyze the spectroscopic time series for the OTIS grism time series.
+The extracted spectrum and dynamic spectrum (how it varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
+Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.
+
+\begin{figure*}
+\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
+\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
+The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
+}\label{fig:otisLWflatVsNoFlat}
 \end{figure*}

### 2020-01-12 ms.tex
wavelength binned time series.

@@
 \gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
+\caption{The position variations along the dispersion direction cause large fluctuations in the time series.
+}\label{fig:otisLWflatVsNoFlat}
+\end{figure*}
+
+The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
+
+\begin{figure*}
+\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.55\textwidth}{}}
 \caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
 The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
-}\label{fig:otisLWflatVsNoFlat}
+}\label{fig:otisWavebinTSeries}
 \end{figure*}

### 2020-01-14 ms.tex
showing unaligned versus mostly aligned time series

@@
 \gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
+\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
+The crosshatch pattern is also 
+The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
+}\label{fig:otisLWflatVsNoFlat}
+\end{figure*}
+
+The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
+
+\begin{figure*}
+\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Time Series without Alignment}
+\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_aligned.pdf}{0.49\textwidth}{Time Series with Alignment}}
 \caption{The position variations along the dispersion direction cause large fluctuations in the time series.
-}\label{fig:otisLWflatVsNoFlat}
-\end{figure*}
-
-The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
-
-\begin{figure*}
-\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.55\textwidth}{}}
-\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
-The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
+These are dramatically reduced when cross-correlating and finding the peak to adjust for wavelength shifts
 }\label{fig:otisWavebinTSeries}

### 2020-01-18 ms.tex
showing the offsets along the dispersion direction.
showing LW + SW shifts simultaneously, which agree closely

@@
 	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
-	JWST's NIRCam instrument has very lower rates of persistence (<1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
 \end{itemize}
@@
 
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
-The aperture shifting appears to increase the flux errors with centroid shifts.
-}\label{fig:otisLWSWtserShift}
-\end{figure*}
-
 The locations of the subarrays have ROWCORNER=431.
@@
 We also analyze the spectroscopic time series for the OTIS grism time series.
-The extracted spectrum and dynamic spectrum (how it varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
+The extracted spectrum and dynamic spectrum (how each wavelength varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
 Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.
@@
 }\label{fig:otisWavebinTSeries}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{spec_offsets_o9LEDwf322w2Flat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{}}
+\caption{The position variations along the dispersion direction for this time series test are two orders of magnitude larger than expectation for flight.
+}\label{fig:otisWavebinTSeries}
+\end{figure*}
+
+\subsection{Using SW centroid for LW grism}
+
+We attempt to use the centroids form the SW imaging as input for a broadband grism aperture.
+This potentially provides a way to input centroid information without cross-correlating a spectrum.
+However, the SW centroids add more noise to the photometry as seen in Figure \ref{fig:otisLWSWtserShift}.
+\textcolor{red}{\bf Did I properly multiply shifts by -0.5?}
+
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
+\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
+The aperture shifting appears to increase the flux errors with centroid shifts.
+}\label{fig:otisLWSWtserShift}
 \end{figure*}
@@
 
-\appendix
-
 %\section{Extra Info}

### 2020-01-19 ms.tex
minor wording changes

@@
 
-\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
+\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
 
@@
 \caption{Time series of the simultaneous SW/LW Time Series Stability test
-\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
 }\label{fig:otisLWSWtser}
@@
 \caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
-The crosshatch pattern is also 
-The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
+There are small offsets in the flux os the spectrum also because of the flat field.
 }\label{fig:otisLWflatVsNoFlat}

### 2020-01-20 ms.tex
deleted the now duplicated dispersion offset figure and moved that caption info to the other figures

@@
 \gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Time series of the simultaneous SW/LW Time Series Stability test
+\caption{Time series of the simultaneous SW/LW Time Series Stability test.
+The image motion in this test due to vibrations and oscillations is two orders of magnitude larger than expeced in flight.
+The complicated PSF and low signal on the short wavelength channel compromise its sensitivity whereas the long wavelength broadband flux is dominated by lamp instability.
 }\label{fig:otisLWSWtser}
@@
 We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
-Figure \ref{fig:otisLWSWtserShift} shows the dramatic effect of subtracting the columns and rows from each aperture.
+Figure \ref{fig:otisLWcolrowSub} shows the dramatic effect of subtracting the columns and rows from each aperture.
 
@@
 Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
-}\label{fig:otisLWSWtserShift}
+}\label{fig:otisLWcolrowSub}
 \end{figure*}
@@
 These are dramatically reduced when cross-correlating and finding the peak to adjust for wavelength shifts
-}\label{fig:otisWavebinTSeries}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{spec_offsets_o9LEDwf322w2Flat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{}}
-\caption{The position variations along the dispersion direction for this time series test are two orders of magnitude larger than expectation for flight.
 }\label{fig:otisWavebinTSeries}

### 2020-01-20 ms.tex
updated dynamic spectrum w/ colorbrand F322W2 flat

@@
 %\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.55\textwidth}{Dynamic Spectrum}
-\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Broadband Time Series}}
+\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.58\textwidth}{Dynamic Spectrum}
+\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}}
 %\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}

### 2020-01-20 ms.tex
compare aligned versus un-aligned dynamic spectrum.

--- 2020-01-20 ms.tex
@@
 %\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.55\textwidth}{Dynamic Spectrum}
-\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Broadband Time Series}}
-%\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}
-%}
-\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes), that also show up in the integrated broadband time series.
-The effect of image motion along the dispersion direction is visible as broad stripes
+\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.49\textwidth}{Dynamic Spectrum}
+\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW_aligned}{0.49\textwidth}{Dynamic Spectrum with Alignment}}
+\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes).
+These are dramatically reduced when using cross correlation
 }\label{fig:otisLWdynSpec}
 \end{figure*}
+
+%\begin{figure*}
+%\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}
+%\end{figure*}
 
@@
 
+\clearpage
 \subsection{Using SW centroid for LW grism}

### 2020-02-03 ms.tex
small wording changes throughout

@@
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
-Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
+Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector.
+	These can be reduced with reference pixels or background subtraction.
 	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
 	Fortunately, the bias offset produces by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
-	This noise would  only become relevant when attempting to observe integrations of 1 group up the ramp.
+	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
@@
 \startdata
-Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
-Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
+%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
+%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
 CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
@@
 GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
-Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging & N\\
+Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole \& flood-illuminated imaging & N\\
 \enddata
@@
 \begin{itemize}
-	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
+	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
 	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
@@
 \begin{figure*}
+\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
+\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
+There are small offsets in the flux os the spectrum also because of the flat field.
+}\label{fig:otisLWflatVsNoFlat}
+\end{figure*}
+
+\begin{figure*}
 %\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
@@
 
-\begin{figure*}
-\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
-\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
-There are small offsets in the flux os the spectrum also because of the flat field.
-}\label{fig:otisLWflatVsNoFlat}
-\end{figure*}
-
 The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
@@
 }\label{fig:otisLWSWtserShift}
+\end{figure*}
+
+\subsection{Differential Spectrum}
+We investigate whether the lamp fluctuations can be removed by dividing by a signal-to-noise-weighted broadband time series.
+\begin{figure*}
+\gridline{\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_differential.pdf}{0.49\textwidth}{Differential Time series}}
+\caption{Differential time series
+}\label{fig:otisLWDiffdynSpec}
 \end{figure*}
@@
 In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
-While 1/f is highly correlated within an aperture and results in a large value.
+While 1/f is highly correlated within an aperture and results in a large value of noise per integration, the integrations are all statistically independent.
+Threfore, on 10 minute long timescales, the total noise of the readout electronics including 1/f and dark current in the aperture drops to 10 ppm.
 
@@
 	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
+	Fortunately, the pointing drifts are expected to be very small other than brief and infrequent High Gain Antenna moves, so the expected standard deviation of flux due to pointing jitter is only $\sim$ 6 ppm.
 	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.

### 2020-02-05 ms.tex
added figure for OTIS fringing
showing evidence for fringing in CV3 data

@@
 
-The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{fringing_grism_otis.pdf}
+\caption{The average OTIS spectrum over the time series grism test shows evidence for fringing.
+An illustrative sinusoidal function is plotted for comparison.
+}\label{fig:avgOtisGrismSpecFringing}
+\end{figure}
+
+The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec} and is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
 However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
@@
 There are also peaks at 1px and 20 px that are likely spurious aliases of the pixel grid.}\label{fig:cv3ExtractedSpectrum}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
+\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing.
+An illustrative sinusoidal function is plotted for comparison.
+}\label{fig:CV3GrismSpecFringing}
 \end{figure}

### 2020-02-06 ms.tex
more text and cleaning up of fringing section.

@@
 The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
-We investigate whether this can manifest itself on the spectrum with the NIRCam grism.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
-\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
-\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
-The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
-A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
-\textcolor{red}{double check the scatter in spectrum to photon + read noise}
-\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
-}\label{fig:integratedOtisGrismSpec}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{fringing_grism_otis.pdf}
-\caption{The average OTIS spectrum over the time series grism test shows evidence for fringing.
-An illustrative sinusoidal function is plotted for comparison.
-}\label{fig:avgOtisGrismSpecFringing}
-\end{figure}
-
-The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec} and is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
-However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
-\textcolor{red}{\bf Is this fringing?}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{labLED_ind_spec_CV3NRCN036810.pdf}
-\includegraphics[width=.49\columnwidth]{labLED_spec_periodo_CV3NRCN036810.pdf}
-\caption{The CV3 extracted spectrum shows large structure.
-After normalizing, the periodogram shows a significant peak at a period of 37 pixels with a formal false alarm probability of $10^{-18}$.
-Is this fringing?
-There are also peaks at 1px and 20 px that are likely spurious aliases of the pixel grid.}\label{fig:cv3ExtractedSpectrum}
-\end{figure}
+Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
+We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.
+
+Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
+The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
+The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
+The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
+The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
+These oscillations increase in frequency at longer wavelengths (X pixels).
+The variations have peak-to-valley amplitudes of about 10\%.
+However, we expect that the fringing structure will hold relatively constant during time so long as the pointing is stable at the sub-pixel level.
 
@@
 
+\subsection{Extracted Spectra and periodograms}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
+\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
+\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
+The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
+A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
+\textcolor{red}{In retrospect, this noise is due to the flat fielding, but averaging over many spectra with better flat fielding and some motion along the dispersion direction shows subtle fringing in Figure \ref{fig:avgOtisGrismSpecFringing}}
+}\label{fig:integratedOtisGrismSpec}
+\end{figure}
+
+The fringing is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{fringing_grism_otis.pdf}
+\caption{The average OTIS spectrum over the time series grism test shows evidence for fringing.
+An illustrative sinusoidal function is plotted for comparison.
+}\label{fig:avgOtisGrismSpecFringing}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{labLED_ind_spec_CV3NRCN036810.pdf}
+\includegraphics[width=.49\columnwidth]{labLED_spec_periodo_CV3NRCN036810.pdf}
+\caption{The CV3 extracted spectrum shows large structure.
+After normalizing, the periodogram shows a significant peak at a period of 37 pixels with a formal false alarm probability of $10^{-18}$.
+Is this fringing?
+There are also peaks at 1px and 20 px that are likely spurious aliases of the pixel grid.}\label{fig:cv3ExtractedSpectrum}
+\end{figure}
+
 %% To help institutions obtain information on the effectiveness of their 

### 2020-02-06 ms.tex
minor clarifications and fixes.

@@
 \includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
-\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing.
-An illustrative sinusoidal function is plotted for comparison.
+\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
+An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
 }\label{fig:CV3GrismSpecFringing}
@@
 We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
-This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the oscillations
+This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the position oscillations.
 For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.

### 2020-02-07 ms.tex
distinguishing box extaction for broadband test with spectrum test
updating to do list

@@
 In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
-Note that this experiment with result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
+Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
 We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
@@
 
+\clearpage
 \subsection{OTIS Tests}
@@
 We perform photometry on a single knot of emission as highlighted as the blue circular aperture.
-For the grism time series, we use a rectangular aperture and a vertically offset background box.
+For the grism time series broadband test, we use a rectangular aperture and a vertically offset background box.
 }\label{fig:otisPSFs}

### 2020-02-13 ms.tex
updating table with grism spec numbers

@@
 
-\begin{deluxetable*}{ccc}[b!]
-\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
+\begin{deluxetable*}{ccccc}[b!]
+\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummaryWLP8}
 \tabletypesize{\footnotesize}
@@
 \tablehead{
+\colhead{Aperture} &
+\multicolumn{2}{c}{WLP8} &
+\multicolumn{2}{c}{Grism 0.17 $\mu$m bin}\\
 \colhead{Noise Description} &
+\colhead{$\sigma$} &
+\colhead{$\sigma$} &
 \colhead{$\sigma$} &
@@
 \colhead{DN} &
-\colhead{ppm}\\
-}
+\colhead{ppm} &
+\colhead{DN} &
+\colhead{ppm}\\}
 \startdata
-Ideal Photon Noise & 4,400 & 113 \\
-Ideal Uncorrelated Read Noise & 1,300 & 33 \\
+Ideal Photon Noise & 4,400 & 113 & 1,520 & 364 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 & 510 & 120 \\
 \hline
-Measured Read Noise (no correction) & 23,500 & 600 \\
-Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
-Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
-Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
-Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
-Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
-Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 \\
-Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 \\
-Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
+Measured Read Noise (no correction) & 23,500 & 600 & & \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 & & \\
+Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
+Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 & & \\
+Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
+Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
+Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
+Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
+Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
 \enddata

### 2020-02-15 ms.tex
adding some scary correlated read noise values

@@
 Ideal Photon Noise & 4,400 & 113 & 1,520 & 364 \\
-Ideal Uncorrelated Read Noise & 1,300 & 33 & 510 & 120 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 & 470 & 113 \\
 \hline
@@
 Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 & & \\
+Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,100 & 1,705 \\
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\

### 2020-02-15 ms.tex
added some info on grism time series

@@
 
-\begin{deluxetable*}{ccccc}[b!]
+\begin{deluxetable*}{c|cc|cc}[b!]
 \tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummaryWLP8}
@@
 \enddata
-\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
-The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF.
+\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
+The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 4.2$\times 10^6$ DN during and integration for the grism PSF.
 The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).

### 2020-02-16 ms.tex
adding more numbers for grism aperture and 1/f noise

@@
 \hline
-Measured Read Noise (no correction) & 23,500 & 600 & & \\
-Measured Read Noise (reference pixel correction) & 10,800 & 280 & & \\
+Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 81,220 & 19,450  \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 & 12,900 & 3,090 \\
 Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,100 & 1,705 \\
+Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,120 & 1,705 \\
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\

### 2020-02-18 ms.tex
few tiny updates to grism ap 1/f noise sec

@@
 \begin{deluxetable*}{c|cc|cc}[b!]
-\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummaryWLP8}
+\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummary1overf}
 \tabletypesize{\footnotesize}
@@
 However, there are no side reference pixels or background regions available on the middle two amplifiers.
-Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
-Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
-Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
-For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
+Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.
+
+We give some illustrative numbers for a 0.17 $\mu$m wide bin of a grism spectrum as shown in Figure \ref{tab:noiseSummary1overf}.
+Without reference pixel subtraction, the grism apertures have standard deviations of 81,200 DN.
+Reference pixel subtraction drops this value to 12,900 DN and row-by-row subtraction drops it to 7,120 DN.
+For a well depth of 60\%, there are $4.2 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
 Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!

### 2020-02-18 ms.tex
more specifics on read noise with correct dispersion direction and smaller aperture

@@
 \startdata
-Ideal Photon Noise & 4,400 & 113 & 1,520 & 364 \\
-Ideal Uncorrelated Read Noise & 1,300 & 33 & 470 & 113 \\
+Ideal Photon Noise & 4,400 & 113 & 1,420 & 390 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 & 348 & 95 \\
 \hline
-Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 81,220 & 19,450  \\
-Measured Read Noise (reference pixel correction) & 10,800 & 280 & 12,900 & 3,090 \\
+Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 77,600 & 21,200  \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,640 & 2,640 \\
 Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,120 & 1,705 \\
+Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,630 & 992 \\
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
@@
 \tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
-The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 4.2$\times 10^6$ DN during and integration for the grism PSF.
-The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
+The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
+The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
 The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
@@
 
-We give some illustrative numbers for a 0.17 $\mu$m wide bin of a grism spectrum as shown in Figure \ref{tab:noiseSummary1overf}.
-Without reference pixel subtraction, the grism apertures have standard deviations of 81,200 DN.
-Reference pixel subtraction drops this value to 12,900 DN and row-by-row subtraction drops it to 7,120 DN.
-For a well depth of 60\%, there are $4.2 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
+We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.25 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
+Without reference pixel subtraction, the grism apertures have standard deviations of 77,600 DN.
+Reference pixel subtraction drops this value to 9,640 DN and row-by-row subtraction drops it to 3,630 DN.
+For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,420 DN assuming a gain of 1.84.
 Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
-Expressed in ppm, the read noise after processing with row-by-row subtraction is 90 ppm as compared to a photon noise of 74 ppm for a CDS subtraction (2 groups in ramp).
+Expressed in ppm, the read noise after processing with row-by-row subtraction is 990 ppm as compared to a photon noise of 95 ppm for a CDS subtraction (2 groups in ramp).
+
+Given the high 1/f read noise, it is important to maximize the number of samples up the ramp.
+The read noise averages down like $\sqrt{N}$ statistics (ie. each read can be assumed independent and identically distributed).
+Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 13 reads to average per integration.
+For RAPID and BRIGHT1 modes, there should therefore be 13 groups and for BRIGHT2, there should be at least 7 groups (of 2 frames each).
+This would make the photon noise about equal to the read noise but ideally the read noise should be a small fraction of the photon noise.
 

### 2020-02-25 ms.tex
added a note on using a small aperture to reduce 1/f noise

@@
 
+\clearpage
 \subsection{Subpixel Crosshatching}
@@
 The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
-However, there are no side reference pixels or background regions available on the middle two amplifiers.
+However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
 Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.
@@
 \end{figure*}
+
+Given the high level of correlation between pixels, another way to reduce 1/f noise is with a small aperture.
+For example, a 15 pixel wide aperture results in measured read noise of 990 ppm for the same 0.17$\mu$m wide bin centered at 4.25$\mu$m whereas a 3 pixel wide aperture results in a measured read noise of 290 ppm, which is below the expected photon noise.
+For a one pixel wide aperture, the measured read noise is only 230 ppm.
+Of course such small apertures will be subject to other losses by missing so much of the PSF.
+Therefore, the spectroscopic pipeline should either use a small aperture or provide extra weights to the brightest pixels such as in optimal extraction \citep[e.g.][]{horne1986optimalE}.
+If one calculates the weights to the spectra simply by the signal-to-noise while assuming each pixel's noise is independent, the weights are not heavy enough for the brightest pixels.
+Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights
 

### 2020-03-06 ms.tex
Updates from Overleaf

--- 2020-02-18 ms.tex
@@
 
-\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
+\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
 
@@
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
-Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector.
-	These can be reduced with reference pixels or background subtraction.
+Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
 	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
 	Fortunately, the bias offset produces by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
-	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).
+	This noise would  only become relevant when attempting to observe integrations of 1 group up the ramp.
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
@@
 	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
-	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+	JWST's NIRCam instrument has very lower rates of persistence (<1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
 \end{itemize}
@@
 The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
-Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
-We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.
-
-Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
-The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
-The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
-The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
-The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
-These oscillations increase in frequency at longer wavelengths (X pixels).
-The variations have peak-to-valley amplitudes of about 10\%.
-However, we expect that the fringing structure will hold relatively constant during time so long as the pointing is stable at the sub-pixel level.
+We investigate whether this can manifest itself on the spectrum with the NIRCam grism.
 
@@
 \centering
-\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
-\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
-An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
-}\label{fig:CV3GrismSpecFringing}
+\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
+\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
+\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
+The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
+A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
+\textcolor{red}{double check the scatter in spectrum to photon + read noise}
+\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
+}\label{fig:integratedOtisGrismSpec}
+\end{figure}
+
+The fringing doesn't show up in the OTIS spectrum from Figure \ref{fig:integratedOtisGrismSpec}, probably because of the broad PSF.
+However, the CV3 image in Figure \ref{fig:cv3ExtractedSpectrum} shows a lot of structure in the spectrum.
+\textcolor{red}{\bf Is this fringing?}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{fringing_placeholder.png}
+\caption{The CV3 extracted spectrum shows dramatic structure.
+Is this fringing?}\label{fig:cv3ExtractedSpectrum}
 \end{figure}
@@
 
-\clearpage
+\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
+
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
+NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
+
+We simulate the effect of this jitter on NIRCam time series observations with the following steps:
+\begin{itemize}
+	\item Fit the existing flat field to a crosshatch model in the Fourier domain
+	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
+	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Multiply the PSF by the simulated flat field
+	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
+	\item Bin the simulated images into the native pixel size
+	\item Divide by the pixel-to-pixel flat field
+	\item Measure the relative flux with a photometric aperture
+\end{itemize}
+
+We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
+$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
+We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
+Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
+For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
+This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
+For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
+\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
+\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
+\caption{
+The steps of the sub-pixel crosshatch photometry simulation are shown here.
+We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
+This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
+A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
+Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
+The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
+}\label{fig:crossHatchSimPSF}
+\end{figure}
+
+We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
+\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
+We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
+We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
+This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
+
+We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
+The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
+For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
+These simulated operations represent pointing drift on the subpixel scale.
+
+We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
+The aperture is re-centered by the same position as the shift direction.
+For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
+While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
+The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
+\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
+\caption{
+The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
+Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
+The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
+These are correctable with smooth functions such as polynomials.
+}\label{fig:subpixScanSimulation}
+\end{figure}
+
+The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
+The amplitude of the flux changes is potentially up to 300 ppm.
+This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
+
+Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}
+Smooth functions, such as polynomials, with centroid position will likely 
+Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
+When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
+Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
+Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
+This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
+
+\subsubsection{Time Series Simulation}
+The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not fully corrected by the reaction wheels.
+The JWST attitude control system team provided a simulation of the expected ``line of sight'' pointing performance shown in Figure \ref{fig:tserPointingFull}.
+The line of sight pointing does not include thermal expansion and contraction between instruments that occurs on $\sim$hour long timescales.
+The simulation also ignored high frequency ($>$1 Hz) that would blur the PSF but not affect the integration-to-integration time series behavior.
+Typical time series integrations are $\sim$ 10 to $\sim$100 seconds in duration.
+The transit durations are of order $\sim$1-3 hours.
+
+The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
+These moves are designed to keep the antenna pointing at ground-based stations for telemetry or data download.
+Fortunately, the errors due to High Gain Antenna moves damp quickly on $\lesssim$ 1 minute e-folding timescales.
+This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
+Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
+The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
+Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
+Therefore, the largest contributor to pointing variations will likely be thermal expansion and contraction between JWST instruments.
+
+\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
+
+\begin{figure*}
+\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
+\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
+\caption{The line of sight pointing motion is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
+This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
+}\label{fig:tserPointingFull}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
+\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
+\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
+}\label{fig:tserPointingZoom}
+\end{figure*}
+
+\begin{figure*}
+\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
+\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
+The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
+}\label{fig:tserPointingAndFlux}
+\end{figure*}
+
 \subsubsection{Position of SubGrism Array}
@@
 On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
-We fit the crosshatch pattern to three regions of the ALONG detector, which is the one used for the NIRCam grism time series mode:
-\begin{enumerate}
-	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (4,5) \label{subgrism64pos}
-	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (4,1984)
+We fit the crosshatch pattern to three regions of the detector:
+\begin{itemize}
+	\item The 2048$\times$64 SUBGRISM64 nominal position at the bottom of the array. Bottom Left corner is (0,0)
+	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector. Bottom Left corner is (0,1983)
 	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
-\end{enumerate}
+\end{itemize}
 
 The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
-We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
-The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
-The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
 The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are anomalous.
 The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
@@
 
-\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
-
-The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
-NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
-
-We simulate the effect of this jitter on NIRCam time series observations with the following steps:
-\begin{itemize}
-	\item Fit the existing flat field to a crosshatch model in the Fourier domain
-	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
-	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Multiply the PSF by the simulated flat field
-	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
-	\item Bin the simulated images into the native pixel size
-	\item Divide by the pixel-to-pixel flat field
-	\item Measure the relative flux with a photometric aperture
-\end{itemize}
-
-We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
-We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
-$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
-We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
-Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
-For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
-This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
-For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
-\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
-\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
-\caption{
-The steps of the sub-pixel crosshatch photometry simulation are shown here.
-We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
-This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
-A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
-Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
-The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
-}\label{fig:crossHatchSimPSF}
-\end{figure}
-
-We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
-\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
-We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
-We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
-This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
-
-We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
-The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
-For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
-These simulated operations represent pointing drift on the subpixel scale.
-
-We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
-The aperture is re-centered by the same position as the shift direction.
-For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
-While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
-The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
-\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
-\caption{
-The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
-Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
-The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
-These are correctable with smooth functions such as polynomials.
-}\label{fig:subpixScanSimulation}
-\end{figure}
-
-The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
-The amplitude of the flux changes is potentially up to 300 ppm.
-This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
-
-Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
-A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
-Alternatively, a Gaussian process regression could be applied.
-Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
-When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
-Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
-Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
-This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
-
-\subsubsection{Time Series Simulation}
-The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
-The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
-
-The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
-These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
-Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
-This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
-Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
-The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
-Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
-Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
-
-\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
-
-\begin{figure*}
-\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
-\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
-\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
-This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
-}\label{fig:tserPointingFull}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
-\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
-\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
-}\label{fig:tserPointingZoom}
-\end{figure*}
-
-We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
-First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
-We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
-The resulting flux variations are very small compared to factors like the 1/f noise.
-The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
-Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
-Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
-
-\begin{figure*}
-\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
-\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
-The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
-}\label{fig:tserPointingAndFlux}
-\end{figure*}
-
 \clearpage
@@
 The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-There are also dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+There are dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).
@@
 \startdata
-%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
-%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
+Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
+Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
 CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
@@
 GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
-Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole \& flood-illuminated imaging & N\\
+Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole flood-illuminated imaging & N\\
 \enddata
@@
 However, the 1/f noise that correlates along the fast-read (X) direction is more difficult to remove with reference pixels.
-Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row and the 4 amplifiers can exhibit different 1/f noise. 
+Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row.
 Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
@@
 If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
-This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
-Fortunately, there are ways to significantly reduce the 1/f noise.
-
-\begin{deluxetable*}{c|cc|cc}[b!]
-\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummary1overf}
+This would be a very inefficient observations if the read noise dominated the $\sim$113 ppm photon noise.
+As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
+
+\begin{deluxetable*}{ccc}[b!]
+\tablecaption{Summary of Noise Sources in Weak Lens +8 Aperture Dark Test}\label{tab:noiseSummaryWLP8}
 \tabletypesize{\footnotesize}
@@
 \tablehead{
-\colhead{Aperture} &
-\multicolumn{2}{c}{WLP8} &
-\multicolumn{2}{c}{Grism 0.17 $\mu$m bin}\\
 \colhead{Noise Description} &
-\colhead{$\sigma$} &
-\colhead{$\sigma$} &
 \colhead{$\sigma$} &
@@
 \colhead{DN} &
-\colhead{ppm} &
-\colhead{DN} &
-\colhead{ppm}\\}
+\colhead{ppm}\\
+}
 \startdata
-Ideal Photon Noise & 4,400 & 113 & 1,520 & 364 \\
-Ideal Uncorrelated Read Noise & 1,300 & 33 & 470 & 113 \\
+Ideal Photon Noise & 4,400 & 113 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 \\
 \hline
-Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 81,220 & 19,450  \\
-Measured Read Noise (reference pixel correction) & 10,800 & 280 & 12,900 & 3,090 \\
-Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 7,120 & 1,705 \\
-Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
-Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
-Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
-Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
-Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
+Measured Read Noise (no correction) & 23,500 & 600 \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 \\
+Measured Read Noise (reference channel subtraction) & 9,700 & 250 \\
+Measured Read Noise (row-by-row median subtraction) & 6,000 & 150 \\
+Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 \\
+Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 \\
+Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 \\
+Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 \\
+Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 \\
 \enddata
-\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
-The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 4.2$\times 10^6$ DN during and integration for the grism PSF.
+\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 Time Series.
+The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF.
 The noise is the sum within a 70 pixel radius source aperture and 75 to 100 pixel background aperture (in DN) or relative to the photon signal (in ppm).
@@
 In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
-Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
+Note that this experiment with result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
 We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
@@
 However, there are no side reference pixels or background regions available on the middle two amplifiers.
-Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.
-
-We give some illustrative numbers for a 0.17 $\mu$m wide bin of a grism spectrum as shown in Figure \ref{tab:noiseSummary1overf}.
-Without reference pixel subtraction, the grism apertures have standard deviations of 81,200 DN.
-Reference pixel subtraction drops this value to 12,900 DN and row-by-row subtraction drops it to 7,120 DN.
-For a well depth of 60\%, there are $4.2 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
+Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
+Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
+Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
+For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
 Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
@@
 \begin{itemize}
-	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
+	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read noise)
 	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
@@
 
-\clearpage
 \subsection{OTIS Tests}
@@
 
-\subsubsection{Pass and a Half Grism Time Series Test - Photometry}
+\subsubsection{Pass and a Half Grism Time Series Test}
 The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
@@
 We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
-This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the position oscillations.
+This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the oscillations
 For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
@@
 We perform photometry on a single knot of emission as highlighted as the blue circular aperture.
-For the grism time series broadband test, we use a rectangular aperture and a vertically offset background box.
+For the grism time series, we use a rectangular aperture and a vertically offset background box.
 }\label{fig:otisPSFs}
@@
 \gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Time series of the simultaneous SW/LW Time Series Stability test.
-The image motion in this test due to vibrations and oscillations is two orders of magnitude larger than expeced in flight.
-The complicated PSF and low signal on the short wavelength channel compromise its sensitivity whereas the long wavelength broadband flux is dominated by lamp instability.
+\caption{Time series of the simultaneous SW/LW Time Series Stability test
+\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
 }\label{fig:otisLWSWtser}
+\end{figure*}
+
+\begin{figure*}
+%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
+\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
+\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
+The aperture shifting appears to increase the flux errors with centroid shifts.
+}\label{fig:otisLWSWtserShift}
 \end{figure*}
@@
 We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
-Figure \ref{fig:otisLWcolrowSub} shows the dramatic effect of subtracting the columns and rows from each aperture.
+Figure \ref{fig:otisLWSWtserShift} shows the dramatic effect of subtracting the columns and rows from each aperture.
 
@@
 Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
-}\label{fig:otisLWcolrowSub}
-\end{figure*}
-
-\subsubsection{Pass and a Half Grism Time Series Test - Spectroscopy}
-
-\begin{figure*}
-\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
-\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
-There are small offsets in the flux os the spectrum also because of the flat field.
-}\label{fig:otisLWflatVsNoFlat}
-\end{figure*}
-
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.49\textwidth}{Dynamic Spectrum}
-\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW_aligned}{0.49\textwidth}{Dynamic Spectrum with Alignment}}
-\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes).
-These are dramatically reduced when using cross correlation
-}\label{fig:otisLWdynSpec}
-\end{figure*}
-
-%\begin{figure*}
-%\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}
-%\end{figure*}
-
-We also analyze the spectroscopic time series for the OTIS grism time series.
-The extracted spectrum and dynamic spectrum (how each wavelength varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
-Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.
-
-The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
-
-\begin{figure*}
-\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Time Series without Alignment}
-\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_aligned.pdf}{0.49\textwidth}{Time Series with Alignment}}
-\caption{The position variations along the dispersion direction cause large fluctuations in the time series.
-These are dramatically reduced when cross-correlating and finding the peak to adjust for wavelength shifts
-}\label{fig:otisWavebinTSeries}
-\end{figure*}
-
-\clearpage
-\subsection{Using SW centroid for LW grism}
-
-We attempt to use the centroids form the SW imaging as input for a broadband grism aperture.
-This potentially provides a way to input centroid information without cross-correlating a spectrum.
-However, the SW centroids add more noise to the photometry as seen in Figure \ref{fig:otisLWSWtserShift}.
-\textcolor{red}{\bf Did I properly multiply shifts by -0.5?}
-
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
-The aperture shifting appears to increase the flux errors with centroid shifts.
 }\label{fig:otisLWSWtserShift}
-\end{figure*}
-
-\subsection{Differential Spectrum}
-We investigate whether the lamp fluctuations can be removed by dividing by a signal-to-noise-weighted broadband time series.
-\begin{figure*}
-\gridline{\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_differential.pdf}{0.49\textwidth}{Differential Time series}}
-\caption{Differential time series
-}\label{fig:otisLWDiffdynSpec}
 \end{figure*}
@@
 In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
-While 1/f is highly correlated within an aperture and results in a large value of noise per integration, the integrations are all statistically independent.
-Threfore, on 10 minute long timescales, the total noise of the readout electronics including 1/f and dark current in the aperture drops to 10 ppm.
+While 1/f is highly correlated within an aperture and results in a large value.
 
@@
 	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
-	Fortunately, the pointing drifts are expected to be very small other than brief and infrequent High Gain Antenna moves, so the expected standard deviation of flux due to pointing jitter is only $\sim$ 6 ppm.
 	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.
@@
 
-\subsection{Extracted Spectra and periodograms}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
-\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
-\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
-The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
-A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
-\textcolor{red}{In retrospect, this noise is due to the flat fielding, but averaging over many spectra with better flat fielding and some motion along the dispersion direction shows subtle fringing in Figure \ref{fig:avgOtisGrismSpecFringing}}
-}\label{fig:integratedOtisGrismSpec}
-\end{figure}
-
-The fringing is very subtle in Figure \ref{fig:avgOtisGrismSpecFringing}, probably because of the broad PSF.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{fringing_grism_otis.pdf}
-\caption{The average OTIS spectrum over the time series grism test shows evidence for fringing.
-An illustrative sinusoidal function is plotted for comparison.
-}\label{fig:avgOtisGrismSpecFringing}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{labLED_ind_spec_CV3NRCN036810.pdf}
-\includegraphics[width=.49\columnwidth]{labLED_spec_periodo_CV3NRCN036810.pdf}
-\caption{The CV3 extracted spectrum shows large structure.
-After normalizing, the periodogram shows a significant peak at a period of 37 pixels with a formal false alarm probability of $10^{-18}$.
-Is this fringing?
-There are also peaks at 1px and 20 px that are likely spurious aliases of the pixel grid.}\label{fig:cv3ExtractedSpectrum}
-\end{figure}
-
 %% To help institutions obtain information on the effectiveness of their 
@@
 
+\appendix
+
 %\section{Extra Info}

### 2020-03-09 ms.tex
added covariance weighted formulae and reference.

--- 2020-02-25 ms.tex
@@
 Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
+Measured Read Noise (profile-weighted summation)	& & & 1,310 & 355 \\
 \enddata
@@
 If one calculates the weights to the spectra simply by the signal-to-noise while assuming each pixel's noise is independent, the weights are not heavy enough for the brightest pixels.
-Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights
+This is because the observations will largely be in the foreground limit (where the variance is equal to the number of photons), where weighting by the profile for pixel $j$ (P$_j$) divided by the variance (V$_i$) becomes
+\begin{equation}
+w_j = P_j / V_j = N_{ph} / N_{ph} = 1.0,
+\end{equation}
+where $N_{ph}$ is the number of photons on that pixel.
+
+However, if one generalizes the weighted average to a covariance matrix \citep{schmelling1995averagingCorrelatedData}, the weights become,
+\begin{equation}
+w_j = \sum_{i=1}^{m} \left( C^{-1}\right)_{ij} P_j,\label{eq:covarianceWeighted}
+\end{equation}
+where $C^{-1}$ is the inverse of the covariance matrix between pixels $i$ and $j$ and $m$ is the number of pixels in the summation.
+Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights.
+If we assume the read noise is perfectly correlated along the spectral direction and uncorrelated along the spatial direction, then equation \ref{eq:covarianceWeighted} becomes
+\begin{equation}
+w_j = \frac{P_j}{N_{ph} + N_{px} \sigma_R^2},
+\end{equation}
+where $N_{px}$ is the number of spectral pixels that will be binned and $\sigma_R$ is the read noise per pixel.
+Thus, for large values of $N_{px}$ (up to 512 for an amplifier), the $\sigma_R \approx 14e^-$ of read noise per pixel, can compound to 100,400 e$^e-$ and the weighting approaches
+\begin{equation}
+w_j \propto P_j.
+\end{equation}
+Profile weighting should therefore lower the error on wavelength-binned time series.
+For the grism aperture experiment, we find that profile weighting gives a measured read noise of 355 ppm.
 

### 2020-03-12 ms.tex
spectral and spatial covariances

@@
 
+\subsubsection{Empirical Covariance Matrix}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
+\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpeSpatial}
+\end{figure}
+
 %% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
@@
 Therefore, the corrected read noise per integration should be:
-\begin{equation}\label{bestRNCorrection}
+\begin{equation}\label{eq:bestRNCorrection}
 RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}
@@
 \textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}
+
+\subsubsection{Impact to Grism Time series}
+We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
+In this case, we assume row-by-row subtraction is performed and that the CDS noise from the OTIS ground-based test is representative of flight.
+Then, the equivalent grism aperture noise to equation \ref{eq:bestRNCorrection} is
+\begin{equation}
+RN_{grism,0.17\mu\mathrm{m}} = \frac{5,130 DN}{ \sqrt{N_{frames}}}.
+\end{equation}
+For the grism aperture
 

### 2020-03-12 ms.tex
more studies of read noise covariance matrix and optimal weighting

@@
 where $N_{px}$ is the number of spectral pixels that will be binned and $\sigma_R$ is the read noise per pixel.
-Thus, for large values of $N_{px}$ (up to 512 for an amplifier), the $\sigma_R \approx 14e^-$ of read noise per pixel, can compound to 100,400 e$^e-$ and the weighting approaches
+Thus, for large values of $N_{px}$ (up to 512 for an amplifier), the $\sigma_R \approx 14e^-$ of read noise per pixel, can compound to 100,400 e$^-$ and the weighting approaches
 \begin{equation}
@@
 For the grism aperture experiment, we find that profile weighting gives a measured read noise of 355 ppm.
-
-\subsubsection{Empirical Covariance Matrix}
+Thus, profile weighting still does not reduce the standard deviation over an extraction aperture that is just 1 pixel wide at the peak grism flux.
+We show the real covariance matrix in Section \ref{sec:empCovarianceMatrix}.
+
+\subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
+The ideal weighting of the spectrum from Equation \ref{eq:covarianceWeighted} depends on the covariance matrix $C_{ij}$.
+We use CDS (correlated double sampling) read pairs of OTIS long dark data (108 frames) with reference pixel corrections to estimate $C_{ij}$.
+We consider a wavelength bin that is 100 pixels in the dispersion direction (0.1$\mu$m) and 14 spatial spatial pixels.
+Figure \ref{fig:covSpecSpatial} shows the covariance matrix of this wavelength bin, taken from the median of 20 regions of the detector.
+The diagonal elements are consistent with NIRCam detector performance with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
+It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance nearly uniformly at 36~$(e^-)^2$.
+Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$16 $(e^-)^2$ that falls off to $\sim 10 (e^-)^2$.
 
@@
 \includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
-\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpeSpatial}
+\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpecSpatial}
 \end{figure}

### 2020-03-14 ms.tex
updates to abstract and known detector effects

@@
 We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector lab.
-
+Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
+Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
+Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
+In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
+Future performance tests during commissioning and the early release science will still be needed to assess the noise floor on stars, which are more stable than the available LED lamps used in lab-based tests.
 \end{abstract}
@@
 The NIRCam grism mode will collect moderate resolution R$\sim$1100-1700 spectra over the wavelength range from 2.4 to 5.0~$\mu$m.
-This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
+This grism mode can be used simultaneously with short wavelength weak lens imaging or (in future cycles) the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
 If it becomes an approved and implemented mode, the DHS will permit spectroscopy simultaneous from 1.0 to 2.0~$\mu$m because of a dichroic beamsplitter that divides the light from NIRCam into two different channels.
@@
 \begin{itemize}[noitemsep]
-	\item \textbf{Pre-amp reset offsets:} (an Asic-related effect) 
+	\item \textbf{Pre-amplifier reset offsets:} (an Asic-related effect) 
 The resets cause discontinuities in the pedestal level of all pixels between frames.
 Pre-amp resets can also appear in slope images (DN/second) because NIRCam's amplifiers are reset once per frame (not once per integration).
-This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can.
+This is an effect where averaging over more pixels does not decrease the noise, but reference pixel or background subtraction can efficiently remove the pre-amp offsets.
 These are discussed further in Section \ref{sec:preAmp}.
@@
 Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
-	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Add more details and citations}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
+	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Is there a good citation?}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
@@
 	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
-	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
 \end{itemize}
@@
 The timescales for pre-amp resets are relevant to exoplanet time series, which have transit durations of $\sim$0.5 to 3 hours for typical targets.
-However, reference pixel subtraction can efficiently remove pre-amp drifts, so with proper data reduction and subarrays that include reference pixels, the pre-amp drifts can be dramatically reduced.
-It is also likely that background subtraction can mitigate the pre-amp reset offsets from time series integrations.
-The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are saved with active pixels.
+However, reference pixel subtraction or background subtraction can efficiently remove pre-amp drifts, so with proper data reduction, the pre-amp drifts can be effectively eliminated.
+The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are saved with active pixels, so reference pixels will always be available for the grism.
 
@@
 The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7 seconds in duration).
-These pre-amp resets per frame causes discontinuities over every frame within an integration, but there is an upside:
-Over long timescales (10$^3$ seconds), these resets pre-amp resets will keep the bias drifts hovering around zero without any long slopes or drifts.
-This is helpful in keeping the detector counts below the 65,536 DN saturation limit and thus pre-amp resets permit a larger usable well depth over the counts from 0 to 65,536 DN.
-Without pre-amp resets, the counts in a detector could potentially drift towards 65,536 DN and shrinks the usable well depth.
+Fortunately, the pixels within an amplifier move together, so reference pixel subtraction or background subtraction will efficiently remove the offsets.
+%These pre-amp resets per frame causes discontinuities over every frame within an integration, but there is an upside:
+%Over long timescales (10$^3$ seconds), these resets pre-amp resets will keep the bias drifts hovering around zero without any long slopes or drifts.
+%This is helpful in keeping the detector counts below the 65,536 DN saturation limit and thus pre-amp resets permit a larger usable well depth over the counts from 0 to 65,536 DN.
+%Without pre-amp resets, the counts in a detector could potentially drift towards by thousands of DN and shrink the usable well depth.
 
@@
 This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
+Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in APT.
 On the flip side, the four amplifiers will have different behaviors such as offsets in the bias level.
 The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
-If a spectrum of a source is extracted without any vertical background extraction, the amplifier offsets cause sharp discontinuities in the summed spectrum.
-
-Fortunately, the amplifier offsets are efficiently removed by reference pixels.
-For example, we subtract the median of the 4 reference pixels from each column and this efficiently removes the bias signal from each amplifier shown in Figure \ref{fig:ampOffsetsOtisGrismSlope} (middle panel and bottom panel).
+If a spectrum of a source is extracted without any vertical background extraction or reference pixel correction, the amplifier offsets cause sharp discontinuities in the summed spectrum.
+
+Fortunately, the amplifier offsets are efficiently removed by reference pixels and background subtraction.
+For example, subtracting the average reference pixel in each amplifier will reduce the offsets between amplifiers, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (second from top panel).
 It should be noted, however, that there are gradients in the bias signal within each amplifier.
-If we simply subtract the median value of all reference pixels within an amplifier without applying them on a per-column basis, there are still discontinuities in the spectrum.
-In addition to reference pixels, background subtraction along each column removes the amplifier boundary effect.
-If the boundaries somehow proved to be an issue for time series spectra, the WINDOW subarray mode, which uses a single amplifier (at the cost of 4 times the frame time) is an option.
+One could subtract the mean reference pixel in each column to reduce these gradients, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (third fro top panel) but given that there are only 4 reference pixels at the bottom of each column, this introduces extra noise in the subtraction.
+Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
 
@@
 This is visible when examining the time series of pixels as they are read out within a frame in the order they are addressed.\footnote{See a diagram of the readout directions at \url{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-instrumentation/nircam-detector-overview/nircam-detector-readout}}
-The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops roughly like a 1/f power law in the power spectrum of the time series.
+The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
 Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
@@
 Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
-NIRCam has a "GRISMC" grism that will disperse along the column direction but this mode would not work with horizontal stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
-The benefits of a horizontal stripe subarray and a faster sampling rate must be weighed against the price of correlated 1/f noise along the spectrum that is not easily subtracted.
+NIRCam has a ``GRISMC" grism that will disperse along the column direction but this mode would not work with horizontal stripe subarrays and would therefore saturate on bright targets with $K \lesssim 5.5$.
+For this reason, the ``GRISMC'' is not currently available for time series observations.
 
@@
 These oscillations increase in frequency at longer wavelengths (X pixels).
-The variations have peak-to-valley amplitudes of about 10\%.
-However, we expect that the fringing structure will hold relatively constant during time so long as the pointing is stable at the sub-pixel level.
+The variations have peak-to-valley amplitudes of about 8\%.
+However, we expect that the fringing structure will hold relatively constant during time due to the temperature stability of the instrument.
 
@@
 The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
-One possible projection of a zincblende structure is shown in Figure \ref{fig:crossHatchA5}.
-In this perspective, the projected bond angles are 44.4$\degree$, 67.8$\degree$ and 67.8$\degree$.
-These surface topological variations with crosshatch patterns are likely related to the observed patterns in the flat fields, which appear as quantum efficiency variations.
-We deduce that the crosshatch pattern is mostly likely related to the crystal lattice structure of the HgCdTe substrate and not the pixel circuitry.
+A projection of zincblende structure is shown in Figure \ref{fig:crossHatchA5} relative to the observed crosshatch patterns.
+The similarity between the crosshatch patterns in the flat field and the topological variations observed in \citet{chang2008surfaceMorphologyHgCdTe} leads to the likely conclusion that the surface variations lead to quantum efficiency variations.
+Thus, the crosshatch pattern is mostly likely related to the crystal lattice structure of the HgCdTe substrate and not the pixel circuitry.
 
@@
 Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$) onto the [211] miller plane.
+These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
 }\label{fig:crossHatchA5}
@@
 This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
-\textcolor{red}{Can we justify this more?}
+\textcolor{red}{Can we justify this more? I thought it would be pixels$^2$}
 
@@
 for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e_b=0.26 \pm 0.01$ px$^{-1}$.
+In other words, the separations between the vectors are $67.699 \degree, 67.831 \degree$, and $44.470 \degree$.
 The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
@@
 Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
-The primary crosshatch tends to be aligned closely, but no exactly, with either the X or Y axis.
+The primary crosshatch tends to be aligned closely, but not exactly, with either the X or Y axis.
 The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
@@
 We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
+\textcolor{red}{\textbf{Update this for latest full frame grism field point}}
 
@@
 	\item Multiply the PSF by the simulated flat field
-	\item Scan the PSF along the X and Y directions up to a magnitude of 6 mas
+	\item Shift the PSF along the X and Y directions up to a magnitude of 6 mas
 	\item Bin the simulated images into the native pixel size
@@
 The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
-The amplitude of the flux changes is potentially up to 300 ppm.
+The amplitude of the flux changes is potentially up to 150 ppm.
 This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
@@
 However, the SW centroids add more noise to the photometry as seen in Figure \ref{fig:otisLWSWtserShift}.
-\textcolor{red}{\bf Did I properly multiply shifts by -0.5?}
 

### 2020-03-15 ms.tex
miscellaneous edits as well as MMM/PPP tables from CV3.

@@
 Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
-The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
-There are also dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
+The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
+We also used dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
 The GL dewar experiments used flight-like detectors, but a different controller (Leach).
@@
 
-\begin{deluxetable*}{ccCrlcc}[b!]
+\begin{deluxetable*}{ccCrlccc}[b!]
 \tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
@@
 \colhead{Instrument Mode} &
-\colhead{Flight Hardware?} \\
+\colhead{Flight Hardware?}&
+\colhead{Controller} \\
 \colhead{} &
@@
 \colhead{(ppm)} &
+\colhead{} &
 \colhead{} &
@@
 %Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
-CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y\\
-OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y\\
-OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y \\
-GL dewar   & Steward Obs.  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N \\
-Asic dewar & Steward Obs.  & 2017-2019  &       	& LED           & pinhole \& flood-illuminated imaging & N\\
+CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y & Asic \\
+OTIS       & NASA Johnson  & 2017       &      	& Continuum     & Darks & Y & Asic\\
+OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y & Asic\\
+OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y & Asic\\
+GL dewar   & U of Arizona  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N & Leach\\
+Asic dewar & U of Arizona  & 2017-2019  &       	& LED           & flood-illuminated imaging & N & Asic\\
 \enddata
@@
 The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
-They also do not contain photon noise in the background, which can mask the electronic noise sources.
+They also do not contain photon noise in the background, which can make electronic noise sources harder to see.
 We study here the contributions from read noise, 1/f noise and dark current.
@@
 Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
-These side reference pixels also cannot give any information about the read noise correlations that happen on shorter length scales than 512 pixels (5 ms).
+These side reference pixels also cannot correct for read noise correlations that happen on shorter length scales than 512 pixels (5 ms).
 
@@
 
-This theoretical read noise should be compared to the photon noise expected inside an aperture during photometric stability time series applications.
+This theoretical read noise is smaller than the photon noise expected inside an aperture during photometric stability time series applications.
 The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
@@
 \subsection{Lessons Learned from CV3 Tests}\label{sec:CV3Lessons}
+
+\begin{figure*}
+\gridline{\fig{ES-WLP8SUB_pipeline_parameters.pdf}{0.39\textwidth}{WLP8 Time Series}
+\fig{{ES-FULL4_pipeline_parameters.pdf}}{0.39\textwidth}{FULL4 Time Series}}
+\caption{Flat fielding, linearity corrections and intrapixel capacitance corrections have a relatively small impact on the time series precisions measured during the CV3 test.
+Each table lists the measured noise (in ppm) when we turn on/off IPC correction (vertical direction), flat fielding (horizontal direction) and the linearity correction (diagonal direction).
+The IPC and flat fielding corrections are negligible.
+Above 50\% well depth, the HgCdTe detectors become less sensitive to photons, so applying the linearity correction naturally increases the apparent noise.
+}\label{fig:CV3pipeParamsWLP8}
+\end{figure*}
+
 Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.

### 2020-03-17 ms.tex
edits to CV3 description

@@
 
-CV3 included a series of exposures over nearly 24 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
+CV3 included a series of exposures about 16 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
 The LED was a narrowband source at 1.55 $\mu$m, which was used in imaging mode since this would result in a narrow-lined spectrum.
@@
 Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
-The hexagonal PSF is summed with circular aperture with a radius of 70 pixels.
+
+We applied the ramps-to-slopes pipeline \texttt{nchdas} to do reference pixel correction, apply a bad pixel mask and calculate slopes or differences of the reads.
+The reference pixel correction uses the top/bottom pixels to remove pre-amp resets and side reference pixels to reduce the 1/f noise.
+The hexagonal PSF is summed with circular aperture with a radius of 70 pixels and a background annulus spanning from 75 to 100 pixels using the \texttt{photutils} package \citep{bradley2016photutilsv0p3}.
 The central peak may used to find a centroid of the star and center the circular aperture.
@@
 
-It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter than the FULL1 through FULLQ tests.
+It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter on short timescales than the FULL1 through FULLQ tests.
 After removing a linear fit to the time series (to account for long term trends in the lamp), the standard deviation of the WLP8SUB data is 500 ppm whereas the FULL tests range from 1020 to 1540 ppm.
@@
 
-There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
+We consider two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
 \begin{enumerate}[noitemsep]
 	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
-	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
+	\item That the lamp is variable on short time scales of a frame (10.74 seconds) and sampling.\label{item:lampReasonCV3subFull}
 \end{enumerate}
+As listed in Table \ref{tab:noiseSummary1overf}, the theoretical uncorrelated noise for double-correlated samples (CDS) is about 33 ppm.
+However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
+When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm.
+Since the full frame imaging had 2 samples (2 groups in RAPID mode), the read noise should be 280 ppm.
+The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\sqrt{2/20}$ or 89 ppm.
+So, read noise differences can account for 200 ppm differences between the two modes.
+\textcolor{red}{\bf Continue HERE!}
+
 The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.

### 2020-03-20 ms.tex
CV3 - writing about un-illuminated regions

@@
 \begin{deluxetable*}{c|cc|cc}[b!]
-\tablecaption{Summary of Noise Sources in OTIS Dark Test}\label{tab:noiseSummary1overf}
+\tablecaption{Summary of Noise Sources in OTIS Dark Test}
 \tabletypesize{\footnotesize}
@@
 The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
+\label{tab:noiseSummary1overf}
 \end{deluxetable*}
@@
 However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
-When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm.
-Since the full frame imaging had 2 samples (2 groups in RAPID mode), the read noise should be 280 ppm.
+When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm for the long wavelength detector.
+Due to the source lamp setup, we average the flux from detector A1 and B4, which lowers the read noise by $\sqrt{2}$  to 200 ppm.
+As a check, we perform aperture photometry on an un-illuminated regions of the time series stability tests.
+We find a standard deviation of 172 ppm, due to slight differences in the read noise between detectors and the illumination.
+So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations.
+
 The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\sqrt{2/20}$ or 89 ppm.
-So, read noise differences can account for 200 ppm differences between the two modes.
+There is no region of the 320$\times$320 subarray that is as big as the source aperture and illuminated to empirical test this estimate.
+The difference of  83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
+
 \textcolor{red}{\bf Continue HERE!}
 
-The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
-If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^- \approx 930 $DN.
-This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
-Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm.
-{\textbf{\textcolor{red}{(Note, here I have used the effective read noise for 90 groups on JDox, but should corrected to 20 groups)}}}
-This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
-However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.
+This is smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
 

### 2020-03-21 ms.tex
a little description of the A/B anti-correlation

@@
 
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.69\columnwidth]{plot_mmm_showTemperatures_False_AB_sides.pdf}
+\caption{Time Series plot through the CV3 photometric stability campaign for the A1 and B4 detectors.
+The flux on the two detectors is highly anti-correlated so the flux is averaged between them for future analyses.
+The anti-correlation likely arises due to the lamp source motion that preferentially couples with one fiber and then the other.
+}\label{fig:CV3longTserAB}
+\end{figure}
+
 A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
@@
 \begin{itemize}
-	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
+	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read.
+This is  expected because more ramps reduce the 1/f and read noise, but the disparity (500 ppm versus 1200 ppm) is too large to be due to read noise alone.
 	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
@@
 \end{itemize}
-We summarize the lessons from the tests here.
 

### 2020-03-21 ms.tex
more on CV3 and switched from t series to A vs B

@@
 The OSIM simulates the PSF expected when a star or other point source illuminates the JWST instruments.
-While other tests described in this work illuminated the science instrument detectors in different ways, the point spread function most closely resembled the JWST flight point spread function.
+The point spread functions from CV3 most closely resembled the JWST flight point spread function and WLP8 defocused image of all ground based tests discussed in this work.
+Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.
+
+\subsubsection{Comparison of Subarray and Full Frame Stability Tests}
 
@@
 By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with telescope pointing jitter or seeing variations during an observation.
-Similarly, NIRCam can employ a weak lens to defocus a star's light.
+Similarly, NIRCam time series observations can employ a weak lens to defocus a star's light.
 Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
@@
 
+The LED lamp was coupled to optical fibers to illuminate two separate detectors simultaneously with the intention of having two independent measurements to compare.
+Unfortunately, the coupling mechanism into the fibers is sensitive to the lamp position, so the flux from the two detectors is highly anti-correlated, as shown in Figure \ref{fig:CV3longTserAB}.
+To better remove this fiber coupling effect, we average the flux from the two detectors for the rest of this discussion.
+This reduces the standard deviation of the time series to 500-1500 ppm.
+
 \begin{figure}[!hbtp]
 \centering
-\includegraphics[width=.69\columnwidth]{plot_mmm_showTemperatures_False_AB_sides.pdf}
-\caption{Time Series plot through the CV3 photometric stability campaign for the A1 and B4 detectors.
-The flux on the two detectors is highly anti-correlated so the flux is averaged between them for future analyses.
-The anti-correlation likely arises due to the lamp source motion that preferentially couples with one fiber and then the other.
-}\label{fig:CV3longTserAB}
+\includegraphics[width=.39\columnwidth]{cv3_A_vs_B_all.pdf}
+\caption{The light from an LED lamp is split into two optical fibers, which are highly anti-correlated likely because vibrations move the lamp relative to the fibers to couple one fiber better than the other.
+Here, the time series fit to a second order polynomial in time to remove long term trends and then the aperture flux for two detectors' fluxes are plotted against each other.
+For the discussion of CV3 tests forward, we average the two detectors (A1 and B4) to reduce this effect.}\label{fig:CV3longTserAB}
 \end{figure}
@@
 A time series of all possible modes is shown in Figure \ref{fig:CV3longTser}.
-The full frame modes (FULL1 through FULLQ) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
+The full frame modes (FULL1 through FULL6) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
 This ensured that during these 4 different types of subarray/full frame window sizes, the well depths achieved were similar.
 
-It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter on short timescales than the FULL1 through FULLQ tests.
+It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter on short timescales than the FULL1 through FULL6 tests.
 After removing a linear fit to the time series (to account for long term trends in the lamp), the standard deviation of the WLP8SUB data is 500 ppm whereas the FULL tests range from 1020 to 1540 ppm.
@@
 For the WLP8SUB mode, a linear least squares fit is performed to the groups as a function of time and the slope of this line is the count rate on a pixel.
-The large number of groups used to fit this line ensures that the read noise is reduced by $\sim 1/\sqrt{N_G}$, where $N_G$ is the number of groups.
-
-We consider two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
-\begin{enumerate}[noitemsep]
-	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
-	\item That the lamp is variable on short time scales of a frame (10.74 seconds) and sampling.\label{item:lampReasonCV3subFull}
-\end{enumerate}
-As listed in Table \ref{tab:noiseSummary1overf}, the theoretical uncorrelated noise for double-correlated samples (CDS) is about 33 ppm.
-However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
-When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm for the long wavelength detector.
-Due to the source lamp setup, we average the flux from detector A1 and B4, which lowers the read noise by $\sqrt{2}$  to 200 ppm.
-As a check, we perform aperture photometry on an un-illuminated regions of the time series stability tests.
-We find a standard deviation of 172 ppm, due to slight differences in the read noise between detectors and the illumination.
-So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations.
-
-The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\sqrt{2/20}$ or 89 ppm.
-There is no region of the 320$\times$320 subarray that is as big as the source aperture and illuminated to empirical test this estimate.
-The difference of  83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
-
-\textcolor{red}{\bf Continue HERE!}
-
-This is smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
-
-Under scenario \ref{item:lampReasonCV3subFull}, the short timescale variations of efficiently averaged out by sampling the reads multiple times up the ramp.
+The large number of groups used to fit this line ensures that the read noise is reduced as compared to the FULL 2 group tests by $2/\sqrt{N_G}$, where $N_G$ is the number of groups.
 
@@
 
-\subsection{Lessons Learned from CV3 Tests}\label{sec:CV3Lessons}
-
-\begin{figure*}
-\gridline{\fig{ES-WLP8SUB_pipeline_parameters.pdf}{0.39\textwidth}{WLP8 Time Series}
+We consider two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
+\begin{enumerate}[noitemsep]
+	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
+	\item That the lamp is variable on short time scales of a frame (10.74 seconds) and sampling.\label{item:lampReasonCV3subFull}
+\end{enumerate}
+As listed in Table \ref{tab:noiseSummary1overf}, the theoretical uncorrelated read noise for double-correlated samples (CDS) is about 33 ppm.
+However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
+When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm for the long wavelength detector.
+Due to the source lamp setup discussed in Figure \ref{fig:CV3longTserAB}, we average the flux from detector A1 and B4, which lowers the read noise by $\sqrt{2}$  to 200 ppm.
+As a check, we perform aperture photometry on an un-illuminated regions of the time series stability tests and average the results of the two detectors.
+We find a standard deviation of 1100 to 1490 e$^-$/s or 150 ppm to 200 ppm of the 7.5$\times 10^6 e^-$/s flux, likely due to slight differences in the 1/f noise within the exposures.
+So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations and not read noise alone.
+
+The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\times \sqrt{2/20}$= 89 ppm.
+There is no un-illuminated region of the 320$\times$320 subarray that is as big as the source aperture so there is not empirical check on this 89 ppm estimate.
+The difference of 83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
+Instead, we conclude that the lamp has significant short-timescale variability that the faster samples used on the SUB320 test can average over.
+The take-away from the comparison between subarrays is that one can reduce the read noise and short timescale variability with more samples up the ramp and a smaller subarray.
+
+\subsubsection{Lessons Learned on the Pipeline from CV3 Tests}\label{sec:CV3Lessons}
+
+\begin{figure*}
+\gridline{\fig{ES-WLP8SUB_pipeline_parameters.pdf}{0.39\textwidth}{SUB320 Time Series}
 \fig{{ES-FULL4_pipeline_parameters.pdf}}{0.39\textwidth}{FULL4 Time Series}}
@@
 
-Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.
-We were able to determine the best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps to produce light curve.
+We were investigated best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps to produce light curve.
 We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
 After the calibrated images are created, we experimented with different types of aperture photometry including different geometries, background calculations and aperture sizes.
+
+We find that the intrapixel capacitance (IPC) correction, flat fielding and linearity correction have relatively small impacts on photometric precision.
+In Figure \ref{fig:CV3pipeParamsWLP8} we show the standard deviation of the flux after averaging the A1 and B4 detectors and dividing by a linear fit to remove long-term trends for two example tests SUBThe IPC correction and
 

### 2020-03-22 ms.tex
describing non-linearity results from the CV3 tests

@@
 
-We were investigated best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps to produce light curve.
+We investigated best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps that go into producing light curves.
 We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
@@
 We find that the intrapixel capacitance (IPC) correction, flat fielding and linearity correction have relatively small impacts on photometric precision.
-In Figure \ref{fig:CV3pipeParamsWLP8} we show the standard deviation of the flux after averaging the A1 and B4 detectors and dividing by a linear fit to remove long-term trends for two example tests SUBThe IPC correction and
+In Figure \ref{fig:CV3pipeParamsWLP8} we show the standard deviation of the flux after averaging the A1 and B4 detectors and removing a linear trend.
+We quote standard deviations for two example tests: SUB320 and FULL4.
+The IPC corrections matter less than 0.01 ppm, because the deconvolution kernel conserves flux and just moves it around.
+The flat fielding correction is less than 0.3 ppm because the image motion is at the sub-pixel level.
+
+The linearity correction does consistently increase the signal to noise by 7 to 23 ppm but this is a natural consequence of the np photodiode in our detectors.
+This is because the photodiode becomes decreasingly less sensitive to photons as it the well capacity is approached.
+At the extreme of saturation, the photodiode no longer senses new photons so you would measure a standard deviation of 0 ppm.
+The weak lens PSF illuminates the pixels to 15,000 to 30,000 DN or 25-50\% well depth and the non-linearity for this well depth is 0.5 to 2\%.
+This means that the measured standard deviation for linearized data should be about 1\% larger than for raw data, similar to the measurements in Figure \ref{fig:CV3pipeParamsWLP8}.
+We therefore conclude that the non-linearity correction makes a small difference to the final derived precision.
 

### 2020-03-25 ms.tex
a few notes on how I did the background subtraction for the OTIS grism amp offset analysis

@@
 It should be noted, however, that there are gradients in the bias signal within each amplifier.
-One could subtract the mean reference pixel in each column to reduce these gradients, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (third fro top panel) but given that there are only 4 reference pixels at the bottom of each column, this introduces extra noise in the subtraction.
+One could subtract the mean reference pixel in each column to reduce these gradients, shown in Figure \ref{fig:ampOffsetsOtisGrismSlope}, (third from top panel) but given that there are only 4 reference pixels at the bottom of each column, this introduces extra noise in the subtraction.
 Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
+Here, we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
+This is repeated for all columns.
 

### 2020-04-14 ms.tex
fixing up the covariance weighted summation stuff

@@
 \begin{equation}
-w_j = \sum_{i=1}^{m} \left( C^{-1}\right)_{ij} P_j,\label{eq:covarianceWeighted}
+w_j = P_j \sum_{i=1}^{m} \left( C^{-1}\right)_{ij},\label{eq:covarianceWeighted}
 \end{equation}
 where $C^{-1}$ is the inverse of the covariance matrix between pixels $i$ and $j$ and $m$ is the number of pixels in the summation.
+The optimally weighted flux ($f_{opt}$) then becomes
+\begin{equation}
+f_{opt} = \frac{\sum_{j=1}^{m} w_j S_j}{\sum_{j=1}^{m} w_j P_j},
+\end{equation}
+where $S_j$ is the background subtracted flux.
+
+% the longer form I'm not using
+%the weighted flux becomes,
+%\begin{equation}\label{eq:covarianceWeighted}
+%f_{opt} = \frac{\sum_{i,j=0}^{m} C^{-1}_{ij} S_j P_j}{\sum_{i,j=0}^{m} C^{-1}_{ij} P_j^2},
+%\end{equation}
+%where $C^{-1}$ is the inverse of the covariance matrix between pixels $i$ and $j$ and $m$ is the number of pixels in the summation and $S_j$ is the background subtracted flux.
+
 Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights.
@@
 \end{equation}
+
 Profile weighting should therefore lower the error on wavelength-binned time series.
@@
 Figure \ref{fig:covSpecSpatial} shows the covariance matrix of this wavelength bin, taken from the median of 20 regions of the detector.
-The diagonal elements are consistent with NIRCam detector performance with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
+The diagonal elements are consistent with published NIRCam detector performance tables with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
 It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance nearly uniformly at 36~$(e^-)^2$.
@@
 The LED lamp was coupled to optical fibers to illuminate two separate detectors simultaneously with the intention of having two independent measurements to compare.
-Unfortunately, the coupling mechanism into the fibers is sensitive to the lamp position, so the flux from the two detectors is highly anti-correlated, as shown in Figure \ref{fig:CV3longTserAB}.
-To better remove this fiber coupling effect, we average the flux from the two detectors for the rest of this discussion.
+Unfortunately, vibrations and jitter in the optical setup affect the relative flux in the two fibers.
+The coupling mechanism into the fibers is sensitive to the lamp position, so the flux from the two detectors is highly anti-correlated, as shown in Figure \ref{fig:CV3longTserAB}.
+To redice this fiber coupling effect, we average the flux from the two detectors for the rest of this discussion.
 This reduces the standard deviation of the time series to 500-1500 ppm.
@@
 This ensured that during these 4 different types of subarray/full frame window sizes, the well depths achieved were similar.
+However, the groups are fit to a line for each pixel, so the useful portion of the ramp is the time between the last and first read or 20.2 seconds for the 320$\times$320 subarray versus 10.7 seconds for the FULL1 through FULL6 tests.
 
@@
 We find a standard deviation of 1100 to 1490 e$^-$/s or 150 ppm to 200 ppm of the 7.5$\times 10^6 e^-$/s flux, likely due to slight differences in the 1/f noise within the exposures.
+If we use a row-by-row subtraction, as discussed in Section \ref{sec:indAmpAvg}, the read noise can be reduced.
+We use a robust mean row-by-row subtraction for a background annulus from 95 to 190 pixels and this reduces the measured read noise on a dark (un-illuminated) region to 60 to 100 ppm.
 So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations and not read noise alone.

### 2020-04-16 ms.tex
rewriting some on CV3 WLP8 tests

@@
 
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
+\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpecSpatial}
+\end{figure}
+
 %% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
@@
 If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
-\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also empirically verify this with a slope fit to multiple images.}
+\textcolor{red}{\bf Also empirically verify this with a slope fit to multiple images.}
 For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be $1.8 \times10^8$ DN, having a photon uncertainty of 9,100 DN or 51 ppm.
@@
 We find a standard deviation of 1100 to 1490 e$^-$/s or 150 ppm to 200 ppm of the 7.5$\times 10^6 e^-$/s flux, likely due to slight differences in the 1/f noise within the exposures.
-If we use a row-by-row subtraction, as discussed in Section \ref{sec:indAmpAvg}, the read noise can be reduced.
-We use a robust mean row-by-row subtraction for a background annulus from 95 to 190 pixels and this reduces the measured read noise on a dark (un-illuminated) region to 60 to 100 ppm.
 So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations and not read noise alone.
@@
 The difference of 83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
+Thus, we rule out \ref{item:readNReasonCV3subFull} as the main noise source.
 Instead, we conclude that the lamp has significant short-timescale variability that the faster samples used on the SUB320 test can average over.
-The take-away from the comparison between subarrays is that one can reduce the read noise and short timescale variability with more samples up the ramp and a smaller subarray.
+%The take-away from the comparison between subarrays is that one can reduce the read noise and short timescale variability with more samples up the ramp and a smaller subarray.
+
+\subsubsection{Row-by-row Background Subtraction}
+
+Even though we rule out read noise as the dominant noise source, we investigate ways to reduce the fractional contribution of read noise.
+If we use a row-by-row subtraction, as discussed in Section \ref{sec:indAmpAvg}, the read noise can be reduced.
+We use a procedure that reduces the 1/f electronic noise.
+First, we find the robust mean flux for each row of the background annulus with radii of 95 and 195 pixels.
+We then, subtract this value from the entire row of the image and perform aperture photometry on the residual image surrounding the source with a circular aperture of 70 pixels.
+This procedure reduces the measured read noise on a dark (un-illuminated) region to 60 to 100 ppm.
 

### 2020-04-16 ms.tex
more on CV3 and added covariance weights

@@
 \clearpage
-\subsection{OTIS Long Darks}\label{sec:longDarks}
+\subsection{Long Darks}\label{sec:longDarks}
 
@@
 \centering
-\includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
-\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpecSpatial}
+\includegraphics[width=.7\columnwidth]{cov_weighted_weights.pdf}
+\caption{Spectral extraction weights for simple summation, conventional optimal extraction and covariance-weighting.}\label{fig:covWeightedSummation}
 \end{figure}
@@
 
-\subsubsection{Lessons Learned on the Pipeline from CV3 Tests}\label{sec:CV3Lessons}
+\subsubsection{Best Pipeline Practices from CV3 Tests}\label{sec:CV3Lessons}
 
@@
 
-We investigated best practices for the pipeline and analysis by running the raw data through the pipeline and changing the steps that go into producing light curves.
+We investigated best practices for the pipeline and analysis by running the raw data through the pipeline and sequentially adding and subtracting steps that go into producing light curves.
 We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
@@
 We quote standard deviations for two example tests: SUB320 and FULL4.
-The IPC corrections matter less than 0.01 ppm, because the deconvolution kernel conserves flux and just moves it around.
-The flat fielding correction is less than 0.3 ppm because the image motion is at the sub-pixel level.
+The IPC corrections matter less than 0.01 ppm, because the deconvolution kernel conserves flux.
+So long as the aperture is significantly wider than the 3$\times$3 pixel kernel, the flux in an aperture should be constant.
+The flat fielding correction has less than a 2 ppm impact to the standard deviation because the image motion is at the sub-pixel level.
 
@@
 This is because the photodiode becomes decreasingly less sensitive to photons as it the well capacity is approached.
-At the extreme of saturation, the photodiode no longer senses new photons so you would measure a standard deviation of 0 ppm.
+Note that at the extreme of saturation, the photodiode no longer senses new photons so you would measure a standard deviation of 0 ppm.
+Therefore, the np photodiode naturally decreases the measured standard deviation of flux that will appear larger with a non-linearity correction.
+
 The weak lens PSF illuminates the pixels to 15,000 to 30,000 DN or 25-50\% well depth and the non-linearity for this well depth is 0.5 to 2\%.
@@
 	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
-	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
+	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus) because it reduces the read noise.
 	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
-	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
 \end{itemize}
@@
 	\item IPC corrections ($\lesssim 0.01$ ppm)
-	\item Flat-fielding ($\lesssim 0.3$ ppm)
+	\item Flat-fielding ($\lesssim 2$ ppm)
 \end{itemize}
@@
 A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
-However, there is no feasible way to place a point source lamp at infinity to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
+However, there is no feasible way to place a point source lamp far enough away to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
 During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain to the detectors.

### 2020-04-19 ms.tex
typed of derivation of covariance weighted optimal flux

@@
 The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
-The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).}
+The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).
+For the grism, statistics are shown for a representative 0.17~$\mu$m wide wavelength bin centered on 3.34~$\mu$m.}
 \label{tab:noiseSummary1overf}
@@
 
-We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.25 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
+We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
 Without reference pixel subtraction, the grism apertures have standard deviations of 77,600 DN.
@@
 Given the high level of correlation between pixels, another way to reduce 1/f noise is with a small aperture.
-For example, a 15 pixel wide aperture results in measured read noise of 990 ppm for the same 0.17$\mu$m wide bin centered at 4.25$\mu$m whereas a 3 pixel wide aperture results in a measured read noise of 290 ppm, which is below the expected photon noise.
+For example, a 15 pixel wide aperture results in measured read noise of 990 ppm for the same 0.17$\mu$m wide bin centered at 3.34$\mu$m whereas a 3 pixel wide aperture results in a measured read noise of 290 ppm, which is below the expected photon noise.
 For a one pixel wide aperture, the measured read noise is only 230 ppm.
-Of course such small apertures will be subject to other losses by missing so much of the PSF.
-Therefore, the spectroscopic pipeline should either use a small aperture or provide extra weights to the brightest pixels such as in optimal extraction \citep[e.g.][]{horne1986optimalE}.
-If one calculates the weights to the spectra simply by the signal-to-noise while assuming each pixel's noise is independent, the weights are not heavy enough for the brightest pixels.
-This is because the observations will largely be in the foreground limit (where the variance is equal to the number of photons), where weighting by the profile for pixel $j$ (P$_j$) divided by the variance (V$_i$) becomes
+Of course such small apertures will be subject to other losses by missing so much of the PSF and the photon noise will be a larger fraction of the flux.
+Therefore, a weighting scheme expanded from optimal extraction \citep{horne1986optimalE} is preferred.
+
+\subsubsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}
+
+Here, we provide a modification to the optimal extraction formula from \citet{horne1986optimalE}, that uses the covariance matrix of correlated pixels.
+The goal is to find a scheme that estimates the total flux by summing the value in each pixel $j$.
+We start by calculating a profile function $P_j$ that describes the fraction of the total flux in pixel $j$.
+The profile is normalized so that
 \begin{equation}
-w_j = P_j / V_j = N_{ph} / N_{ph} = 1.0,
+\sum_{j=1}^{m} P_j = 1.
 \end{equation}
-where $N_{ph}$ is the number of photons on that pixel.
-
-However, if one generalizes the weighted average to a covariance matrix \citep{schmelling1995averagingCorrelatedData}, the weights become,
+Any pixel is can be used to estimate the total flux $f_i$ by dividing by the profile.
 \begin{equation}
-w_j = P_j \sum_{i=1}^{m} \left( C^{-1}\right)_{ij},\label{eq:covarianceWeighted}
+f_j = \frac{S_j}{P_j},
 \end{equation}
-where $C^{-1}$ is the inverse of the covariance matrix between pixels $i$ and $j$ and $m$ is the number of pixels in the summation.
-The optimally weighted flux ($f_{opt}$) then becomes
+where $S_j$ is the background-subtracted flux.
+Therefore, the flux total is a weighted average of each pixel's estimate of the total flux $f_j$.
+The goal becomes a weighting scheme to determine which weights $w_j$ minimize the variance in the total background estimate:
 \begin{equation}
-f_{opt} = \frac{\sum_{j=1}^{m} w_j S_j}{\sum_{j=1}^{m} w_j P_j},
+f_{opt} = \frac{\sum_{j=1}^{m} w_j \frac{S_j}{P_j}}{\sum_{j=1}^{m} w_j}.
 \end{equation}
-where $S_j$ is the background subtracted flux.
-
-% the longer form I'm not using
-%the weighted flux becomes,
-%\begin{equation}\label{eq:covarianceWeighted}
-%f_{opt} = \frac{\sum_{i,j=0}^{m} C^{-1}_{ij} S_j P_j}{\sum_{i,j=0}^{m} C^{-1}_{ij} P_j^2},
+
+If one assumes that all pixels are independent (and have zero correlation), the optimal weights (ones that minimize the variance in $f_{opt}$) are
+\begin{equation}
+w_j = \frac{1}{\mathrm{Var}(\frac{S_j}{P_j})} = \frac{1}{\frac{1}{P_j^2} \mathrm{Var}(S_j)} = \frac{P_j^2}{V_j},
+\end{equation}
+where Var() is the variance or the expectation of the deviation from the mean and $V_j =$Var$(S_j$) \citep{horne1986optimalE}.
+Exoplanet observations, where high signal to noise is needed to remove the planet from star signal, are generally in the foreground limit (where the variance is approximately equal to the number of photons).
+In this case, both the profile $P_j$ and variance $V_j$ will be proportional to the number of photons $N_{phot}$, so the pre-multiplier of the flux become
+\begin{equation}
+\frac{w_j}{P_j} \approx \frac{N_{phot}^2}{N_{phot} N_{phot}} = 1.0.
+\end{equation}
+Therefore, using this traditional formula will provide little difference with straight summation,
+\begin{equation}
+f_{sum} = \sum_{j=1}^{m} S_j.
+\end{equation}
+
+However, in the presence of noise correlations, the formulae become modified.
+The optimal weights for correlated data are \citep{schmelling1995averagingCorrelatedData} the sum of the inverse covariance matrix,
+\begin{equation}\label{eq:covarianceweights}
+w_j = \sum_{i=0}^{m} C_{ij}^{-1},
+\end{equation}
+where $C_{ij}$ is the covariance (Cov()) of the variable $S_i/P_i$ with $S_j/P_j$,
+\begin{equation}
+C_{ij} = \mathrm{Cov}\left(\frac{S_i}{P_i},\frac{S_j}{P_j}\right) = \frac{1}{P_i P_j} \mathrm{Cov}(S_i,S_j).
+\end{equation}
+
+%Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights.
+%If we assume the read noise is perfectly correlated along the spectral direction and uncorrelated along the spatial direction, then equation \ref{eq:covarianceweights} becomes
+%\begin{equation}
+%w_j = \frac{P_j}{N_{ph} + N_{px} \sigma_R^2},
 %\end{equation}
-%where $C^{-1}$ is the inverse of the covariance matrix between pixels $i$ and $j$ and $m$ is the number of pixels in the summation and $S_j$ is the background subtracted flux.
-
-Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights.
-If we assume the read noise is perfectly correlated along the spectral direction and uncorrelated along the spatial direction, then equation \ref{eq:covarianceWeighted} becomes
-\begin{equation}
-w_j = \frac{P_j}{N_{ph} + N_{px} \sigma_R^2},
-\end{equation}
-where $N_{px}$ is the number of spectral pixels that will be binned and $\sigma_R$ is the read noise per pixel.
-Thus, for large values of $N_{px}$ (up to 512 for an amplifier), the $\sigma_R \approx 14e^-$ of read noise per pixel, can compound to 100,400 e$^-$ and the weighting approaches
-\begin{equation}
-w_j \propto P_j.
-\end{equation}
-
-Profile weighting should therefore lower the error on wavelength-binned time series.
-For the grism aperture experiment, we find that profile weighting gives a measured read noise of 355 ppm.
-Thus, profile weighting still does not reduce the standard deviation over an extraction aperture that is just 1 pixel wide at the peak grism flux.
-We show the real covariance matrix in Section \ref{sec:empCovarianceMatrix}.
+%where $N_{px}$ is the number of spectral pixels that will be binned and $\sigma_R$ is the read noise per pixel.
+%Thus, for large values of $N_{px}$ (up to 512 for an amplifier), the $\sigma_R \approx 14e^-$ of read noise per pixel, can compound to 100,400 e$^-$ and the weighting approaches
+%\begin{equation}
+%w_j \propto P_j.
+%\end{equation}
+%
+%Profile weighting should therefore lower the error on wavelength-binned time series.
+%For the grism aperture experiment, we find that profile weighting gives a measured read noise of 355 ppm.
+%Thus, profile weighting still does not reduce the standard deviation over an extraction aperture that is just 1 pixel wide at the peak grism flux.
+%We show the real covariance matrix in Section \ref{sec:empCovarianceMatrix}.
 
 \subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
-The ideal weighting of the spectrum from Equation \ref{eq:covarianceWeighted} depends on the covariance matrix $C_{ij}$.
+The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
 We use CDS (correlated double sampling) read pairs of OTIS long dark data (108 frames) with reference pixel corrections to estimate $C_{ij}$.

### 2020-04-21 ms.tex
updating covariance plots, showing average cross sections and correct weighting scheme

@@
 \end{equation}
-where Var() is the variance or the expectation of the deviation from the mean and $V_j =$Var$(S_j$) \citep{horne1986optimalE}.
+where Var() is the variance or the expectation of the squared deviation from the mean and $V_j =$Var$(S_j$) \citep{horne1986optimalE}.
 Exoplanet observations, where high signal to noise is needed to remove the planet from star signal, are generally in the foreground limit (where the variance is approximately equal to the number of photons).
@@
 However, in the presence of noise correlations, the formulae become modified.
-The optimal weights for correlated data are \citep{schmelling1995averagingCorrelatedData} the sum of the inverse covariance matrix,
+The optimal weights for correlated data are the sums of the inverse covariance matrix along one dimension  \citep{schmelling1995averagingCorrelatedData},
 \begin{equation}\label{eq:covarianceweights}
@@
 The diagonal elements are consistent with published NIRCam detector performance tables with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
-It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance nearly uniformly at 36~$(e^-)^2$.
-Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$16 $(e^-)^2$ that falls off to $\sim 10 (e^-)^2$.
+It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance nearlynear 36~$(e^-)^2$.
+Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$20 $(e^-)^2$.
 
@@
 \centering
-\includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
-\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpecSpatial}
+\includegraphics[width=.6\columnwidth]{spec_spatial_cov.pdf}
+\caption{The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
+The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
+The detector's diagonal elements are consistent with expected performance of $\approx 13^2 (e^-)^2=169 (e^-)^2$.
+Spatially, the pixels' have a strong covariance of 36~$(e^-)^2$ and a somewhat smaller spatial covariance of 20$(e^-)^2$.}\label{fig:covSpecSpatial}
 \end{figure}
@@
 \centering
-\includegraphics[width=.7\columnwidth]{cov_weighted_weights.pdf}
+\includegraphics[width=.6\columnwidth]{cross_sections_cov.pdf}
+\caption{Average covariance along the spatial and spectral directions for a given pixel spacing.}\label{fig:covSpecSpatialDiff}
+\end{figure}
+
+The empirical covariance matrix from Figure \ref{fig:covSpecSpatial} is used to estimate the optimal pixel weights using Equation \ref{eq:covarianceweights}.
+We reduce the noise and jaggedness of the empirical covariance matrix in Figure \ref{fig:covSpecSpatial} by averaging the value along the diagonal, across all spectral pixels and across the spatial pixels with the same value of $i -j$.
+The resulting optimal weighting function $w_j/P_j$ is plotted in Figure \ref{fig:covWeightedSummation}.
+Here, the profile is the value from \texttt{pynrc}, which uses \texttt{webbpsf}.
+This optimal weighting significantly increases the contributions from the inner pixels
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.5\columnwidth]{cov_weighted_weights.pdf}
 \caption{Spectral extraction weights for simple summation, conventional optimal extraction and covariance-weighting.}\label{fig:covWeightedSummation}

### 2020-04-24 ms.tex
added the variance formula and result of covariance-weighted summation

@@
 Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
-Measured Read Noise (profile-weighted summation)	& & & 1,310 & 355 \\
+Measured Read Noise (covariance-weighted summation)	& & & 854 & 231 \\
 \enddata
@@
 C_{ij} = \mathrm{Cov}\left(\frac{S_i}{P_i},\frac{S_j}{P_j}\right) = \frac{1}{P_i P_j} \mathrm{Cov}(S_i,S_j).
+\end{equation}
+
+The variance in the flux is
+\begin{equation}
+\mathrm{Var}(f_{opt}) = \frac{1}{\sum_{j=1}^m w_j}.
 \end{equation}

### 2020-04-24 ms.tex
added updated results all down the grism aperture column

@@
 \startdata
-Ideal Photon Noise & 4,400 & 113 & 1,420 & 390 \\
-Ideal Uncorrelated Read Noise & 1,300 & 33 & 348 & 95 \\
+Ideal Photon Noise & 4,400 & 113 & 1,430 & 388 \\
+Ideal Uncorrelated Read Noise & 1,300 & 33 & 350 & 94 \\
 \hline
-Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 77,600 & 21,200  \\
-Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,640 & 2,640 \\
+Measured Read Noise with amplifier offsets (no correction) & 23,500 & 600 & 80,930 & 21,900  \\
+Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,900 & 2,680 \\
 Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,630 & 992 \\
+Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,860 & 1044 \\
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
@@
 Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
-Measured Read Noise (covariance-weighted summation)	& & & 854 & 231 \\
+Measured Read Noise (variance-weighted summation)	& & & 3,060 & 830 \\
+Measured Read Noise (covariance-weighted summation)	& & & 850 & 230 \\
 \enddata

### 2020-04-29 ms.tex
updating covariance weighting method and results sections

@@
 We consider a wavelength bin that is 100 pixels in the dispersion direction (0.1$\mu$m) and 14 spatial spatial pixels.
-Figure \ref{fig:covSpecSpatial} shows the covariance matrix of this wavelength bin, taken from the median of 20 regions of the detector.
-The diagonal elements are consistent with published NIRCam detector performance tables with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
-It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance nearlynear 36~$(e^-)^2$.
-Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$20 $(e^-)^2$.
+We also subtract the CDS frames by the median of each row-by-row and the median of each column column-by-column to reduce the amplifier offsets and 1/f noise as done in Figure \ref{fig:longDarkPhot}.
+
+Figure \ref{fig:covSpecSpatial} shows the covariance matrix of this wavelength bin, taken from the median covariance matrix of 20 regions of the detector.
+The diagonal elements $\sim 150 (e^-)^2$ are smaller than published NIRCam detector performance tables ($\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$).
+However, if we skip the row-by-row and column-by-column subtraction step, they are consistent with $\sigma^2 \approx 13^2 (e^-)^2=169 (e^-)^2$.
+It is clear that 1/f noise causes covariance most prominently along the spectral direction (the fast-read direction), with a covariance near 20~$(e^-)^2$.
+Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$10 $(e^-)^2$.
 
@@
 The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
-The detector's diagonal elements are consistent with expected performance of $\approx 13^2 (e^-)^2=169 (e^-)^2$.
-Spatially, the pixels' have a strong covariance of 36~$(e^-)^2$ and a somewhat smaller spatial covariance of 20$(e^-)^2$.}\label{fig:covSpecSpatial}
+The detector's diagonal elements are better than the read noise squared due to the row-by-row and column-by-column subtraction step.
+Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
 \end{figure}
@@
 Here, the profile is the value from \texttt{pynrc}, which uses \texttt{webbpsf}.
-This optimal weighting significantly increases the contributions from the inner pixels
+This optimal weighting significantly increases the contributions from the inner pixels compared to variance weights.
+The optimal weighting scheme also negatively weights some pixels outside the core of the PSF to reduce correlated noise.
 
@@
 \end{figure}
+
+Optimal covariance weighting significantly lowers the contribution of read noise to the overall error budget.
+We test this with a series of grism images with no photon noise added.
+We do background subtraction along the dispersion and spatial directions.
+We perform sum extraction over a 15 spatial pixels and then combine together 170 spectral pixels into a 0.17 $\mu$m wavelength bin.
+The standard deviation of sum extraction is 3,860 DN, which is 2.7$\times$ the read noise, as shown in Table \ref{tab:noiseSummary1overf}.
+The standard deviation of the extracted flux drops to 3,060 DN if optimal extraction is used.
+
+We use Equation \ref{eq:covarianceweights}, to further beat down the read noise.
+For the covariance weights, we assume constant off-diagonal weights of 15 (e$^-)^2$ and do not include the spectral covariance.
+The resulting standard deviation of 850 DN is now 60\% of the photon noise.
+Thus, we recommend optimal covariance weighting when extracting grism time series.
+As the number of groups of the ramp is increased, the read noise should drop as 1/$\sqrt{N_G}$ so the covariance weighting most important when $N_G$ is small.
+
+The methodology in calculating $P_j$ and Cov($S_i,S_j$) can significantly affect the precision on the time series.
+Typically $P_j$ and the photon noise contribution to Cov($S_i,S_j$) can be found by fitting smooth functions (polynomials) along the dispersion direction.
+If $P_j$ is calculated from each image individually, it will inherit the 1/f noise variations of each image.
+Therefore, we hold $P_j$ constant along the time series with a value saved from the middle image at all wavelengths.
+Alternatively, $P_j$ could be calculated from a PSF library or theoretically from \texttt{WebbPSF} \citep{perrin2014webbpsf}.
 

### 2020-04-29 ms.tex
tiny modification to abstract
reorganized and got rid of everything going in paper 2

@@
 \usepackage{enumitem}
+\listfiles
 
@@
 
-\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}
+\title{JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series}
 
@@
 
-\author{Rafia Bushra}
+\author{Karl Misselt?}
 \affiliation{Steward Observatory \\
@@
 
-\author{Stephanie Striegel}
-\affiliation{Department of Physics \& Astronomy \\
-San Jose State University \\
-One Washington Square \\
-San Jose, CA 95192, USA}
+\author{Jarron Leisenring?}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
+\author{Thomas Beatty?}
+\affiliation{Steward Observatory \\
+933 North Cherry Avenue \\
+Tucson, AZ 85721, USA}
+
+\author{Thomas P Greene?}
 \affiliation{NASA Ames Research Center \\
@@
 
-\author{Xander Levinson}
-\affiliation{Department of Astronomy \& Astrophysics \\
-University of California, Santa Cruz \\
-1156 Highland Street \\
-Santa Cruz, CA 95062, USA}
-\affiliation{NASA Ames Research Center \\
-Space Science and Astrobiology Division \\
-Moffett Field, CA 94035, USA}
-
-\author{Karl Misselt}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Jarron Leisenring}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Kenneth Don}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Douglas Kelly}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Thomas Beatty}
-\affiliation{Steward Observatory \\
-933 North Cherry Avenue \\
-Tucson, AZ 85721, USA}
-
-\author{Thomas P Greene}
-\affiliation{NASA Ames Research Center \\
-Space Science and Astrobiology Division \\
-Moffett Field, CA 94035, USA}
+\author{Peiman Maghami?}
+
+\author{Michael McElwain}
 
@@
 This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide the lessons learned from ground-based characterization of the NIRCam H2RG detectors, which will be used for exoplanet spectra.
-%and are the same type of detectors used in JWST's NIRISS and NIRSpec instruments.
-We summarize the lessons learned from tests at NASA Goddard, NASA Johnson and the University of Arizona detector lab.
+Here, we provide estimates of the noise source affecting JWST NIRCam time series.
 Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
 Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
+We also describe a covariance weighting scheme that can significantly lower the contributions from 1/f noise as compared to sum extraction.
 Pointing jitter and high gain antenna moves on top of the detectors' subpixel crosshatch patterns will produce relatively small variations $\lesssim 10$ ppm, before they are corrected.
 In contrast to the HST WFC3 detectors, persistence due to charge trapping will have a negligible effect on time series.
-Future performance tests during commissioning and the early release science will still be needed to assess the noise floor on stars, which are more stable than the available LED lamps used in lab-based tests.
 \end{abstract}
@@
 Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.
-Section \ref{sec:experiments} describes the experiments on the ground that are used to prepare for JWST observations in flight.
-
-\section{Known Detector Effects}\label{sec:knownEffects}
+
+\section{List of Known Detector Effects}\label{sec:knownEffects}
 An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
@@
 
-\subsection{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}
+\section{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}
 
@@
 \clearpage
-
-\subsection{1/f Noise}
+\section{1/f Noise}
 The readout circuitry for NIRCam and other JWST NIR instruments introduces correlated noise from pixel-to-pixel.
@@
 
-\subsection{Fringing}
-
-The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
-Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
-We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.
-
-Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
-The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
-The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
-The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
-The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
-These oscillations increase in frequency at longer wavelengths (X pixels).
-The variations have peak-to-valley amplitudes of about 8\%.
-However, we expect that the fringing structure will hold relatively constant during time due to the temperature stability of the instrument.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
-\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
-An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
-}\label{fig:CV3GrismSpecFringing}
-\end{figure}
-
-\clearpage
-\subsection{Subpixel Crosshatching}
-
-\subsubsection{Subpixel Crosshatching Characterization}
-The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
-The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
-The angle between these lines are 67.8$\degree$, 67.7$\degree$ and 44.5$\degree$.
-These angles and patterns can be analyzed with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
-
-The angles of the crosshatch patterns are determined by the crystal pattern of HgCdTe.
-HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
-HgCdTe detectors are manufactured using molecular beam epitaxy upon a substrate, a process which can result in topological defects with peak to valley amplitudes of 5-20 nm in height variations \citep{chang2008surfaceMorphologyHgCdTe}.
-The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes.
-
-The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
-A projection of zincblende structure is shown in Figure \ref{fig:crossHatchA5} relative to the observed crosshatch patterns.
-The similarity between the crosshatch patterns in the flat field and the topological variations observed in \citet{chang2008surfaceMorphologyHgCdTe} leads to the likely conclusion that the surface variations lead to quantum efficiency variations.
-Thus, the crosshatch pattern is mostly likely related to the crystal lattice structure of the HgCdTe substrate and not the pixel circuitry.
-
-The crosshatch structure of the detectors extends down to the subpixel level, so it will not be fully corrected with a flat field division.
-This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
-Atomic force microscopy shows topological features that are approximately 1.2~$\mu$m in width \citep{chang2008surfaceMorphologyHgCdTe} compared to the 18~$\mu$m pixel sizes.
-The width of the structures can also be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
-We estimate that the crosshatch pattern oriented at 90.9$\degree$ crosses 1 horizontal pixel for every 64 vertical pixels.
-While crossing the boundary, there are $\approx 38$ rows where the crosshatch pattern spans more than 2 pixels.
-If the crosshatch pattern has a tophat response function, then these 38 rows where the pattern spans two pixels imply a tophat full width of 0.6 pixels or a physical width of 10.8~$\mu$m for an 18~$\mu$m pixel pitch.
-This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
-We expect that the crosshatch pattern's width varies among detectors and that a tophat function is a poor approximation of the actual subpixel response.
-Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
-\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
-\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
-\caption{
-The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
-The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
-The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
-Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
-}\label{fig:crossHatchA5}
-\end{figure}
-
-The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (resolving crystal structures) and smallest for the long wavelengths.
-This is visible both in the throughput cross section of the flat field and the Fourier amplitude of the crosshatch as a function of wavelength.
-We find a steeper wavelength dependence to the crosshatch pattern near 0.9$\degree$ from horizontal in the frequency domain or 0.9$\degree$ from vertical in the length domain.
-%We also fit the crosshatch pattern.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{cross_sec_of_crosshatch.pdf}
-\includegraphics[width=.49\columnwidth]{fourier_power_from_fit.pdf}
-\caption{
-The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better.
-The shorter wavelengths have deeper crosshatch troughs (left) and higher Fourier amplitudes (right).
-}\label{fig:crossHatchWavelengthDep}
-\end{figure}
-
-\subsubsection{Crosshatch Pattern Modeling}
-We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
-We divide the 2D Fourier power spectral density by the number of pixels in an input image.
-This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
-\textcolor{red}{Can we justify this more? I thought it would be pixels$^2$}
-
-We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
-\begin{equation}\label{eq:analyticPSDradial}
-f(k_{x,i}',k_{y,i}', a_i, b,c) = a_i \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
-\end{equation}
-where $k_x'$ and $k_y'$ are rotated frequency coordinates in the parallel and perpendicular directions, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorentzian full width at half maximum of the perpendicular dependence.
-For each of the three angles, there is a set of rotated coordinates centered at $(k_{x,0},k_{y,0})$= (0,0) following:
-\begin{equation}
-k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
-\end{equation}
-and
-\begin{equation}
-k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
-\end{equation}
-We include three angles so that the total power spectral density is
-\begin{equation}
-f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e_b\right)},
-\end{equation}
-
-This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
-Finally, we include an exponential term that fits the broad azimuthally symmetric background to all the power spectra,
-where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e_b$ is the radial background exponential constant.
-We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
-
-For the F300M filter and ALONG detector, we find 
-for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e_b=0.26 \pm 0.01$ px$^{-1}$.
-In other words, the separations between the vectors are $67.699 \degree, 67.831 \degree$, and $44.470 \degree$.
-The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
-
-NIRCam's 10 SCA's have very similar crosshatch angles with separations of 44.5 $\degree$ and 67.7 to 67.8 $\degree$.
-They tend to have one primary crosshatch axis oriented either along the X pixels or the Y pixels, with two flanking axes at $\sim 67.7 \degree$ to either side.
-The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
-The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
-Figure \ref{fig:crosshatchModelGallery} shows the best-fit crosshatch 2D power spectra.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
-\caption{
-Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
-The primary crosshatch tends to be aligned closely, but not exactly, with either the X or Y axis.
-The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
-}\label{fig:crosshatchModelGallery}
-\end{figure}
-
-\clearpage
-\subsubsection{Position of SubGrism Array}
-
-The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
-The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
-On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
-We fit the crosshatch pattern to three regions of the ALONG detector, which is the one used for the NIRCam grism time series mode:
-\begin{enumerate}
-	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (4,5) \label{subgrism64pos}
-	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (4,1984)
-	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
-\end{enumerate}
-
-The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
-We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
-The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
-The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
-The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
-The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
-We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
-\textcolor{red}{\textbf{Update this for latest full frame grism field point}}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64.pdf}\\
-\vspace{0.2in}
-\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64_psd.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
-\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64_psd.pdf}\\
-\caption{
-The top of the array has the smallest level of crosshatching and the middle has the largest.
-This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array (first plot from top), the full frame position near Y=512 (second plot from top) and the nominal SUBGRISM64 at the bottom of the array (third plot from top).
-The bottom left corner for each subarray is listed in parentheses in the title of the flat field plot and the best-fit amplitudes are listed in the title of the power spectral density plot.
- }\label{fig:subpixScanSimulation}
-\end{figure}
-
-\subsubsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
-
-The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
-NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
-
-We simulate the effect of this jitter on NIRCam time series observations with the following steps:
-\begin{itemize}
-	\item Fit the existing flat field to a crosshatch model in the Fourier domain
-	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
-	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
-	\item Multiply the PSF by the simulated flat field
-	\item Shift the PSF along the X and Y directions up to a magnitude of 6 mas
-	\item Bin the simulated images into the native pixel size
-	\item Divide by the pixel-to-pixel flat field
-	\item Measure the relative flux with a photometric aperture
-\end{itemize}
-
-We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
-We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
-$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
-We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
-Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
-For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
-This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
-For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
-\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
-\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
-\caption{
-The steps of the sub-pixel crosshatch photometry simulation are shown here.
-We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
-This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
-A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
-Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
-The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
-}\label{fig:crossHatchSimPSF}
-\end{figure}
-
-We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
-\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
-We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
-We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
-This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
-
-We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
-The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
-For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
-These simulated operations represent pointing drift on the subpixel scale.
-
-We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
-The aperture is re-centered by the same position as the shift direction.
-For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
-While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
-The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
-\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
-\caption{
-The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
-Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
-The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
-These are correctable with smooth functions such as polynomials.
-}\label{fig:subpixScanSimulation}
-\end{figure}
-
-The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
-The amplitude of the flux changes is potentially up to 150 ppm.
-This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
-
-Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
-A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
-Alternatively, a Gaussian process regression could be applied.
-Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
-When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
-Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
-Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
-This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
-
-\subsubsection{Time Series Simulation}
-The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
-The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
-
-The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
-These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
-Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
-This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
-Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
-The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
-Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
-Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
-
-\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
-
-\begin{figure*}
-\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
-\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
-\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
-This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
-}\label{fig:tserPointingFull}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
-\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
-\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
-}\label{fig:tserPointingZoom}
-\end{figure*}
-
-We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
-First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
-We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
-The resulting flux variations are very small compared to factors like the 1/f noise.
-The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
-Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
-Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
-
-\begin{figure*}
-\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
-\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
-The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
-}\label{fig:tserPointingAndFlux}
-\end{figure*}
-
-\clearpage
-
-\subsection{Random Telegraph Noise and RC pixels}
-Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
-The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
-These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.
-
-For Weak Lens photometric aperture (such as a 70 pixel radius aperture), there will be of order 2-4 pixels exhibiting RTN.
-The RTN may not be removed by jump detection algorithms if they are similar order of magnitude to the photon noise for a single pixel ($\sim$180 DN).
-If these are not identified, the RTN can contribute $\sim$200 counts in 4$\times 10^7$ or 5 ppm changes.
-
-There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
-These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
-There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
-
-\begin{figure*}
-\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{RTN Pixels} 
-\fig{{example_rc.pdf}}{0.45\textwidth}{RC pixels}}
-\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
-Examples are shown for RTN and RC pixels.
-}\label{fig:RTNandRC}
-\end{figure*}
-
-\clearpage
-\section{Ground-based Experiments}\label{sec:experiments}
-
-Table \ref{tab:testSummary} contains a summary of the ground-based tests that were performed on NIRCam detectors.
-The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
-We also used dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
-The GL dewar experiments used flight-like detectors, but a different controller (Leach).
-The Asic dewar located at Steward Observatory in Tucson, Arizona used the same kind of detectors as NIRCam, the same kind of asic controllers and the same flight software, but no flight-like optics.
-These two different kinds of detector electronics can be compared against each other to help isolate optical-related systematics, detector-related systematics and electronics-related systematics.
-
-The instrument modes tested included mostly imaging with narrowband LEDs, but there was also a test with spectroscopy on a broadband source.
-The one test with a broadband source was an OTIS stability test at NASA Johnson was a grism spectroscopy mode, which illuminated the long wavelength detector with a slitless spectrum covering 2.4 to 4.0~$\mu$m for the F322W2 filter, as seen in Figure \ref{fig:ampOffsetsOtisGrismSlope}.
-The WLP8 imaging tests are where a point source is de-focused by 8 waves with a weak lens (WLP8), as shown in Figure \ref{fig:WLP8PSF}.
-This mode was designed for wavefront sensing, but is also useful for high-precision time series because it spreads the light over many pixels.
-The weak lens produces a point spread function (PSF) that is hexagonal like JWST's mirrors and has a flat-to-flat width of $\sim$108 pixels and a vertex-to-vertex width of $\sim$136 pixels.
-The hexagonal PSF also has a central vertical peak which can be used for aperture centering.
-The tests with the GL and ASIC dewars did not have NIRCam optics and instead were flood illuminated with a light source that had large spatial variations due to a non-uniform source.
-
-\begin{deluxetable*}{ccCrlccc}[b!]
-\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
-\tabletypesize{\footnotesize}
-%\tablecolumns{7}
-%\tablenum{2}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Name} &
-\colhead{Location} &
-\colhead{Test Year} &
-\colhead{Best Stability} & 
-\colhead{Light Source} & 
-\colhead{Instrument Mode} &
-\colhead{Flight Hardware?}&
-\colhead{Controller} \\
-\colhead{} &
-\colhead{} &
-\colhead{(YYYY)} &
-\colhead{(ppm)} &
-\colhead{} &
-\colhead{} &
-\colhead{} &
-\colhead{}
-}
-\startdata
-%Lockheed CV& Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & \nodata \\ 
-%Reset per int test & Lockheed Martin& 2014??    & \nodata   & Darks         & Long Darks & Y \\ 
-CV 3       & NASA Goddard  & 2016       & 500   	& LED           & WLP8 imaging & Y & Asic \\
-OTIS       & NASA Johnson  & 2017       &      	& Continuum     & Darks & Y & Asic\\
-OTIS       & NASA Johnson  & 2017       &   2200    	& Continuum     & Grism spectroscopy & Y & Asic\\
-OTIS       & NASA Johnson  & 2017       &   21,000    	& Continuum     & WLP8 Imaging & Y & Asic\\
-GL dewar   & U of Arizona  & 2015-2016  &       	& LED	        & flood-illuminated imaging & N & Leach\\
-Asic dewar & U of Arizona  & 2017-2019  &       	& LED           & flood-illuminated imaging & N & Asic\\
-\enddata
-\tablecomments{Cryogenic vacuum (CV), Optical Telescope element and Integrated Science (OTIS).}
-\end{deluxetable*}
-
-\clearpage
 \subsection{Long Darks}\label{sec:longDarks}
@@
 
-\subsubsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
+\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
 A slight modification to the above strategy is to average each amplifier individually.
@@
 
-\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
+\subsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
 
@@
 
-\subsubsection{Reference Channel Subtraction}
+\subsection{Reference Channel Subtraction}
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
@@
 
-\subsubsection{PCA Correction}
+\subsection{PCA Correction}
 Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
@@
 
-\subsubsection{Grism Aperture}
+\subsection{Grism Aperture}
 The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
@@
 
-\subsubsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}
+\subsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}
 
@@
 
-\subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
+\subsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
 The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
@@
 %% See the notebooks wlp8_psf_image.ipynb and noise_sources_wlp8.ipynb for calculations
-\subsubsection{The impact of correlated read noise on time series}
+\subsection{The impact of correlated read noise on time series}
 We consider here some example science impacts of correlated read noise in these photometric apertures.
@@
 
-\subsubsection{Impact to Grism Time series}
+\subsection{Impact to Grism Time series}
 We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
@@
 
-\subsection{Goddard Cryogenic Vacuum (CV) Stability Tests}
-
-During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with the Optical telescope element simulator (OSIM).
-The ISIM has all the instruments with their internal optics and detectors but no telescope mirrors.
-The OSIM simulates the PSF expected when a star or other point source illuminates the JWST instruments.
-The point spread functions from CV3 most closely resembled the JWST flight point spread function and WLP8 defocused image of all ground based tests discussed in this work.
-Although the light curves from the CV3 stability tests were not able to achieve photon-limited performance to study the precision of transit and eclipse spectroscopy, there were some lessons learned from this data.
-
-\subsubsection{Comparison of Subarray and Full Frame Stability Tests}
-
-CV3 included a series of exposures about 16 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
-The LED was a narrowband source at 1.55 $\mu$m, which was used in imaging mode since this would result in a narrow-lined spectrum.
-While the spectroscopic modes are expected to be the most scientifically interesting modes for studying exoplanet atmospheres, the broadband lamps needed to produce a spectrum tend to be less stable than LEDs.
-Therefore, the test was designed with an LED with the hope of measuring the precision possible with the NIRCam optics and detector.
-
-As with the spatial scanning mode on HST \citep[e.g.][]{mccullough2012spatialScan,deming13}, spreading the light of a source over many pixels can improve the precision of spectroscopy.
-This is also accomplished by ground-based observatories by either de-focusing the telescope \citep{southworth2009defocusing} or by employing a beam-shaping diffuser \citep{stefansson2017diffusers}.
-By spreading the light source over many pixels, the light curve becomes less sensitive to flat fielding or intra-pixel sensitivity errors with telescope pointing jitter or seeing variations during an observation.
-Similarly, NIRCam time series observations can employ a weak lens to defocus a star's light.
-Figure \ref{fig:WLP8PSF} show the PSF of the +8 wave defocused images during the CV3 stability tests.
-
-We applied the ramps-to-slopes pipeline \texttt{nchdas} to do reference pixel correction, apply a bad pixel mask and calculate slopes or differences of the reads.
-The reference pixel correction uses the top/bottom pixels to remove pre-amp resets and side reference pixels to reduce the 1/f noise.
-The hexagonal PSF is summed with circular aperture with a radius of 70 pixels and a background annulus spanning from 75 to 100 pixels using the \texttt{photutils} package \citep{bradley2016photutilsv0p3}.
-The central peak may used to find a centroid of the star and center the circular aperture.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
-\caption{Weak Lens +8 PSF during CV3 testing.
-The central peak is used for centroiding, while the entire PSF is used for aperture photometry.
-A 70 pixel radius aperture (shown here is a black circle) is used for the source aperture.}\label{fig:WLP8PSF}
-\end{figure}
-
-The LED lamp was coupled to optical fibers to illuminate two separate detectors simultaneously with the intention of having two independent measurements to compare.
-Unfortunately, vibrations and jitter in the optical setup affect the relative flux in the two fibers.
-The coupling mechanism into the fibers is sensitive to the lamp position, so the flux from the two detectors is highly anti-correlated, as shown in Figure \ref{fig:CV3longTserAB}.
-To redice this fiber coupling effect, we average the flux from the two detectors for the rest of this discussion.
-This reduces the standard deviation of the time series to 500-1500 ppm.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.39\columnwidth]{cv3_A_vs_B_all.pdf}
-\caption{The light from an LED lamp is split into two optical fibers, which are highly anti-correlated likely because vibrations move the lamp relative to the fibers to couple one fiber better than the other.
-Here, the time series fit to a second order polynomial in time to remove long term trends and then the aperture flux for two detectors' fluxes are plotted against each other.
-For the discussion of CV3 tests forward, we average the two detectors (A1 and B4) to reduce this effect.}\label{fig:CV3longTserAB}
-\end{figure}
-
-A series of detector stability tests was performed using this +8 wave weak lens and 1.55 $\mu$m LED in a few different modes.
-A time series of all possible modes is shown in Figure \ref{fig:CV3longTser}.
-The full frame modes (FULL1 through FULL6) used 2 samples of the ramp for integration times of 21.5 seconds whereas the subarrays were tuned to have a similar integration time (21.3 sec for 20 Groups of a 320$\times$320 subarray and 25.1 seconds for 6 groups of a 640$\times$640 subarray).
-This ensured that during these 4 different types of subarray/full frame window sizes, the well depths achieved were similar.
-However, the groups are fit to a line for each pixel, so the useful portion of the ramp is the time between the last and first read or 20.2 seconds for the 320$\times$320 subarray versus 10.7 seconds for the FULL1 through FULL6 tests.
-
-It is apparent from Figure \ref{fig:CV3longTser} that the WLP8SUB test with a 320$\times$320 subarray and 20 groups of the ramp has smaller scatter on short timescales than the FULL1 through FULL6 tests.
-After removing a linear fit to the time series (to account for long term trends in the lamp), the standard deviation of the WLP8SUB data is 500 ppm whereas the FULL tests range from 1020 to 1540 ppm.
-For the FULL 2048$\times$2048 pixel integrations with 2 groups up the ramp, the count rate of photons is calculated in each pixel by subtracting the two groups (ie two reads for this RAPID mode) from each other and dividing by the group time (time between these two reads for this RAPID mode).
-For the WLP8SUB mode, a linear least squares fit is performed to the groups as a function of time and the slope of this line is the count rate on a pixel.
-The large number of groups used to fit this line ensures that the read noise is reduced as compared to the FULL 2 group tests by $2/\sqrt{N_G}$, where $N_G$ is the number of groups.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.79\columnwidth]{plot_mmm.pdf}
-\caption{Time Series plot through the CV3 photometric stability campaign.
-All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
-13 tests (FULL1 through FULL6) are all in full frame mode, while SUB used a 320$\times$320 subarray and SUB640 used a 640$\times$640 subarray.
-The WLP8SUB showed smaller standard deviation that the full frame tests, when the linear trend is removed.}\label{fig:CV3longTser}
-\end{figure}
-
-We consider two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
-\begin{enumerate}[noitemsep]
-	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
-	\item That the lamp is variable on short time scales of a frame (10.74 seconds) and sampling.\label{item:lampReasonCV3subFull}
+\clearpage
+\section{Fringing}
+
+The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
+Fringing will be less noticeable when many wavelengths are mixed together, but with grism spectra where the wavelengths are separated, the interference effects are more pronounced.
+We investigate whether this can manifest itself on the spectrum with the NIRCam grism by looking for periodic signatures that vary in frequency as a function of wavelength.
+
+Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
+The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
+The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
+The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
+The resulting spectrum shows high frequency ($\sim$0.2 px$^{-1}$ to $\sim$0.5 px$^{-1}$) variations far in excess of the photon and read noise.
+These oscillations increase in frequency at longer wavelengths (X pixels).
+The variations have peak-to-valley amplitudes of about 8\%.
+However, we expect that the fringing structure will hold relatively constant during time due to the temperature stability of the instrument.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
+\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
+An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
+}\label{fig:CV3GrismSpecFringing}
+\end{figure}
+
+\clearpage
+\section{Subpixel Crosshatching}
+
+\subsubsection{Subpixel Crosshatching Characterization}
+The flat field of the ALONG detector, which is used for NIRCam grism series, has a pronounced crosshatch pattern visible in Figure \ref{fig:crossHatchA5}.
+The patterns are located at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ counter-clockwise from the $+$X direction of the detector.
+The angle between these lines are 67.8$\degree$, 67.7$\degree$ and 44.5$\degree$.
+These angles and patterns can be analyzed with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
+
+The angles of the crosshatch patterns are determined by the crystal pattern of HgCdTe.
+HgCdTe has a zincblende structure with tetrahedral bond angles where each Hg or Cd atom is surrounded by 4 Te atoms \citep{gemain2012mercVacanciesHgCdTe}.
+HgCdTe detectors are manufactured using molecular beam epitaxy upon a substrate, a process which can result in topological defects with peak to valley amplitudes of 5-20 nm in height variations \citep{chang2008surfaceMorphologyHgCdTe}.
+The surface morphology of the HgCdTe crystal shows that the crosshatch patterns are are oriented along the intersection of the (211) growth plane of the crystal and the 8 HgCdTe slip planes.
+
+The relative angles of the HgCdTe slip planes and (211) growth plane are 44.42$\degree$, 67.79$\degree$ and 67.79$\degree$ \citep{chang2008surfaceMorphologyHgCdTe}, very close to the observed crosshatch angles.
+A projection of zincblende structure is shown in Figure \ref{fig:crossHatchA5} relative to the observed crosshatch patterns.
+The similarity between the crosshatch patterns in the flat field and the topological variations observed in \citet{chang2008surfaceMorphologyHgCdTe} leads to the likely conclusion that the surface variations lead to quantum efficiency variations.
+Thus, the crosshatch pattern is mostly likely related to the crystal lattice structure of the HgCdTe substrate and not the pixel circuitry.
+
+The crosshatch structure of the detectors extends down to the subpixel level, so it will not be fully corrected with a flat field division.
+This sub-pixel structure has been imaged with microscopy on a Euclid HgCdTe detector \citep{shapiro2018crosshatch}.
+Atomic force microscopy shows topological features that are approximately 1.2~$\mu$m in width \citep{chang2008surfaceMorphologyHgCdTe} compared to the 18~$\mu$m pixel sizes.
+The width of the structures can also be estimated from the behavior for crosshatch lines as they cross pixel boundaries \citep{ninan2019crosshatchHPF}.
+We estimate that the crosshatch pattern oriented at 90.9$\degree$ crosses 1 horizontal pixel for every 64 vertical pixels.
+While crossing the boundary, there are $\approx 38$ rows where the crosshatch pattern spans more than 2 pixels.
+If the crosshatch pattern has a tophat response function, then these 38 rows where the pattern spans two pixels imply a tophat full width of 0.6 pixels or a physical width of 10.8~$\mu$m for an 18~$\mu$m pixel pitch.
+This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
+We expect that the crosshatch pattern's width varies among detectors and that a tophat function is a poor approximation of the actual subpixel response.
+Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
+\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
+\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
+\caption{
+The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
+The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
+The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
+Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
+These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
+}\label{fig:crossHatchA5}
+\end{figure}
+
+The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (resolving crystal structures) and smallest for the long wavelengths.
+This is visible both in the throughput cross section of the flat field and the Fourier amplitude of the crosshatch as a function of wavelength.
+We find a steeper wavelength dependence to the crosshatch pattern near 0.9$\degree$ from horizontal in the frequency domain or 0.9$\degree$ from vertical in the length domain.
+%We also fit the crosshatch pattern.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{cross_sec_of_crosshatch.pdf}
+\includegraphics[width=.49\columnwidth]{fourier_power_from_fit.pdf}
+\caption{
+The crosshatch pattern changes as a function of wavelength, possibly because the shorter wavelengths resolve the structure better.
+The shorter wavelengths have deeper crosshatch troughs (left) and higher Fourier amplitudes (right).
+}\label{fig:crossHatchWavelengthDep}
+\end{figure}
+
+\subsection{Crosshatch Pattern Modeling}
+We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
+We divide the 2D Fourier power spectral density by the number of pixels in an input image.
+This was experimentally determined to give a power spectral density that does not change with the dimensions of the input image.
+\textcolor{red}{Can we justify this more? I thought it would be pixels$^2$}
+
+We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
+\begin{equation}\label{eq:analyticPSDradial}
+f(k_{x,i}',k_{y,i}', a_i, b,c) = a_i \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
+\end{equation}
+where $k_x'$ and $k_y'$ are rotated frequency coordinates in the parallel and perpendicular directions, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorentzian full width at half maximum of the perpendicular dependence.
+For each of the three angles, there is a set of rotated coordinates centered at $(k_{x,0},k_{y,0})$= (0,0) following:
+\begin{equation}
+k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
+\end{equation}
+and
+\begin{equation}
+k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
+\end{equation}
+We include three angles so that the total power spectral density is
+\begin{equation}
+f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e_b\right)},
+\end{equation}
+
+This model has 8 free parameters: three angles ($\theta_i$, three amplitudes ($a_i$), a joint parallel exponential constant ($b$) and joint Lorentzian width ($c$).
+Finally, we include an exponential term that fits the broad azimuthally symmetric background to all the power spectra,
+where $d$ is the amplitude of the radial ``background'', $k_r= \sqrt{k_x^2+k_y^2}$ is the radial frequency and $e_b$ is the radial background exponential constant.
+We only fit the region of the power spectral density above frequencies of 0.05 px$^{-1}$ to focus on the high frequency component of the flat field where the crosshatch is most prevalent.
+
+For the F300M filter and ALONG detector, we find 
+for $\theta_1 = 0.906 \pm 0.001 \degree, \theta_2 = 68.605 \pm 0.001 \degree, \theta_3 = 113.075 \pm 0.001, a_1 = 2.774 \pm 0.002 \times 10^{-7}, a_2 = 1.569 \pm 0.002 \times 10^{-7}, a_3 = 1.744 \pm 0.002 \times 10^{-7}, b=0.345 \pm 0.0005 $ px$^{-1}$, $c=2.05 \pm 0.07 \times 10^{-2}$ px$^{-1}$, $d=6.78 \pm 0.01 10^{-3}$ and $e_b=0.26 \pm 0.01$ px$^{-1}$.
+In other words, the separations between the vectors are $67.699 \degree, 67.831 \degree$, and $44.470 \degree$.
+The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
+
+NIRCam's 10 SCA's have very similar crosshatch angles with separations of 44.5 $\degree$ and 67.7 to 67.8 $\degree$.
+They tend to have one primary crosshatch axis oriented either along the X pixels or the Y pixels, with two flanking axes at $\sim 67.7 \degree$ to either side.
+The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
+The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
+Figure \ref{fig:crosshatchModelGallery} shows the best-fit crosshatch 2D power spectra.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
+\caption{
+Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
+The primary crosshatch tends to be aligned closely, but not exactly, with either the X or Y axis.
+The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
+}\label{fig:crosshatchModelGallery}
+\end{figure}
+
+\clearpage
+\subsection{Position of SubGrism Array}
+
+The crosshatch pattern varies in amplitude and angular dependence from one physical location on the detector to another.
+The ALONG detector has more pronounced crosshatching toward the middle of the detector that falls off toward the perimeter.
+On the other hand, the BLONG detector has more pronounced crosshatching towards the boundary.
+We fit the crosshatch pattern to three regions of the ALONG detector, which is the one used for the NIRCam grism time series mode:
+\begin{enumerate}
+	\item The 2048$\times$64 SUBGRISM position at the bottom of the array where the bottom left corner is (4,5) \label{subgrism64pos}
+	\item A 2048$\times$64 theoretical subarray at the top of the ALONG detector where the bottom left corner is (4,1984)
+	\item A 2048$\times$64 cutout of the full frame detector that is centered on the grism time series field point.
 \end{enumerate}
-As listed in Table \ref{tab:noiseSummary1overf}, the theoretical uncorrelated read noise for double-correlated samples (CDS) is about 33 ppm.
-However, the dark frame tests in Section \ref{sec:longDarks} show that 1/f noise significantly increases this value.
-When reference pixel corrections are applied to the data and a 70 pixel source radius is used, the measured CDS read noise from the dark test is 280 ppm for the long wavelength detector.
-Due to the source lamp setup discussed in Figure \ref{fig:CV3longTserAB}, we average the flux from detector A1 and B4, which lowers the read noise by $\sqrt{2}$  to 200 ppm.
-As a check, we perform aperture photometry on an un-illuminated regions of the time series stability tests and average the results of the two detectors.
-We find a standard deviation of 1100 to 1490 e$^-$/s or 150 ppm to 200 ppm of the 7.5$\times 10^6 e^-$/s flux, likely due to slight differences in the 1/f noise within the exposures.
-So, the measured standard deviation of ~1000 ppm during the full-frame tests is due largely to lamp variations and not read noise alone.
-
-The WLP8SUB integrations had 20 groups, so the measured read noise should be 280 ppm $\times \sqrt{2/20}$= 89 ppm.
-There is no un-illuminated region of the 320$\times$320 subarray that is as big as the source aperture so there is not empirical check on this 89 ppm estimate.
-The difference of 83 ppm between the measured full frame read noise and the calculated subarray is not enough to explain the full difference in precision between the two tests.
-Thus, we rule out \ref{item:readNReasonCV3subFull} as the main noise source.
-Instead, we conclude that the lamp has significant short-timescale variability that the faster samples used on the SUB320 test can average over.
-%The take-away from the comparison between subarrays is that one can reduce the read noise and short timescale variability with more samples up the ramp and a smaller subarray.
-
-\subsubsection{Row-by-row Background Subtraction}
-
-Even though we rule out read noise as the dominant noise source, we investigate ways to reduce the fractional contribution of read noise.
-If we use a row-by-row subtraction, as discussed in Section \ref{sec:indAmpAvg}, the read noise can be reduced.
-We use a procedure that reduces the 1/f electronic noise.
-First, we find the robust mean flux for each row of the background annulus with radii of 95 and 195 pixels.
-We then, subtract this value from the entire row of the image and perform aperture photometry on the residual image surrounding the source with a circular aperture of 70 pixels.
-This procedure reduces the measured read noise on a dark (un-illuminated) region to 60 to 100 ppm.
-
-\subsubsection{Best Pipeline Practices from CV3 Tests}\label{sec:CV3Lessons}
+
+The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
+The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
+The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
+The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
+The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
+We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
+\textcolor{red}{\textbf{Update this for latest full frame grism field point}}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64.pdf}\\
+\vspace{0.2in}
+\includegraphics[width=0.99\columnwidth]{subg_pos_topGrism64_psd.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_fullfGrismRegion_psd.pdf}\\
+\includegraphics[width=0.99\columnwidth]{subg_pos_subgrism64_psd.pdf}\\
+\caption{
+The top of the array has the smallest level of crosshatching and the middle has the largest.
+This is visible in the flat field images (top three panels) and their power spectral density functions (bottom three panels) for three different sections of the A5 detector: a theoretical ``aperture'' position at the top of the array (first plot from top), the full frame position near Y=512 (second plot from top) and the nominal SUBGRISM64 at the bottom of the array (third plot from top).
+The bottom left corner for each subarray is listed in parentheses in the title of the flat field plot and the best-fit amplitudes are listed in the title of the power spectral density plot.
+ }\label{fig:subpixScanSimulation}
+\end{figure}
+
+\subsection{Subpixel Crosshatching Calculation}\label{sec:CrosshatchSim}
+
+The subpixel crosshatch pattern can potentially introduce time-variable noise as the point spread function drifts with telescope pointing drifts, long timescale jitter.
+NIRCam observations are expected to have a root-mean-square deviation of 6.0 mas in each axis when measured in 15 second intervals over a 10,000 second observation.\footnote{See \url{https://jwst-docs.stsci.edu/display/JTI/JWST+Pointing+Performance\#JWSTPointingPerformance-Pointing\_stabilityPointingstability}}
+
+We simulate the effect of this jitter on NIRCam time series observations with the following steps:
+\begin{itemize}
+	\item Fit the existing flat field to a crosshatch model in the Fourier domain
+	\item Extrapolate the crosshatch model to higher frequencies (30 px$^{-1}$) to estimate the sub-pixel structure
+	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Multiply the PSF by the simulated flat field
+	\item Shift the PSF along the X and Y directions up to a magnitude of 6 mas
+	\item Bin the simulated images into the native pixel size
+	\item Divide by the pixel-to-pixel flat field
+	\item Measure the relative flux with a photometric aperture
+\end{itemize}
+
+We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
+$60^2$) to convert from the scale-invariant Power Spectral Density to the simulated PSD.
+We then assign random phases uniformly from 0 to 2$\pi$ for the complex Fourier plane because the original image's complex phase distribution is similar to uniform.
+Finally, we take the real part of the inverse Fourier transform to create an oversampled image, as shown in \ref{fig:crossHatchSimPSF}.
+For comparison to the original flat in Figure \ref{fig:crossHatchA5}, we binned to the oversampled flat field to the native LW pixel (1.0 native pixels=60.0 oversampled pixels $\approx$0.063 \arcsec).
+This simulated pixel flat field with dimensions of 26 by 26 LW pixels has a peak of 1.15 to trough of 0.90 with a robust standard deviation of 0.05.
+For comparison, the middle of the original F300M flat for the ALONG detector has a robust standard deviation 0.06.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.32\columnwidth]{sim_flat_Oversampled_plot.pdf}
+\includegraphics[width=.32\columnwidth]{sim_flat_Pixel_plot.pdf}
+\includegraphics[width=.32\columnwidth]{psf_with_phot_ap_with_crosshatch.pdf}
+\caption{
+The steps of the sub-pixel crosshatch photometry simulation are shown here.
+We simulate an over-sampled flat (left) by extrapolating the power spectrum to frequencies above the pixel sampling level.
+This simulated flat is binned to the native pixel resolution to produce a pixel flat field (middle) that would be used by a standard pipeline that has no sub-pixel corrections.
+A \texttt{WebbPSF} point spread function is created at the oversampled resolution, multiplied by the oversampled flat field and then binned to native resolution (right).
+Finally, the simulated image is divided by the pixel flat field as would be performed in a standard pipeline reduction.
+The simulated PSF shows the source and background apertures used in the simulation, which are centered on the PSF.
+}\label{fig:crossHatchSimPSF}
+\end{figure}
+
+We next calculate a point spread function using \texttt{webbpsf} \citep{perrin2014webbpsf}, oversampled by a factor of 60.
+\texttt{webbpsf} includes an optional blurring due to high frequency pointing jitter.
+We set this Gaussian blurring parameter to 1 mas to simulate a worst-case scenario where the pointing drift is dominated by long-timescale behavior with minimal high frequency jitter.
+We multiply the oversampled \texttt{webbpsf} source by the simulated oversampled flat and bin this to native pixel resolution to create a simulated observation as shown in Figure \ref{fig:crossHatchSimPSF}.
+This simulated observation is divided by the binned simulated flat as would be done by a standard pipeline's flat field correction.
+
+We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
+The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
+For each shifted PSF, we multiply this by the subpixel crosshatch pattern and bin the result.
+These simulated operations represent pointing drift on the subpixel scale.
+
+We calculate aperture photometry with a circular aperture with a radius of 7 pixels and a background annulus from 7 to 10 pixels on each of the observations.
+The aperture is re-centered by the same position as the shift direction.
+For each sub-pixel pointing drift, the aperture sum is subtracted by the background flux average per pixel multiplied by the pixel area of the source aperture.
+While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
+The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{scan_F300M_x_short_scan.pdf}
+\includegraphics[width=.49\columnwidth]{scan_F300M_y_short_scan.pdf}
+\caption{
+The simulated subpixel crosshatch pattern from Figure \ref{fig:crossHatchSimPSF} for the F300M filter will cause spurious flux changes with small pointing drifts.
+Here we show scans in the X direction and Y direction from the center of the image and a subpixel scale.
+The amplitude of these scans is 6.3 mas for the $\sim$63 mas/px plate scale of the LW detector.
+These are correctable with smooth functions such as polynomials.
+}\label{fig:subpixScanSimulation}
+\end{figure}
+
+The subpixel crosshatch structure does indeed create flux variations with image motion as shown in Figure \ref{fig:subpixScanSimulation}.
+The amplitude of the flux changes is potentially up to 150 ppm.
+This is significant when compared to atmospheric features of giant planets ($\lesssim$ 100 ppm) or the transit depth of an Earth-like planet transiting a sun-like star ($\lesssim$ 80 ppm).
+
+Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
+A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
+Alternatively, a Gaussian process regression could be applied.
+Centroiding is possible in imaging and spectroscopic modes using PSF fitting or cross-correlation.
+When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
+Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
+Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
+This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
+
+\subsection{Time Series Simulation}
+The JWST fine steering mirror (FSM) is designed to correct any telescope pointing errors that are not full corrected by the reaction wheels.
+The JWST attitude control system team provided a simulation of the expected pointing performance shown in Figure \ref{fig:tserPointingFull}.
+
+The dominant variations in the pointing in the simulation from Figure \ref{fig:tserPointingFull} are High Gain Antenna (HGA) moves.
+These are moves are designed to keep the antenna pointing at ground-based antennas for telemetry or data download.
+Fortunately, the errors due to HGA moves damp quickly on $\lesssim$ 1 minute e-folding timescales, as show in Figure \ref{fig:tserPointingZoom}.
+This means that for 1 minute integrations, only about 1\% of integrations will be affected by HGA moves and the data for these moves could be discarded.
+Other pointing errors can be caused by reaction wheel jitter, the MIRI cryocooler and fuel slosh in the fuel tanks.
+The effect of the reaction wheels and MIRI cryocooler will be to blur the PSF over an integration since they are higher frequency $\gtrsim 1$ Hz.
+Fuel slosh happens at the beginning of a visit after the telescope is slewed, but will dampen quickly on 100 second timescales.
+Therefore, the largest contributor to pointing variations will likely be HGA moves and thermal inter-boresight motion.
+
+\textcolor{red}{Once, we have thermal inter-boresight motion, show how this affects pointing/flux}
 
 \begin{figure*}
-\gridline{\fig{ES-WLP8SUB_pipeline_parameters.pdf}{0.39\textwidth}{SUB320 Time Series}
-\fig{{ES-FULL4_pipeline_parameters.pdf}}{0.39\textwidth}{FULL4 Time Series}}
-\caption{Flat fielding, linearity corrections and intrapixel capacitance corrections have a relatively small impact on the time series precisions measured during the CV3 test.
-Each table lists the measured noise (in ppm) when we turn on/off IPC correction (vertical direction), flat fielding (horizontal direction) and the linearity correction (diagonal direction).
-The IPC and flat fielding corrections are negligible.
-Above 50\% well depth, the HgCdTe detectors become less sensitive to photons, so applying the linearity correction naturally increases the apparent noise.
-}\label{fig:CV3pipeParamsWLP8}
+\gridline{\fig{histos_v2_v3.pdf}{0.45\textwidth}{Pointing Histograms} 
+\fig{tser_v2_v3_zoom_none.pdf}{0.45\textwidth}{Pointing Time Series} }
+\caption{The typical pointing stability is expected to be extremely stable to within a standard deviation of 2.4 mas (0.04 long wavelength pixels).
+This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
+}\label{fig:tserPointingFull}
 \end{figure*}
 
-We investigated best practices for the pipeline and analysis by running the raw data through the pipeline and sequentially adding and subtracting steps that go into producing light curves.
-We experimented with the methodology for turning raw detector reads up the ramp into count rates on the detector, the intrapixel capacitance (IPC) correction, flat fielding, reference pixel correction and detector non-linearity.
-After the calibrated images are created, we experimented with different types of aperture photometry including different geometries, background calculations and aperture sizes.
-
-We find that the intrapixel capacitance (IPC) correction, flat fielding and linearity correction have relatively small impacts on photometric precision.
-In Figure \ref{fig:CV3pipeParamsWLP8} we show the standard deviation of the flux after averaging the A1 and B4 detectors and removing a linear trend.
-We quote standard deviations for two example tests: SUB320 and FULL4.
-The IPC corrections matter less than 0.01 ppm, because the deconvolution kernel conserves flux.
-So long as the aperture is significantly wider than the 3$\times$3 pixel kernel, the flux in an aperture should be constant.
-The flat fielding correction has less than a 2 ppm impact to the standard deviation because the image motion is at the sub-pixel level.
-
-The linearity correction does consistently increase the signal to noise by 7 to 23 ppm but this is a natural consequence of the np photodiode in our detectors.
-This is because the photodiode becomes decreasingly less sensitive to photons as it the well capacity is approached.
-Note that at the extreme of saturation, the photodiode no longer senses new photons so you would measure a standard deviation of 0 ppm.
-Therefore, the np photodiode naturally decreases the measured standard deviation of flux that will appear larger with a non-linearity correction.
-
-The weak lens PSF illuminates the pixels to 15,000 to 30,000 DN or 25-50\% well depth and the non-linearity for this well depth is 0.5 to 2\%.
-This means that the measured standard deviation for linearized data should be about 1\% larger than for raw data, similar to the measurements in Figure \ref{fig:CV3pipeParamsWLP8}.
-We therefore conclude that the non-linearity correction makes a small difference to the final derived precision.
-
-After experimenting with these configurations, we find the following pipeline steps are important:
-\begin{itemize}
-	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read.
-This is  expected because more ramps reduce the 1/f and read noise, but the disparity (500 ppm versus 1200 ppm) is too large to be due to read noise alone.
-	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
-	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus) because it reduces the read noise.
-	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
-\end{itemize}
-
-We also found reduction steps that had very little impact on the final photometric precision including
-\begin{itemize}
-	\item IPC corrections ($\lesssim 0.01$ ppm)
-	\item Flat-fielding ($\lesssim 2$ ppm)
-\end{itemize}
+\begin{figure*}
+\gridline{\fig{tser_v2_v3_zoom_1.pdf}{0.45\textwidth}{Pointing Series Zoom 1} 
+\fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
+\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
+}\label{fig:tserPointingZoom}
+\end{figure*}
+
+We simulate the change in flux as a function of position using our oversampled flat field, as in Figure \ref{fig:subpixScanSimulation}.
+First, we bin the sub-pixel jitter time series into 1 minute time bins to represent 1 minute integrations, as shown in Figure \ref{fig:tserPointingAndFlux}.
+We then use the positions to shift the PSF on the oversampled flat field as listed at the beginning of this section.
+The resulting flux variations are very small compared to factors like the 1/f noise.
+The standard deviation of the time series due to small line-of-sight telescope jitter on top of the subpixel crosshatching pattern is only 6 ppm.
+Therefore, the line-of-sight subpixel jitter is expected to have a small affect on NIRCam stability.
+Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
+
+\begin{figure*}
+\gridline{\fig{subpx_jitter_sim.pdf}{0.7\textwidth}{}}
+\caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
+The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
+}\label{fig:tserPointingAndFlux}
+\end{figure*}
 
 \clearpage
-\subsection{OTIS Tests}
-
-A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
-However, there is no feasible way to place a point source lamp far enough away to simulate the imaging of astrophysical objects onto a JWST instrument, so an alternate lamp setup is used.
-During these tests, there were two configurations 1) the ``half pass" tests where lamp sources within the optical system and 2) ``pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain to the detectors.
-
-\subsubsection{Pass and a Half Grism Time Series Test - Photometry}
-The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
-Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
-The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
-A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
-Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
-This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
-The telescope is suspended vertically and can potentially swing under these vibrations.
-
-The point spread function through the weak lens and optical setup create a very unusual point spread function for the short wavelength channel, shown in Figure \ref{fig:otisPSFs} that has multiple clumps of emission.
-We perform aperture photometry on a knot of emission at (1090 px, 230 px) for the short wavelength detector.
-This knot is concentrated enough to fit with a 2D Gaussian and centroid this Gaussian to ~0.2 pixels, which can be used to track the motions of the PSF due to the position oscillations.
-For the long wavelength detector, we initially extract a box aperture to create a broadband light curve.
+
+\section{Random Telegraph Noise and RC pixels}
+Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
+The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
+These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.
+
+For Weak Lens photometric aperture (such as a 70 pixel radius aperture), there will be of order 2-4 pixels exhibiting RTN.
+The RTN may not be removed by jump detection algorithms if they are similar order of magnitude to the photon noise for a single pixel ($\sim$180 DN).
+If these are not identified, the RTN can contribute $\sim$200 counts in 4$\times 10^7$ or 5 ppm changes.
+
+There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
+These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
+There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
 
 \begin{figure*}
-\gridline{\fig{wlp8_otis_psf.pdf}{0.7\textwidth}{WLP8 Image} }
-\gridline{\fig{{grism_otis_psf.pdf}}{0.7\textwidth}{Grism Image}}
-\caption{Median images of the short wavelength (SW) weak lens mode and long wavelength (LW) grism spectroscopy that were used simultaneously in a grism time series stability test.
-Due to the OTIS optics setup, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 (Figure \ref{fig:WLP8PSF}) or flight.
-We perform photometry on a single knot of emission as highlighted as the blue circular aperture.
-For the grism time series broadband test, we use a rectangular aperture and a vertically offset background box.
-}\label{fig:otisPSFs}
+\gridline{\fig{example_rtn.pdf}{0.45\textwidth}{RTN Pixels} 
+\fig{{example_rc.pdf}}{0.45\textwidth}{RC pixels}}
+\caption{Pixels sometimes exhibit unusual behaviors that are not related to counting photon flux.
+Examples are shown for RTN and RC pixels.
+}\label{fig:RTNandRC}
 \end{figure*}
 
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Time series of the simultaneous SW/LW Time Series Stability test.
-The image motion in this test due to vibrations and oscillations is two orders of magnitude larger than expeced in flight.
-The complicated PSF and low signal on the short wavelength channel compromise its sensitivity whereas the long wavelength broadband flux is dominated by lamp instability.
-}\label{fig:otisLWSWtser}
-\end{figure*}
-
-The locations of the subarrays have ROWCORNER=431.
-This means there are not top or bottom reference pixels.
-If we use a horizontally-displaced background region, the pre-amp offsets will not be properly subtracted.
-We therefore subtract the median from each column and then each row (not including the grism aperture).
-We subtract the median of each column first to remove the amplifier offsets and then the median of each row second to reduce the 1/f noise.
-Figure \ref{fig:otisLWcolrowSub} shows the dramatic effect of subtracting the columns and rows from each aperture.
-
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{raw_tser_LWgrisMPPVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Slope Images}
-\fig{raw_tser_LWgrisMMMRowColSubVertBackbox_otisSWLWsimult.pdf}{0.49\textwidth}{Column-by-column and row-by-row subtraction}}
-\caption{The grism time series contains correlated read noise due to pre-amplifier offsets over each amplifier and 1/f noise in the horizontal (fast read) direction.
-Row-by-row-subtraction dramatically decreases the noise due to 1/f noise while column-by-column subtraction dramatically decreases the pre-amplifier offset noise.
-}\label{fig:otisLWcolrowSub}
-\end{figure*}
-
-\subsubsection{Pass and a Half Grism Time Series Test - Spectroscopy}
-
-\begin{figure*}
-\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
-\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
-There are small offsets in the flux os the spectrum also because of the flat field.
-}\label{fig:otisLWflatVsNoFlat}
-\end{figure*}
-
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.49\textwidth}{Dynamic Spectrum}
-\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW_aligned}{0.49\textwidth}{Dynamic Spectrum with Alignment}}
-\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes).
-These are dramatically reduced when using cross correlation
-}\label{fig:otisLWdynSpec}
-\end{figure*}
-
-%\begin{figure*}
-%\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}
-%\end{figure*}
-
-We also analyze the spectroscopic time series for the OTIS grism time series.
-The extracted spectrum and dynamic spectrum (how each wavelength varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
-Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.
-
-The wavelength-binned time series shows dramatic variations (shown in Figure \ref{fig:otisWavebinTSeries}) due to the shifts in the dispersion direction.
-
-\begin{figure*}
-\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Time Series without Alignment}
-\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_aligned.pdf}{0.49\textwidth}{Time Series with Alignment}}
-\caption{The position variations along the dispersion direction cause large fluctuations in the time series.
-These are dramatically reduced when cross-correlating and finding the peak to adjust for wavelength shifts
-}\label{fig:otisWavebinTSeries}
-\end{figure*}
-
 \clearpage
-\subsection{Using SW centroid for LW grism}
-
-We attempt to use the centroids form the SW imaging as input for a broadband grism aperture.
-This potentially provides a way to input centroid information without cross-correlating a spectrum.
-However, the SW centroids add more noise to the photometry as seen in Figure \ref{fig:otisLWSWtserShift}.
-
-\begin{figure*}
-%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
-\gridline{\fig{tser_LWSW_OTIS_w_shift.pdf}{0.6\textwidth}{Grism Time Series}}
-\caption{Same as Figure \ref{fig:otisLWSWtser} but where the SW shifts were applied (with a scaling factor of 0.5) to the long wave.
-The aperture shifting appears to increase the flux errors with centroid shifts.
-}\label{fig:otisLWSWtserShift}
-\end{figure*}
-
-\subsection{Differential Spectrum}
-We investigate whether the lamp fluctuations can be removed by dividing by a signal-to-noise-weighted broadband time series.
-\begin{figure*}
-\gridline{\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_differential.pdf}{0.49\textwidth}{Differential Time series}}
-\caption{Differential time series
-}\label{fig:otisLWDiffdynSpec}
-\end{figure*}
-
-\clearpage
-
-\subsubsection{Half Pass Subarray Size Tests}
-
-As with the CV3 tests in Section \ref{sec:CV3Lessons} and Figure \ref{fig:CV3longTser}, we found the highest precision lightcurves when using subarray read configurations.
-Figure \ref{fig:OTISsubarrays} shows the many subarrays explored in a set of time series.
-As the number of reads up the ramp becomes larger and larger, the standard deviation increases.
-This would be expected if the read noise contributed significantly to the standard deviation so that ramp fitting decreases the read noise.
-The perplexing thing is, though, that this is even true if we throw away all the intermediate reads.
-That is, with all readout modes, count rate (ie. slope image is approximated by the last subtracted by the first read.
-Here the number of reads in between these is irrelevant.
-A possible way to explain the superior standard deviation for the smallest 2048$\times$64 subarray is not that more reads increase precision on the slopes but rather the small subarray has a smaller contribution from spatially correlated noise.
-When larger frames are read out, for example, the 1/f noise becomes increasingly uncorrelated from read to read.\textcolor{red}{Wrote this when very tired. Is this correct and logical?}
-
-Note that the integration times are different for these 4 tests.
-They are 39.9, 39.9, 32.3, 31.8 and 32.2 for the 64-STRIPE, 128-STRIPE, 256-STRIPE, 256-WIND and FULLFRAME respectively.
-Perhaps the lamp has oscillations on a timescale that are averaged out efficiently at 39.9 seconds but not 32.3 seconds?
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
-\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
-The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
-With this very crude box extraction (and no background subtraction), the standard deviation decreases as the number of groups up the ramp becomes more numerous.
-This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
-\caption{An experiment with circular background-subtracted photometry shows dramatically improved precisions over raw aperture sums in Figure \ref{fig:OTISsubarrays}.
-Additionally, a median subtraction of all background pixels per row improves the precision.}\label{fig:OTISSubConfigCircularAp}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-128-STRIPE-72.pdf}
-\includegraphics[width=0.48\columnwidth]{apertures_for_NRCN83-256-STRIPE-72.pdf}
-\includegraphics[width=.48\columnwidth]{subarray_config_tser_backsub_rect.pdf}
-\caption{Subarray configuration test during OTIS. The position of the background subtraction box has a dramatic effect on the precision of the time series.
-This is due to correlated 1/f noise along the horizontal fast-read direction.
-If the background subtraction box is on an adjacent amplifier, it captures a very different 1/f noise behavior than if it is on a shared amplifier.
-The amplifier boundary is shown as a vertical blue dashed line.
-\textcolor{red}{To do: understand better why the vertically offset box is better? Also, show the aperture as a separate figure.}
-\textcolor{blue}{Now I understand it as coming from which amplifier the background box is on.}}\label{fig:OTISRectBacksub}
-\end{figure}
-
-\clearpage
-\subsection{GL Dewar Tests}
-\begin{figure*}
-\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
-		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
-		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{Two photometric apertures are placed on the subarray, where they both see common-mode variations in the lamp.
-The ratio of the time series of each aperture shows a handful of integrations at the beginning that stand out, which quickly stabilize to the 240 ppm level.
-}\label{fig:GLtSeries}
-\end{figure*}
-
-The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
-The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
-Comparing the GL dewar results to the asic dewar can be helpful in isolating the source of noise sources in the NIRCam system.
-If the GL dewar and asic dewar share the same types of correlated noise sources, these can be attributed to the detectors.
-If the asic dewar introduces or eliminates some correlated noise sources, these can be attributed to the readout electronics.
-
-For the GL dewar, an LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
-Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
-The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
-This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
-If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
-As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
-This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detector.
-
-\begin{figure*}
-\gridline{\fig{ap_labels_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Apertures}
-		\fig{raw_tser_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Raw time series}
-		\fig{refcor_phot_S02illum1miAllBacksub_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
-\caption{We repeat the time series as Figure \ref{fig:GLtSeries} but add a vertically displaced background subtraction box to each aperture.
-The background boxes reduce the ``ramp-up'' effect and longer timescale variations of the detector.
-The ratio of the time series of each aperture has a larger scatter larger than Figure \ref{fig:GLtSeries} because subtracting the background adds to the 1/f noise (correlated along the horizontal direction) rather than reducing the 1/f noise.
-}\label{fig:GLtSeriesBacksub}
-\end{figure*}
-
-We also introduce a background aperture, shown in Figure \ref{fig:GLtSeriesBacksub} to remove background variations and any amplifier offsets that could affect the flux.
-The resulting time series has a smaller amplitude ``warmup'' and smaller oscillations than Figure \ref{fig:GLtSeries}.
-When we divide the background-subtracted flux for each aperture by the other to make a ratio time series, the resulting noise is higher than in Figure \ref{fig:GLtSeries}.
-This indicates that the background subtraction step introduces more noise than it removes when comparing the differential flux between the two apertures.
-We suspect that 1/f noise in the background aperture causes this increase.
-To conclude, background subtraction improves the absolute flux stability but worsens the differential flux across the apertures.
-When observing an exoplanet time series, for example, scientists may wish to use one reduction technique for the absolute time series to derive the planet orbital parameters, say.
-Then, when analyzing the spectrum, they may wish to use an alternate technique to assess the differential flux from one wavelength to another.
-
-\subsubsection{Across Detectors}
-We also examine the time series across detectors from ``Run104'' to test whether there are systematics unique to each detector/readout electronics.
-We compare aperture photometry on the S02 versus S03 detector with background subtraction.
-The resulting time series are shown in Figure \ref{fig:GLtSeriesAcrossDetectors}.
-We an Allan variance diagram to show how well the flux scales like $\sqrt{N}$ statistics for $N$ integrations.
-The curves track the expected $\sqrt{N}$ behavior but lie well above the theoretical read and photon noise limit.
-This is likely because the 1/f noise is highly correlated within the aperture whereas the theoretical and photon noise limit assumes that the noise in each pixel is independent.
-We do not quire reach the noise levels interesting to the exoplanet noise regime (30-100 ppm).
-
-\begin{figure*}
-\gridline{\fig{raw_tser_crossDetectorS02Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S02 detector}
-		\fig{raw_tser_crossDetectorS03Backsub_GLrun104.pdf}{0.48\textwidth}{Time series for S03 detector}}
-		\fig{allan_var_removelinear_True_gl_across_detectors.pdf}{0.48\textwidth}{Allan variance diagram for the ratio of the S02 to S03 background-subtracted detector fluxes}
-\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
-The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works below the 100 ppm is not measurable with this test.}\label{fig:GLtSeriesAcrossDetectors}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_side_backsub_removelinear_True_3.pdf}{0.48\textwidth}{Allan Variance}}
-\caption{The same test as Figure \ref{fig:GLtSeriesAcrossDetectors} shows {\bf dramatically} smaller noise if (1) the aperture size is increased and (2) a horizontally displaced aperture is used to reduce 1/f noise.}\label{fig:GLtSeriesRun112}
-\end{figure*}
-
-\clearpage
-
-\subsection{Run 112 - Subarray 4}
-We also investigate a slightly longer time series for GL dewar which approaches the timescales of interest to exoplanet transit lightcurves.
-Figure \ref{fig:GLtSeriesRun112} shows the flux ratio between detectors S01 and S02 for the Run 112 Subarray 4 ``Hi4'' test.
-The Allan variance plot again scales like the $\sqrt{N}$ statistics but above the theoretical noise limit.
-
-\begin{figure*}
-\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4_no_backsub.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio No Background Sub}
-\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
-\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}\label{fig:GLtSeriesRun112}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
-\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
-\caption{Allans variance for background-subtracted rectangular photometry on the S02 and S03 detectors.
-The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
-\end{figure*}
-
-\subsection{Run 112 - Subarray 6}
-Subarray 6 had higher lamp current and thus higher counts and lower photon noise, which approaches the exoplanet atmospheric feature regime (30-100 ppm).
-In this test, we take the ratio of flux on one detector to the other.
-This removes the lamp variations but allows the
-
-It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
-This is surprising given that S01 is a short wavelength cutoff detector, S02 is a short wavelength cutoff detector and SO3 is a long wavelength cutoff detector.
-Furthermore, the S01 and S02 detectors are powered by a different pair of cards than the S03 detector.
-
-\begin{figure*}
-\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_no_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio No Background Sub}
-\fig{azlab_ratio_tser_gldewar_run112_sub6_hi4_side_backsub_biggerAp.pdf}{0.48\textwidth}{Time series for S01 / S03 Ratio With {\it Side} Background Sub}}
-\caption{Time series for rectangular photometry on the S01 and S03 detectors as well as side background-subtracted Rectangular photometry.
-The background aperture was placed on the side reference pixels to reduce 1/f noise.}\label{fig:GLtSeriesRun112sub6}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long 320 Multi-Exposure Baseline}
-\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
-\caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
-Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
-For the GL dewar, the ratio of the two detectors' fluxes (after background subtraction) scales like $\sqrt{N}$ statistics down to the $\sim$60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
-\end{figure*}
-
-\clearpage
-\subsection{Asic Dewar Tests}
-We performed a variety of stability tests using a dewar with the same type of detectors, readout electronics and temperature control as the in-flight parts.
-The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
-The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (3.0 to 3.6~$\mu$m) LEDs.
-The LEDS are type LMS17LED-R and LMS34LED-R from Electro Optical Components, Inc.
-
-The dewar has limited space for optical illumination so the LEDs' light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
-The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
-The illuminated portions of the detector are used for aperture extractions while the shadows are used for background subtraction apertures.
-
-No LEDs used in ground-based tests were as stable as the desired precisions relevant to exoplanet targets (sub 30 ppm), so multiple arrays are used to correct for lamp variations during illuminated stability tests.
-The best absolute stability of an LED measured on a detector was 0.05\% ppm over 2 hours.
-More typically, the variations were 1\%, although the current measured with a multimeter was stable to 0.1\%.
-A ratio time series is constructed by dividing the time series derived from one detector to another time series from a different detector.
-
-\subsubsection{Persistence}\label{sec:persistence}
+
+\subsection{Persistence}\label{sec:persistence}
 HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.
@@
 
-\clearpage
-\subsubsection{Reference pixels versus background subtraction}
-One important question that can affect the placement of subarrays is whether background subtraction effectively achieves the same result as with reference pixel correction.
-This is tested in Figure \ref{fig:BackgVsRefpix}.
-In this case, the background aperture is displaced horizontally from the source aperture and within the same amplifier to best reduce 1/f noise and pre-amplifier offsets.
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf256_no_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=False, 4968 ppm}
-\fig{azlab_ratio_tser_rpi_vs_rpf_nobacksub_rpf256_no_backsub_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=True, Bsub=False, 221 ppm}}}
-{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_with_bsub_no_refpix_rpf256_with_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Refpix=False, Bsub=True, 198.2 ppm}
-\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Refpix =True, Bsub=True, 197.1 ppm}}}
-{\gridline{\fig{azlab_ratio_tser_baseline_bsub_by_frame}{0.33\textwidth}{Refpix=False, Bsub=Frame By Frame, 197.5 ppm}}}
-\caption{The time series of the flux ratio between two detectors shows that background subtraction achieves most of the value (within 1 ppm) of reference pixel correction to remove pre-amplifier offsets and 1/f noise.
-Furthermore, the background subtraction can be performed on the slope images rather than on a frame-by-frame basis, to get within 0.4 ppm of the value using reference pixels.
-}\label{fig:BackgVsRefpix}
-\end{figure*}
-
-\clearpage
-\subsubsection{Pre-Amplifier Reset Test}
-We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
-We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
-
-Each pre-amplifier is reset once per frame by the current flight parameters.
-This causes amplifier offsets because each amplifier is reset to a different value with some noise, as visible in Figure \ref{fig:RPFrefpix}.
-The pre-amplifier resets, however, can be largely corrected for by reference pixels or background subtraction.
-Figure \ref{fig:RPFrefpix} also shows a corrected image where the top reference pixels (a 512 pixel wide 4 pixel tall region per amplifier) is used to subtract the amplifier offsets.
-
-\begin{figure*}
-{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.8\textwidth}{No Reference Pixels RPF}}}
-{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.8\textwidth}{Reference Pixel RPF}}}
-\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
-\end{figure*}
-
-As a further demonstration that reference pixels can subtract amplifier offsets or background subtraction, we show time series for tests with a reset per frame and a reset per integration in Figure \ref{fig:RPFvsRPItseries}.
-The resets-per-frame have similar noise to the resets-per-integration on short timescales.
-For the 2048x256 subarray, the standard deviation were 197 ppm and 183 ppm for RPF and RPI respectively.
-For the 2048x64 subarray, the standard deviations were 327 ppm and 180 ppm for RPF and RPI respectively.
-The difference between these is dominated by the slope through the test.
-We suspect the flatter slow during RPI is a coincidence because the the resets within an integration (less than one minute) are unlikely to propagate a gradual slope over several hours.
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf256_no_bsub_no_refpx_both_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
-\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi256_no_bsub_no_refpx_both_NRCRPIBSELINE0P9MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
-{\gridline{\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpf064_no_bsub_no_refpx_both_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
-\fig{azlab_ratio_tser_rpi_vs_rpf_no_bsub_no_refpix_rpi064_no_bsub_no_refpx_both_NRCRPI64STRIPE1P5MA.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
-\caption{Reset per integration versus reset per frame where no reference pixel correction and no background subtraction have been applied.}\label{fig:RPFvsRPItseries}
-\end{figure*}
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
-\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
-{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
-\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
-\caption{Reset per integration versus reset per frame where both reference pixel correction and background subtraction have been applied.}\label{fig:RPFvsRPItseries}
-\end{figure*}
-
-We also repeat the long baseline test with a 2048x256 subarray and 8 groups up the ramp but this time with no illumination.
-This allows us to compare the noise in e-/px when illuminated versus the noise in e-/px.
-If these two values are the same, this indicates that electronic noise enters both detectors and limits photometry precision in ppm.
-We find instead that the illuminated data has a much higher standard deviation (9 e$^-$/px, compared to the theoretical 1.8 e$^-$/px averaged over the aperture).
-The dark time series had a standard deviation of 1.9 e$^-$/px compared to the theoretical (uncorrelated) 0.2 e$^-$/px averaged over the aperture.
-
-\clearpage
-
-\subsubsection{Stripe versus Window Mode}
-JWST users may select between two types of subarrays within NIRCam grism time series.
-This is specified with the Astronomy Proposal Tools (APT) software in the ``NIRCam Grism Time Series'' template with ``No. of Output Channels".
-When the output channels are set to 4 (stripe mode), the frame time is approximately four times faster than 1 output channel (window mode).
-The exact timing is slightly different than a factor of 4 due to overheads.
-The advantage of stripe mode is that it allows more samples up the ramp in an integration and also shorter minimum integration times to enable observations of brighter sources.
-The stripe mode uses four different amplifiers, which could potentially lead to differences between the 4 regions each 512 pixels wide.
-The stripe mode is the same as standard full frame imaging when the height of the stripe is 2048 pixels tall.
-
-Figure \ref{fig:stripeVsWindowAZlab04} shows the time series for a stripe versus window mode test.
-In both cases the subarray is SUBGRISM256, which is 2048 pixels wide and 256 pixels tall.
-The subarray is placed at the top of the detector where 4 rows of reference pixels are accessible.
-In each case, these are the ratios of time series between two Long wavelength detectors derived from aperture photometry with background subtraction.
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode Time Series}
-\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
-\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier), but the overall trends are similar.
-}\label{fig:stripeVsWindowAZlab04}
-\end{figure*}
-
-The window mode does have the benefit of only using one amplifier.
-This means that 1/f noise can be subtracted along rows whereas in stripe mode, 1/f noise has to be subtracted an an amplifier by amplifier basis (within 512 wide amplifier regions).
-The trade-off is that there are 4 times fewer frames per second.
-We assess the relative value of the 1/f correction versus different reads by placing the source aperture horizontally more than 512 pixels from the background aperture.
-For stripe mode, this means that the apertures are on different amplifiers.
-For window mode, this means the apertures are on the same amplifier.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=0.7\columnwidth]{darkwindow_img.pdf}
-\includegraphics[width=.7\columnwidth]{darkstripe_img.pdf}
-\caption{The noise characteristics and tradeoffs of stripe (4 amplifier outputs) versus window (1 amplifier output) are visible in this dark integration.
-The stripe mode has 8 groups while the window has 2 groups for the same integration time.
-The increased number of groups allows for averaging dark frames but the individual amplifiers can have their own 1/f noise characteristics that will not be subtracted by reference pixels on the leftmost and rightmost amplifiers.}\label{fig:darkWindowVsDarkStripe}
-\end{figure}
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_larger_backsep_stripe.pdf}{0.49\textwidth}{Stripe Mode Time Series, 379 ppm}
-\fig{azlab_ratio_tser_larger_backsep_window.pdf}{0.49\textwidth}{Window Mode Time series, 339 ppm}}}
-\caption{When the background aperture is displaced by more than 512 pixels from the source aperture, window mode becomes slightly preferable.
-}\label{fig:stripeVsWindowAZlab04LargerBacksep}
-\end{figure*}
-
-\clearpage
-\subsubsection{Subarray Size Comparisons}
-NIRCam grism time series users can choose between full frame, SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarray sizes, which are 2048, 256, 128 and 64 pixels tall and 2048 pixels wide.
-The taller subarrays have the advantage of more background pixels (or a reference star) to use in analysis.
-The taller subarrays also are needed to fit the short wavelength WEAK LENS +8 PSF observed simultaneously with the long wavelength grism.
-Otherwise, the WEAK LENS +4 PSF must be observed or a fraction of the WEAK LENS +8 PSF used.
-The shorter subarrays have the advantage of faster frame times, permitting observations of brighter stars or more samples up the ramp than taller subarrays.
-We used the same lamp LED current for the SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarrays and tuned the integration times to be similar by setting the number of RAPID groups as 8, 16 and 32 for the three subarrays respectively.
-The resulting integration times are 10.8995, 10.8155 and 10.7735 seconds respectively.
-No clear trend is seen in the time series shown in Figure \ref{fig:subarraySizes}.
-In this example, the background aperture was always parallel to the source aperture to best remove 1/f noise.
-\textbf{\textcolor{red}{Show what happens if the background aperture and source apertures are on different amplifiers and/or if they are vertical with respect to the source aperture}}
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
-\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
-\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
-{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
-\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
-\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
-\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
-If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable.
-\textbf{\textcolor{red}{How does this make sense?
-Did I possibly change how the side reference pix correction was done between the 3 tests?
-Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019.
-Processed the files on Jul 10 18:06. Indeed, they were processed slightly differently, but the smoothing method matters very little.
-Karl very astutely points out that the 2048x256 has reference pixels on the top but the 2048x128 and 2048x64 do NOT have reference pixels at the top, so pre-amp reset issues are very likely.} }}\label{fig:subarraySizes}
-\end{figure*}
-
-\subsubsection{Persistence with Long and Short Illumination}
+\subsection{Persistence with Long and Short Illumination}
 We estimate the persistence level by illuminating the detectors to $\sim$80\% well depth for either 30 seconds or 30 minutes and observe the slopes after the LED is turned off.
@@
 
-\clearpage
-\subsubsection{Multiple apertures within a detector}
-\begin{figure*}
-{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n487Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{}}}
-{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.99\textwidth}{Apertures}}}
-{\gridline{\fig{individual_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA.pdf}{0.49\textwidth}{Time Series of Apertures}}}
-\caption{Time series for 2 apertures on each detector.}\label{fig:twoApPerDetector}
-\end{figure*}
-
-\begin{figure*}
-{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn487Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{}}}
-{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn489Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{Apertures}}}
-{\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
-\caption{Time series for many apertures on each detector, binned into 70 equal time bins.}\label{fig:manyApPerDetector}
-\end{figure*}
-
-\begin{figure*}
-{\gridline{\fig{ap_labels_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Apertures on Detector 489}}}
-{\gridline{\fig{raw_tser_AZlab05baseline_multiAps_6p0mA_NRCBSELINE6P0MA.pdf}{0.7\textwidth}{Time series for each aperture}}}
-\caption{Time series for many apertures on the 489 detector after row-by-row and column-by-column background subtraction.
-Each amplifier has its own 1/f noise character, but the lamp variations measured on this detector move in concert across all detectors.}\label{fig:manyApOn489}
-\end{figure*}
-
-\clearpage
-\subsubsection{Dark Baseline Test}\label{sec:darkBaseline}
-In Figure \ref{fig:darkBaselineAllan}, we show that the noise in a series of dark integrations averages with the square root of the number of integrations.
-While 1/f is highly correlated within an aperture and results in a large value of noise per integration, the integrations are all statistically independent.
-Threfore, on 10 minute long timescales, the total noise of the readout electronics including 1/f and dark current in the aperture drops to 10 ppm.
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
-\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
-Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
-While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent when examining this dark (un-illuminated) data.
-}\label{fig:darkBaselineAllan}
-\end{figure*}
-
-\clearpage
-\subsubsection{Co-added Versus Un-coadded data}\label{sec:coadds}
-In Figure \ref{fig:coaddedData}, we compare data that was taken in READ mode.
-In this case, there were 1000 integrations with a 2048x256 stripe illuminated with the lamp on all four detectors.
-In the case of NFRAME=4, the data are co-added with bit-shift operations whereas for NFRAME=1, all data is used.
-There are 2 groups with NFRAME=4 and 8 groups with NFRAME=1.
-The primary difference between the two are
-\begin{itemize}
-\item the reference pixel correction is performed on frame-by-frame basis for NFRAME=1 and on a co-added group of 4 for NFRAME=4
-\item the slope is calculated with all 8 groups
-\end{itemize}.
-This differences did not have a large overall impact on stability of the lightcurves.
-
-\begin{figure*}
-{\gridline{\fig{azlab_ratio_tser_azlab06_baseline3}{0.47\textwidth}{RAPID mode with NFRAME=1}
-\fig{azlab_ratio_tser_azlab06_nint4.pdf}{0.47\textwidth}{Co-added with NFRAME=4}}}
-\caption{Co-added with NFRAME=4 versus 8 groups RAPID data.
-Using reference pixel subtraction on the individual reads in RAPID mode does not substantially improve the ratio time series of the two detectors as compared with co-added data where reference pixel correction was applied to the group (which is an average of the 4 frames).}\label{fig:coaddedData}
-\end{figure*}
-
-\clearpage
-\subsubsection{Reference pixel time series}
-\begin{figure*}
-{\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}
-\caption{Reference pixels cannot easily explain the trends between detectors.}\label{fig:refpixTSeries}
-\end{figure*}
-
-\begin{figure*}
-{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance from Raw Series}
-\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance with Linear Detrending}}}
-{\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}
-\caption{Time series for the ratio of two apertures within a detector.}\label{fig:allanVarianceWithinDetector}
-\end{figure*}
-
-We also show a time series immediately after where the lamp was turned on in Figure \ref{fig:indTSeriesAfterLamp}.
-Unlike with HST, there is no clear ramp-up behavior.
-
-\begin{figure*}
-{\gridline{\fig{individual_stripe64_1p5_mA_rpt2.pdf}{0.99\textwidth}{}}}
-\caption{Time series immediately after a lamp is turned on.}\label{fig:indTSeriesAfterLamp}
-\end{figure*}
-
-\clearpage
-\subsection{Temperature Changes}
-\subsubsection{FPA temperature change}
-We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
-As can be seen in Figure \ref{fig:indTSeriesAfterLamp} (bottom panel) the Lakeshore temperature controlling a baseplate where the largest thermal mass sits is constant to within 3 mK.
-The FPA temperature is adjusted upward by 300 mK about 75 minutes into the test and held at this higher value.
-The change in temperature results in a 0.1\% increase in flux (ie. 1000 ppm).
-In terms of slopes, this resulted in a change of 2.3 DN/s/px for detector 487 and 3.6 DN/s/px for detector 489.
-For the integration times of 10.77 seconds, this amounts to 25 to 39 DN accumulated within an integration.
-This is lower than the value of 80 DN for a 100 mK change in \citet{hall2005jwstArrays}, likely because it is calculated over the slope of an image rather than the absolute counts.
-
-The reaction to FPA changes in temperature is likely a fractional effect rather than an absolute number of DN.
-This is because both detectors change by about 0.10\% even though their relative peak counts were 25,000 DN/px and 39,000 DN/px for detectors 487 and 489.
-
-In flight, the FPA is expected to be stable to about 1 mK.
-If we take the observed flux change (1000 ppm per 300 mK), the fractional change will be about 3 ppm.
-We therefore expect detector temperature fluctuations to be a relatively small part of the time series error budget.
-
-\begin{figure*}
-{\gridline{\fig{individual_azlab05_baseline_tchange.pdf}{0.99\textwidth}{}}}
-\caption{Time series during an adjustment to the FPA set point.}\label{fig:indTSeriesAfterLamp}
-\end{figure*}
-
-\subsubsection{Lakeshore Temperature Change}
-
-\begin{figure*}
-{\gridline{\fig{individual_azlab06_sub320_lakeshore_to_39p7.pdf}{0.99\textwidth}{}}}
-\caption{Time series during an adjustment to the Lakeshore set point.}\label{fig:indTSeriesLakeshore39p7}
-\end{figure*}
-
-\subsubsection{FPA Temperature Oscillations}
-When the temperature control loop on the FPA is working improperly, there can be oscillations in the FPA temperature, as shown in Figure \ref{fig:indTSeriesTMCoscillations}.
-In this example, the oscillations happen at a period of 19.3 minutes.
-The LED fluctuations are signfiicantly longer with a period of $\sim$100 to $\sim$125 minutes.
-
-\begin{figure*}
-{\gridline{\fig{individual_azlab06_sub320_tmc_oscillations.pdf}{0.99\textwidth}{}}}
-\caption{Time series during a $\sim$ 20 minute oscillation in the TMC temperature.}\label{fig:indTSeriesTMCoscillations}
-\end{figure*}
-
-\clearpage
-\subsubsection{Box Temperature}
-The box temperature leads the flux variations by 4.9 minutes, likely due to the thermal delay between the box and the LED mounted to the box.
-
-\begin{figure*}
-{\gridline{\fig{azlab08_sub320_multiexp_temp_correlation.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
-\fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
-\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}\label{fig:LEDTcorrelation}
-\end{figure*}
-
-\begin{figure*}
-{\gridline{\fig{azlab08_sub320_multiexp_corrected.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
-\fig{azlab08_sub320_lakeshore_tchange_corrected.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}\label{fig:LEDTcorrection}
-\caption{After removing the 4.9 hour time offset and a linear trend with temperature, the fluctuations are greatly reduced.}
-\end{figure*}
-
-\subsubsection{Detector Temperature}
-
-\begin{figure*}
-{\gridline{\fig{individual_azlab08_sub320_multi_exp_fpat_dt.pdf}{0.98\textwidth}{}}}
-\caption{A small change of the FPA temperatures is inserted without heating up the box.
-The FPA temperature clearly correlates with flux, but has a different scaling with each detector.}\label{fig:fpaTChangeSmall}
-\end{figure*}
-
-\clearpage
-\subsection{Reference Pixels versus No Reference Pixels}
-One question to answer is, can background subtraction subtract off noise just as well as reference pixels?
-We compare time series on source boxes subtracted by a background box on data that has been reference pixel subtracted and data that has not been reference pixel subtracted.
-As before, the background boxes are offset horizontally from the source boxes to best capture 1/f noise.
-For the baseline test, with a 2048x256 subarray, the standard deviation was 197.11 ppm with reference pixel correction.
-Repeating the experiment with no reference pixel correction, the standard deviation was 198.19 ppm.
-This test indicates that horizontally displaced background box is sufficient in removing pre-amp offsets and 1/f noise from the source aperture.
-However, for some cases (like NIRCam grism time series), the background subtraction will be done vertically and so side reference pixels will be desired.
-
-If no top reference pixels are available (such as in the 2048x64 subarray test), and only side reference pixels are available, the benefits are even smaller.
-For the 2048x64 1.5 mA test with reset-per-frame, the standard deviation was 326.9 ppm with reference pixel correction and 327.2 ppm without reference pixel correction.
-
-If the background subtraction apertures have a vertical displacement from the source, then 1/f noise becomes a more significant contributor to the errors.
-This is where side reference pixel subtraction becomes a more valuable correction.
-Figure \ref{fig:RefpixWithVertOffsetBackground} shows the time series with and without reference pixel correction if the background aperture is vertically offset from the source aperture.
-
-\begin{figure*}
-\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx487_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{}}
-\gridline{\fig{ap_labels_azlab04_rpf256_voffset_bsub_with_refpx489_NRCBSELINE0P9MA.pdf}{0.7\textwidth}{Apertures for 2048x256 stripe}}
-{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_with_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x256}
-\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf256_voffset_bsub_no_refpx_NRCBSELINE0P9MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x256}}}
-{\gridline{\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_with_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{Ref Pixel-Corrected, 2048x64}
-\fig{azlab_ratio_tser_voffset_background_phot_azlab04_rpf064_voffset_bsub_no_refpx_NRC64STRIPE1P5MA.pdf}{0.33\textwidth}{No Ref Pixels Used, 2048x64}}}
-\caption{If a background aperture is vertically displaced from the source aperture, the reference pixels are important in reducing 1/f noise.}\label{fig:RefpixWithVertOffsetBackground}
-\end{figure*}
-
-\clearpage
-\subsection{320 Subarray test}
-We also explored the stability of a $320 \times 320$ subarray.
-The subarray was placed at a strategic location on each detector to allow horizontally-displaced background aperture as shown in Figure \ref{fig:sub320AperturesAZlab06}.
-
-Surprisingly, the subarray mode had considerably higher scatter from integration to integration than stripe mode.
-They both had 1000 integrations, a 6.0 mA LED current and similar aperture widths.
-The subarray mode had 10 groups versus 8 groups with the stripe mode.
-The subarray was $320 \times 320$ with one amplifier output whereas the stripe mode was $2048 \times 256$ with 4 amplifier outputs.
-
-The subarray time series is very sensitive to the fast-frame resets where the entire array is quickly reset at the beginning of an integration.
-These resets are needed to ensure that pixels outside a subarray don't overfill their well capacity and leak into the subarray.
-When NFF=512, the fast-frame resets are cycled through 4 different sections of the detector.
-This results in a cycling pattern with a period of 4 integrations shown in Figure \ref{fig:sub320vsStripeBaseline2}.
-When NFF=2048, there is no cycling pattern shown in Figure \ref{fig:sub320NFF512vs2048}.
-
-\begin{figure*}
-\gridline{
-\fig{ap_labels_azlab06sub320Baseline487_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 487}\\
-\fig{ap_labels_azlab06sub320Baseline488_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 488}
-}
-\gridline{
-\fig{ap_labels_azlab06sub320Baseline489_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 489}\\
-\fig{ap_labels_azlab06sub320Baseline490_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 490}
-}
-\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 test with a $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
-\end{figure*}
-
-\begin{figure*}
-\gridline{
-\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
-\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
-}
-\gridline{
-\fig{individual_azlab06_sub320_6p0mA_t100_110.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$}\\
-\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{100-110 min Zoom $320 \times 320$}
-}
-\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher oscillations than the stripe mode.
-A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
-NGROUP=10, NINT=1000.
-}\label{fig:sub320vsStripeBaseline2}
-\end{figure*}
-
-\begin{figure*}
-\gridline{
-\fig{individual_azlab06_sub320_9p0mA}{0.49\textwidth}{5-8 min Zoom $320 \times 320$ NGROUP=2}
-}
-\caption{The time series of the AZLab 06 $320 \times 320$ subarray still has oscillations every 4 integrations with NGROUP=2, NINT=3600.
-}\label{fig:sub320vsStripeBaseline2}
-\end{figure*}
-
-\begin{figure*}
-\gridline{
-\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=512}\\
-\fig{individual_azlab06_sub320_nff2048_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=2048}
-}
-\caption{The time series of the AZLab 06 $320 \times 320$ subarray is very sensitive tot he fast frame resets.
-When NFF=512, the fast frame resets cycle through the $320 \times 320$ subarray every 4 integrations, resulting in a 4-integration cycle.
-When NFF=2048, there is no long a 4-integration long pattern.
-}\label{fig:sub320NFF512vs2048}
-\end{figure*}
-
-\clearpage
-
-\subsection{Asic Voltages}
-\begin{figure*}
-\gridline{
-\fig{individual_azlab07_baseline2_487_and_490_binned.pdf}{0.89\textwidth}{Asic Voltages and Detector fluxes on 487 and 489}\\
-}
-\caption{Asic voltages do not show obvious strong correlations with flux. There's a slight correlation with VRST\_V.
-}\label{fig:asicVoltageAndFlux}
-\end{figure*}
-
-\clearpage
-
-\subsection{Idle versus exposing residuals}
-The current loads on the asics are different when they are in idle mode (resetting and not collecting data) versus exposing (collecting reads up the ramps).
-We induced a higher load on detector 487 on purpose by running a $\sim$ 3 hour exposure while the remaining detectors ran in idle mode.
-We then started an exposure with all 4 detectors to see if detector 487 exhibited a different time series than the remaining 3 detectors.
-The result shown in Figure \ref{fig:idleVersusExposing320}.
-\begin{figure*}
-\gridline{
-\fig{individual_azlab06_sub320_idle_vs_exp.pdf}{0.49\textwidth}{Data collection versus idle reset}
-}
-\caption{The time series of the AZLab 06 $320 \times 320$ subarrays on all four detectors look the same for the first hour even though detector 487 had a higher current draw 3 hours preceding the exposure because it had a higher current draw.}\label{fig:idleVersusExposing320}
-\end{figure*}
-
-\clearpage
-
-\subsection{Illumination Variations}
-
-The illumination pattern varies slightly over the course of the AZLab 06 baseline stability test.
-The illumination changes are small enough that large amounts of averaging are needed to view it.
-We first create a ``flat-field'' image by averaging all illuminated data (images 24 through 1000) during the AZLab 06 baseline test.
-We then create an ``average1'' image toward the early parts of the lightcurve (images 24-165) where the flux is lower.
-We create an ``average2'' image at late parts of the lightcurve (images 700-1000) where the flux is higher.
-Both of the ``average'' and ``average2'' images are divided by the ``flat field'' to reveal subtle changes in illumination.
-Finally, a crosscut along the X direction is plotted while averaging 126 pixels in the vertical direction.
-The results is that the illumination pattern is not constant in time, with a subtle band centered near X$\approx$ 730 pixels on Detector 488 that varies in amplitude.
-
-\begin{figure*}
-\gridline{\fig{azlab06_illum_baseline_plot_region_487.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
-\fig{azlab06_illum_baseline_plot_region_488.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
-\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_487.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
-\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_488.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
-\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
-There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange487-488}
-\end{figure*}
-
-\begin{figure*}
-\gridline{\fig{azlab06_illum_baseline_plot_region_489.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}
-\fig{azlab06_illum_baseline_plot_region_490.pdf}{0.49\textwidth}{Region over which the pixels are averaged and plotted}}
-\gridline{\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_489.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (488)}
-\fig{azlab06_illum_baseline_slope_flat_fielded_profile_plot_490.pdf}{0.49\textwidth}{Flat-fielded count rates during the early and late parts of the baseline test (490)}}
-\caption{There are subtle illumination pattern changes visible when average large chunks of data during the baseline test.
-There is a vertical band of illumination that changes from the early versus late parts of the time series.}\label{fig:baselineIllumChange489-490}
-\end{figure*}
-
-We also examine the slope and intercept of the illumination as a function of time.
-We applying the following processing steps:
-\begin{enumerate}
-	\item Apply side and top reference pixels to all frames
-	\item	Calculate slope images from ramp images using \texttt{ncdas}
-	\item Subtract 1/f noise with a row-by-row subtraction by the average of un-illuminated pixels
-	\item Calculate an average flat field over the entire time series of illuminated ata
-	\item Divide each image by the flat field
-	\item Collapse the illuminated region along the Y direction to make an illumination profile
-	\item Fit the illumination profile to a line and save the slope and intercept
-\end{enumerate}
-Figure \ref{fig:illumGradientChangeOverTime} shows the slope and intercept calculated for the illumination profile over time.
-It is clear that there is a gradient in the image that also correlates with the flux.
-This may explain detector 490's different behavior over time.
-
-\begin{figure*}
-\gridline{
-\fig{illum_slope_and_intercept_487.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 487}
-\fig{illum_slope_and_intercept_489.pdf}{0.49\textwidth}{Illumination Gradient Change over Time on 489}
-}
-\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detectors on detectors 487 and 489.
-The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}
-\end{figure*}
-
-\begin{figure*}
-\gridline{
-\fig{ratio_for_AZLab06_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489}
-\fig{allan_variance_for_AZLab06_Baseline_487_intercepts}{0.49\textwidth}{Allan variance of the ratio line series}
-}
-\caption{We can take the line intercept from Figure \ref{fig:illumGradientChangeOverTime} to calculate the flux.
-This averages like $\sqrt{N}$ statistics.
-}\label{fig:illumGradientChangeOverTime}
-\end{figure*}
-
-Given how well the Line Intercept ratio between detectors 487 and 489 averages like $\sqrt{N}$ statistics in Figure \ref{fig:illumGradientChangeOverTime}, we look at the multi-exposure test to examine longer baselines.
-
-\begin{figure*}
-\gridline{\fig{ratio_for_AZLab06_Multi-Exposure_Baseline_487.pdf}{0.49\textwidth}{Ratio of the best fit line intercepts of 487 and 489 over the long multi-exposure test}}
-\gridline{
-\fig{allan_variance_for_AZLab06_Multi-Exposure_Baseline_487_intercepts.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from the best-fit slope intercept}
-\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.49\textwidth}{Allan variance of the 487/489 ratio from Aperture Photometry}
-}
-\caption{We repeat the experiment from Figure \ref{fig:illumGradientChangeOverTime} but this time over a long multi-exposure test.
-The line-fit method achieves worse results on short timescales but better results on long timescales.}\label{fig:illumGradientChangeOverTimeMultiExpBaseline}
-\end{figure*}
-
-\clearpage
-
-\subsection{Long multi-exposure Test}
-A long multi-exposure time series shows the noise properties on timescales up to a few hours.
-This long series also enables a clearer trending with temperature and flux.
-
-The measured fluxes are highly correlated with the TMC current.
-
-\begin{figure*}
-{\gridline{\fig{individual_azlab06_sub320_multi_exp.pdf}{0.48\textwidth}{AZLab06 Long Multi-Exposure Time series}
-\fig{all_var_azlab06_sub320_multi_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{AZLab06 Allan variance for Multi-exp Series}}}
-\fig{individual_azlab06_sub320_multi_exp_w_temp}{0.48\textwidth}{Multi-Exposure Time series with temperature data}
-\caption{We strung together 4 long exposures to create an extended time series.
-There are no obvious transients or exponentials at the exposure boundaries, which are marked as vertical blue lines.
-As with previous tests, the standard deviation of the flux ratio between two detectors (487 and 489) is well above the photon and read noise value and furthermore doesn't scale with the $\sqrt{N}$ for $N$ points in a bin.
-}\label{fig:AZlab06LongMultiExp}
-\end{figure*}
-
-\clearpage
-\subsection{Noise floor}
-
-Allan variance plots indicate that there is a noise floor across detectors of about 50-60 ppm as shown in Figure \ref{fig:allanVarianceAZ04AZ05}.
-
-\begin{figure*}
-{\gridline{\fig{allan_var_removelinear_True_azlab05baseline.pdf}{0.48\textwidth}{AZLab05 Allan variance}
-\fig{allan_var_removelinear_True_azlab06lamp_warm.pdf}{0.48\textwidth}{AZLab06 Allan variance}}}
-\caption{Allan variance across two detectors in the AZ Lab stability tests.}\label{fig:allanVarianceAZ04AZ05}
-\end{figure*}
-
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
-\acknowledgments
-
-\clearpage
-\section{Expected In-Flight Performance with JWST}
-
 \section{Conclusions}
@@
 
-We evaluate results of ground-based tests of the NIRCam instrument for exoplanet time series.
-These tests include a variety of optical setups from the full telescope structure and flight components to small lab dewar tests with flight-like components and flight-like electronics.
 We evaluate the largest sources of noise that add to JWST's error budget and list them below.
@@
 
+%% If you wish to include an acknowledgments section in your paper,
+%% separate it off from the body of the text using the \acknowledgments
+%% command.
+\acknowledgments
+
 \section*{acknowledgements}

### 2020-04-29 ms.tex
further edits to make this paper focused on contributions to error budget

@@
 
-\author{Michael McElwain}
+\author{Michael McElwain?}
 
@@
 
-We use Equation \ref{eq:covarianceweights}, to further beat down the read noise.
+We use Equation \ref{eq:covarianceweights}, to further reduce the read noise.
 For the covariance weights, we assume constant off-diagonal weights of 15 (e$^-)^2$ and do not include the spectral covariance.
@@
 Fortunately, the subpixel crosshatch systematic is a smooth function of pointing drift, shown in Figure \ref{fig:subpixScanSimulation}.
-A polynomial function can be fit to this subpixel dependence then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
+A polynomial function can be fit to this subpixel dependence and then the centroid of each integration can be inserted as an argument to the function to provide a correction as a function of time.
 Alternatively, a Gaussian process regression could be applied.
@@
 This pointing model only shows the line of sight variations, not including thermal distortions or the high frequency ($>$1 Hz) jitter.
+The V2 and V3 are the observatory axes perpendicular to the telescope boresight axes.
 }\label{fig:tserPointingFull}
@@
 \caption{The pointing time series from Figure \ref{fig:tserPointingFull} is binned into a 1 minute cadence and used as an input shifts to the crosshatch model.
-The very precise pointing expected by JWST will produce very small flux variations on the crosshatch pattern with an expected standard deviation of only 6 ppm.
+The very precise pointing expected by JWST will produce very small flux variations (``rel flux'' axis) on the crosshatch pattern with an expected standard deviation of only 6 ppm.
 }\label{fig:tserPointingAndFlux}
@@
 
-\clearpage
-
-\subsection{Persistence}\label{sec:persistence}
+\section{Persistence}\label{sec:persistence}
 HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.
@@
 	It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
-	Fortunately, 1/f noise appears to average like $1/\sqrt{N_{int}} $ from integration to integration.
+	Fortunately, 1/f noise averages like $1/\sqrt{N_{int}} $ from integration to integration.
 	We found efficient reductions in 1/f noise by subtracting the median value from each row in each amplifier.
 	This will be possible for imaging time series but not grism spectroscopy, where one must use the outer background regions in the spectral dispersion direction to reduce 1/f noise.
-	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise.
+	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise using sum extraction.
+	A covariance weighting scheme described in Section \ref{sec:optimalCovWeights} will significantly lower the read noise
 	\item \textbf{Subpixel Sensitivity:} The NIRCam detectors all exhibit some degree of crosshatching patterns along crystallographic planes of HgCdTe.
@@
 The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
-It should be noted that the ``depletion region'' is depleted in {\it mobile charge carriers}, but is {\it not} depleted in net charge because has a net positive charge in the N-type depletion region and negative charge in the P-type depletion region.
+It should be noted that the ``depletion region'' is depleted in {\it mobile charge carriers}, but is {\it not} depleted in net charge because it has a net positive charge in the N-type depletion region and negative charge in the P-type depletion region.
 
@@
 The minimum voltage is several thousands of counts above zero to ensure that fluctuations in the bias signal do not go below 0.
-The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full saturation of a pixel.
+The 65,536 DN level is tuned to be just above the HgCdTe full well capacity to measure full well capacity of a pixel.
 

### 2020-04-30 ms.tex
edits to 1/f noise section

@@
 This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide estimates of the noise source affecting JWST NIRCam time series.
-Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (300 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
+Here, we provide estimates of the noise sources affecting JWST NIRCam time series.
+Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (230 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
 Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
@@
 A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.
+For difficult biosignatures, noise levels less than 10 ppm (parts per million) are required and this value shrinks in the presence of clouds.
 
 Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
-Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.
+Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep[e.g.][]{vanderburg2014twoWheeledKeplerPhot,beichman2014pasp}.
 
@@
 
-Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon and read noise.
+Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon noise.
+Sections \ref{sec:preAmp} through \ref{sec:persistence} detail these noise contributions.
+We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact.
 
@@
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
+	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets above.
 	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
 	This is a noise source where most of the noise power is concentrated at low frequencies.
-	1/f noise causes spatial correlations in the fast-read direction (along detector rows).
+	1/f noise causes spatial correlations primarily in the fast-read direction (along detector rows).
 It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage.
@@
 
-It should be noted that the detector effects related to the asic circuit can be specific to the ``personality'' of each asic.
-The asics all have different asic load files which are tuned to minimize the power consumption and dark current in a particular asic.
-Since the asic load files are specific to each detector, they may exhibit different noise properties.
-Some caution should be taken when comparing noise tests with engineering grade or rejected detectors with the flight detectors.
+We discuss these noise contributions in more detail in Sections \ref{sec:preAmp} through \ref{sec:persistence}.
+However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less them $\sim$ 1 ppm) to the time series.
 
@@
 This is repeated for all columns.
+This background subtraction method will efficiently remove the pre-amplifier offsets to the level where amplifier discontinuities become smaller than the combined read and photon noise in the image.
 
@@
 Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
-The periodogram shows many spikes at high frequency including one at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
+
+Figure \ref{fig:pixelTSeriesPSpec} shows that the noise power drops nearly like 1/f from the lowest frequency in a frame to $\sim$1000 Hz, where the curve flattens out.
+This indicates that the noise is closer to white noise, where each pixel's noise would be statistically independent from the others, at high frequencies.
+The periodogram also shows many spikes at high frequency on top of the 1/f noise.
+One of these prominent spies occurs at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
 
@@
 1/f rises above the white noise level at 70 cycles / 1400 Hz for amplifier 1 and the intersection ranges from 70 to 135 across the 4 amplifiers.
+The message from this power spectrum is that the read noise is significantly correlated from pixel to pixel and this will affect both high precision spectroscopy and high precision photometry.
 
@@
 As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (ie.
-timescales longer than 100 cycles as measured in the 10$\mu$s time to address the pixels).
+timescales longer than 100 cycles, where a cycle is the 10$\mu$s time to address a pixel).
 Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
@@
 They also do not contain photon noise in the background, which can make electronic noise sources harder to see.
-We study here the contributions from read noise, 1/f noise and dark current.
+We study here the contributions from read noise, including the 1/f noise from the electronics.
 This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
@@
 A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
-The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
+The detectors are read in full frame mode so that each frame is 10.73677 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
 We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
@@
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, ``Reduced Data" using reference pixels and ``ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
+{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, reference pixel-correction that uses the top, bottom and side reference pixels and finally a method using a row-by-row median subtraction.
 {\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
-The most important step for reducing the noise in the time series is row-by-row subtraction to remove the 1/f noise.
+Both the pre-amplifier offsets and row-by-row 1/f subtractions are important to reduce the effective read noise in the aperture.
 }\label{fig:longDarkPhot}
@@
 
+\subsection{Photometric Aperture}\label{sec:photApertureDark}
+
 What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
 We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
-Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
+%Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
 The background subtraction will largely remove the offsets affecting the whole 512$\times$2048 amplifier.
 However, the correlated 1/f noise along the X direction will not be subtracted efficiently by an annulus.
-Instead, a row-by-row line fit to the background would be more effective.
+Instead, a row-by-row line fit to the background can be more effective.
 
@@
 In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
-Therefore, the read noise is expected to be 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
+Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
 When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.
 
-In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for 1/f noise using reference pixels or otherwise).
+In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for amplifier offsets or 1/f noise using reference pixels or otherwise).
 If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
 This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
-Fortunately, there are ways to significantly reduce the 1/f noise.
+Fortunately, there are ways to significantly reduce the pre-amplifier offsets and 1/f noise.
 
 \begin{deluxetable*}{c|cc|cc}[b!]
-\tablecaption{Summary of Noise Sources in OTIS Dark Test}
+\tablecaption{Summary of Noise Sources in Long Dark Test}
 \tabletypesize{\footnotesize}
@@
 We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
-The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN, but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
-
-Since these 8 reference pixels in each row are not sufficient to remove all 1/f noise in each row, so we perform another correction step:
+The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
+
+\subsection{Row-by-Row Subtraction}\label{sec:photRowByRow}
+
+Since these 8 reference pixels in each row are not sufficient to remove all 1/f noise in each row, we perform another correction step:
 We find the median of each group up the ramp along the fast read (X) direction and subtract this from every row.
@@
 The A3 detector used for weak lens photometry has reduced 1/f noise.
-The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
+%The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
 
@@
 This individual amplifier dramatically decreases the errors.
-The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm.
-Therefore, this simple approach can dramatically decrease the 1/f noise to below the photon limit.
+The standard deviations of the background-subtracted photometry range from 2,540 to 3,300 DN or 65 to 85 ppm across detectors.
+Therefore, this simple approach can dramatically decrease the 1/f noise to well below the photon limit.
 This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).
@@
 
-We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
+We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:photRowByRow}.
 We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
 The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
-This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than 5 milliseconds, which the median subtraction cannot remove.
+This enables subtraction of 1/f noise that has length scales shorter than the line time (ie timescales shorter than 512 clock cycles or 5 milliseconds), which the median subtraction cannot remove.
 
@@
 
-\textcolor{red}{\bf Continue Here!}
-
-\subsection{Reference Channel Subtraction}
+\subsubsection{Reference Channel Subtraction}
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
 Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
-We attempt to subtract an amplifier 0's time series from all amplifiers.
+We subtract an amplifier 0's time series from all amplifiers.
 Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
@@
 \includegraphics[width=.32\columnwidth]{pixeltime_series_1.pdf}
-\includegraphics[width=.32\columnwidth]{all_amp_periodograms.pdf}
+%\includegraphics[width=.32\columnwidth]{all_amp_periodograms.pdf}
 \caption{The time series for all 4 amplifiers share common-mode behaviors for some intervals but not always (left and middle plots).
@@
 The left panel shows the a time near the beginning of a frame, where amplifiers 1 ad 2 share some common-mode read noise.
-The middle panel shows another part of the time series where Amplifiers 1 and 2 have more disparate noise signatures.
-The right panel shows the periodogram of each amplifier's time series over the first 10$^5$ clock cycles (0.1) seconds, which exhibits no consistent peaks.
+The right panel shows another part of the time series where Amplifiers 1 and 2 have more disparate noise signatures.
 }\label{fig:darkPixelTimeSeries}
@@
 
-\subsection{PCA Correction}
+\subsubsection{PCA Correction}
 Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
@@
 Here, we assume the dark current is negligible.
-Next, we mask all bad pixels by setting all pixels with $| f | > 200$ DN to 0 DN to remove bad pixels that can drive the principal components.
+Next, we mask all bad pixels by setting all pixels with an absolute value larger than 200 DN and replace them with 0 DN to remove bad pixels that can drive the principal components.
 The first 10 principal components are plotted in Figure \ref{fig:pcaEigenvectors} for two example groups (54 and 55).
@@
 To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
+However, we stop the PCA at this point because it does not do as well as the simple row-by-row amplifier-by-amplifier subtraction performed in Section \ref{sec:indAmpAvg}.
 
@@
 We therefore quantify error source over 1 hour duration.
-If the smallest stripe subarray is used, frame time is 0.34 seconds.
+If the smallest stripe subarray 2048$\times$64 is used, frame time is 0.34 seconds.
 For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
@@
 
-\subsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}
+\subsubsection{Optimally Co-Variance Weighted Flux}\label{sec:optimalCovWeights}
 
@@
 
-\subsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
+\subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
 The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
@@
 
-\subsection{Impact to Grism Time series}
+\subsubsection{Impact to Grism Time series}
 We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:Conclusion}
 The NIRCam instrument will be a valuable tool to characterize the atmospheres of exoplanets with its grism time series mode.

### 2020-05-02 ms.tex
small edits and reorganization mostly to pca and grism aperture sections

@@
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
+We also re-label the times to include the reset time that would normally occur after each integration, so the
+
 Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
@@
 
-\subsubsection{Reference Channel Subtraction}
-We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
-Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
-We subtract an amplifier 0's time series from all amplifiers.
-Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
-The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
-This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
-On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.
-
-The net effect of this method is to increase the noise over a row-by-row median subtraction.
-The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
-This means the the correlations within an amplifier are not efficiently subtracted and may be propagated to the remaining amplifiers.
-
 \begin{figure*}[!hbtp]
@@
 
+\subsubsection{Reference Channel Subtraction}
+We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
+Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
+We subtract an amplifier 0's time series from all amplifiers.
+Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
+The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
+This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.
+On the other hand, if the each amplifier exhibits its own individual correlated noise behavior, the reference amplifier will fail to subtract out all correlated noise and may introduce more noise.
+
+The net effect of this method is to increase the noise over a row-by-row median subtraction.
+The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
+This means the the correlations within an amplifier are not efficiently subtracted and may be propagated to the remaining amplifiers.
+
 \subsubsection{PCA Correction}
+
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
+\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
+\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
+Pre-amplifier reset values are seen in the first principal component, and change from one group (one read in RAPID) to another.
+These are residual values not fully subtracted by reference pixels.
+The principal components generally increase in frequency with principal component number.
+In other words, the highest frequency principal components explain the least amount of the variance as would be expected for 1/f noise.
+}\label{fig:pcaEigenvectors}
+\end{figure*}
+
 Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
@@
 Each row represents a different noise iteration.
-First, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
+First, we apply reference pixel correction to remove the pre-amplifier resets.
+Next, we calculate the mean value of each pixel in the 108 group stack and subtract all groups by this mean image.
 This removes all bias levels and focuses on the time variability of the pixels.
@@
 The first 10 principal components explain 14\% of the total variance in each group up the ramp.
-The principal components from one group to another are different, but the ordering of these components generally follows a pattern of increasing frequency with higher order principal components.
+The principal components from one group to another are different, but the ordering of these components generally follows a pattern of increasing frequency with higher order principal components (smaller eigenvalues).
 This is expected for 1/f noise where the lowest frequencies have most of the power.
@@
 We use 20 principal components as a starting point for this method.
-The final time series has and measured standard deviation of 5,300 to 5,500 DN within the background-subtracted aperture.
+The final time series has a measured standard deviation of 5,300 to 5,500 DN within the background-subtracted aperture.
 This is comparable to the row and column subtraction standard deviation of 5,500 to 6,500 DN.
@@
 
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_54.pdf}
-\includegraphics[width=.4\columnwidth]{pca_dark_amp_all_extra_bias_sub_grp_55.pdf}
-\caption{The first 10 principal component eigenvectors identified from group 54 (left) and group 55 (right).
-The pre-amplifier reset values are seen in the first principal component, and change from one group (one read in RAPID) to another.
-The principal components generally increase in frequency with principal component number.
-In other words, the highest frequency principal components explain the least amount of the variance as would be expected for 1/f noise.
-}\label{fig:pcaEigenvectors}
-\end{figure*}
-
 In another approach, we treat each amplifier separately so that the principal components are calculated independently.
 This approach means that a noise signature in 3 amplifiers but not the fourth does not propagate to fourth amplifier when subtracting the PCA-based model.
-This individual-amplifier essentially has four times the number of degrees of freedom, so we fit with only the first 5 principal components in each amplifier.
+This individual-amplifier model has four times the number of variables as the combined PCA approach, so we fit with only the first 5 principal components in each amplifier.
 The resulting eigenvectors are shown in Figure \ref{fig:pcaEigenvectorsIndAmp}.
@@
 To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
-However, we stop the PCA at this point because it does not do as well as the simple row-by-row amplifier-by-amplifier subtraction performed in Section \ref{sec:indAmpAvg}.
+However, we stop the PCA at this point because it does not do as well as the simple row-by-row amplifier-by-amplifier mean subtraction performed in Section \ref{sec:indAmpAvg}.
 
@@
 \end{figure*}
-
-\clearpage
-
-\subsection{Grism Aperture}
-The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
-This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
-The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
-However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
-Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers.
-
-We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
-Without reference pixel subtraction, the grism apertures have standard deviations of 77,600 DN.
-Reference pixel subtraction drops this value to 9,640 DN and row-by-row subtraction drops it to 3,630 DN.
-For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,420 DN assuming a gain of 1.84.
-Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
-Expressed in ppm, the read noise after processing with row-by-row subtraction is 990 ppm as compared to a photon noise of 95 ppm for a CDS subtraction (2 groups in ramp).
-
-Given the high 1/f read noise, it is important to maximize the number of samples up the ramp.
-The read noise averages down like $\sqrt{N}$ statistics (ie. each read can be assumed independent and identically distributed).
-Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 13 reads to average per integration.
-For RAPID and BRIGHT1 modes, there should therefore be 13 groups and for BRIGHT2, there should be at least 7 groups (of 2 frames each).
-This would make the photon noise about equal to the read noise but ideally the read noise should be a small fraction of the photon noise.
-
-The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
-The transit durations for most exoplanets considered is several hours long.
-We therefore quantify error source over 1 hour duration.
-If the smallest stripe subarray 2048$\times$64 is used, frame time is 0.34 seconds.
-For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
-Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
-In section \ref{sec:darkBaseline}, we show from dark frames, that the read noise is statistically independent from integration to integration.
-
-For a concrete example, we consider a primary transit of WASP-80 b observed with the F444W grism time series mode.
-The exposure parameters that give a peak pixel count of 35,000 DN or 40\% well depth are a 2048$\times$256 stripe mode with BRIGHT1 read mode for 12 groups.
-These integrations are 31 seconds in duration.
-Each integration will have a 7.8$\times 10^7$ DN in a broadband aperture, so the photon noise per integration is 6,500 DN or 83 ppm.
-Over 1 hour (111 integrations), the photon noise will be 8 ppm if all integrations are independent.
 
@@
 \end{figure*}
+
+\subsection{Grism Extraction}
+
+The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
+This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
+The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
+However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
+Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers for the F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px) and right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px).
+
+We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
+Without reference pixel subtraction, the grism apertures have standard deviations of 77,600 DN.
+Reference pixel subtraction drops this value to 9,640 DN and row-by-row subtraction drops it to 3,630 DN.
+For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,420 DN assuming a gain of 1.84.
+Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series.
+Expressed in ppm, the read noise after processing with row-by-row subtraction is 990 ppm as compared to a photon noise of 95 ppm for a CDS subtraction (2 groups in ramp).
+
+Given the high 1/f read noise, it is important to maximize the number of samples up the ramp.
+The read noise averages down like $\sqrt{N}$ statistics (ie. each read can be assumed independent and identically distributed).
+Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 13 reads to average per integration.
+For RAPID and BRIGHT1 modes, there should therefore be 13 groups and for BRIGHT2, there should be at least 7 groups (of 2 frames each).
+This would make the photon noise about equal to the read noise but ideally the read noise should be a small fraction of the photon noise.
 
@@
 %We show the real covariance matrix in Section \ref{sec:empCovarianceMatrix}.
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.6\columnwidth]{spec_spatial_cov.pdf}
+\caption{The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
+The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
+The detector's diagonal elements are better than the read noise squared due to the row-by-row and column-by-column subtraction step.
+Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.6\columnwidth]{cross_sections_cov.pdf}
+\caption{Average covariance along the spatial and spectral directions for a given pixel spacing.}\label{fig:covSpecSpatialDiff}
+\end{figure}
 
@@
 Surprisingly, there is also a covariance between spatial pixels (the slow read direction) of $\sim$10 $(e^-)^2$.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.6\columnwidth]{spec_spatial_cov.pdf}
-\caption{The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
-The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
-The detector's diagonal elements are better than the read noise squared due to the row-by-row and column-by-column subtraction step.
-Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.6\columnwidth]{cross_sections_cov.pdf}
-\caption{Average covariance along the spatial and spectral directions for a given pixel spacing.}\label{fig:covSpecSpatialDiff}
-\end{figure}
 
@@
 \subsection{The impact of correlated read noise on time series}
+
+The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
+The transit durations for most exoplanets considered is several hours long.
+We therefore quantify error source over 1 hour duration.
+If the smallest stripe subarray 2048$\times$64 is used, frame time is 0.34 seconds.
+For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
+Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
+%In section \ref{sec:darkBaseline}, we show from dark frames, that the read noise is statistically independent from integration to integration.
+
+For a concrete example, we consider a primary transit of WASP-80 b observed with the F444W grism time series mode.
+The exposure parameters that give a peak pixel count of 35,000 DN or 40\% well depth are a 2048$\times$256 stripe mode with BRIGHT1 read mode for 12 groups.
+These integrations are 31 seconds in duration.
+Each integration will have a 7.8$\times 10^7$ DN in a broadband aperture, so the photon noise per integration is 6,500 DN or 83 ppm.
+Over 1 hour (111 integrations), the photon noise will be 8 ppm if all integrations are independent.
+
 We consider here some example science impacts of correlated read noise in these photometric apertures.

### 2020-05-04 ms.tex
replaced all the long dark simulated grism aperture stuff with new sims and spectral extraction.

@@
 \centering
-\includegraphics[width=.32\columnwidth]{aps_3_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_int_015_014.pdf}
-\includegraphics[width=.32\columnwidth]{aps_0_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014.pdf}
-\includegraphics[width=.32\columnwidth]{aps_1_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014_rowColSub.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5red.pdf}
-\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5redRowCol.pdf}
-\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5.
-As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-The photometric aperture is made to represent a similar one to the F322W2 grism trace.
+\includegraphics[width=.32\columnwidth]{spec_aps_pairwiseSubNoRed_otisLongDarkSimGrism.pdf}
+\includegraphics[width=.32\columnwidth]{spec_aps_pairwiseSubRed_covWeights_otisLongDarkSimGrism.pdf}
+\includegraphics[width=.32\columnwidth]{spec_aps_pairwiseSub_backsub_otisLongDarkSimGrism.pdf}
+\includegraphics[width=.32\columnwidth]{tser_pairwiseSub_noRed01.pdf}
+\includegraphics[width=.32\columnwidth]{tser_pairwiseSubRed.pdf}
+\includegraphics[width=.32\columnwidth]{tser_pairwiseSubRed_backsub.pdf}
+\caption{The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column row-by-row subtraction (right).
+The spectrum (outlined in red aperture box) is dispersed along the fast read (horizontal) direction, so it is particularly susceptible to 1/f noise.
+This is seen in the below each image, which dramatically decreases from 21,900 ppm to 1044 ppm with column-by-column, row-by-row subtraction.
+Here, the simulated grism image for an F322W2 filter covers the rightmost amplifier so only reference pixels and horizontal pixels with X < 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}

### 2020-05-05 ms.tex
added a plot to show the clear advantage of covariance weighting

@@
 This is seen in the below each image, which dramatically decreases from 21,900 ppm to 1044 ppm with column-by-column, row-by-row subtraction.
-Here, the simulated grism image for an F322W2 filter covers the rightmost amplifier so only reference pixels and horizontal pixels with X < 300 can be used to reduce the 1/f noise.
+Here, the simulated grism image for an F322W2 filter covers the rightmost amplifier so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}
@@
 \centering
-\includegraphics[width=.6\columnwidth]{spec_spatial_cov.pdf}
-\caption{The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
+\includegraphics[width=.49\columnwidth]{spec_spatial_cov.pdf}
+\includegraphics[width=.49\columnwidth]{cross_sections_cov.pdf}
+\caption{Left: The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
 The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
 The detector's diagonal elements are better than the read noise squared due to the row-by-row and column-by-column subtraction step.
+Right: The spectral (X) and spatial (Y) directions from the matrix are averaged to build up a higher signal to noise covariance profile.
 Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
@@
 \centering
-\includegraphics[width=.6\columnwidth]{cross_sections_cov.pdf}
 \caption{Average covariance along the spatial and spectral directions for a given pixel spacing.}\label{fig:covSpecSpatialDiff}
@@
 \centering
-\includegraphics[width=.5\columnwidth]{cov_weighted_weights.pdf}
-\caption{Spectral extraction weights for simple summation, conventional optimal extraction and covariance-weighting.}\label{fig:covWeightedSummation}
+\includegraphics[width=.66\columnwidth]{cov_weighted_weights.pdf}
+\includegraphics[width=.32\columnwidth]{zoom_cov_vs_var_tser.pdf}
+\caption{ {\it Left:} Covariance weighting using the empirical covariance matrix has more severe weighting than simple summation and conventional variance weighting used in optimal extraction.
+{\it Right:} Covariance weighting will dramatically lower the scatter in the dark frame time series compared to variance weighting.}\label{fig:covWeightedSummation}
 \end{figure}

### 2020-05-07 ms.tex
edited text on empirical covariance matrix section

@@
 \usepackage{enumitem}
+\usepackage{amsmath}
 \listfiles
@@
 \includegraphics[width=.32\columnwidth]{tser_pairwiseSubRed_backsub.pdf}
-\caption{The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column row-by-row subtraction (right).
+\caption{ {\it Top Row:} The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column row-by-row subtraction (right).
 The spectrum (outlined in red aperture box) is dispersed along the fast read (horizontal) direction, so it is particularly susceptible to 1/f noise.
-This is seen in the below each image, which dramatically decreases from 21,900 ppm to 1044 ppm with column-by-column, row-by-row subtraction.
-Here, the simulated grism image for an F322W2 filter covers the rightmost amplifier so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
+{\it Bottom Row:} The standard deviation of the time series dramatically decreases from 21,900 ppm to 2,680 ppm with reference pixels and 1044 ppm with column-by-column, row-by-row subtraction for the 3.34 $\mu$m bin.
+Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (512 pixels wide) and part of the leftmost amplifer, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}
@@
 The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
-However, there are no side reference pixels or horizontally-offset background regions available on the middle two amplifiers.
-Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves, especially on the middle two amplifiers for the F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px) and right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px).
+However, there are only limited background regions along the horizontal direction to use to subtract out 1/f noise.
+This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px).
 
 We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
-Without reference pixel subtraction, the grism apertures have standard deviations of 77,600 DN.
-Reference pixel subtraction drops this value to 9,640 DN and row-by-row subtraction drops it to 3,630 DN.
-For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,420 DN assuming a gain of 1.84.
+Without reference pixel subtraction, the grism apertures have standard deviations of 80,930 DN.
+Reference pixel subtraction drops this value to 9,900 DN and row-by-row subtraction drops it to 3,860 DN.
+For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,430 DN assuming a gain of 1.8.
 Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series.
-Expressed in ppm, the read noise after processing with row-by-row subtraction is 990 ppm as compared to a photon noise of 95 ppm for a CDS subtraction (2 groups in ramp).
+Expressed in ppm, the read noise after processing with row-by-row subtraction is 1,044 ppm as compared to a photon noise of 390 ppm for a CDS subtraction (2 groups in ramp).
 
@@
 The read noise averages down like $\sqrt{N}$ statistics (ie. each read can be assumed independent and identically distributed).
-Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 13 reads to average per integration.
-For RAPID and BRIGHT1 modes, there should therefore be 13 groups and for BRIGHT2, there should be at least 7 groups (of 2 frames each).
+Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 7 reads to average per integration.
+For RAPID and BRIGHT1 modes, there should therefore be 7 groups and for BRIGHT2, there should be at least 4 groups (of 2 frames each).
 This would make the photon noise about equal to the read noise but ideally the read noise should be a small fraction of the photon noise.
@@
 Given the high level of correlation between pixels, another way to reduce 1/f noise is with a small aperture.
-For example, a 15 pixel wide aperture results in measured read noise of 990 ppm for the same 0.17$\mu$m wide bin centered at 3.34$\mu$m whereas a 3 pixel wide aperture results in a measured read noise of 290 ppm, which is below the expected photon noise.
-For a one pixel wide aperture, the measured read noise is only 230 ppm.
-Of course such small apertures will be subject to other losses by missing so much of the PSF and the photon noise will be a larger fraction of the flux.
+For example, a 13 pixel wide aperture results in measured read noise of 1044 ppm for the same 0.17$\mu$m wide bin centered at 3.34$\mu$m whereas a 3 pixel wide aperture results in a measured read noise of 290 ppm, which is below the expected photon noise.
+However, this will sacrifice photons, so there must be a balance between reducing 1/f noise while capturing as many photons as possible.
 Therefore, a weighting scheme expanded from optimal extraction \citep{horne1986optimalE} is preferred.
@@
 The profile is normalized so that
-\begin{equation}
+\begin{equation*}
 \sum_{j=1}^{m} P_j = 1.
-\end{equation}
+\end{equation*}
 Any pixel is can be used to estimate the total flux $f_i$ by dividing by the profile.
-\begin{equation}
+\begin{equation*}
 f_j = \frac{S_j}{P_j},
-\end{equation}
+\end{equation*}
 where $S_j$ is the background-subtracted flux.
@@
 The goal becomes a weighting scheme to determine which weights $w_j$ minimize the variance in the total background estimate:
-\begin{equation}
+\begin{equation*}
 f_{opt} = \frac{\sum_{j=1}^{m} w_j \frac{S_j}{P_j}}{\sum_{j=1}^{m} w_j}.
-\end{equation}
+\end{equation*}
 
 If one assumes that all pixels are independent (and have zero correlation), the optimal weights (ones that minimize the variance in $f_{opt}$) are
-\begin{equation}
+\begin{equation}\label{eq:varianceweights}
 w_j = \frac{1}{\mathrm{Var}(\frac{S_j}{P_j})} = \frac{1}{\frac{1}{P_j^2} \mathrm{Var}(S_j)} = \frac{P_j^2}{V_j},
@@
 In this case, both the profile $P_j$ and variance $V_j$ will be proportional to the number of photons $N_{phot}$, so the pre-multiplier of the flux become
-\begin{equation}
+\begin{equation*}
 \frac{w_j}{P_j} \approx \frac{N_{phot}^2}{N_{phot} N_{phot}} = 1.0.
-\end{equation}
+\end{equation*}
 Therefore, using this traditional formula will provide little difference with straight summation,
-\begin{equation}
+\begin{equation}\label{eq:StraightSummation}
 f_{sum} = \sum_{j=1}^{m} S_j.
@@
 
+In Section \ref{sec:empCovarianceMatrix}, we compare the results of straight summation (Equation \ref{eq:StraightSummation}), variance weighting (Equation \ref{eq:varianceweights}) and covariance weighting (Equation \ref{eq:covarianceweights}).
 %Simply variance weighting the spectra by the read and photon noise does not provide heavy enough weights.
@@
 \includegraphics[width=.49\columnwidth]{cross_sections_cov.pdf}
-\caption{Left: The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
-The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections and column-by-column and row-by-row subtractions have been performed.
-The detector's diagonal elements are better than the read noise squared due to the row-by-row and column-by-column subtraction step.
-Right: The spectral (X) and spatial (Y) directions from the matrix are averaged to build up a higher signal to noise covariance profile.
+\caption{{\it Left:} The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
+The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections, column-by-column subtraction and row-by-row subtraction have been performed.
+The detector's diagonal elements are slightly below the published detector read noise ($13^2 = 169 (e^-)^2$) due to the row-by-row and column-by-column subtraction step.
+{\it Right:} The spectral (X) and spatial (Y) directions from the matrix are averaged to build up a higher signal to noise covariance profile.
 Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
@@
 
-\begin{figure}[!hbtp]
-\centering
-\caption{Average covariance along the spatial and spectral directions for a given pixel spacing.}\label{fig:covSpecSpatialDiff}
-\end{figure}
-
 \subsubsection{Empirical Covariance Matrix}\label{sec:empCovarianceMatrix}
 The ideal weighting of the spectrum from Equation \ref{eq:covarianceweights} depends on the covariance matrix $C_{ij}$.
-We use CDS (correlated double sampling) read pairs of OTIS long dark data (108 frames) with reference pixel corrections to estimate $C_{ij}$.
+We use a long dark exposure from the Optical Telescope Element and Integrated Science test performed at NASA Johnson on August 23, 2017 to estimate the read noise in $C_{ij}$.
+We process the data by performing a CDS (correlated double sampling) read pairs of long dark data (108 frames) with reference pixel corrections, column-by-column median subtraction and row-by-row median subtraction.
+These represent the steps that will be performed on grism time series before extraction.
 We consider a wavelength bin that is 100 pixels in the dispersion direction (0.1$\mu$m) and 14 spatial spatial pixels.
-We also subtract the CDS frames by the median of each row-by-row and the median of each column column-by-column to reduce the amplifier offsets and 1/f noise as done in Figure \ref{fig:longDarkPhot}.
+The resulting images are similar to Figure \ref{fig:longDarkPhot} (right).
 
@@
 We reduce the noise and jaggedness of the empirical covariance matrix in Figure \ref{fig:covSpecSpatial} by averaging the value along the diagonal, across all spectral pixels and across the spatial pixels with the same value of $i -j$.
+Here, the profile is the value from \texttt{pynrc}, which uses \texttt{webbpsf}.
+We assume that the photon and background noise is $\sqrt{N_{phot}}$ and that they are completely uncorrelated from on pixel to next, so the covariance matrix is the sum, in quadrature, of the empirical read noise covariance matrix and a diagonal photon noise matrix.
+
 The resulting optimal weighting function $w_j/P_j$ is plotted in Figure \ref{fig:covWeightedSummation}.
-Here, the profile is the value from \texttt{pynrc}, which uses \texttt{webbpsf}.
 This optimal weighting significantly increases the contributions from the inner pixels compared to variance weights.
@@
 Optimal covariance weighting significantly lowers the contribution of read noise to the overall error budget.
-We test this with a series of grism images with no photon noise added.
-We do background subtraction along the dispersion and spatial directions.
-We perform sum extraction over a 15 spatial pixels and then combine together 170 spectral pixels into a 0.17 $\mu$m wavelength bin.
+We test this with a series of grism images with a constant spectrum of an A0V star added to the CDS read pairs, but do not add photon noise to focus on the read noise contribution.
+We do background subtraction along the dispersion and spatial directions, as would be done in a spectroscopic extraction pipeline.
+We perform sum extraction over a 15 spatial pixels and then combine together 165 spectral pixels into a 0.165 $\mu$m wavelength bin.
 The standard deviation of sum extraction is 3,860 DN, which is 2.7$\times$ the read noise, as shown in Table \ref{tab:noiseSummary1overf}.

### 2020-05-08 ms.tex
added a plot showing the noise contributions for a generic source

@@
 
-\subsection{Row-by-Row Subtraction}\label{sec:photRowByRow}
+\subsubsection{Row-by-Row Subtraction}\label{sec:photRowByRow}
 
@@
 
-\subsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
+\subsubsection{Mean Row by Amplifier}\label{sec:indAmpAvg}
 A slight modification to the above strategy is to average each amplifier individually.
@@
 
-\subsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
+\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
 
@@
 \subsection{The impact of correlated read noise on time series}
+
+So far, we have discussed the magnitude of correlated read noise on an integration-by-integration basis, but it is also helpful to see its impact on the transit depth or eclipse depth of an exoplanet.
+For context, the features size of atmospheric signatures on archetypical planets are expected to be $\sim$300 ppm for hot Jupiters and Neptunes but only 10 ppm for cool Super-Earths like K2-3 b \citep{greene2016jwst_trans}.
+The 
+ with clouds have molecular features of $\sim$300 ppm, most easily-observable planets, such as hot Jupiters, are expected to have molecular atmospheric features of $\sim$200 to $\sim$500 ppm \citep{schlawin2018JWSTforecasts,greene2016jwst_trans}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.59\columnwidth]{generic_src_errors.pdf}
+\caption{Bright sources, where only a handful of groups per integration are possible without saturation, can be dominated by read noise due to correlated errors and small photon noise.
+}\label{fig:genericSourceErrorContrib}
+\end{figure}
 

### 2020-05-09 ms.tex
wrote description of the generic source w/ read noise contribution plot

--- 2020-05-07 ms.tex
@@
 
-\subsection{Grism Extraction}
+\subsection{Grism Extraction}\label{sec:GrismDarkExtraction}
 
@@
 
-The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
-The transit durations for most exoplanets considered is several hours long.
-We therefore quantify error source over 1 hour duration.
-If the smallest stripe subarray 2048$\times$64 is used, frame time is 0.34 seconds.
-For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
-Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
-%In section \ref{sec:darkBaseline}, we show from dark frames, that the read noise is statistically independent from integration to integration.
-
-For a concrete example, we consider a primary transit of WASP-80 b observed with the F444W grism time series mode.
-The exposure parameters that give a peak pixel count of 35,000 DN or 40\% well depth are a 2048$\times$256 stripe mode with BRIGHT1 read mode for 12 groups.
-These integrations are 31 seconds in duration.
-Each integration will have a 7.8$\times 10^7$ DN in a broadband aperture, so the photon noise per integration is 6,500 DN or 83 ppm.
-Over 1 hour (111 integrations), the photon noise will be 8 ppm if all integrations are independent.
-
-We consider here some example science impacts of correlated read noise in these photometric apertures.
-We will evaluate the performance of a WEAK LENS +8 mode photometric time series, as will be common with NIRCam grism time series observations.
-For a pessimistic scenario, we assume a 15,000 DN read noise contributes to every pair of reads for the 70 pixel radius aperture (and 75 to 100 pixel background subtraction annulus).
-If the read noise is tolerable under this scenario, then it should have a minimal impact on photometric time series.
-If it is a problem, we will discuss methods of mitigation such as the row-by-row subtraction above.
-
-We also assume that each read/frame is statistically independent from the other.
-Therefore, the uncorrected read noise per integration is:
-\begin{equation}
-RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}},
-\end{equation}
-where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the A3 detector.
-If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
-\textcolor{red}{\bf Also empirically verify this with a slope fit to multiple images.}
-For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be $1.8 \times10^8$ DN, having a photon uncertainty of 9,100 DN or 51 ppm.
-Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames that fill to 60\% well depth.
-As an example, a $K$=8.5 magnitude star observed in full frame WEAK LENS +8 imaging mode with 6 RAPID groups up the ramp sampling and the F210M filter would have a photon noise equal to the (uncorrected) read noise and fill the detector to 54\% well depth.
-
-We have demonstrated that row-by-row and amplifier-by-amplifier median subtraction can substantially reduce the read noise for a correlated double sample subtraction from 23,500 DN to 2,900 DN.
-Therefore, the corrected read noise per integration should be:
-\begin{equation}\label{eq:bestRNCorrection}
-RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}
-\end{equation}
-\textcolor{red}{\bf This is for the ALONG detector.
-Update for the A3 detector}
-For the same $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode, the read noise per integration should be 1,700 DN.
-Fortunately, this is now a small fraction of the photon uncertainty of 9,100 DN and only amounts to an increase in noise over the 51 ppm photon by 9 ppm per integration.
-
-\textcolor{red}{\bf Include more calculations on how the individual frame read noise would impact many frames in a time series of a bright target vs a faint target.}
-
-\subsubsection{Impact to Grism Time series}
-We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
-In this case, we assume row-by-row subtraction is performed and that the CDS noise from the OTIS ground-based test is representative of flight.
-Then, the equivalent grism aperture noise to equation \ref{eq:bestRNCorrection} is
-\begin{equation}
-RN_{grism,0.17\mu\mathrm{m}} = \frac{5,130 DN}{ \sqrt{N_{frames}}}.
-\end{equation}
-For the grism aperture
-
-\clearpage
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{generic_src_errors.pdf}
+\caption{Bright sources, where only a handful of groups per integration are possible without saturation, can be dominated by read noise if simple sum extraction is used.
+A covariance-weighted extraction can substantially decrease the contribution of correlated read noise to below the photon limit.
+The errors here are for a grism time series wavelength bin that is 0.17$\mu$m wide centered on 3.34 $\mu$m for a G-type host star and a 3 hour transit duration.
+}\label{fig:genericSourceErrorContrib}
+\end{figure}
+
+So far, we have discussed the magnitude of correlated read noise on an integration-by-integration basis, but here we explore how it will impact science.
+We calculate the expected noise in the transit depth or eclipse depth of a generic exoplanet.
+For this calculation, we assume a planet orbits a G-type 5800 K star, has a 3 hour transit duration and is observed with a 2048$\times$256 stripe subarray and is read out in RAPID mode with 1 frame per group and 4 amplifiers (No.
+of output channels=4).
+We consider a range of $K$ magnitudes from 6 to 11.
+We then calculate the maximum number of groups up the ramp that can be commanded while keeping the peak pixel count below 50\% well depth to safely avoid severe non-linearities.
+From there, we calculate the noise due to photon counting statistics (ie. $\sqrt{N_{phot}}$) and compare it to the read noise.
+As in Section \ref{sec:GrismDarkExtraction}, we focus on a 0.17~$\mu$m wide bin centered at 3.34~$\mu$m
+
+Figure \ref{fig:genericSourceErrorContrib} shows the photon noise as a function of $K$ Vega magnitude.
+The photon noise scales as $\sqrt{f}$, where $f$ is the flux because it is in the foreground limit.
+The read noise drops slowly with $K$ magnitude because the time to reset between integrations takes a smaller and smaller fraction of the total exposure as the number of groups per integration grows.
+We show the read noise assuming sum extraction (1044 ppm for CDS integration) and covariance-weighted extraction using Equation \ref{eq:covarianceweights} (230 ppm for CDS integration).
+If a sum extraction is used, the read noise will dominate for $K \lesssim 8.7$.
+However, covariance weights can ensure that photon shot noise is more dominant.
+
+Some of the most interesting targets will be nearby bright sources, where the photon noise is small and the feature size is small.
+For context, the features size of atmospheric signatures on archetypical planets are expected to be $\sim$300~ppm for hot Jupiters and Neptunes but only 10 ppm for cool Super-Earths like K2-3 b if they have high metallicity atmospheres \citep{greene2016jwst_trans}.
+Therefore, observations of transiting cool super-Earths will require careful treatment of the correlated read noise, such as the covariance weighting scheme, to achieve the precision needed to probe their atmospheres.
+
+We note that Figure \ref{fig:genericSourceErrorContrib} shows a somewhat counter-intuitive result: read noise dominates for bright source and becomes less important for faint sources.
+For typical observations, such as faint galaxies or distant stars, the opposite is true: read noise is more of a concern for faint sources than bright ones.
+So why is there a discrepancy?
+The difference in these two science cases is that for exoplanet transit observations, the detector well depth is filled to approximately the same level ($\sim 32,000$ DN or 50\% well depth per pixel) regardless if the system's magnitude is 6 or 11.
+For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
+This is different from a faint galaxy in the $K > 20$ range, which will not fill the detector well.
+For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.
+
 \section{Fringing}
@@
 These angles and patterns can be analyzed with a 2D power spectrum as shown in Figure \ref{fig:crossHatchA5}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
+\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
+\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
+\caption{
+The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
+The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
+The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
+Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
+These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
+}\label{fig:crossHatchA5}
+\end{figure}
 
@@
 Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
-\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
-\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
-\caption{
-The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
-The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
-The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
-Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
-These three relative crosshatch angles (67.8$\degree$, 67.7$\degree$ and 44.5$\degree$) are similar to a projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom, 67.8$\degree$, 67.8$\degree$, 44.4$\degree$).
-}\label{fig:crossHatchA5}
-\end{figure}
 

### 2020-05-10 ms.tex
updated the crosshatch calculation for latest Full Frame Grism field point

@@
 %% using aastex version 6.2
-\documentclass{aastex62}
+\documentclass[]{aastex62}
 
@@
 
-\begin{figure}[!hbtp]
+\begin{figure*}[!hbtp]
 \centering
@@
 The long dark exposure example of 108 integrations shows the behavior over long timescales.}\label{fig:ampResetDark}
-\end{figure}
+\end{figure*}
 
@@
 }\label{fig:ampOffsetsOtisGrismSlope}
-\end{figure}
-
-\clearpage
+\end{figure*}
+
 \section{1/f Noise}
@@
 For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
-This is different from a faint galaxy in the $K > 20$ range, which will not fill the detector well.
+This is different from a faint galaxy in the $K > 22$ range, which will not fill the detector well.
 For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.
@@
 
-Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing where a broadband point source is dispersed by the grism.
-The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{nchdas}.
-The background is subtracted with a 2nd order polynomial fit and the flux is extracted with an optimally weighted summation \citep[e.g.][]{horne1986optimalE}.
+\begin{figure*}[!hbtp]
+\centering
+\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
+\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
+An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
+}\label{fig:CV3GrismSpecFringing}
+\end{figure*}
+
+Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing at NASA Goddard where a broadband point source is dispersed by the grism.
+The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{ncdhas}.
+The background is subtracted with a 2nd order polynomial fit and the flux is extracted with a variance-weighted summation \citep[e.g.][]{horne1986optimalE}.
 The spectrum is normalized by a 3rd order spline fit with 400 knots to remove the broad shape of the spectrum and the throughput curves.
@@
 The variations have peak-to-valley amplitudes of about 8\%.
-However, we expect that the fringing structure will hold relatively constant during time due to the temperature stability of the instrument.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.99\columnwidth]{fringing_grism_cv3.pdf}
-\caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
-An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
-}\label{fig:CV3GrismSpecFringing}
-\end{figure}
-
-\clearpage
+Figure \ref{fig:cv3ExtractedSpectrum} also shows an illustrative fringing model that increases in frequency as the wavelength decreases.
+
+The fringing pattern is clearly visible in the grism spectrum, so it will be imprinted on all grism spectra.
+However, this fringing pattern should be a function of the detector thickness and should remain constant for a fixed position in the detector.
+The grism time series observations will be performed with target acquisition to reliably centroid on the source to better than 0.15 long wavelength pixels.
+We therefore expect that the fringing pattern will be repeatable from one observation to the next.
+For use in stellar characterization, however, it may be helpful to divide this fringing pattern out from a correction function made from a standard star.
+
 \section{Subpixel Crosshatching}
@@
 This is more than twice the estimate from \citet{ninan2019crosshatchHPF} for an HgCdTe used on the Habitable Planet Finder.
-We expect that the crosshatch pattern's width varies among detectors and that a tophat function is a poor approximation of the actual subpixel response.
+We expect that the crosshatch pattern's width varies among detectors or that a tophat function is a poor approximation of the actual subpixel response.
 Within NIRCam detectors, there are large variations in the strength and orientation of crosshatch features.
 
-The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (resolving crystal structures) and smallest for the long wavelengths.
+The crosshatch pattern is wavelength dependent, as seen in Figure \ref{fig:crossHatchWavelengthDep}, where the throughput variations are the largest for short wavelengths (better resolving crystal structures) and smallest for the long wavelengths.
 This is visible both in the throughput cross section of the flat field and the Fourier amplitude of the crosshatch as a function of wavelength.
@@
 In other words, the separations between the vectors are $67.699 \degree, 67.831 \degree$, and $44.470 \degree$.
-The uncertainties were simply derived from the diagonals of the covariance matrix and likely are underestimated.
-
-NIRCam's 10 SCA's have very similar crosshatch angles with separations of 44.5 $\degree$ and 67.7 to 67.8 $\degree$.
-They tend to have one primary crosshatch axis oriented either along the X pixels or the Y pixels, with two flanking axes at $\sim 67.7 \degree$ to either side.
-The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
-The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
-Figure \ref{fig:crosshatchModelGallery} shows the best-fit crosshatch 2D power spectra.
+The uncertainties were simply derived from the diagonals of the covariance matrix and may be underestimated.
 
@@
 
-\clearpage
+NIRCam's 10 SCA's have very similar crosshatch angles with separations of 44.5 $\degree$ and 67.7 to 67.8 $\degree$ as seen in Figure \ref{fig:crosshatchModelGallery}.
+They all have one primary crosshatch axis oriented either along the X pixels or the Y pixels, with two flanking axes at $\sim 67.7 \degree$ to either side.
+The long wavelength arrays have a more pronounced crosshatch than the short wavelength arrays.
+The NRCB4 array's primary crosshatch direction is most closely aligned with a pixel axis (the Y direction) than any SCA.
+Figure \ref{fig:crosshatchModelGallery} shows the best-fit crosshatch 2D power spectra.
+
 \subsection{Position of SubGrism Array}
@@
 \end{enumerate}
-
-The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
-We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
-The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
-The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
-The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
-The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
-We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
-\textcolor{red}{\textbf{Update this for latest full frame grism field point}}
 
@@
 \end{figure}
+
+The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.
+The first position is nearly the same as the SUBGRISM64 subarray position in the grism time series mode, except that the SUBGRISM64 includes the first 5 rows which are excluded here from the crosshatch analysis.
+The field point used for the SUBGRISM64 mode is expected to be the same one as will be used for the SUBGRISM128 and SUBGRISM256 subarrays.
+The position at the top of the ALONG detector has the smallest amplitude of crosshatch pattern in all three directions.
+The best-fit amplitudes are used as input to the jitter simulations in Section \ref{sec:CrosshatchSim}.
+We find that the maximum flux change for a 0.1 pixel shift is 118 ppm for the nominal grism position, 108 ppm for the top of the array and 153 ppm at the full frame grism position.
 

### 2020-05-11 ms.tex
edits to persistence and conclusions

@@
 
-\author{Karl Misselt?}
+\author{Jarron Leisenring?}
 \affiliation{Steward Observatory \\
@@
 
-\author{Jarron Leisenring?}
+\author{Karl Misselt?}
 \affiliation{Steward Observatory \\
@@
 
-\subsection{Crosshatch Pattern Modeling}
+\subsection{Crosshatch Pattern Modeling}\label{sec:crosshatchModeling}
 We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
@@
 We include three angles so that the total power spectral density is
-\begin{equation}
+\begin{equation}\label{eq:fullPSDmodel}
 f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c) + d \exp{\left(-k_r/e_b\right)},
@@
 We simulate the effect of this jitter on NIRCam time series observations with the following steps:
-\begin{itemize}
+\begin{enumerate}
 	\item Fit the existing flat field to a crosshatch model in the Fourier domain
@@
 	\item Simulate an over-sampled PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
+	\item Shift the PSF along the X and Y directions (as much as 6 mas) \label{it:xHatchShiftPSF}
 	\item Multiply the PSF by the simulated flat field
-	\item Shift the PSF along the X and Y directions up to a magnitude of 6 mas
 	\item Bin the simulated images into the native pixel size
-	\item Divide by the pixel-to-pixel flat field
-	\item Measure the relative flux with a photometric aperture
-\end{itemize}
-
-We take the exponential model with best-fit parameters for the F300M filter and extend the exponential function out to an oversampling factor of 60 times the LW pixels.
+	\item Divide by the pixel-to-pixel flat field (as would be done in pipeline)
+	\item Measure the relative flux with a photometric aperture with the same shift applied \label{it:xHatchApPhot}
+\end{enumerate}
+
+As discussed, in Section \ref{sec:crosshatchModeling}, we fit equation \ref{eq:fullPSDmodel} to the measured power spectral density of the F300M filter for the frequencies above 0.05 px$^{-1}$.
 We evaluate equation \ref{eq:analyticPSDradial} for frequencies in the oversampled image from 0 px$^{-1}$ to 30 px$^{-1}$ and multiply this by the number of pixels and the square of the oversampling factor (ie.
@@
 
-We repeat the last steps of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
+We repeat steps \ref{it:xHatchShiftPSF} through \ref{it:xHatchApPhot} of the observation simulation by shifting the over-sampled PSF by sub-pixel amounts.
 The subpixel shifts of the over-sampled PSF are performed with \texttt{scipy.ndimage.shift}.
@@
 While the simulations here include no background flux, we use the background subtraction to simulate the operations applied by a photometry pipeline.
+These are also expected to be similar to a spectroscopic pipeline for a narrow spectral region or spectral line.
 The differential flux between the centered PSF and the shifted one is shown in Figure \ref{fig:subpixScanSimulation}.
@@
 When the LW grism time series mode is enabled, SW imaging data will automatically be collected simultaneously enabling the SW centroids to be used to track the motion of the dispersed grism image.
-Furthermore, the pixels for time series modes can be characterized in detail because the will be re-used for all time series observations in a given mode.
-Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 6$ mas) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Time-Series+Imaging+Target+Acquisition}
+Furthermore, the pixels for time series modes can be characterized in detail because they will be re-used for all time series observations in a given mode.
+Target acquisition is expected to achieve centroiding accuracy $\lesssim$ 10 mas ($\lesssim 0.15$ long wavelength pixels) for unsaturated target acquisition.\footnote{https://jwst-docs.stsci.edu/near-infrared-camera/nircam-operations/nircam-target-acquisition/nircam-time-series-imaging-target-acquisition}
 This ensures that time series observations will reliably return to the same location within the same set of pixels with every visit.
@@
 \fig{tser_v2_v3_zoom_2.pdf}{0.45\textwidth}{Pointing Series Zoom 2} }
-\caption{Occasional pointing errors are expected to be quickly corrected by the fine steering mirror.
+\caption{Occasional pointing errors due to High Gain Antenna repointings are expected to be quickly corrected by the fine steering mirror with less than 1 minute e-folding timescales.
 }\label{fig:tserPointingZoom}
@@
 Furthermore, centroid motion measurements can be used to correct the flux variations due to subpixel jitter with a polynomial or Gaussian process regression.
+Furthermore, the spacecraft telemetry can be used to identify High Gain Antenna moves to remove the short ($\lesssim$ 1 minute e-folding) centroid vibrations if desired.
 
@@
 
-\clearpage
-
 \section{Random Telegraph Noise and RC pixels}
-Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
-The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
-These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.
-
-For Weak Lens photometric aperture (such as a 70 pixel radius aperture), there will be of order 2-4 pixels exhibiting RTN.
-The RTN may not be removed by jump detection algorithms if they are similar order of magnitude to the photon noise for a single pixel ($\sim$180 DN).
-If these are not identified, the RTN can contribute $\sim$200 counts in 4$\times 10^7$ or 5 ppm changes.
-
-There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
-These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
-There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
 
@@
 
+Several pixels exhibit RC (exponential) behavior and other exhibit unpredictable jumps in their DC levels.
+The jumps are called Random Telegraph Noise (RTN) and some examples are shown in Figure \ref{fig:RTNandRC}.
+These are rare events (400-1000 pixels out of 4$\times 10^6$) so they are unlikely to end up in a grism or in-focus aperture.
+
+For Weak Lens photometric aperture (such as a 70 pixel radius aperture), there will be of order 2-4 pixels exhibiting RTN.
+The RTN may not be removed by jump detection algorithms if they are similar order of magnitude to the photon noise for a single pixel ($\sim$180 DN).
+If these are not identified, the RTN can contribute $\sim$200 counts in 4$\times 10^7$ or 5 ppm changes.
+
+There are also RC pixels (as shown in Figure \ref{fig:RTNandRC}) that have exponential curves like a resister-capacitor circuit.
+These pixels consistently show RC behavior and are flagged as ``Do-not-use'' for the pipeline so they may be skipped in the aperture summation.
+There are 15 RC pixels in a 20 pixel tall F444W aperture and 31 RC pixels in a 20 pixel tall F322W2 aperture.
+
 \section{Persistence}\label{sec:persistence}
 HST shows noticeable ramps with each HST orbit due to detector charge trapping \citep{zhou2017chargeTrap}.
+Fortunately, the JWST NIRCam persistence levels are much lower.
+\citet{leisenring2016persistence} find that the persistence rate after saturating the detectors and turning off the lamp is 0.5 DN/sec to 15 DN/sec or 0.28$e^-$ to 6.8$e^-$ at the 30 second mark, depending on the detector.
+
 Lamp sources in our laboratory tests typically have a warm up period lasting several tens of minutes, which makes it difficult to observe this same effect the detector ramps.
@@
 The characteristic timescale for persistence is 12 seconds, as shown in Figure \ref{fig:persistence}.
-Thus, charge trapping release becomes undetectable after 5 minutes and is well below 0.1 DN/s per pixel.
+After 5 minutes, it is well below 0.1 DN/s.
 This release time is considerably faster than for Hubble Space Telescope, where the fast-trap release timescale is 280 seconds and the slow-release timescale is 16,300 \citep{zhou2017chargeTrap}.
@@
 
-\subsection{Persistence with Long and Short Illumination}
-We estimate the persistence level by illuminating the detectors to $\sim$80\% well depth for either 30 seconds or 30 minutes and observe the slopes after the LED is turned off.
-We find a that the slopes rapidly the noise levels ($<$ 10 e$^-$/s) in less than 10 seconds, as shown in Figure \ref{fig:persistenceAZlab04}.
-This is similar to the measurements in \citet{leisenring2016persistence}, who find that the persistence rate after saturating the detectors and turning off the lamp is 0.5 DN/sec to 15 DN/sec or 0.28$e^-$ to 6.8$e^-$ at the 30 second mark, depending on the detector.
-The flight NIRCam long wavelength detectors in \citet{leisenring2016persistence} have smaller persistence signals than the short wavelength detectors.
-The asic dewar persistence test in Figure \ref{fig:persistenceAZlab04} is for a long wavelength detector.
-
-\begin{figure*}
-{\gridline{\fig{persistence_short_log.pdf}{0.49\textwidth}{Short Timescale Persistence. }
-\fig{persistence_long_lin.pdf}{0.49\textwidth}{Long Timescale Persistence}}}
-\caption{The NIRCam long wavelength detectors show very rapid charge trap release timescales, such that the count rates fall below the read noise level in 20 seconds.
-The data are binned to show that there is no detectable persistence on 3000 second timescales.
-An arbitrary offset of 4$e^-$/s is added on the short timescale plot to keep the values positive and possible to plot on a log scale.}\label{fig:persistenceAZlab04}
-\end{figure*}
+We consider an  integration of 30 seconds for a 0.17~$\mu$m wavelength bin (5 spatial pixels by 170 spectral pixels, counting only the pixels above $\sim$ 1000 DN per integration).
+After 1000 seconds, the persistence level falls to $10^{-2}~e^-$/s for the A5 detector \citep{leisenring2016persistence}, the detector used for grism time series..
+In that case, there are 255 $e^-$ electrons released in the exposure compared to a 6.7 $\times 10^6 e^-$ collected from the source or 40 ppm.
+Contrast this with HST observations of GJ 1214 b, where the ramp effect is 4000 ppm \citep{berta2012flat_gj1214} over the $\sim$45 minute visibility window for an HST orbit.
 
@@
 	It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise.
-	Fortunately, 1/f noise averages like $1/\sqrt{N_{int}} $ from integration to integration.
+	Fortunately, 1/f noise averages like $1/\sqrt{N_{int}} $ from integration to integration after background subtraction.
 	We found efficient reductions in 1/f noise by subtracting the median value from each row in each amplifier.
@@
 	For detector read modes and the long wavelength grism with a small number of groups up the ramp ($<6$ for the short wave weak lens mode), the 1/f noise will be larger than the photon noise using sum extraction.
-	A covariance weighting scheme described in Section \ref{sec:optimalCovWeights} will significantly lower the read noise
+	A covariance weighting scheme described in Section \ref{sec:optimalCovWeights} can significantly lower the read noise from $\sim$1000 ppm to $\sim$250 ppm per read.
 	\item \textbf{Subpixel Sensitivity:} The NIRCam detectors all exhibit some degree of crosshatching patterns along crystallographic planes of HgCdTe.
-	Crosshatching structures extend down to the subpixel level where they will not be corrected for in standard flat fielding procedures, especially at the wavelengths that are below Nyquist sampling ($< 3.7\mu$m for the long wavelength and ($1.8\mu$m for the short wavelength).
+	Crosshatching structures extend down to the subpixel level where they will not be corrected for in standard flat fielding procedures, especially at the wavelengths that are below Nyquist sampling ($< 3.7\mu$m for the long wavelength) and ($1.8\mu$m for the short wavelength).
 	The ALONG detector (used for grism time series) experiences the most pronounced crosshatching amplitudes.
-	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 7 mas (or 0.1 NIRCam long wavelength pixels).
-	Fortunately, the pointing drifts are expected to be very small other than brief and infrequent High Gain Antenna moves, so the expected standard deviation of flux due to pointing jitter is only $\sim$ 6 ppm.
+	We estimate that up to 150 ppm variations in flux can occur for small pointing drifts of 6 mas (or 0.1 NIRCam long wavelength pixels).
+	Fortunately, the line-of-site pointing drifts are expected to be very small (2 mas) other than brief and infrequent High Gain Antenna moves, so the standard deviation of flux due to pointing jitter is expected to be only $\sim$ 6 ppm.
 	The variations in flux at the subpixel level appear smooth enough that they could likely be calibrated as a function of position.
@@
 	JWST shows a much smaller ``hook effect'' and also much faster charge trap timescales, such that we expect it to be a negligible contributor so the NIRCam error budget.
-	Long timescale traps contribute less then 1e-/DN/px so they are less problematic.
+	Long timescale traps contribute less then 0.01 e-/s/px after 1000 seconds so they are less problematic.
 \end{itemize}
@@
 \section*{acknowledgements}
-MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
-This research has made
-use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at \url{http://exoplanets.org}; SIMBAD database, operated at CDS, Strasbourg,
-France; NASA's Astrophysics Data System Bibliographic
-Services; the M, L, T, and Y dwarf compendium
-housed at \url{http://DwarfArchives.org}; the SpeX Prism
-Libraries at \url{http://www.browndwarfs.org/spexprism}; and the \texttt{astropy} package \citep{astropy2013}. 
-The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
-We are most fortunate to have the opportunity to conduct observations from this mountain.
+
+\software{\texttt{astropy} package \citep{astropy2013},
+\texttt{pynrc},
+\texttt{numpy},
+\texttt{scipy},
+\texttt{pysynphot} \citep{lim2015pysynphot},
+\texttt{ncdhas},
+\texttt{photutils} \citep{bradley2016photutilsv0p3},
+\texttt{matplotlib}
+}
 

### 2020-05-11 ms.tex
title update
fixing multiply defined labels

@@
 
-\title{JWST Noise Floor I: Systematic Error Sources with JWST NIRCam Time Series}
+\title{JWST Noise Floor I: Systematic Error Sources in JWST NIRCam Time Series}
 
@@
 The bottom left corner for each subarray is listed in parentheses in the title of the flat field plot and the best-fit amplitudes are listed in the title of the power spectral density plot.
- }\label{fig:subpixScanSimulation}
+ }\label{fig:crosshatchGrismPos}
 \end{figure}
 
-The three subarrays considered are shown in Figure \ref{fig:subpixScanSimulation}.
+The three subarrays considered are shown in Figure \ref{fig:crosshatchGrismPos}.
 We exclude reference pixels (which form a 4 pixel wide boundary around the detector) and an additional row on the bottom and top of the array because these illuminated rows are outliers in the flat field.

### 2020-05-12 ms.tex
following request to move from possible author to aknowledgements
fixed tiny inconsistency in the faint source example

@@
 Moffett Field, CA 94035, USA}
-
-\author{Peiman Maghami?}
 
@@
 For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
-This is different from a faint galaxy in the $K > 22$ range, which will not fill the detector well.
+This is different from a faint galaxy in the $K > 20$ range, which will not fill the detector well.
 For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.
@@
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
+Thanks to Peiman Maghami for providing the line of site pointing jitter simulation for use in estimating the subpixel sensitivity as well explaining sources of pointing error.
 

### 2020-05-22 ms.tex
fixes to abstract and keywords from TG

@@
 This promising science from JWST, however, will require exquisite precision and understanding of systematic errors that can impact the time series of planets crossing in front of and behind their host stars.
-This is especially true if JWST is used to search for biosignatures in temperature atmospheres on Earth-sized planets that may contain liquid water.
-Here, we provide estimates of the noise sources affecting JWST NIRCam time series.
-Correlated electronic noise (1/f noise) in the detectors can limit the sensitivity of grism time series for a given frame (230 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames.
+This is especially true if JWST is used to search for biosignatures in temperate atmospheres and other weak signatures.
+Here, we provide estimates of the noise sources affecting JWST NIRCam time-series data.
+Correlated electronic noise (1/f noise) in the detectors can limit the precision of grism time series for a given frame (230 ppm to 1000 ppm depending on the extraction method), but will average down like $\sqrt{N}$ for $N$ frames/reads.
 Care should be taken to include as many frames as possible per visit to reduce this 1/f noise source: thus, we recommend the smallest detector subarray sizes one can tolerate, 4 output channels and readout modes that minimize skipped frames (RAPID or BRIGHT2).
@@
 %% keywords and the rules for their use.
-\keywords{stars: atmospheres --- stars: individual (\objectname{KIC 12557548}) ---
-stars: variables: general}
+\keywords{Concept: Astronomical detectors --- Concept: Exoplanet atmospheres --- Concept: Near infrared astronomy}
 
@@
 
-JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 12 $\mu$m
+JWST will provide powerful new measurements of exoplanet atmospheres with spectroscopy from 0.6 to 28 $\mu$m
 \citep{beichman2014pasp,greene2016jwst_trans,howe2017informationJWST,barstow2015jwstSystematics,schlawin2018JWSTforecasts}.

### 2020-05-22 ms.tex
edits to intro from TG

@@
 Alternatively, 10 transits of TRAPPIST-1e could be sufficient if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
-A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.
+A critical question in studying planets like TRAPPIST-1 d/e with small spectroscopic signatures, however, is whether photon-limited performance is possible with JWST observations.
 For difficult biosignatures, noise levels less than 10 ppm (parts per million) are required and this value shrinks in the presence of clouds.
@@
 The NIRCam grism mode will collect moderate resolution R$\sim$1100-1700 spectra over the wavelength range from 2.4 to 5.0~$\mu$m.
-This grism mode can be used simultaneously with short wavelength weak lens imaging or (in future cycles) the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
-If it becomes an approved and implemented mode, the DHS will permit spectroscopy simultaneous from 1.0 to 2.0~$\mu$m because of a dichroic beamsplitter that divides the light from NIRCam into two different channels.
-The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$) inaccessible by other modes.
+This grism mode can be used simultaneously with short wavelength weak lens imaging or (in future cycles) Dispersed Hartmann Sensor spectroscopy \citep{schlawin2017dhs}.
+If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m using a wavefront sensor.
+The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$ mag (Vega)) inaccessible by other modes.
+Either the DHS or weak lens imaging can be run simultaneously with the long wavelength grism thanks to a dichroic beamsplitter.
 
 Given the finite lifetime of the JWST mission set by onboard fuel, it is important to understand the systematic errors before launch to maximize the science return of the observatory.
-We discuss the major sources of systematic errors that can affect the NIRCam instrument.
+We discuss the major sources of systematic errors that can affect time-series observations with the NIRCam instrument.
 Parallel efforts to characterize other instrument's noise sources are being done, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
 
-Section \ref{sec:knownEffects} lists the known systematic effects that can impeded high precision time series and increase the noise above the photon noise.
+Section \ref{sec:knownEffects} lists the known systematic effects that can degrade the precision of time series measurements compared to the the photon noise limit.
 Sections \ref{sec:preAmp} through \ref{sec:persistence} detail these noise contributions.

### 2020-05-25 ms.tex
edited a few comments from TG and updated fringing model

@@
 \section{List of Known Detector Effects}\label{sec:knownEffects}
-An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
-However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
+An ideal HgCdTe detector would simply count the photons incident on its surface (as described in Appendix \ref{sec:detectorPrimer}).
+The NIRCam, NIRSpec and NIRISS instruments on JWST use Teledyne HAWAII2RG HgCdTe detectors.
+For NIRCam, the eight short wavelength detectors have a 2.5 $\mu$m cutoff while the two long wavelength detectors have a 5.0 $\mu$m cutoff \citep{jdoxNIRCamDetectors}.
+Each of the detectors is connected to a SIDECAR ASIC \citep{loose2006sidecarAsic} that controls how the pixels are read out and reset.
+All detectors are connected to four output amplifiers that can be read out simultaneously on four vertical stripes of the detectors.
+Each pixel's NP semiconductor junction may be measured non-destructively multiple times (referred to as ``reads'' or ``samples'') before the pixel is reset, ending an integration.
+The combination of all the pixels as an image is saved as a ``frame'', which together make up an integration, which ends when a pixel is reset.
+The integrations are packaged together into a single ``exposure'' and the frames are co-added into groups of 1 or more frames to save data.
+\citet{jdoxNIRCamDetectorPatterns} contains more information on the readout patterns.
+
+There are many non-ideal effects, however, that can affect the stability of a light curve measurement of a transiting exoplanet.
 Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics.
@@
 
-\begin{itemize}[noitemsep]
-	\item \textbf{Pre-amplifier reset offsets:} (an Asic-related effect) 
+The following sources of noise introduce random variations to time series:
+\begin{enumerate}[noitemsep]
+	\item \textbf{Pre-amplifier reset offsets:} (a SIDECAR ASIC-related effect) 
 The resets cause discontinuities in the pedestal level of all pixels between frames.
@@
 	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets above.
-	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
+	\item \textbf{1/f noise:} The JWST readout integrated circuits (ROICs) have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
 	This is a noise source where most of the noise power is concentrated at low frequencies.
@@
 1/f noise can be reduced by subtracting the values from background pixels or reference pixels.
-	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response of pixels is not perfectly uniform.
-	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
-	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
-	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
@@
 	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
-	Fortunately, the bias offset produces by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
+	Fortunately, the bias offset produced by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
 	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).
+	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
+	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
+Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array and exhibited 1 jump in a 20 minute exposure.
+\end{enumerate}
+
+In addition to these random effects, there are also systematic effects that are time-variable only due variations in other variables such as temperature and telescope pointing:
+\begin{enumerate}[resume]
+	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response within pixels is not perfectly uniform.
+	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
+	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
+	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
-For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
+For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 DN changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
 Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to mostly $\lesssim$ 1 mK.
@@
 If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK \citep{hall2005jwstArrays}.
-	\item \textbf{ASIC Temperature Fluctuations:} The asic temperature will change as the operating mode.
-For example, in the CV3 stability test, the temperature of the A asic changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
+	\item \textbf{SIDECAR ASIC Temperature Fluctuations:} The SIDECAR ASIC temperature will change with the operating mode.
+For example, in the CV3 stability test, the temperature of the A SIDECAR ASIC changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
 	This temperature change is expected to be smaller in flight due to adjustments in the operations to run all four amplifiers regardless of how many are used to collect science data.
-	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
-	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
-Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
 	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Is there a good citation?}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
@@
 	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
-\end{itemize}
+\end{enumerate}
 
@@
 
-It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car asic, and how much they contribute to the error budget.
+It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car SIDECAR ASIC, and how much they contribute to the error budget.
 The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
@@
 \caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
-An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
+An illustrative fringing model is plotted for a constant-thickness 350 $\mu$m layer to better see how the frequencies change as a function of wavelength (X pixel).
 }\label{fig:CV3GrismSpecFringing}
@@
 This produces a negative charge on the P-type side.
-Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge.
+Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge on the N-type side.
 The resulting voltage difference is called the contact potential.
 In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
-This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it contains no mobile charge carriers.
+This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it is depleted of mobile charge carriers.
 The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
@@
 Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
-The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type.
+The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type semi-conductor.
 
@@
 
-\subsection{Charge Trapping}
+\section{Charge Trapping}
 All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
@@
 
-\subsection{Extracted Spectra and periodograms}
+\section{Extracted Spectra and periodograms}
 

### 2020-05-25 ms.tex
TG comments through section 3

@@
 Each pixel's NP semiconductor junction may be measured non-destructively multiple times (referred to as ``reads'' or ``samples'') before the pixel is reset, ending an integration.
+An analog-to-digital convert turns the number of electrons collected in the detector into count of Data Numbers (DNs) between 0 and 16 bits (65,536) with a gain of $\sim$1.8 for the long-wavelength detectors and $\sim$2.0 for the short-wavelength detectors.
 The combination of all the pixels as an image is saved as a ``frame'', which together make up an integration, which ends when a pixel is reset.
@@
 \begin{enumerate}[noitemsep]
-	\item \textbf{Pre-amplifier reset offsets:} (a SIDECAR ASIC-related effect) 
+	\item \textbf{Pre-amplifier reset offsets:} (a SIDECAR ASIC-related effect) \label{it:preAmpOffsets}
 The resets cause discontinuities in the pedestal level of all pixels between frames.
@@
 	This temperature change is expected to be smaller in flight due to adjustments in the operations to run all four amplifiers regardless of how many are used to collect science data.
-	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Is there a good citation?}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
+	\item \textbf{Detector Fringing} The thin $\sim 6\mu$m layer of the H2RG detectors or other optics can cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
+Older HgCdTe detectors contained a CdZnTe layer that caused a prominent fringing pattern \citep{finger2008HgCdTeCharacterization}, but JWST detectors have the CdZnTe removed so the fringe pattern comes from a different optical layer.
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
@@
 	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
-	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation on all detectors \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
 \end{enumerate}
@@
 
-\section{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}
-
-The NIRCam detectors' pre-amplifiers (pre-amps) have a reference voltage that can drift with time.
+\section{Pre-amplifier Offsets and Amplifier Boundaries}
+
+\subsection{Pre-amplifier Offsets}\label{sec:preAmp}
+The NIRCam detectors' pre-amplifiers (pre-amps) in the SIDECAR ASIC have a reference voltage that can drift with time, introduced as error source \ref{it:preAmpOffsets}.
 This can affect the pedestal level of all pixels over long ($\gtrsim$ 20 minute timescales).
@@
 The NIRCam detectors are reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
-One set of darks was collected at Lockheed CV with a reset only once per integration to study the effects of the pre-amplifier resets.
+One set of darks was collected at during NIRCam cryogenic vacuum pre-delivery testing at Lockheed Martin with a reset only once per integration to study the effects of the pre-amplifier resets.
 
@@
 However, reference pixel subtraction or background subtraction can efficiently remove pre-amp drifts, so with proper data reduction, the pre-amp drifts can be effectively eliminated.
-The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are saved with active pixels, so reference pixels will always be available for the grism.
+The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are nearby and saved with active pixels.
 
@@
 \caption{Reference pixel time series for a two frame integration (Left) and a long dark integration of 108 frames (Right).
-Each of the plots show that the pre-amplifier resets between frames in an integration cause discontinuities in the reference signal.
+Each of the plots show that the SIDECAR ASIC pre-amplifier resets between frames in an integration cause discontinuities in the reference signal.
 Amplifiers 1 and 4 track the time all through a frame with the side reference pixels, whereas amplifiers 2 and 3 in the middle only contain information on the bottom and top reference pixels at the beginning and ending of a frame.
@@
 This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
-Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in APT.
-On the flip side, the four amplifiers will have different behaviors such as offsets in the bias level.
+Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in the Astronomer's Proposal Tool \citep[APT][]{apt2020p2}.
+On the flip side, the four amplifiers will have different behaviors such as gains and offsets in the bias level.
 The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
@@
 Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
-Here, we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
+Here, in Figure \ref{fig:ampOffsetsOtisGrismSlope} (bottom panel), we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
 This is repeated for all columns.
@@
 The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
-Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from amplifier over 108 dark frames.
+Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left amplifier (512-1023 px) over 108 dark frames.
 To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.

### 2020-05-27 ms.tex
Fixing TG comments on section 4.1

@@
 The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
-Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left amplifier (512-1023 px) over 108 dark frames.
-To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
-Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
+Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left amplifier (512-1023 px) over 108 dark groups in RAPID read mode.
+The dark frames were part of a single integration taken at NASA Johnson during the OTIS (Optical Telescope element + Integrated Science instrument module) cryogenic test.
+To create the periodogram, each group is subtracted by the average of all groups to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
 
@@
 \includegraphics[width=.4\columnwidth]{preamp_removed_grp_54.pdf}
-\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
+\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 RAPID groups.
 The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000 Hz.
@@
 
-It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the side-car SIDECAR ASIC, and how much they contribute to the error budget.
+It is instructive to look at dark frames to isolate the contributions of the read-out electronics, including the SIDECAR ASIC, and how much they contribute to the error budget.
 The dark frames do not have issues with the photometric stability of illumination lamps, which is a persistent challenge with ground-based tests.
@@
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
-We also re-label the times to include the reset time that would normally occur after each integration, so the
+We also re-label the times to include the reset time that would normally occur after each integration, so the effective exposure time is increased to 38.6 min (\textcolor{red}{\bf Fix this - should be 29.0 min}).
 
@@
 In this work, we use \texttt{ncdhas}.
-As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
+As seen in Figure \ref{fig:longDarkPhot}, reference pixels are read closely enough in time to reduce the large offsets between amplifiers.
 The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
@@
 \includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
-\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
+\caption{Time series data of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, reference pixel-correction that uses the top, bottom and side reference pixels and finally a method using a row-by-row median subtraction.
+{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction (left), reference pixel-correction that uses the top, bottom and side reference pixels (middle) and finally a method using a row-by-row median subtraction (right).
 {\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.

### 2020-05-27 ms.tex
finished with all of TG's specific comments

@@
 We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
+We place 3 different identical source apertures on the detector for comparison of different regions.
 %Also, Figure \ref{fig:WLP8PSF} shows an example weak lens PSF with this aperture.
@@
 This theoretical read noise is smaller than the photon noise expected inside an aperture during photometric stability time series applications.
-The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
-The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
-The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
+To calculate the photon noise as well as convert the noise into parts per million, we need to assume a well filling fraction for the integrations.
+Here, we assume a peak pixel counts of 30,000 DN or about 60\% well depth.
+With this detector well filling fraction and a Weak Lens +8 point spread function, the number of DN collected within a 70 pixel radius aperture is was $S_{tot}=3.9\times 10^7$ DN during the integration.
+The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 1.8$ for the LW detectors).
 In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
@@
 
-In our experimental time series, however, the standard deviation in the time series in these 3 apertures is 22,000 to 25,000 DN (without any attempt to correct for amplifier offsets or 1/f noise using reference pixels or otherwise).
+In our experimental time series, however, the standard deviation in the time series in these 3 aperture source locations is 22,000 to 25,000 DN (without any attempt to correct for amplifier offsets or 1/f noise using reference pixels or otherwise).
 If uncorrected, this extra read noise will contribute 560 to 630 ppm to the time series per read pair!
@@
 Measured Read Noise (reference pixel correction) & 10,800 & 280 & 9,900 & 2,680 \\
+Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,860 & 1044 \\
+Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
+Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
 Measured Read Noise (reference channel subtraction) & 9,700 & 250 & & \\
-Measured Read Noise (row-by-row subtraction) & 6,000 & 150 & 3,860 & 1044 \\
 Measured Read Noise (20 Component PCA subtraction) & 5,400 & 140 & & \\
-Measured Read Noise (smoothed 161 px kernel interpolating over aperture) & 3,300 & 85 & & \\
 Measured Read Noise (5 Component PCA on each amplifier) & 3,200 & 81 & & \\
-Measured Read Noise (row-by-row amp-by-amp mean subtraction) & 2,900 & 75 & & \\
-Measured Read Noise (smoothed 40 px kernel on top of aperture) & 900 & 23 & & \\
 Measured Read Noise (variance-weighted summation)	& & & 3,060 & 830 \\
@@
 \enddata
-\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
-The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
+\tablecomments{We evaluate the theoretical and measured noise sources from 54 read pairs contained in a long dark integration.
+The ppm units and photon uncertainties are calculated by assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
 The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
 The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).
-For the grism, statistics are shown for a representative 0.17~$\mu$m wide wavelength bin centered on 3.34~$\mu$m.}
+For the grism, statistics are shown for a representative 0.165~$\mu$m wide (165 pixel) wavelength bin centered on 3.34~$\mu$m.}
 \label{tab:noiseSummary1overf}
@@
 We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
-The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
+The standard deviation of the flux for the 3 source apertures drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
 
@@
 
-\subsubsection{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
-
-We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:photRowByRow}.
+\subsubsection{More sophisticated 1/f noise reduction techniques}
+We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:photRowByRow} and \ref{sec:indAmpAvg}.
+None of these techniques yielded better results than mean row-by-row by amplifier in Section \ref{sec:indAmpAvg}, so readers not interested in these methods can skip to Section \ref{sec:GrismDarkExtraction}.
+
+\paragraph{Smoothed Kernel Subtraction}\label{sec:smoothKernelSub}
 We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
-The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
+The kernel is a uniform normalized kernel 1 pixel in height and 161 pixels along a row.
 This enables subtraction of 1/f noise that has length scales shorter than the line time (ie timescales shorter than 512 clock cycles or 5 milliseconds), which the median subtraction cannot remove.
-
-This smoothing kernel makes a dramatic improvement to the final weak lens aperture time series, as shown in Figure \ref{fig:longDarkWithRowKernel}.
-The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
-For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
-For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.
-
-\begin{figure*}[!hbtp]
-\centering
-\includegraphics[width=.37\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1}
-\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
-\includegraphics[width=.37\columnwidth]{zoom_long_dark_row_by_row_group_sub.pdf}
-\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
-\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image where a 40 pixel wide and 1 pixel tall averaging kernel was applied along the fast read direction of every group.
-Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise from $\sim$6,000 DN to $\sim$700 DN in the aperture.
-}\label{fig:longDarkWithRowKernel}
-\end{figure*}
-
-The dramatic difference from the smoothing kernel is beyond what is possible for a real source.
-This is because the 40 pixel wide kernel was applied all the way through the source aperture, which would subtract and distort any signal from a star/planet source.
-In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
-Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
-We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
+Care must be taken not to apply the kernel through the source aperture, which would subtract and distort any signal from a star.
+The kernel should be wider than the source aperture diameter and interpolate through the source points.
+
 We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
 \texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
-This efficiently interpolates over bad pixels and can also interpolate over the source aperture.
+This efficiently interpolates over bad pixels and can also interpolate over the source aperture by creating a circle of NaN values around the source.
 Our smoothing kernel is a flat boxcar normalized to 1.0.
-This more realistic kernel results in higher noise because of its larger window size and because it interpolates over the aperture points.
-The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
-This is still larger than the 1,300 DN expectation for uncorrelated read noise, but is below the ideal photon noise limit when integrations reach 60\% well depth.
+The resulting time series has a standard deviation of 2800 DN to 3700 ppm, which is slightly larger than the much simpler row-by-row amplifier-by-amplifier subtraction in Section \ref{sec:indAmpAvg}.
 
@@
 
-\subsubsection{Reference Channel Subtraction}
+\paragraph{Reference Channel Subtraction}
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
 Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
-We subtract an amplifier 0's time series from all amplifiers.
+We subtract the first amplifier's time series (pixels X=1 through X=512) from all amplifiers.
 Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
@@
 
-\subsubsection{PCA Correction}
+\paragraph{PCA Correction}
 
@@
 Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
-Each row represents a different noise iteration.
+Each row represents a different noise instatiation.
 First, we apply reference pixel correction to remove the pre-amplifier resets.
@@
 {\it Bottom Row:} The standard deviation of the time series dramatically decreases from 21,900 ppm to 2,680 ppm with reference pixels and 1044 ppm with column-by-column, row-by-row subtraction for the 3.34 $\mu$m bin.
-Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (512 pixels wide) and part of the leftmost amplifer, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
+Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (each 512 pixels wide) and part of the leftmost amplifer, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}
@@
 However, there are only limited background regions along the horizontal direction to use to subtract out 1/f noise.
-This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px).
-
-We give some illustrative numbers for a 0.165 $\mu$m wide bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
+This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$1100 px).
+
+We give some illustrative numbers for a 0.165 $\mu$m wide (R$\sim$20) bin of a grism spectrum centered on 3.34 $\mu$m as listed in Table \ref{tab:noiseSummary1overf}.
 Without reference pixel subtraction, the grism apertures have standard deviations of 80,930 DN.
 Reference pixel subtraction drops this value to 9,900 DN and row-by-row subtraction drops it to 3,860 DN.
+We use the pixels from X=1 to X=301 for the row-by-row subtraction to ensure there is essentially no source flux being subtracted.
 For a well depth of 60\%, there are $3.7 \times 10^6$ DN of source counts in the 0.17 $\mu$m bin, which amounts to a photon error of 1,430 DN assuming a gain of 1.8.
@@
 The goal is to find a scheme that estimates the total flux by summing the value in each pixel $j$.
-We start by calculating a profile function $P_j$ that describes the fraction of the total flux in pixel $j$.
+We start by calculating a profile function $P_j$ in the spatial direction that describes the fraction of the total flux in pixel $j$.
 The profile is normalized so that
@@
 \end{equation*}
-Any pixel is can be used to estimate the total flux $f_i$ by dividing by the profile.
+The summation for NIRCam would be along the Y (spatial) direction for a fixed wavelength.
+
+Any pixel is can be used to estimate the total flux by dividing by the profile.
 \begin{equation*}
@@
 \end{equation*}
-Therefore, using this traditional formula will provide little difference with straight summation,
+Therefore, using this traditional formula for bright sources will provide nearly the same extraction as straight summation,
 \begin{equation}\label{eq:StraightSummation}
@@
 {\it Right:} The spectral (X) and spatial (Y) directions from the matrix are averaged to build up a higher signal to noise covariance profile.
-Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
+Spectrally, the pixels have a covariance of $\sim$20~$(e^-)^2$ expected from 1/f noise. Spatially, they have a somewhat smaller covariance of $\sim$10$(e^-)^2$.}\label{fig:covSpecSpatial}
 \end{figure}
@@
 We reduce the noise and jaggedness of the empirical covariance matrix in Figure \ref{fig:covSpecSpatial} by averaging the value along the diagonal, across all spectral pixels and across the spatial pixels with the same value of $i -j$.
-Here, the profile is the value from \texttt{pynrc}, which uses \texttt{webbpsf}.
+Here, the profile is the value from \texttt{pynrc} \citep{leisenring2020pynrc0p8dev}, which uses \texttt{webbpsf} \citep{perrin2014webbpsf}.
 We assume that the photon and background noise is $\sqrt{N_{phot}}$ and that they are completely uncorrelated from on pixel to next, so the covariance matrix is the sum, in quadrature, of the empirical read noise covariance matrix and a diagonal photon noise matrix.
@@
 
-Optimal covariance weighting significantly lowers the contribution of read noise to the overall error budget.
+Conventional optimal variance weighting slightly lowers the contribution of read noise to the overall error budget
 We test this with a series of grism images with a constant spectrum of an A0V star added to the CDS read pairs, but do not add photon noise to focus on the read noise contribution.
@@
 We perform sum extraction over a 15 spatial pixels and then combine together 165 spectral pixels into a 0.165 $\mu$m wavelength bin.
-The standard deviation of sum extraction is 3,860 DN, which is 2.7$\times$ the read noise, as shown in Table \ref{tab:noiseSummary1overf}.
-The standard deviation of the extracted flux drops to 3,060 DN if optimal extraction is used.
-
-We use Equation \ref{eq:covarianceweights}, to further reduce the read noise.
+The standard deviation of sum extraction (green weights in Figure \ref{fig:covWeightedSummation}) is 3,860 DN, which is 2.7$\times$ the read noise, as shown in Table \ref{tab:noiseSummary1overf}.
+The standard deviation of the extracted flux drops to 3,060 DN if optimal extraction (orange weights in Figure \ref{fig:covWeightedSummation}) is used.
+
+Optimal covariance weighting {\it significantly} lowers the contribution of read noise to the overall error budget.
+We use Equation \ref{eq:covarianceweights} (blue weights in Figure \ref{fig:covWeightedSummation}, to further reduce the read noise.
 For the covariance weights, we assume constant off-diagonal weights of 15 (e$^-)^2$ and do not include the spectral covariance.
@@
 Typically $P_j$ and the photon noise contribution to Cov($S_i,S_j$) can be found by fitting smooth functions (polynomials) along the dispersion direction.
-If $P_j$ is calculated from each image individually, it will inherit the 1/f noise variations of each image.
+If $P_j$ is calculated from each integration individually, it will inherit the 1/f noise variations of each integration.
 Therefore, we hold $P_j$ constant along the time series with a value saved from the middle image at all wavelengths.
-Alternatively, $P_j$ could be calculated from a PSF library or theoretically from \texttt{WebbPSF} \citep{perrin2014webbpsf}.
+Alternatively, $P_j$ could be calculated from a PSF library or theoretically from \texttt{webbpsf} \citep{perrin2014webbpsf}.
 
@@
 A covariance-weighted extraction can substantially decrease the contribution of correlated read noise to below the photon limit.
-The errors here are for a grism time series wavelength bin that is 0.17$\mu$m wide centered on 3.34 $\mu$m for a G-type host star and a 3 hour transit duration.
+The errors here are for a grism time series wavelength bin that is 0.165$\mu$m wide centered on 3.34 $\mu$m for a G-type host star and a 3 hour transit duration.
 }\label{fig:genericSourceErrorContrib}
@@
 The read noise drops slowly with $K$ magnitude because the time to reset between integrations takes a smaller and smaller fraction of the total exposure as the number of groups per integration grows.
-We show the read noise assuming sum extraction (1044 ppm for CDS integration) and covariance-weighted extraction using Equation \ref{eq:covarianceweights} (230 ppm for CDS integration).
+We show the read noise assuming sum extraction using Equation \ref{eq:StraightSummation} (1044 ppm for CDS integration) and covariance-weighted extraction using Equation \ref{eq:covarianceweights} (230 ppm for CDS integration).
 If a sum extraction is used, the read noise will dominate for $K \lesssim 8.7$.
-However, covariance weights can ensure that photon shot noise is more dominant.
+However, covariance weights can ensure that read noise is smaller than photon shot noise for $K > 6.0$.
 
@@
 We note that Figure \ref{fig:genericSourceErrorContrib} shows a somewhat counter-intuitive result: read noise dominates for bright source and becomes less important for faint sources.
-For typical observations, such as faint galaxies or distant stars, the opposite is true: read noise is more of a concern for faint sources than bright ones.
-So why is there a discrepancy?
-The difference in these two science cases is that for exoplanet transit observations, the detector well depth is filled to approximately the same level ($\sim 32,000$ DN or 50\% well depth per pixel) regardless if the system's magnitude is 6 or 11.
+The reason is that for exoplanet transit observations, the detector well depth is filled to approximately the same level ($\sim 32,000$ DN or 50\% well depth per pixel) regardless if the system's magnitude is 6 or 11.
 For the bright source with a few groups up the ramp, the read noise will be a larger fraction of 32,000 DN than for a faint source with many groups up the ramp.
-This is different from a faint galaxy in the $K > 20$ range, which will not fill the detector well.
-For a fixed exposure time, a $K=25$ and $K=20$ galaxies would be observed with approximately the same number of groups per integration so the read noise in DN from each source in an integration would be approximately the same whereas the number of DN from the source per integration would be 100 times larger for the $K=20$ galaxy.
 
@@
 An illustrative fringing model is plotted for a constant-thickness 350 $\mu$m layer to better see how the frequencies change as a function of wavelength (X pixel).
+The green point shows the error due to photon and read noise at 2.86 $\mu$m.
 }\label{fig:CV3GrismSpecFringing}
@@
 
-Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing at NASA Goddard where a broadband point source is dispersed by the grism.
+Figure \ref{fig:cv3ExtractedSpectrum} shows an extracted spectrum from Cryogenic Vacuum 3 testing at NASA Goddard in January, 2016 after delivery of the instrument and upgrades to the detectors.
+A broadband point source is dispersed by the grism.
 The slope image is calculated from the raw ramp using the internal NIRCam ramps-to-slopes pipeline \texttt{ncdhas}.
@@
 Figure \ref{fig:cv3ExtractedSpectrum} also shows an illustrative fringing model that increases in frequency as the wavelength decreases.
+The model assumes a 350 $\mu$m thick layer of material with an index of refraction $n$ of 2.7.
 
@@
 
-We evaluate the largest sources of noise that add to JWST's error budget and list them below.
+We list the known sources of error that can impact time series stability in Section \ref{sec:knownEffects}.
+Of these error sources, we identify the 3 largest error terms to the JWST NIRCam error budget.
+The conclusion on these three sources of error are listed below:
 
@@
           \texttt{spiderman} \citep{louden2017spiderman},
-          \texttt{pynrc} \url{https://github.com/JarronL/pynrc},
+          \texttt{pynrc} \citep{leisenring2020pynrc0p8dev},
           \texttt{emcee} \citep{foreman-mackey2013emcee},

### 2020-05-28 ms.tex
incorporated ME comments

@@
 
-Given the finite lifetime of the JWST mission set by onboard fuel, it is important to understand the systematic errors before launch to maximize the science return of the observatory.
-We discuss the major sources of systematic errors that can affect time-series observations with the NIRCam instrument.
+Given the finite lifetime of the JWST mission set by onboard fuel, it is important to characterize the systematic errors before launch to maximize the science return of the observatory.
+We discuss the known sources of systematic errors that can affect time-series observations with the NIRCam instrument.
 Parallel efforts to characterize other instrument's noise sources are being done, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
@@
 The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
-The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between regions of the detector.
+The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between readout amplifiers of the detector.
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
@@
 The one exception is that the Long Wavelength A-side detector (A5) exhibited $\sim$ 20 min oscillations with an amplitude of 15-20 mK when using the Temperature Monitor Control (TMC) 1 active thermal control.
-Fortunately, the TMC 2 control does not undergo these oscillations and will be employed in orbit.
+Fortunately, the TMC 2 control (with an independent set of hardware) does not undergo these oscillations and will be employed in orbit.
 If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK \citep{hall2005jwstArrays}.
@@
 	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation on all detectors \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+	\item \textbf{Reciprocity Faillure:} The response of a HgCdTe detector can change with the brightness of a source, which is called reciprocity failure \citep{biesiadzinski2011reciprocityFailure}.
+	The brightness of a star and planet system does not change significantly with time, so it will not significantly affect the {\it precision} of a lightcurve, but could affect {\it accuracy} because the filter bandpass and stellar spectral energy distribution.
+	It is possible that reciprocity failure could introduce a systematic offset, slope or curvature that depends on the count rate of the detector.
 \end{enumerate}
@@
 We note that the 4 channels can sometimes exhibit the same 1/f correlation behavior, as shown in Figure \ref{fig:darkPixelTimeSeries}.
-Another option to remove 1/f noise is to subtract the illuminated amplifier with a target in it by un-illuminated channels.
-We subtract the first amplifier's time series (pixels X=1 through X=512) from all amplifiers.
+Another option to remove 1/f noise is to subtract the 3 out of 4 output amplifiers that have the source on them by the 1 output amplifier without the target.
+We subtract the first amplifier's time series (pixels X=1 through X=512) from all amplifiers by shifting and flipping the 2048$\times$256 image sub-section to the corners of the 4 amplifiers at (X=1, X=513, X=1025 and X=1537).
 Of course, this means that this amplifier is perfectly subtracted and no noise or signal remains in this 1/4 of the image.
-The subtraction step should increase the read noise on an individual pixel by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
+The subtraction step should increase the read noise on an individual pixel (for the remaining 3 output amplifiers) by $\sim \sqrt{2}$ because the errors from the subtracted pixel should add in quadrature to the original pixels.
 This increase in read noise on a per-pixel level might be acceptable if it decreases the correlated errors along the rows.

### 2020-05-28 ms.tex
Updates from Overleaf

--- 2020-05-27 ms.tex
@@
 
-\author{Michael McElwain?}
+\author{Michael McElwain}
+\affiliation{NASA Goddard Space Flight Center \\
+Exoplanets and Stellar Astrophysics Laboratory \\
+Greenbelt, MD 20771, USA}
 
@@
 
-JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses at exoplanet atmospheres.
+JWST transmission and emission spectra of transiting exoplanets will provide invaluable glimpses of exoplanet atmospheres.
 These spectra will reveal the composition and temperature structure at a level never achieved before.
@@
 Alternatively, 10 transits of TRAPPIST-1e could be sufficient if the planet's atmosphere has CO$_2$ and CH$_4$ biosignatures similar to early-Earth \citep{krissansen-totton2018trappist1eJWST}.
-A critical question in studying planets like TRAPPIST-1 d/e with small spectroscopic signatures, however, is whether photon-limited performance is possible with JWST observations.
+A critical question in studying planets like TRAPPIST-1 d/e, however, is whether photon-limited performance is possible with JWST observations.
 For difficult biosignatures, noise levels less than 10 ppm (parts per million) are required and this value shrinks in the presence of clouds.
 
-Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
+Experience with the \textit{Hubble Space Telescope} (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected \citep[e.g.][]{beichman2014pasp}.
 Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep[e.g.][]{vanderburg2014twoWheeledKeplerPhot,beichman2014pasp}.
 
-The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode with its long wavelength channel \citep{greene2017jatisNIRCam}.
+The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode with its long wavelength (LW) channel \citep{greene2017jatisNIRCam}.
 This slitless grism mode is analogous to the WFC3 grism on HST that has been successfully employed on many transiting planets \citep[e.g.][]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
 The NIRCam grism mode will collect moderate resolution R$\sim$1100-1700 spectra over the wavelength range from 2.4 to 5.0~$\mu$m.
-This grism mode can be used simultaneously with short wavelength weak lens imaging or (in future cycles) Dispersed Hartmann Sensor spectroscopy \citep{schlawin2017dhs}.
-If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m using a wavefront sensor.
-The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$ mag (Vega)) inaccessible by other modes.
-Either the DHS or weak lens imaging can be run simultaneously with the long wavelength grism thanks to a dichroic beamsplitter.
+This grism mode can be used simultaneously with short wavelength weak lens imaging or (in future cycles) the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}.
+If it becomes an approved and implemented mode, the DHS will permit spectroscopy simultaneous from 1.0 to 2.0~$\mu$m because of a dichroic beamsplitter that divides the light from NIRCam into two different channels.
+The DHS mode will permit time series spectroscopy on very bright targets ($K_S \sim 1$) inaccessible by other modes.
 
 Given the finite lifetime of the JWST mission set by onboard fuel, it is important to understand the systematic errors before launch to maximize the science return of the observatory.
-We discuss the major sources of systematic errors that can affect time-series observations with the NIRCam instrument.
-Parallel efforts to characterize other instrument's noise sources are being done, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
-
-Section \ref{sec:knownEffects} lists the known systematic effects that can degrade the precision of time series measurements compared to the the photon noise limit.
+We discuss the major sources of systematic errors that can affect the NIRCam instrument.
+Parallel efforts to characterize other instrument's noise sources are being carried out, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
+
+Section \ref{sec:knownEffects} lists the known systematic effects that can impede high precision time series and increase the noise above the photon noise.
 Sections \ref{sec:preAmp} through \ref{sec:persistence} detail these noise contributions.
-We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact.
+We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact for JWST.
 
 \section{List of Known Detector Effects}\label{sec:knownEffects}
-An ideal HgCdTe detector would simply count the photons incident on its surface (as described in Appendix \ref{sec:detectorPrimer}).
-The NIRCam, NIRSpec and NIRISS instruments on JWST use Teledyne HAWAII2RG HgCdTe detectors.
-For NIRCam, the eight short wavelength detectors have a 2.5 $\mu$m cutoff while the two long wavelength detectors have a 5.0 $\mu$m cutoff \citep{jdoxNIRCamDetectors}.
-Each of the detectors is connected to a SIDECAR ASIC \citep{loose2006sidecarAsic} that controls how the pixels are read out and reset.
-All detectors are connected to four output amplifiers that can be read out simultaneously on four vertical stripes of the detectors.
-Each pixel's NP semiconductor junction may be measured non-destructively multiple times (referred to as ``reads'' or ``samples'') before the pixel is reset, ending an integration.
-An analog-to-digital convert turns the number of electrons collected in the detector into count of Data Numbers (DNs) between 0 and 16 bits (65,536) with a gain of $\sim$1.8 for the long-wavelength detectors and $\sim$2.0 for the short-wavelength detectors.
-The combination of all the pixels as an image is saved as a ``frame'', which together make up an integration, which ends when a pixel is reset.
-The integrations are packaged together into a single ``exposure'' and the frames are co-added into groups of 1 or more frames to save data.
-\citet{jdoxNIRCamDetectorPatterns} contains more information on the readout patterns.
-
-There are many non-ideal effects, however, that can affect the stability of a light curve measurement of a transiting exoplanet.
+An ideal HgCdTe detector simply counts the photons incident on its surface (as described in section \ref{sec:detectorPrimer}).
+However, there are many non-ideal effects that can affect the stability of a light curve of a transiting exoplanet.
 Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics.
-These known detector effects that can impact stability are listed briefly and then in more detail as related to the JWST NIRCam detectors below that.
-
-The following sources of noise introduce random variations to time series:
-\begin{enumerate}[noitemsep]
-	\item \textbf{Pre-amplifier reset offsets:} (a SIDECAR ASIC-related effect) \label{it:preAmpOffsets}
+The known detector effects that can impact stability are listed briefly and then discussed in more detail as related to the JWST NIRCam detectors.
+
+\begin{itemize}[noitemsep]
+	\item \textbf{Pre-amplifier reset offsets:} (an ASIC-related effect) 
 The resets cause discontinuities in the pedestal level of all pixels between frames.
@@
 	\item \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
-The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
+The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons using 4 pixels simultaneously in parallel.
 The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between regions of the detector.
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
-	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets above.
-	\item \textbf{1/f noise:} The JWST readout integrated circuits (ROICs) have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
+	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets described above.
+	\item \textbf{1/f noise:} The JWST HgCdTe readout electronics have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
 	This is a noise source where most of the noise power is concentrated at low frequencies.
@@
 1/f noise can be reduced by subtracting the values from background pixels or reference pixels.
+	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response within a pixel is not perfectly uniform.
+	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
+	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
+	Crosshatching patterns on HgCdTe detectors, which all JWST near-infrared instruments use, exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Even/odd offsets:} Alternating columns have different bias levels.
@@
 	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
-	Fortunately, the bias offset produced by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
-	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).
-	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
-	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
-Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array and exhibited 1 jump in a 20 minute exposure.
-\end{enumerate}
-
-In addition to these random effects, there are also systematic effects that are time-variable only due variations in other variables such as temperature and telescope pointing:
-\begin{enumerate}[resume]
-	\item \textbf{Intrapixel sensitivity:} Telescope pointing drifts and jitter can impact the amount of flux measured if the response within pixels is not perfectly uniform.
-	This has a particularly strong impact on the time series from the Spitzer IRAC instrument \citep{ingalls2016spitzerRepeatability}.
-	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
-	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
+	Fortunately, the bias offset produced by kTC noise will easily subtract out when fitting a slope image from multiple samples up the ramp.
+	This noise would only become relevant when attempting to make use of the first group of a ramp, such as when only 1 group is commanded.
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
-For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$ 80 DN changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
+For example, laboratory tests show that 100 mK temperature fluctuations can result in $\sim$80 ADU changes on the detector that are not corrected by reference pixels \citep{hall2005jwstArrays}.
 Fortunately, the detectors are actively thermally controlled to keep the temperature fluctuations to mostly $\lesssim$ 1 mK.
-The one exception is that the Long Wavelength A-side detector (A5) exhibited $\sim$ 20 min oscillations with an amplitude of 15-20 mK when using the Temperature Monitor Control (TMC) 1 active thermal control.
+The one exception is that the NIRCam LW A-side detector (A5) exhibited $\sim$ 20 min oscillations with an amplitude of 15-20 mK when using the Temperature Monitor Control (TMC) 1 active thermal control.
 Fortunately, the TMC 2 control does not undergo these oscillations and will be employed in orbit.
 If necessary, the effect of temperature fluctuations can be calibrated to $\pm 1 e^-$ for excursions less than $\pm$ 50 mK \citep{hall2005jwstArrays}.
-	\item \textbf{SIDECAR ASIC Temperature Fluctuations:} The SIDECAR ASIC temperature will change with the operating mode.
-For example, in the CV3 stability test, the temperature of the A SIDECAR ASIC changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
+	\item \textbf{ASIC Temperature Fluctuations:} The ASIC temperature will change depending on the operating mode.
+For example, in the CV3 stability test, the temperature of the A ASIC changed by $\sim$80 mK when the readout mode was switched from full frame to subarray.
 	This temperature change is expected to be smaller in flight due to adjustments in the operations to run all four amplifiers regardless of how many are used to collect science data.
-	\item \textbf{Detector Fringing} The thin $\sim 6\mu$m layer of the H2RG detectors or other optics can cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
-Older HgCdTe detectors contained a CdZnTe layer that caused a prominent fringing pattern \citep{finger2008HgCdTeCharacterization}, but JWST detectors have the CdZnTe removed so the fringe pattern comes from a different optical layer.
+	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can move with time.
+	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
+Fortunately, RTN appears in only $\sim$1000 pixels out of 4$\times 10^6$ on the array.
+	\item \textbf{Detector Fringing} \textbf{\textcolor{red}{Is there a good citation?}} The thin $\sim 5\mu$m layers of the H2RG detectors will cause interference patterns on the array due to constructive and destructive interference of light at wavelengths similar to the thickness of the layers.
 If the detector fringe pattern changes with time, it will change the throughput of a grism image.
 	\item \textbf{Charge Trapping} A major correlated error source on HST WFC3 is the ``hook effect'' \citep{berta2012flat_gj1214}.
-	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
-	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation on all detectors \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
-\end{enumerate}
+	The hook effects is due to charge can be trapped within the detector's depletion region, initially lowering the flux, and then released at later times thereby increasing the flux \citep{zhou2017chargeTrap}.
+	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
+\end{itemize}
 
 We discuss these noise contributions in more detail in Sections \ref{sec:preAmp} through \ref{sec:persistence}.
-However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less them $\sim$ 1 ppm) to the time series.
-
-\section{Pre-amplifier Offsets and Amplifier Boundaries}
-
-\subsection{Pre-amplifier Offsets}\label{sec:preAmp}
-The NIRCam detectors' pre-amplifiers (pre-amps) in the SIDECAR ASIC have a reference voltage that can drift with time, introduced as error source \ref{it:preAmpOffsets}.
+However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less than $\sim$ 1 ppm) to the time series.
+
+\section{Pre-amp Reset Offsets from the Lockheed Martin Cryo-Vacuum Test}\label{sec:preAmp}
+
+The NIRCam detectors' pre-amplifiers (pre-amps) have a reference voltage that can drift with time.
 This can affect the pedestal level of all pixels over long ($\gtrsim$ 20 minute timescales).
@@
 The NIRCam detectors are reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
-One set of darks was collected at during NIRCam cryogenic vacuum pre-delivery testing at Lockheed Martin with a reset only once per integration to study the effects of the pre-amplifier resets.
+One set of darks was collected at the Lockheed Martin (Lockheed) cryo-vacuum (CV) test with a reset only once per integration to study the effects of the pre-amplifier resets.
 
@@
 However, reference pixel subtraction or background subtraction can efficiently remove pre-amp drifts, so with proper data reduction, the pre-amp drifts can be effectively eliminated.
-The NIRCam grism subarrays and dispersed source location are placed at the edge of the NIRCam Long Wavelength detector to ensure reference pixels are nearby and saved with active pixels.
+The NIRCam grism subarrays and dispersed source location are placed at the edge of the LW detector to ensure reference pixels are saved with active pixels, so reference pixels will always be available for grism data.
 
 Figure \ref{fig:ampResetDark} shows an example time series of the reference pixels for a dark exposure.
-The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7 seconds in duration).
+The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7~s in duration).
 Fortunately, the pixels within an amplifier move together, so reference pixel subtraction or background subtraction will efficiently remove the offsets.
@@
 \caption{Reference pixel time series for a two frame integration (Left) and a long dark integration of 108 frames (Right).
-Each of the plots show that the SIDECAR ASIC pre-amplifier resets between frames in an integration cause discontinuities in the reference signal.
+Each of the plots show that the pre-amplifier resets between frames in an integration cause discontinuities in the reference signal.
 Amplifiers 1 and 4 track the time all through a frame with the side reference pixels, whereas amplifiers 2 and 3 in the middle only contain information on the bottom and top reference pixels at the beginning and ending of a frame.
@@
 NIRCam's STRIPE mode and full frame mode both employ 4 amplifiers to simultaneously read out or reset 4 pixels at once.
-This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
-Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in the Astronomer's Proposal Tool \citep[APT][]{apt2020p2}.
-On the flip side, the four amplifiers will have different behaviors such as gains and offsets in the bias level.
+This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increases the number of reads for a detector pixel before saturation to average readout noise.
+Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in APT.
+On the flip side, the four amplifiers will have different behaviors such as separate offsets in the bias level.
 The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
@@
 Instead, one can use the background region for each column ($\sim$80 pixels) to best remove gradients and the amplifier offsets.
-Here, in Figure \ref{fig:ampOffsetsOtisGrismSlope} (bottom panel), we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
+Here, we find the average of all pixels from Y=0 to 15 and Y=190 to 256 in each column and subtract this value from the whole column.
 This is repeated for all columns.
@@
 The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
-Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left amplifier (512-1023 px) over 108 dark groups in RAPID read mode.
-The dark frames were part of a single integration taken at NASA Johnson during the OTIS (Optical Telescope element + Integrated Science instrument module) cryogenic test.
-To create the periodogram, each group is subtracted by the average of all groups to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
+Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the readout amplifier over 108 dark frames.
+To create the periodogram, the reference pixels are used to remove amplifier offsets between frames.
+Next, the average of all frames is subtracted to remove the bias and all pixels that deviate by more than 80 DN from the average are masked to eliminate bad pixels.
 
@@
 The periodogram also shows many spikes at high frequency on top of the 1/f noise.
-One of these prominent spies occurs at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
+One of these prominent spikes occurs at the line reset time of 524 clock cycles, which is the time to read out all the pixels in a row for the amplifier and line overheads before moving to the next row.
 
@@
 1/f rises above the white noise level at 70 cycles / 1400 Hz for amplifier 1 and the intersection ranges from 70 to 135 across the 4 amplifiers.
-The message from this power spectrum is that the read noise is significantly correlated from pixel to pixel and this will affect both high precision spectroscopy and high precision photometry.
+This power spectrum shows that the read noise is significantly correlated from pixel to pixel and this will affect both high precision spectroscopy and high precision photometry.
 
@@
 \includegraphics[width=.4\columnwidth]{preamp_removed_grp_54.pdf}
-\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 RAPID groups.
+\caption{{\it Left:} The average Lomb-Scargle periodogram from Amplifier 1's time series over 108 groups.
 The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000 Hz.
@@
 The 1/f noise can be reduced by subtracting reference pixels and/or active pixels over the aperture of interest.
-As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (ie.
-timescales longer than 100 cycles, where a cycle is the 10$\mu$s time to address a pixel).
+As the power spectrum shows, the 1/f noise begins to contribute significantly for frequencies below 1000 Hz (i.e., timescales longer than 100 cycles, where a cycle is the 10$\mu$s time to address a pixel).
 Ideally, source apertures would be less than 100 pixels wide so that background subtraction along rows will remove the 1/f noise but this is impossible for grism spectra dispersed along the rows.
@@
 We study here the contributions from read noise, including the 1/f noise from the electronics.
-This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
+This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as crosstalk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
 
 A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
-The detectors are read in full frame mode so that each frame is 10.73677 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
+The detectors are read in full frame mode so that each frame is 10.73677~s in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
 We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
-We also re-label the times to include the reset time that would normally occur after each integration, so the effective exposure time is increased to 38.6 min (\textcolor{red}{\bf Fix this - should be 29.0 min}).
-
-Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
+We also re-label the times to include the reset time that would normally occur after each integration, so the Figure \ref{fig:longDarkPhot} shows an example dark read pair from frame 55 minus frame 54.
 In the raw data, there are 4 prominent vertical stripes that are 512 pixels wide and 2048 pixels tall due to offsets in the read-out amplifiers.
@@
 In this work, we use \texttt{ncdhas}.
-As seen in Figure \ref{fig:longDarkPhot}, reference pixels are read closely enough in time to reduce the large offsets between amplifiers.
-The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
+As seen in Figure \ref{fig:longDarkPhot}, reference pixels can be used to reduce the large offsets between amplifiers.
+The reference pixels are comprised of a 4 pixel boundary along the edges of the detector, which are not connected to detector photodiodes and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
 The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 4096 reference pixels to average for each amplifier at the bottom and top of the arrays.
@@
 Only 4 pixels on the left and 4 pixels on the right side may be used to subtract the 1/f noise in a given row and the 4 amplifiers can exhibit different 1/f noise. 
-Therefore, significantly residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
+Therefore, significant residuals remain along the fast-read (X) direction in the reference-corrected read pair shown in Figure \ref{fig:longDarkPhot}.
 These side reference pixels also cannot correct for read noise correlations that happen on shorter length scales than 512 pixels (5 ms).
@@
 \includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
-\caption{Time series data of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
+\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5.
 The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
-{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction (left), reference pixel-correction that uses the top, bottom and side reference pixels (middle) and finally a method using a row-by-row median subtraction (right).
+{\it Top:} Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from ``Raw" data using no reference pixel correction, reference pixel-correction that uses the top, bottom and side reference pixels and finally a method using a row-by-row median subtraction.
 {\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
@@
 
-What is most useful for exoplanet transit measurements is the photometric stability within an aperture or spectrum.
+Exoplanet transit measurements are dependent on the photometric stability within an aperture or spectrum.
 We therefore perform aperture photometry on the dark frame as if it were a weak lens image with a 70 pixel radius circular source aperture and a 75 to 100 pixel background annulus illustrated in Figure \ref{fig:longDarkPhot}.
@@
 This theoretical read noise is smaller than the photon noise expected inside an aperture during photometric stability time series applications.
-The number of DN collected within a 70 pixel radius aperture for WLP8 data in our CV3 detector stability test with 2 groups in RAPID (ie a correlated double sample) was $S_{tot}=3.9\times 10^7$ DN during the integration.
+The number of DN collected within a 70 pixel radius aperture for a weak lens plus 8 waves (WLP8) image in our CV3 detector stability test with 2 groups in RAPID, equivalent to a correlated double sample (CDS), was $S_{tot}=3.9\times 10^7$ DN during the integration.
 The peak pixel counts in this integration were 30,000 DN or about 60\% well depth for the A1 detector.
-The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the SW detectors).
+The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 2.0$ for the short wave (SW) detectors).
 In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
-Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
+Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (i.e., CDS).
 When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.
@@
 This read noise would be $\sim$5$\times$ the $\sim$113 ppm photon noise.
-Fortunately, there are ways to significantly reduce the pre-amplifier offsets and 1/f noise.
+However, there are ways to significantly reduce the pre-amplifier offsets and 1/f noise.
 
@@
 \enddata
-\tablecomments{The theoretical and measured noise sources in one integration for a Weak Lens +8 and Grism Time Series.
+\tablecomments{The theoretical and measured noise sources in one integration for a weak lens +8 waves and grism time series.
 The ppm units are assuming a peak 60\% well depth or 3.9$\times 10^7$ DN during an integration for the weak lens PSF and 3.7$\times 10^6$ DN during and integration for the grism PSF.
 The noise is reported for the the aperture/spectral extraction (in DN) or relative to the photon signal (in ppm).
-The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (Correlated Double Sampling or CDS mode).
+The integration is assumed to be a bright source with 2 groups of 1 integration each up the ramp (i.e., CDS).
 For the grism, statistics are shown for a representative 0.17~$\mu$m wide wavelength bin centered on 3.34~$\mu$m.}
@@
 
-These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
+These large correlations in read noise can be reduced with the reference pixels, which are designed to track electronic noise without the presence of background photon noise.
 We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
-The time series for the 3 apertures considered drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
+The time series for the 3 apertures considered drops to levels from 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
 
@@
 
-In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
+In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN if all noise were uncorrelated.
 The A3 detector used for weak lens photometry has reduced 1/f noise.
@@
 Therefore, this simple approach can dramatically decrease the 1/f noise to well below the photon limit.
-This is possible for Weak Lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).
+This is possible for weak lens photometry but not grism spectroscopy when dispersed parallel to detector rows (the fast-read direction).
 
@@
 
-We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:photRowByRow}.
+We also consider more sophisticated ways to reduce read noise than the median row subtraction discussed in Section~\ref{sec:photRowByRow}.
 We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
 The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
-This enables subtraction of 1/f noise that has length scales shorter than the line time (ie timescales shorter than 512 clock cycles or 5 milliseconds), which the median subtraction cannot remove.
+This enables subtraction of 1/f noise that has length scales shorter than the line time (i.e., timescales shorter than 512 clock cycles or 5 ms), which the median subtraction cannot remove.
 
@@
 The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
-For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
+For the row and column median subtraction applied to the red files, the standard deviation was 6,150, 5,600 and 6,600 DN for apertures 0, 1 and 2.
 For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.
@@
 In reality, the kernel should be wider than the source aperture diameter and interpolate through the source points.
-Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide!
+Note that this experiment would result in perfect subtraction (0 ppm noise) if the kernel was only 1 pixel wide.
 We repeated the experiment with a 161 pixel wide kernel and masked bad pixels and the source pixels.
 We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
-\texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
+\texttt{astropy.convolution.convolve()} ignores all NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
 This efficiently interpolates over bad pixels and can also interpolate over the source aperture.
@@
 %\includegraphics[width=.32\columnwidth]{all_amp_periodograms.pdf}
-\caption{The time series for all 4 amplifiers share common-mode behaviors for some intervals but not always (left and middle plots).
-This is visible in a short segment of the time series of all pixels for an example group up the ramp 53 in a dark ramp where the bias has already been subtracted.
-The pixels time series smoothed with a 51 pixel-wide median filter to better see the low frequency noise.
-The left panel shows the a time near the beginning of a frame, where amplifiers 1 ad 2 share some common-mode read noise.
-The right panel shows another part of the time series where Amplifiers 1 and 2 have more disparate noise signatures.
+\caption{The time series for all 4 amplifiers share common-mode behaviors for some intervals but not always (left and right plots).
+This is visible in a short segment of the time series of all pixels for an example group up-the-ramp 53 in a dark ramp where the bias has already been subtracted.
+The pixels in each time series are smoothed with a 51 pixel-wide median filter to show the low frequency noise.
+The left panel shows the a time near the beginning of a frame, where amplifiers 1 and 2 share some common-mode read noise.
+The right panel shows another part of the time series where amplifiers 1 and 2 have more disparate noise signatures.
 }\label{fig:darkPixelTimeSeries}
@@
 The standard deviations in the time series range from 8,500 DN to 10,800 DN for this reference amplifier method as opposed to the 5,500 DN to 6,600 DN for a row-by-row median.
-This means the the correlations within an amplifier are not efficiently subtracted and may be propagated to the remaining amplifiers.
+This means the correlations within an amplifier are not efficiently subtracted and may be propagated to the remaining amplifiers.
 
@@
 Pre-amplifier reset values are seen in the first principal component, and change from one group (one read in RAPID) to another.
-These are residual values not fully subtracted by reference pixels.
+These are residual values are not fully subtracted by reference pixels.
 The principal components generally increase in frequency with principal component number.
@@
 
-Another approach to treating the 1/f noise is dimensionality reduction with Principal Component Analysis.
+Another approach to treating the 1/f noise is dimensionality reduction with principal component analysis (PCA).
 Here, we assume that the counts for each pixel along a column is a random variable that can be correlated with pixels in other columns.
@@
 
-The PCA subtraction is applied to each group up the ramp and then these groups are subtracted in pairs to create a time series.
+The PCA subtraction is applied to each group up-the-ramp and then these groups are subtracted in pairs to create a time series.
 We use 20 principal components as a starting point for this method.
@@
 We begin by keeping 5 principal components within each amplifier and subtracting these from each amplifier separately.
-The resulting standard deviation of the time series is 2500 to 3820 DN.
-This is improvement is beyond what is possible on a real source because the principal components include pixels over the source aperture.
+The resulting standard deviation of the time series is 2,500 to 3,820 DN.
+This improvement is beyond what is possible on a real source because the principal components include pixels over the source aperture.
 To simulate a real photometry scenario, it is necessary to interpolate over the source aperture points as done in Section \ref{sec:smoothKernelSub} for the smoothing kernel.
-However, we stop the PCA at this point because it does not do as well as the simple row-by-row amplifier-by-amplifier mean subtraction performed in Section \ref{sec:indAmpAvg}.
+However, we stop the PCA at this point because it does not do as well as the simple row-by-row amplifier-by-amplifier mean subtraction performed in Section~\ref{sec:indAmpAvg}.
 
@@
 \includegraphics[width=.32\columnwidth]{tser_pairwiseSubRed_backsub.pdf}
-\caption{ {\it Top Row:} The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column row-by-row subtraction (right).
+\caption{{\it Top Row:} The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column, row-by-row subtraction (right).
 The spectrum (outlined in red aperture box) is dispersed along the fast read (horizontal) direction, so it is particularly susceptible to 1/f noise.
 {\it Bottom Row:} The standard deviation of the time series dramatically decreases from 21,900 ppm to 2,680 ppm with reference pixels and 1044 ppm with column-by-column, row-by-row subtraction for the 3.34 $\mu$m bin.
-Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (512 pixels wide) and part of the leftmost amplifer, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
+Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (512 pixels wide) and part of the leftmost amplifier, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}
@@
 The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
-However, there are only limited background regions along the horizontal direction to use to subtract out 1/f noise.
-This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px).
+However, there are only limited background regions along the horizontal direction available to subtract out 1/f noise.
+This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px).
+
+%, on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$2100 px).
 
@@
 Given the high 1/f read noise, it is important to maximize the number of samples up the ramp.
-The read noise averages down like $\sqrt{N}$ statistics (ie. each read can be assumed independent and identically distributed).
+The read noise averages down like $\sqrt{N}$ statistics (i.e., each read can be assumed independent and identically distributed).
 Therefore, for the example bin size of 0.17~$\mu$m, there should be at least 7 reads to average per integration.
@@
 \end{equation*}
-Any pixel is can be used to estimate the total flux $f_i$ by dividing by the profile.
+Any pixel can be used to estimate the total flux $f_i$ by dividing by the profile.
 \begin{equation*}
@@
 
-If one assumes that all pixels are independent (and have zero correlation), the optimal weights (ones that minimize the variance in $f_{opt}$) are
+If one assumes that all pixels are independent thereby having zero correlation, the optimal weights (ones that minimize the variance in $f_{opt}$) are
 \begin{equation}\label{eq:varianceweights}
@@
 Exoplanet observations, where high signal to noise is needed to remove the planet from star signal, are generally in the foreground limit (where the variance is approximately equal to the number of photons).
-In this case, both the profile $P_j$ and variance $V_j$ will be proportional to the number of photons $N_{phot}$, so the pre-multiplier of the flux become
+In this case, both the profile $P_j$ and variance $V_j$ will be proportional to the number of photons $N_{phot}$, so the pre-multiplier of the flux becomes:           
 \begin{equation*}
@@
 \includegraphics[width=.49\columnwidth]{cross_sections_cov.pdf}
-\caption{{\it Left:} The read noise shows significant correlations between pixels (unlike the traditional assumption that each pixel's noise is statistically independent).
+\caption{{\it Left:} The read noise shows significant correlations between pixels -- unlike the traditional assumption that each pixel's noise is statistically independent.
 The data was computed from a long dark exposure of 54 read pairs where reference pixel corrections, column-by-column subtraction and row-by-row subtraction have been performed.
@@
 {\it Right:} The spectral (X) and spatial (Y) directions from the matrix are averaged to build up a higher signal to noise covariance profile.
-Spatially, the pixels' have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
+Spatially, the pixels have a covariance of 20~$(e^-)^2$ and a somewhat smaller spatial covariance of 10$(e^-)^2$.}\label{fig:covSpecSpatial}
 \end{figure}
@@
 \caption{A CV3 grism spectrum over the time series grism test shows evidence for fringing and where the oscillations exceed the photon and read noise (green point).
-An illustrative fringing model is plotted for a constant-thickness 350 $\mu$m layer to better see how the frequencies change as a function of wavelength (X pixel).
+An illustrative sinusoidal function is plotted for comparison to better see how the frequencies change as a function of wavelength (X pixel).
 }\label{fig:CV3GrismSpecFringing}
@@
 This produces a negative charge on the P-type side.
-Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge on the N-type side.
+Conversely, the positively charged holes from the P-type material flow to the N-type material to complete the valence shell and this produces a net positive charge.
 The resulting voltage difference is called the contact potential.
 In the region where electrons have completed the valence shells in the P-type material and holes in the N-type material, the valence shells are complete.
-This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it is depleted of mobile charge carriers.
+This region spanning across the two semiconductor materials is called the depletion region (pictured in Figure \ref{fig:npSchematic}), because it contains no mobile charge carriers.
 The positive net charge on the N-type material and negative charge in the P-type material causes a voltage (potential) difference across the detector.
@@
 Figure \ref{fig:npSchematic} shows the initial reverse voltage that is applied during a pixel reset. 
-The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type semi-conductor.
+The physical size of the N-type HgCdTe semiconductor is much larger than the P-type HgCdTe because the density of carriers is lower in the N-type.
 
@@
 
-\section{Charge Trapping}
+\subsection{Charge Trapping}
 All HgCdTe detectors show a signal after bright illumination even if the illumination is removed; this is called persistence.
@@
 
-\section{Extracted Spectra and periodograms}
+\subsection{Extracted Spectra and periodograms}
 

### 2020-05-28 ms.tex

--- 2020-05-28 ms.tex
@@
 
-Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
+Experience with the \textit{Hubble Space Telescope} (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected \citep[e.g.][]{beichman2014pasp}.
 Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep[e.g.][]{vanderburg2014twoWheeledKeplerPhot,beichman2014pasp}.
 
-The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode with its long wavelength channel \citep{greene2017jatisNIRCam}.
+The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode with its long wavelength (LW) channel \citep{greene2017jatisNIRCam}.
 This slitless grism mode is analogous to the WFC3 grism on HST that has been successfully employed on many transiting planets \citep[e.g.][]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
@@
 We discuss the known sources of systematic errors that can affect time-series observations with the NIRCam instrument.
-Parallel efforts to characterize other instrument's noise sources are being done, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
+Parallel efforts to characterize other instrument's noise sources are being carried out, such as with MIRI's detectors \citep{matuso2019siAsDetectorStability}.
 
 Section \ref{sec:knownEffects} lists the known systematic effects that can degrade the precision of time series measurements compared to the the photon noise limit.
+
 Sections \ref{sec:preAmp} through \ref{sec:persistence} detail these noise contributions.
-We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact.
+We conclude in Section \ref{sec:Conclusion} that 1/f noise is the largest systematic error followed by subpixel sensitivity, while the dominant HST-related systematic should have a relatively minor impact for JWST.
 
@@
 Here, we review many of the known noise sources that could impact the stability of a time series beyond photon counting statistics.
-These known detector effects that can impact stability are listed briefly and then in more detail as related to the JWST NIRCam detectors below that.
+These known detector effects that can impact stability are listed briefly and then discussed in more detail as related to the JWST NIRCam detectors below that.
 
@@
 	\item \textbf{Amplifier Boundary Discontinuities} The NIRCam detectors can be read out in full frame, stripe and window modes.
-The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons in 4 pixels simultaneously in parallel.
+The full frame and stripe modes make use of 4 amplifiers that can record or reset the accumulated electrons using 4 pixels simultaneously in parallel.
 The parallel operation of the amplifiers reduces the frame time and reset time by a factor of 4 but can introduce subtle voltage biases between readout amplifiers of the detector.
 If these voltage biases are not corrected, they can potentially introduce discontinuities in a spectrum, which crosses amplifier boundaries.
-	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets above.
-	\item \textbf{1/f noise:} The JWST readout integrated circuits (ROICs) have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
+	The amplifier boundary discontinuities are a consequence of the pre-amplifier reset offsets described above.
+	\item \textbf{1/f noise:} The JWST HgCdTe readout integrated circuits (ROICs) have a p-type metal-oxide semiconductor field-effect transistor (PFET) source follower that introduces noise to the images as well as DC biases in the ASIC electronics \citep{rauscher2011irsSquared}.
 	This is a noise source where most of the noise power is concentrated at low frequencies.
@@
 	\item \textbf{kTC noise:} Each reset at the beginning of an integration introduces thermal noise associated with the unknown amount of charge stored in a pixel at the reset voltage level.
-	Fortunately, the bias offset produced by kTC noise will easily subtract out when fitting a slope image from the multiple samples up the ramp.
-	This noise would  only become relevant when attempting to make use of the first group of a ramp (such as when only 1 group is commanded).
-	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can sometimes even move with time.
+	Fortunately, the bias offset produced by kTC noise will easily subtract out when fitting a slope image from multiple samples up the ramp.
+	This noise would  only become relevant when attempting to make use of the first group of a ramp, such as when only 1 group is commanded.
+	\item \textbf{Elevated Columns} There is correlated noise along a column in many frames. These elevated columns can move with time.
 	\item \textbf{Random Telegraph Noise (RTN)} Some of the pixels will exhibit spontaneous changes jumps in signal even with no illumination.
@@
 	It can also appear on JWST detectors because the sub-pixel flat field is not uniform.
-	Crosshatching patterns on HgCdTe detectors (which all JWST near-infrared instruments use) exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
+	Crosshatching patterns on HgCdTe detectors, which all JWST near-infrared instruments use, exist at the sub-pixel level  \citep{shapiro2018crosshatch,ninan2019crosshatchHPF}
 	\item \textbf{Detector Temperature Fluctuations:} The JWST detectors are sensitive to temperature changes on the focal plane arrays.
@@
 	\item \textbf{Charge Trapping} A major correlated error source on HST WFC3 is the ``hook effect'' \citep{berta2012flat_gj1214}.
-	The hook effects is due to charge can be trapped within the detector's depletion region (initially lowering the flux) and then released at later times (increasing the flux) \citep{zhou2017chargeTrap}.
+	The hook effect is due to charge trapped within the detector's depletion region, initially lowering the flux, and then released at later times, thereby increasing the flux \citep{zhou2017chargeTrap}.
 	JWST's NIRCam instrument has very lower rates of persistence ($<$1 DN/sec) at 100 seconds after saturation on all detectors \citep{leisenring2016persistence}, so it is expected that charge trapping will be a minor concern for JWST's HgCdTe detectors.
@@
 We discuss these noise contributions in more detail in Sections \ref{sec:preAmp} through \ref{sec:persistence}.
-However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less them $\sim$ 1 ppm) to the time series.
+However, we exclude the kTC noise, even/odd noise, temperature fluctuations and elevated columns because these are not expected to contribute significantly (less than $\sim$ 1 ppm) to the time series.
 
@@
 The NIRCam detectors are reset once per frame to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
-One set of darks was collected at during NIRCam cryogenic vacuum pre-delivery testing at Lockheed Martin with a reset only once per integration to study the effects of the pre-amplifier resets.
+One set of darks was collected at during NIRCam cryogenic vacuum (CV) test pre-delivery testing at Lockheed Martin with a reset only once per integration to study the effects of the pre-amplifier resets.
 
@@
 Figure \ref{fig:ampResetDark} shows an example time series of the reference pixels for a dark exposure.
-The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7 seconds in duration).
+The pedestal/bias level of the reference pixels undergoes a sharp jump between each frame (10.7~s in duration).
 Fortunately, the pixels within an amplifier move together, so reference pixel subtraction or background subtraction will efficiently remove the offsets.
@@
 NIRCam's STRIPE mode and full frame mode both employ 4 amplifiers to simultaneously read out or reset 4 pixels at once.
-This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increase the number of reads up a detector pixel to average down readout noise.
+This simultaneous use of 4 amplifiers reduces the frame time by a factor of 4 and thus increases the brightness of objects that can be detected before saturation as well as increases the number of reads for a detector pixel before saturation to average down readout noise.
 Users have the option to select the 1 or 4 amplifiers with the ``No. of output channels'' in the Astronomer's Proposal Tool \citep[APT][]{apt2020p2}.
-On the flip side, the four amplifiers will have different behaviors such as gains and offsets in the bias level.
+On the flip side, the four amplifiers will have different behaviors such as separate gains and offsets in the bias level.
 The differential biases between the amplifiers will show up as step function changes in the slope of the image at the amplifier boundaries (512, 1024 and 1536), as visible in Figure \ref{fig:ampOffsetsOtisGrismSlope} (top panel).
@@
 The power spectrum of this pixel-by-pixel time series reveals high power at low frequencies that drops approximately like a 1/f power law in the power spectrum of the time series.
-Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left amplifier (512-1023 px) over 108 dark groups in RAPID read mode.
+
+Figure \ref{fig:pixelTSeriesPSpec} shows the average Lomb Scargle periodogram from the middle left output amplifier (512-1023 px) over 108 dark groups in RAPID read mode.
 The dark frames were part of a single integration taken at NASA Johnson during the OTIS (Optical Telescope element + Integrated Science instrument module) cryogenic test.
@@
 \includegraphics[width=.4\columnwidth]{preamp_removed_grp_54.pdf}
-\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 RAPID groups.
+\caption{{\it Left:} The average Lomb-Scargle periodogram from Amplifier 1's time series over 108 RAPID groups.
 The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000 Hz.
@@
 We study here the contributions from read noise, including the 1/f noise from the electronics.
-This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as cross-talk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
+This experiment with dark frames does not test subtle changes in behavior of the electronic read noise under illumination, such as crosstalk where pixels that have no direct flux from a source in an image correlate with other regions of the detector with high flux rates.
 
 A standard long dark exposure used for detector characterization is a single integration that is 108 groups of 1 frame each (RAPID mode).
-The detectors are read in full frame mode so that each frame is 10.73677 sec in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
+The detectors are read in full frame mode so that each frame is 10.73677~s in duration with 4 output amplifiers in use, thus the total time for the exposure is 19.3 min.
 We use one of these long dark integrations to create simulated time series as if it were observing many consecutive integrations in full frame mode.
 The long darks are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
+
 We also re-label the times to include the reset time that would normally occur after each integration, so the effective exposure time is increased to 38.6 min (\textcolor{red}{\bf Fix this - should be 29.0 min}).
@@
 As seen in Figure \ref{fig:longDarkPhot}, reference pixels are read closely enough in time to reduce the large offsets between amplifiers.
-The reference pixels (making up a 4 pixel boundary on the edges of the detector) are un-illuminated and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
+The reference pixels are comprised of a 4 pixel boundary along the edges of the detector, which are not connected to detector photodiodes and can therefore be used to measure common-mode electronic noise without being affected by photon counting noise.
+
 The reference pixels are most useful for subtracting the offsets between amplifiers because there are 8 rows of 512 pixels or a total of 4096 reference pixels to average for each amplifier at the bottom and top of the arrays.
@@
 Here, we assume a peak pixel counts of 30,000 DN or about 60\% well depth.
-With this detector well filling fraction and a Weak Lens +8 point spread function, the number of DN collected within a 70 pixel radius aperture is was $S_{tot}=3.9\times 10^7$ DN during the integration.
+With this detector well filling fraction and a Weak Lens plus 8 waves (WLP8) point spread function, the number of DN collected within a 70 pixel radius aperture is was $S_{tot}=3.9\times 10^7$ DN during the integration.
 The Poisson shot noise for photons is $N_{phot} = \sqrt{S_{tot}} / \sqrt{G} = 4,400$ DN, where $G$ is the gain ($G \approx 1.8$ for the LW detectors).
 In terms of fractional noise, the photon shot noise should be 113 ppm and the read noise should be 33 ppm.
-Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (ie CDS).
+Therefore, the read noise is expected to be about 1/4 the shot noise for 2 group RAPID read mode (i.e., CDS).
 When averaging together 111 full frames over 60 minutes (an order-of-magnitude transit duration for most planets), the photon noise would contribute 11 ppm and the read noise would contribute 3 ppm.
@@
 
-These large correlations in read noise can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
+These large correlations in read noise can be reduced with the reference pixels, which are designed to track electronic noise without the presence of background photon noise.
 We use the \texttt{ncdhas} pipeline to apply reference pixel correction, which dramatically reduces the amplifier offsets and also reduces 1/f noise correlations along the fast read (X) direction.
-The standard deviation of the flux for the 3 source apertures drops down to 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
+The standard deviation of the flux for the 3 source apertures considered drops down to levels from 10,000 DN to 11,500 DN (depending on detector), but still falls short of the expectation of 1,310 DN if the read noise is uncorrelated.
 
@@
 The kernel is a uniform normalized kernel 1 pixel in height and 161 pixels along a row.
-This enables subtraction of 1/f noise that has length scales shorter than the line time (ie timescales shorter than 512 clock cycles or 5 milliseconds), which the median subtraction cannot remove.
+This enables subtraction of 1/f noise that has length scales shorter than the line time (ie., timescales shorter than 512 clock cycles or 5.12 ms), which the median subtraction cannot remove.
 Care must be taken not to apply the kernel through the source aperture, which would subtract and distort any signal from a star.
@@
 We use the \texttt{astropy.convolution.convolve()} routine, which calculates a convolution of the kernel by the image.
-\texttt{astropy.convolution.convolve()} ignores al NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
+\texttt{astropy.convolution.convolve()} ignores all NaN values in the mask and renormalizes the kernel by the sum of the remaining kernel points.
 This efficiently interpolates over bad pixels and can also interpolate over the source aperture by creating a circle of NaN values around the source.
 Our smoothing kernel is a flat boxcar normalized to 1.0.
-The resulting time series has a standard deviation of 2800 DN to 3700 ppm, which is slightly larger than the much simpler row-by-row amplifier-by-amplifier subtraction in Section \ref{sec:indAmpAvg}.
+The resulting time series has a standard deviation of 2800 DN to 3700 ppm.
+This is slightly larger than the much simpler row-by-row amplifier-by-amplifier subtraction in Section \ref{sec:indAmpAvg}.
 
@@
 \includegraphics[width=.32\columnwidth]{tser_pairwiseSubRed_backsub.pdf}
-\caption{ {\it Top Row:} The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column row-by-row subtraction (right).
+\caption{{\it Top Row:} The read pairs have significant pre-amp offsets and 1/f noise (left), which are reduced by reference pixels (middle) and column-by-column, row-by-row subtraction (right).
 The spectrum (outlined in red aperture box) is dispersed along the fast read (horizontal) direction, so it is particularly susceptible to 1/f noise.
 {\it Bottom Row:} The standard deviation of the time series dramatically decreases from 21,900 ppm to 2,680 ppm with reference pixels and 1044 ppm with column-by-column, row-by-row subtraction for the 3.34 $\mu$m bin.
-Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (each 512 pixels wide) and part of the leftmost amplifer, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
+Here, the simulated grism image for an F322W2 filter spans 3 amplifier channels (each 512 pixels wide) and part of the leftmost amplifier, so only reference pixels and horizontal pixels with X $<$ 300 can be used to reduce the 1/f noise.
 }\label{fig:longDarkGrism}
@@
 The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
-However, there are only limited background regions along the horizontal direction to use to subtract out 1/f noise.
+However, there are only limited background regions along the horizontal direction available to subtract out 1/f noise.
 This will result in increased noise on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for the F444W filter (on the right three amplifiers for the F322W2 filter (2.4 to 4.0 $\mu$m over $\sim$1600 px) and the left two amplifiers for F444W filter (3.9 to 5.0 $\mu$m over $\sim$1100 px).
@@
 
-Any pixel is can be used to estimate the total flux by dividing by the profile.
+Any pixel can be used to estimate the total flux by dividing by the profile.
 \begin{equation*}
